### 2014-09-05 stuff_somewhat_organised.tex
Made a git repo out of it.

\documentclass[11pt, a4paper]{article}
\usepackage{mathptmx}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsthm}
\usepackage{remreset}
\usepackage[utf8]{inputenc}

\begin{document}
\title{Stuff that may well go into the project report}
\author{Trygve Bærland}
\maketitle
\abstract{Funker dette?}
\section{Basics}
\newtheorem{theorem}{Theorem}
\newtheorem{mydef}{Definition}
\newtheorem{ex}{Example}

Let $\Omega \subset \mathbb{R}^d$ be an open, simply connected domain. Then the filtration, or general porous medium equation is
\begin{equation}
\label{GPME}
	\partial_t u = \Delta \Phi(u) + f,
\end{equation}
 where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. More specific assumptions on the nonlinearity $\phi$  and the forcing term $f$ will follow.

\subsection{Problem statement}
I will consider on the following Dirichlet problem:
\begin{equation}
\label{HDP}
	\begin{cases}
		\partial_t u = \Delta \Phi(u) + f, \quad \text{ in } Q_T \\
		u(x,0) = u_0(x), \quad \text{ in } \Omega \\
		u(x,t) = 0, \quad \text{ on } \partial\Omega \times (0,T)
	\end{cases}
\end{equation}

\subsection{Weak formulation}
\begin{mydef}[Weak solutions]
A locally integrale function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of \ref{HDP} if
\begin{enumerate}[i)]
	\item $u \in L^1(Q_T)$ and $\Phi(u) \in L^1(0,T : W_0^{1,1}(\Omega))$\footnote{$f:\Omega \to \mathbb{R}$ is an element of $W^{k,p}(\Omega)$ if all weak derivatives with $|\alpha| \leq k$ exists and are in $L^p(\Omega)$. $W_0^{k,p}$ is the closure of $C^\infty_c(\Omega)$ in $W^{k,p}(\Omega)$.};
	\item $u$ satisfies
		\begin{equation}
		\label{weak}
		\iint_{Q_T} \{\nabla\Phi(u)\cdot \nabla\eta - u\partial_t \eta \}dxdt = \int_\Omega u_0(x)\eta(x,0)dx + \iint_{Q_T}f\eta dxdt
		\end{equation}
		for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on the boundary and has compact support.
\end{enumerate}
\end{mydef}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%					ESTIMATES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Some estimates}
Now we need to make some assumptions on $\Phi$ and $f$:
\begin{enumerate}[i)]
	\item The function $\Phi: \mathbb{R} \to \mathbb{R}$ is continuous, strictly increasing and we assume $\Phi(0) = 0$ without any loss of generality.
\end{enumerate}
For now the assumption that $\phi' > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi \geq 0$. In that case (\ref{GPME}) changes from nodegenerate parabolic to degenerate parabolic. But hopes are high.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%					UNIQUENESS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Uniqueness}
\begin{theorem}[Uniqueness]
	Assuming $u \in L^2(Q_T)$ and that $\Phi \in L^2(0,T : H_0^1(\Omega))$, (\ref{HDP}) has at most one weak solution.
\end{theorem}
\begin{proof}
This is a pretty neat proof using a smart choice of $\eta$. So let's assume $u_1$ and $u_2$ are weak solutions. Then
\begin{equation*}
\iint_{Q_T}\nabla(\Phi(u_2) - \Phi(u_1)) \cdot \nabla \eta - (u_2 - u_1)\partial_t \eta dxdt = 0.
\end{equation*}

Now the inspired move\footnote{Of course, this isn't my proof so that sort of horn-tooting is in good taste.} is choosing
\begin{equation*}
\eta(x,t) = \begin{cases}
		\int_t^T(\Phi(u_2) - \Phi(u_1))ds, \quad &\text{ if } 0 < t < T \\
		0 \quad &\text{ if } t\geq T.
	\end{cases}
\end{equation*}
It is then easily verified that
\begin{equation*}
\begin{cases}
	\partial_t \eta &= -(\Phi(u_2) - \Phi(u_1) ) \\
	\nabla \eta &= \int_t^T(\nabla (\Phi(u_2) - \Phi(u_1))ds,
\end{cases}
\end{equation*}
which put into the integral equality above yields
\begin{equation*}
\iint_{Q_T}(\Phi(u_2) - \Phi(u_1))(u_2 - u_1)dxdt + \iint_{Q_T}\nabla(\Phi(u_2(t)) - \Phi(u_1(t))) \cdot \left(\int_t^T \nabla(\Phi(u_2(s)) - \Phi(u_1(s))ds\right)dtdx = 0.
\end{equation*}
The first integral is nonnegative due to the assumption that $\Phi$ is increasing.
\end{proof}
\end{document}

### 2014-09-05 animation_Barenblatt.m

@@ -1,0 +1,31 @@
+close all
+clear all
+%A small script making an animation of the fundamental solution of the
+%PME in 1D.
+
+%Establishing parameters:
+m=2;
+
+alpha = 1/(m+1);
+beta = alpha;
+k = alpha * (m-1) / (2*m);
+C=0.5;
+%End time:
+T = 1;
+%Time steps:
+nt = 1000;
+
+dt = T/nt;
+
+%Spatial domain:
+x = linspace(-2,2,100);
+
+figure
+for i=1:nt
+    t = dt*i;
+    U = t^(-alpha) * max(0,C-k*abs(x).^2*t^(-2*beta)).^(1/(m-1));
+    pause(0.03)
+    plot(x,U)
+    axis([-2 2 0 10])
+    drawnow
+end

### 2014-09-05 stuff_somewhat_organised.tex
Done with uniqueness proof, I hope.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+In the following proof of uniqueness of weak solutions I'll try out assuming that $\Phi' \geq 0$.
 \section{Uniqueness}
@@
 \end{equation*}
-
 Now the inspired move\footnote{Of course, this isn't my proof so that sort of horn-tooting is in good taste.} is choosing
@@
 	\partial_t \eta &= -(\Phi(u_2) - \Phi(u_1) ) \\
-	\nabla \eta &= \int_t^T(\nabla (\Phi(u_2) - \Phi(u_1))ds,
+	\nabla \eta &= \int_t^T\nabla (\Phi(u_2) - \Phi(u_1))ds,
 \end{cases}
@@
 which put into the integral equality above yields
+\begin{equation}
+\label{unique}
+\begin{aligned}
+	&\iint_{Q_T}(\Phi(u_2) - \Phi(u_1))(u_2 - u_1)dxdt \\ 
+	&+ \iint_{Q_T}\nabla(\Phi(u_2(t)) - \Phi(u_1(t))) \cdot \left(\int_t^T 					\nabla(\Phi(u_2(s)) - \Phi(u_1(s))ds\right)dtdx = 0.
+\end{aligned}
+\end{equation}
+Let's take these in order:
+\begin{enumerate}[i)]
+	\item In the first integral we notice that $u_2 > u_1 \Rightarrow \Phi(u_2) \geq \Phi(u_1)$ and vice versa, so this integral is nonnegative.
+
+	\item For the second integral it is helpful to first only consider integration of the temporal dimensions, leaving us with
+	\begin{align*}
+	&\int_0^T\int_t^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dsdt \\
+	&= \int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds.
+	\end{align*}
+	Due to the symmetry about the line $s=t$, we have
+	\begin{align*}
+	&\int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
+	&= \frac{1}{2}\int_0^T \int_0^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
+	&= \frac{1}{2}\left( \int_0^T \nabla(\Phi(u_2)-\Phi(u_1))dt\right)^2,
+	\end{align*}
+	which is also nonnegative, and therefore the second integral in (\ref{unique}) must also be nonnegative.
+\end{enumerate}
+From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e.
+in $Q_T$.
+Wherever $\Phi'(u) > 0$ we have $u_2 = u_1$, but more care is needed when $u_1$ and $u_1$ take values where $\Phi'(u) = 0$.
+So suppose $u_1 \neq u_2$ on a set $E \subset Q_T$ of positive measure.
+That means $\nabla(\Phi(u_2) - \Phi(u_1)) = 0$ a.e.
+in $E$, and so we can deduce that
 \begin{equation*}
-\iint_{Q_T}(\Phi(u_2) - \Phi(u_1))(u_2 - u_1)dxdt + \iint_{Q_T}\nabla(\Phi(u_2(t)) - \Phi(u_1(t))) \cdot \left(\int_t^T \nabla(\Phi(u_2(s)) - \Phi(u_1(s))ds\right)dtdx = 0.
+\iint_{Q_T}(u_2 - u_1)\partial_t \eta dxdt = 0
 \end{equation*}
-The first integral is nonnegative due to the assumption that $\Phi$ is increasing.
+for all test functions $\eta$ with support in $E$. This gives us that $u_2 = u_1$ a.e. in $E$ as well, so $u_2 = u_1$ a.e. in all of $Q_T$. Whoop-dee-doo!
 \end{proof}

### 2014-09-05 stuff_somewhat_organised.tex
Done some minor corrections.

@@
 
-Let $\Omega \subset \mathbb{R}^d$ be an open, simply connected domain. Then the filtration, or general porous medium equation is
+Let $\Omega \subset \mathbb{R}^d$ be an open, simply connected domain. Then the filtration-, or general porous medium equation is
 \begin{equation}
@@
 \end{equation}
- where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. More specific assumptions on the nonlinearity $\phi$  and the forcing term $f$ will follow.
+ where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. More specific assumptions on the nonlinearity $\Phi$  and the forcing term $f$ will follow.
 
@@
 		u(x,0) = u_0(x), \quad \text{ in } \Omega \\
-		u(x,t) = 0, \quad \text{ on } \partial\Omega \times (0,T)
+		u(x,t) = 0, \quad \text{ on } \partial\Omega \times (0,T).
 	\end{cases}
 \end{equation}
-
+Here $Q_T = \Omega \times (0,T)$, where $T$ may very well be infinite.
 \subsection{Weak formulation}
 \begin{mydef}[Weak solutions]
-A locally integrale function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of \ref{HDP} if
+A locally integrable function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of \ref{HDP} if
 \begin{enumerate}[i)]
@@
 \end{enumerate}
-For now the assumption that $\phi' > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi \geq 0$.
+For now the assumption that $\Phi'(u) > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi'(u) \geq 0$.
 In that case (\ref{GPME}) changes from nodegenerate parabolic to degenerate parabolic.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the following proof of uniqueness of weak solutions I'll try out assuming that $\Phi' \geq 0$.
+In the following proof of uniqueness of weak solutions I'll try out assuming that $\Phi'(u) \geq 0$.
 \section{Uniqueness}
@@
 in $Q_T$.
-Wherever $\Phi'(u) > 0$ we have $u_2 = u_1$, but more care is needed when $u_1$ and $u_1$ take values where $\Phi'(u) = 0$.
+Wherever $\Phi'(u) > 0$ we have $u_2 = u_1$, but more care is needed when $u_1$ and $u_2$ take values where $\Phi'(u) = 0$.
 So suppose $u_1 \neq u_2$ on a set $E \subset Q_T$ of positive measure.
@@
 \end{equation*}
-for all test functions $\eta$ with support in $E$. This gives us that $u_2 = u_1$ a.e. in $E$ as well, so $u_2 = u_1$ a.e. in all of $Q_T$. Whoop-dee-doo!
+for all test functions $\eta$ with support in $E$. This gives us that $u_2 = u_1$ a.e. in $E$ as well, so $u_2 = u_1$. Whoop-dee-doo!
 \end{proof}

### 2014-09-15 stuff_somewhat_organised.tex
Changed to what I for now think is a nicer font.
Apperently did some changes.

--- 2014-09-05 stuff_somewhat_organised.tex
@@
 
-Let $\Omega \subset \mathbb{R}^d$ be an open, simply connected domain. Then the filtration, or general porous medium equation is
+Let $\Omega \subset \mathbb{R}^d$ be an open, bounded, and simply connected domain. Then the filtration, or general porous medium equation is
 \begin{equation}
@@
 \end{equation}
- where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. More specific assumptions on the nonlinearity $\phi$  and the forcing term $f$ will follow.
+ where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. For now we assume that $\Phi$ is continuous and nondecreasing.
 
@@
 		\end{equation}
-		for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on the boundary and has compact support.
+		for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on $\partial \Omega \time [0,T)$ and for $t=T$.
 \end{enumerate}
@@
 \end{enumerate}
-For now the assumption that $\phi' > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi \geq 0$.
+For now the assumption that $\Phi' > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi \geq 0$.
 In that case (\ref{GPME}) changes from nodegenerate parabolic to degenerate parabolic.
@@
 \begin{theorem}[Uniqueness]
-	Assuming $u \in L^2(Q_T)$ and that $\Phi \in L^2(0,T : H_0^1(\Omega))$, (\ref{HDP}) has at most one weak solution.
+	Assuming in addition that $u \in L^2(Q_T)$ and $\Phi(u) \in L^2(0,T : H_0^1(\Omega))$, (\ref{HDP}) has at most one weak solution.
 \end{theorem}

### 2014-09-15 stuff_somewhat_organised.tex

--- 2014-09-05 stuff_somewhat_organised.tex
@@
 \usepackage{amssymb}
+%\usepackage{amsfonts}
+%\usepackage{amsmath}
 \usepackage{fullpage}
@@
 \usepackage[utf8]{inputenc}
+
+\usepackage{lmodern}
 
@@
 
-Let $\Omega \subset \mathbb{R}^d$ be an open, simply connected domain. Then the filtration-, or general porous medium equation is
+Let $\Omega \subset \mathbb{R}^d$ be an open, bounded, and simply connected domain. Then the filtration, or general porous medium equation is
+
 \begin{equation}
@@
 \end{equation}
- where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. More specific assumptions on the nonlinearity $\Phi$  and the forcing term $f$ will follow.
+
+ where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. For now we assume that $\Phi$ is continuous and nondecreasing.
 
@@
 		\end{equation}
-		for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on the boundary and has compact support.
+for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on $\partial \Omega \times [0,T)$ and for $t=T$.
 \end{enumerate}
@@
 \end{enumerate}
+
 For now the assumption that $\Phi'(u) > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi'(u) \geq 0$.
@@
 But hopes are high.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-09-18 stuff_somewhat_organised.tex
Refined a proof and started on L^1-contractivity.

@@
 \abstract{Funker dette?}
+
 \section{Basics}
@@
 \newtheorem{ex}{Example}
+\newtheorem{proposition}{Proposition}
 
@@
 \begin{mydef}[Weak solutions]
-A locally integrable function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of \ref{HDP} if
+A locally integrable function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of (\ref{HDP}) if
 \begin{enumerate}[i)]
@@
 
+\subsection{$L^1$-contractivity}
+Now we'll try to prove the following result:
+
+\begin{proposition}
+For two weak energy solutions $u$ and $\hat{u}$ with initial data $u_0$, $\hat{u}_0$ and forcing terms $f$, $\hat{f}$ respectively, we have for every $t > \tau \geq 0$
+\begin{equation}
+\label{l1_con}
+||(u(t) - \hat{u}(t))_+||_1 \leq ||(u(\tau) - \hat{u}(\tau))_+||_1 + \int_\tau^t ||(f(s) - \hat{f}(s))_+||_1ds. 
+\end{equation}
+\end{proposition}
+
+The proof will be done by establishing the result for smooth solutions of (\ref{HDP}).
+For such a solution to exist we must require that $\Phi'(u) > 0$, as well as some smoothness requirements on $f$ and $\partial\Omega \times (0,T)$ (I will check these smoothness assumptions).
+Then approximating the problem by smooth data, for which the $L^1$-contractivity holds, and pass to the limit.
+
+\subsubsection{$L^1$-contractivity for smooth solutions}
+Let $p: \mathbb{R} \to \mathbb{R}$ be a smooth function satisfying $p(s) = 0$ for $s \leq 0$, $p'(s) \geq 0$ for all $s\in \mathbb{R}$, and $0 \leq p(s) \leq 1$ for $s > 0$.
+Define now $w = \Phi(u) - \Phi(\hat{u})$, and multiply $p(w)$ with the difference of (\ref{GPME}) for $u$ and $\hat{u}$ to get
+\begin{equation*}
+\partial_t(u-\hat{u})p(w) = p(w)\Delta w + p(w)f.
+\end{equation*}
+Integrating over $\Omega$, and using integration by parts on the first part on the right hand side yields
+\begin{align*}
+\int_{\Omega}\partial_t(u-\hat{u})p(w)dx &= -\int_{\Omega}p'(w)|\nabla w|^2dx + \int_{\Omega}p(w)(f-\hat{f}) dx \\
+	&\leq \int_{\Omega}p(w)(f-\hat{f}) dx \\
+	&\leq \int_{\Omega}(f-\hat{f})_+ dx,
+\end{align*}
+where the last step follows from the fact that $0 \leq p(w) \leq 1$.
+Now, let $p$ converge to the Heaviside function $H(w)$.
+Then, it is worth noticing that $H(w) = H(u-\hat{u})$, because of the strict monotonicity of $\Phi$.
+Also see that $\partial_t(u-\hat{u})_+ = \partial_t(u-\hat{u})H(u-\hat{u})$.
+Thus we get that
+\begin{equation*}
+\partial_t \int_{\Omega}(u-\hat{u})_+dx \leq \int_{\Omega}(f-\hat{f})_+ dx,
+\end{equation*}
+and integrating in time from $\tau$ to $t$ yields
+\begin{equation*}
+\int_{\Omega}(u(t)-\hat{u}(t))_+dx \leq \int_{\Omega}(u(\tau)-\hat{u}(\tau))_+dx + \int_\tau^t\int_{\Omega}(f-\hat{f})_+dxdt.
+\end{equation*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the following proof of uniqueness of weak solutions I'll try out assuming that $\Phi'(u) \geq 0$.
 \section{Uniqueness}
@@
 \begin{proof}
-This is a pretty neat proof using a smart choice of $\eta$. So let's assume $u_1$ and $u_2$ are weak solutions. Then
-\begin{equation*}
+This is a pretty neat proof using a smart choice of $\eta$.
+So let's assume $u_1$ and $u_2$ are weak solutions.
+Then, when putting $u_1$ and $u_2$ into (\ref{weak}) and subtracting one from the other, we get
+\begin{equation}
+\label{weak_diff}
 \iint_{Q_T}\nabla(\Phi(u_2) - \Phi(u_1)) \cdot \nabla \eta - (u_2 - u_1)\partial_t \eta dxdt = 0.
-\end{equation*}
+\end{equation}
 Now the inspired move\footnote{Of course, this isn't my proof so that sort of horn-tooting is in good taste.} is choosing
@@
 \end{equation*}
-It is then easily verified that
+We then have
 \begin{equation*}
@@
 \end{equation*}
-which put into the integral equality above yields
+where the time derivation is valid using the First Fundamentel Theorem of Calculus and that $\Phi(u_i) \in L^1(0,T : W_0^{1,1}(\Omega))$ by the definition of weak soultion.
+
+When putting these derivatives into the above equality we end up with
 \begin{equation}
@@
 \end{enumerate}
-From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e.
+From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies, by the first integral that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e.
 in $Q_T$.
-Wherever $\Phi'(u) > 0$ we have $u_2 = u_1$, but more care is needed when $u_1$ and $u_2$ take values where $\Phi'(u) = 0$.
-So suppose $u_1 \neq u_2$ on a set $E \subset Q_T$ of positive measure.
-That means $\nabla(\Phi(u_2) - \Phi(u_1)) = 0$ a.e.
-in $E$, and so we can deduce that
+Actually, we have that $\Phi(u_2) - \Phi(u_1) = 0$ a.e., because wherever $u_2 = u_1$ it is trivially true, and wherever $ u_2 \neq u_1$ it holds from the first integral being zero.
+Thus, $ \nabla (\Phi(u_2) - \Phi(u_1) ) = 0$ a.e.
+and putting this into (\ref{weak_diff}) we get that
 \begin{equation*}
-\iint_{Q_T}(u_2 - u_1)\partial_t \eta dxdt = 0
+\iint_{Q_T}(u_2 - u_1)\partial_t \eta dx dt = 0.
 \end{equation*}
-for all test functions $\eta$ with support in $E$. This gives us that $u_2 = u_1$ a.e. in $E$ as well, so $u_2 = u_1$. Whoop-dee-doo!
+This should hold for any test function $\eta$, and so the weak derivative of $u_2 - u_1$ with respect to time is zero.
+Because $u_2$ and $u_1$ have identical initial condition $u_0$ we conclude that $u_2 = u_1$.
 \end{proof}

### 2014-09-18 trygve_b_written_assignment1.tex
Started on Written assignment 1 in SPRÅK3501.

--- 2014-09-15 stuff_somewhat_organised.tex
@@
 \begin{document}
-\title{Stuff that may well go into the project report}
+
+\title{Written assignment 1 in SPRÅK3501}
 \author{Trygve Bærland}
 \maketitle
-\abstract{Funker dette?}
-\section{Basics}
-\newtheorem{theorem}{Theorem}
-\newtheorem{mydef}{Definition}
-\newtheorem{ex}{Example}
+\section*{First article:}
+\cite{Cifani} is an article showing the main strategy I want to do.
 
-Let $\Omega \subset \mathbb{R}^d$ be an open, bounded, and simply connected domain. Then the filtration, or general porous medium equation is
+\section*{Second article:}
+\cite{Schochet}
 
-\begin{equation}
-\label{GPME}
-	\partial_t u = \Delta \Phi(u) + f,
-\end{equation}
-
- where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. For now we assume that $\Phi$ is continuous and nondecreasing.
-
-\subsection{Problem statement}
-I will consider on the following Dirichlet problem:
-\begin{equation}
-\label{HDP}
-	\begin{cases}
-		\partial_t u = \Delta \Phi(u) + f, \quad \text{ in } Q_T \\
-		u(x,0) = u_0(x), \quad \text{ in } \Omega \\
-		u(x,t) = 0, \quad \text{ on } \partial\Omega \times (0,T).
-	\end{cases}
-\end{equation}
-Here $Q_T = \Omega \times (0,T)$, where $T$ may very well be infinite.
-\subsection{Weak formulation}
-\begin{mydef}[Weak solutions]
-A locally integrable function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of \ref{HDP} if
-\begin{enumerate}[i)]
-	\item $u \in L^1(Q_T)$ and $\Phi(u) \in L^1(0,T : W_0^{1,1}(\Omega))$\footnote{$f:\Omega \to \mathbb{R}$ is an element of $W^{k,p}(\Omega)$ if all weak derivatives with $|\alpha| \leq k$ exists and are in $L^p(\Omega)$.
-$W_0^{k,p}$ is the closure of $C^\infty_c(\Omega)$ in $W^{k,p}(\Omega)$.};
-	\item $u$ satisfies
-		\begin{equation}
-		\label{weak}
-		\iint_{Q_T} \{\nabla\Phi(u)\cdot \nabla\eta - u\partial_t \eta \}dxdt = \int_\Omega u_0(x)\eta(x,0)dx + \iint_{Q_T}f\eta dxdt
-		\end{equation}
-for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on $\partial \Omega \times [0,T)$ and for $t=T$.
-\end{enumerate}
-\end{mydef}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%					ESTIMATES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Some estimates}
-Now we need to make some assumptions on $\Phi$ and $f$:
-\begin{enumerate}[i)]
-	\item The function $\Phi: \mathbb{R} \to \mathbb{R}$ is continuous, strictly increasing and we assume $\Phi(0) = 0$ without any loss of generality.
-\end{enumerate}
-
-For now the assumption that $\Phi'(u) > 0$ is kind of strong, but I hope to generalise (or find analogues for) most of the estimates to the case $\Phi'(u) \geq 0$.
-In that case (\ref{GPME}) changes from nodegenerate parabolic to degenerate parabolic.
-But hopes are high.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%					UNIQUENESS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In the following proof of uniqueness of weak solutions I'll try out assuming that $\Phi'(u) \geq 0$.
-\section{Uniqueness}
-\begin{theorem}[Uniqueness]
-	Assuming in addition that $u \in L^2(Q_T)$ and $\Phi(u) \in L^2(0,T : H_0^1(\Omega))$, (\ref{HDP}) has at most one weak solution.
-\end{theorem}
-\begin{proof}
-This is a pretty neat proof using a smart choice of $\eta$. So let's assume $u_1$ and $u_2$ are weak solutions. Then
-\begin{equation*}
-\iint_{Q_T}\nabla(\Phi(u_2) - \Phi(u_1)) \cdot \nabla \eta - (u_2 - u_1)\partial_t \eta dxdt = 0.
-\end{equation*}
-Now the inspired move\footnote{Of course, this isn't my proof so that sort of horn-tooting is in good taste.} is choosing
-\begin{equation*}
-\eta(x,t) = \begin{cases}
-		\int_t^T(\Phi(u_2) - \Phi(u_1))ds, \quad &\text{ if } 0 < t < T \\
-		0 \quad &\text{ if } t\geq T.
-	\end{cases}
-\end{equation*}
-It is then easily verified that
-\begin{equation*}
-\begin{cases}
-	\partial_t \eta &= -(\Phi(u_2) - \Phi(u_1) ) \\
-	\nabla \eta &= \int_t^T\nabla (\Phi(u_2) - \Phi(u_1))ds,
-\end{cases}
-\end{equation*}
-which put into the integral equality above yields
-\begin{equation}
-\label{unique}
-\begin{aligned}
-	&\iint_{Q_T}(\Phi(u_2) - \Phi(u_1))(u_2 - u_1)dxdt \\ 
-	&+ \iint_{Q_T}\nabla(\Phi(u_2(t)) - \Phi(u_1(t))) \cdot \left(\int_t^T 					\nabla(\Phi(u_2(s)) - \Phi(u_1(s))ds\right)dtdx = 0.
-\end{aligned}
-\end{equation}
-Let's take these in order:
-\begin{enumerate}[i)]
-	\item In the first integral we notice that $u_2 > u_1 \Rightarrow \Phi(u_2) \geq \Phi(u_1)$ and vice versa, so this integral is nonnegative.
-
-	\item For the second integral it is helpful to first only consider integration of the temporal dimensions, leaving us with
-	\begin{align*}
-	&\int_0^T\int_t^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dsdt \\
-	&= \int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds.
-	\end{align*}
-	Due to the symmetry about the line $s=t$, we have
-	\begin{align*}
-	&\int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
-	&= \frac{1}{2}\int_0^T \int_0^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
-	&= \frac{1}{2}\left( \int_0^T \nabla(\Phi(u_2)-\Phi(u_1))dt\right)^2,
-	\end{align*}
-	which is also nonnegative, and therefore the second integral in (\ref{unique}) must also be nonnegative.
-\end{enumerate}
-From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e.
-in $Q_T$.
-Wherever $\Phi'(u) > 0$ we have $u_2 = u_1$, but more care is needed when $u_1$ and $u_2$ take values where $\Phi'(u) = 0$.
-So suppose $u_1 \neq u_2$ on a set $E \subset Q_T$ of positive measure.
-That means $\nabla(\Phi(u_2) - \Phi(u_1)) = 0$ a.e.
-in $E$, and so we can deduce that
-\begin{equation*}
-\iint_{Q_T}(u_2 - u_1)\partial_t \eta dxdt = 0
-\end{equation*}
-for all test functions $\eta$ with support in $E$. This gives us that $u_2 = u_1$ a.e. in $E$ as well, so $u_2 = u_1$. Whoop-dee-doo!
-\end{proof}
+\newpage
+\bibliographystyle{plain}
+\bibliography{project_bibliography.bib}
 \end{document}

### 2014-09-18 trygve_b_written_assignment1.tex
First draft of written assignment 1 done.

@@
 \maketitle
+\section*{Introduction:}
+In my project I will consider a generalisation of the Porous Medium Equation, and specifically try to construct a numerical method that converges to a, in some sense, unique solution.
+
 \section*{First article:}
-\cite{Cifani} is an article showing the main strategy I want to do.
+\subsection*{Summary:}
+\cite{Cifani} presents a numerical method for solving a convection-diffusion equation with fractional, nonlinear diffusion.
+The article starts off by setting up a problem formulation, then introduce an entropy condition that ensures uniqueness of solutions that are bounded and integrable.
+After presenting a numerical method and proving that it converges to the entropy solution, the authors show that the numerical solutions also converge to a function of bounded variation, and hence they prove existence of solutions with bounded variation.
+
+\subsection*{Critique:}
+The article is quite impressive in that it introduces a new class of partial differential equations, and establishes existence, uniqueness and stability of solutions.
+However, it seems to me that the numerical method presented only works on simple problems, in the sense that if the domain cannot easily be made into a nice grid the implementation will be almost impossible.
+
+\subsection*{Reflections:}
+Although this article tackles a class of partial differential equations that easily are much harder to analyse than what I'm setting out to tackle, the overall strategy to get a new sense of existence is very similar to what I aim to do in my work, and hence is a quite useful article.
+Also, the numerical method used here is quite different from the one I will be using.
 
 \section*{Second article:}
-\cite{Schochet}
+\subsection*{Summary:}
+In \cite{Schochet} scalar hyperbolic conservation laws are considered.
+While not using novel numerical method on this class of partial differential equations the author is able to further the field by deriving a rate of convergence for the spectral- and pseudospectral methods.
+
+\subsection*{Critique:}
+The article assumes quite a bit of knowledge on the reader.
+E.g.
+extensive knowledge of Fourier analysis and certain convergence results in this field is assumed.
+This makes it a tough read.
+Luckily, in between paragraphs heavy on mathematical notation, the author is mostly very considerate and provides good discussions.
+
+\subsection*{Reflections:}
+Again, the family of equations considered are different from the ones I will be considered, but in contrast to \cite{Cifani}, the methods of analysis doesn't carry over as well as I'd hoped.
+The numerical method is quite similar to the one I will be using, and that is the main reason for this article's relevance to my work, however there are some key differences that I'm not yet sure of whether are significant or not.
 

### 2014-09-18 animation_Barenblatt.m
Changed animation script to generate a single figure.

@@ -19,13 +19,15 @@ dt = T/nt;
 
 %Spatial domain:
 x = linspace(-2,2,100);
-
+t  = linspace(0, 0.5, 3)
 figure
-for i=1:nt
-    t = dt*i;
-    U = t^(-alpha) * max(0,C-k*abs(x).^2*t^(-2*beta)).^(1/(m-1));
-    pause(0.03)
+axis([-2 2 0 3])
+xlabel('x-axis')
+ylabel('u')
+title('Example of solution for different times')
+hold on
+for dt=linspace(0.01, 0.5, 3)
+    U = dt^(-alpha) * max(0,C-k*abs(x).^2*dt^(-2*beta)).^(1/(m-1));
     plot(x,U)
-    axis([-2 2 0 10])
-    drawnow
 end
+hold off

### 2014-09-23 stuff_somewhat_organised.tex
Skrevet litt mer da veit du.

@@
 \usepackage[utf8]{inputenc}
+\usepackage[toc,page]{appendix}
 
@@
 \maketitle
-\abstract{Funker dette?}
+\abstract{For now, heavily reliant on \cite{vazquez2007porous}}
 
+% My text categories:
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{proposition}{Proposition}[section]
+
+\theoremstyle{definition}
+\newtheorem{mydef}{Definition}[section]
+\newtheorem{example}{Example}[section]
+
+\theoremstyle{remark}
+\newtheorem{obs}{Observation}
+\newtheorem{rem}{Remark}
+
+% Reset numbering for each section
+\numberwithin{equation}{section}
 \section{Basics}
-\newtheorem{theorem}{Theorem}
-\newtheorem{mydef}{Definition}
-\newtheorem{ex}{Example}
-\newtheorem{proposition}{Proposition}
 
@@
 Here $Q_T = \Omega \times (0,T)$, where $T$ may very well be infinite.
-\subsection{Weak formulation}
+\subsection{Weak solutions}
 \begin{mydef}[Weak solutions]
@@
 \end{mydef}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		ENERGY SOLUTIONS:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Energy solutions}
+We define  $\Psi$ as the primitive of $\Phi$ with $\Psi(0) = 0$, i.e.
+\begin{equation*}
+	\Psi(s) = \int_0^s \Phi(u) ds.
+\end{equation*}
+With this in mind we can define energy solutions in the following way:
+\begin{mydef}[Energy solution]
+We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L^1(\Omega)$ and $\Psi(u_0) \in L^1(\Omega)$, and the energy inequality
+\begin{equation}
+\label{energy_ineq}
+\iint_{Q_T} |\nabla \Phi(u)|^2 dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}f\Phi(u)dxdt
+\end{equation}
+holds.
+\end{mydef}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 But hopes are high.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%					L^1-CONTRACTIVITY
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{equation*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 where the time derivation is valid using the First Fundamentel Theorem of Calculus and that $\Phi(u_i) \in L^1(0,T : W_0^{1,1}(\Omega))$ by the definition of weak soultion.
+For the validity of the spatial derivative, confer appendix \ref{sec:derivative}.
 
@@
 \end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				APPENDICES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{appendices}
+\section{Passing derivative inside the integral}
+\label{sec:derivative}
+
+We are now concern with whether
+\begin{equation}
+\label{diff_int}
+	\nabla \int_t^T \varphi(x,s)ds = \int_t^T \nabla\varphi(x,s)ds
+\end{equation}
+holds or not for $\varphi \in L^2(0,T:H_0^1 (\Omega))$. 
+For simplicity we now only consider one spatial dimension.
+
+To begin with, assume that $\psi, \eta \in C^{\infty}_c$, then we have that
+\begin{align*}
+\int_{\Omega}\psi \partial_x\left(\int_t^T \eta(x,s) ds\right)dx &= \int_{\Omega}\psi \lim_{h \to 0}\left(\int_t^T \frac{\eta(x+h,s)-\eta(x,s)}{h} ds\right)dx\\
+&= \int_{\Omega}\psi \lim_{h \to 0}\left(\int_t^T \eta_h(x,s) ds\right)dx.
+\end{align*}
+
+Assuming that $\partial_x \eta(x,s)$ is bounded, we can use the mean value theorem to state that $|\eta_h| \leq  ||\partial_x \eta||_\infty$.
+We also have that $\eta_h(x,s) \to \partial_x \eta(x,s)$ pointwise, and so we're in a position to use the Dominated Convergence theorem to conclude that
+\begin{equation}
+\label{results_diff_first}
+\int_{\Omega}\psi \partial_x\left(\int_t^T \eta(x,s) ds\right)dx = \int_{\Omega}\psi \left(\int_t^T \partial_x\eta(x,s) ds\right)dx.
+\end{equation}
+
+To extend the result to $L^2(0,T:H_0^1 (\Omega))$ we use that $C_c^\infty$ is dense in this space.
+So let $\{\psi_n\},\{\varphi_n\}$ be two sequence converging to $\psi$ and $\varphi$ in $L^2(\Omega)$ and $L^2(0,T:H_0^1(\Omega))$ respectively.
+Considering the left hand side of (\ref{results_diff_first}), we get
+\begin{align*}
+&\left|\int_{\Omega}\psi \partial_x \left( \int_t^T\varphi ds \right)dx - \int_{\Omega}\psi_n \partial_x \left( \int_t^T \varphi_n ds \right) dx \right| \\
+&\leq  \left| \int_{\Omega} \psi \partial_x \left(\int_t^T \varphi - \varphi_n ds\right)dx \right| + \left| \int_{\Omega}(\psi - \psi_n)\partial_x\left(\int_t^T \varphi_n ds\right) dx \right| \\
+&\leq ||\psi||_{L^2(H_0^1)}|(\varphi -\varphi_n)|_{L^2(H_0^1)} + ||\psi-\psi_n||_{L^2}| \varphi_n |_{L^2(H_0^1)} \\
+&\leq ||\psi||_{L^2(H_0^1)}||(\varphi -\varphi_n)||_{L^2(H_0^1)} + ||\psi-\psi_n||_{L^2}|| \varphi_n ||_{L^2(H_0^1)} \\
+&\to 0,
+\end{align*}
+after using the triangle- and Cauchy-Schwarz' inequality as well as the assumptions on convergence.
+
+An exactly similar approach can be done to the right hand side, and so passing the limit in (\ref{results_diff_first}) we get
+\begin{equation}
+\label{result_diff_final}
+\int_\Omega \psi \partial_x\left(\int_t^T \varphi(x,s)ds\right)dx = \int_\Omega \psi \left( \int_t^T \partial_x \varphi(x,s)ds \right) dx.
+\end{equation}
+
+To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.
+\end{appendices}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				BIBLIOGRAPHY
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\bibliographystyle{plain}
+\bibliography{project_bibliography.bib}
 \end{document}

### 2014-09-23 stuff_somewhat_organised.tex
Skrevet enda litt mer.

@@
 
-\theoremstyle{remark}
+%\theoremstyle{plain}
 \newtheorem{obs}{Observation}
@@
 
+\begin{obs}
+With $u_0 \in L^1(\Omega)$ and $f\in L^1(Q_T)$, all the integrals in (\ref{weak}) make sense.
+\end{obs}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{mydef}
+
+\subsubsection{Derivation of energy estimate for classical solutions}
+Suppose $u$ is a smooth solution of (\ref{HDP}). We proceed by multiplying the equation with $\Phi(u)$ to get
+\begin{equation*}
+\Phi(u)\partial_t u = \Phi(u)\Delta \Phi(u) + \Phi(u)f,
+\end{equation*}
+and we notice that $\Phi(u)\partial_t u = \partial_t \Psi(u)$. That means when we integrate over $Q_T$ we have
+\begin{equation*}
+\iint_{Q_T} \partial_t \Psi(u)dxdt = \int_\Omega \Psi(u(T))dx - \int_\Omega \Psi(u_0)dx.
+\end{equation*}
+On the diffusive term we can use integration by parts, so
+\begin{equation*}
+\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_0^T \int_{\partial\Omega} \Phi(u)\nabla \Phi(u) \cdot \hat{n}dS,
+\end{equation*}
+where $\hat{n}$ is the outward unit normal. By the Dirichlet condition
+\begin{equation*}
+\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt,
+\end{equation*}
+and notice that this step would have been valid for homogeneous Neumann condition as well. In toto 
+\begin{equation}
+\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt.
+\end{equation}
+
+\setcounter{obs}{0}
+\begin{obs}
+In contrast to (\ref{energy_ineq}) we have equality for smooth solutions.
+\end{obs}
+
+\begin{obs}
+We can go even further and deal with the last term on the right hand side: Assuming $f,\Phi(u) \in L^2(Q_T)$, then
+\begin{equation*}
+\iint_{Q_T} f\Phi(u)dxdt \leq \left(\iint_{Q_T} f^2 dxdt\right)^\frac{1}{2}\left(\iint_{Q_T} \Phi(u)^2 dxdt\right)^\frac{1}{2},
+\end{equation*}
+by Cauchy-Schwarz'. With the inequality $\sqrt{ab} \leq \frac{1}{4c}a + cb$ for $c>0$
+\begin{equation*}
+\iint_{Q_T} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\iint_{Q_T}\Phi(u)^2dxdt.
+\end{equation*}
+Lastly, because of the homogeneous Dirichlet conditions, we use the Poincaré inequality and set $c$ so that
+\begin{equation*}
+\iint_{Q_T} f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt,
+\end{equation*}
+and the final inequality becomes
+\begin{equation}
+\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
+\end{equation}
+\end{obs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{proof}
+
+\setcounter{obs}{0}
+\begin{obs}
+Provided $\iint_{Q_T} f\Phi(u)dxdt$ in (\ref{energy_ineq}) makes sense, $\Phi(u) \in L^2(0,T: H_0^1(\Omega))$ for weak energy solutions.
+If we can put on a condition on $u$ or any of the data to ensure that $u \in L^2(Q_T)$, we would have a condition under which weak energy solutions are unique.
+Hopefully, no such condition is required, but will perhaps follow from some other estimate.
+\end{obs}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-09-26 stuff_somewhat_organised.tex
Tull med referanse for some reason.
Begynt med eksistens a la Ladyzhenskaya.

@@
 %\usepackage{amsfonts}
-%\usepackage{amsmath}
+\usepackage{amsmath}
 \usepackage{fullpage}
@@
 \usepackage{remreset}
-\usepackage[utf8]{inputenc}
+\usepackage[utf8x]{inputenc}
 \usepackage[toc,page]{appendix}
+\usepackage[numbers]{natbib}
 
@@
 \maketitle
-\abstract{For now, heavily reliant on \cite{vazquez2007porous}}
+\abstract{For now, heavily reliant on \citep{vazquez2007porous}.}
 
@@
 \begin{appendices}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		A
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Passing derivative inside the integral}
@@
 To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.
+
+%%%%%%%%%%%%%%%%%%
+%		B
+%%%%%%%%%%%%%%%%%%
+\section{Some major theorems}
+We now consider the problem of determining a function $u = u(x,t)$ in $\overline{Q}_T$ so that
+\begin{equation}
+\label{lady_parabolic_eq}
+	u_t - \sum_{i=1}^d\frac{d}{dx_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
+\end{equation}
+in $Q_T$ and on $\Gamma_T$
+\begin{equation}
+\label{lady_bc}
+	u\big|_{\Gamma_T} = \psi\big|_{\Gamma_T}
+\end{equation}
+for some known function $\psi$.
+
+Furthermore, we define
+\begin{equation*}
+A(x,t,u,\nabla u) = a(x,t,u,\nabla u) - \sum_{i=1}^d \left[ \frac{\partial a_i(x,t,u,\nabla u)}{\partial u} + \frac{\partial a_i(x,t,u,\nabla u)}{\partial x_i} \right]
+\end{equation*}
+Immediately below is an existence theorem presented on this type of problem taken
+verbatim from \citep[ Theorem 6.1, p. 452]{ladyzhenskaya}.
+
+\begin{theorem}[Existence of classical solutions]
+\label{thm:classical_existence}
+Suppose that the following conditions hold.
+\begin{enumerate}[a)]
+	\item For $(x,t) \in \overline{Q}_T$ and either
+	\begin{equation}
+		\label{exist_cond1}
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \Bigg|_{p=0} \geq 0, \quad A(x,t,u,0)u \geq -b_1 u^2 - b2
+	\end{equation}
+	or
+	\begin{equation}
+	\label{exist_cond2}
+	A(x,t,u,0)u \geq -\Phi(|u|)|u| - b_2, \quad \int_0^\infty \frac{d\tau}{\Phi(\tau)}= \infty, \quad \Phi > 0
+	\end{equation}
+	for arbitrary $u$ and $\xi = (\xi_1, \xi_2, \ldots, \xi_d)$.
+
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and arbitrary $p$ the functions $a_i(x,t,u,p)$ and $a(x,t,u,p)$ are continuous, the $a_i(x,t,u,p)$ are differentiable with respect to $x$, $u$ and $p$ and the following inequalities are satisfied
+	\begin{equation}
+	\label{exist_cond3}
+		\begin{cases}
+			\nu\xi^2 \leq \frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2, \quad \nu > 0 \\
+			\sum_{i=1}^d \left(|a_i| + |\frac{\partial a_i}{\partial u}|\right)(1+|p|) + \sum_{i,j=1}^d |\frac{\partial a_i}{\partial x_j}| + |a| \leq \mu (1 + |p|)^2. 		
+		\end{cases}
+	\end{equation}
+	where $\nu$ and $\mu$ are positive numbers.
+
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a H\H{o}lder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
+
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$ the function $a(x,t,u,p)$ has the partial derivatives $\frac{\partial a}{\partial p_j}$ and $\frac{\partial a}{\partial u}$ and the functions $a_i$ and $a$ satisfy
+	\begin{equation}
+	\label{exist_cond4}
+	\begin{split}
+		&\Bigg| \frac{\partial a_i(x,t,u,p)}{\partial u}, \frac{a_i(x,t+h,u,p) - 		a_i(x,t,u,p)}{h}, \\
+		&\frac{\partial a}{\partial p}, \frac{\partial a}{\partial u}, \frac{a(x,t+h,u,p) - a(x,t,u,p)}{h} \Bigg| \leq \varphi(x,t)
+	\end{split}.
+	\end{equation}
+
+	\item $\psi(x,t) \in H^{2+\beta, 1+\beta/2}(\overline{Q}_T)$ and satisfy
+	\begin{equation}
+	\label{exist_cond5}
+	\psi_t - \frac{d}{dx_i}a_i(x,t,\psi,\psi_x) + a(x,t,\psi,\psi_x) = 0.
+	\end{equation}
+
+	\item $S \in H^{2+\beta}$.
+\end{enumerate}
+
+Under these conditions there exists a unique solution of problem (\ref{lady_parabolic_eq}) with boundary condition (\ref{lady_bc}) from the class $H^{2+\beta, 1+\beta/2}(\overline{Q}_T)$.
+Moreover, this solution has derivatives $u_{xt}$ from $L^2(\overline{Q}_T)$.
+\end{theorem}
+
+\subsection{This existence result applied to our problem}
+The general porous medium equation we are concerned with can be written
+\begin{equation*}
+u_t - \nabla \cdot (\nabla \Phi(u) ) - f(x,t) = 0,
+\end{equation*}
+which is of the form (\ref{lady_parabolic_eq}) with
+\begin{equation}
+a_i(x,t,u,\nabla u) = \Phi'(u) u_{x_i}, \quad a(x,t,u,\nabla) = -f(x,t).
+\end{equation}
+
+Let's go trhough each condition in theorem \ref{thm:classical_existence} to see what assumptions we must make to have a classical solution.
+
+\begin{enumerate}[a)]
+	\item We consider fullfilling (\ref{exist_cond1}). We have
+	\begin{equation*}
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j} = \delta_{ij} \Phi'(u),
+	\end{equation*}
+	and so, since $\Phi'(u) \geq 0$ is assumed,
+	\begin{equation*}
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j}\Bigg|_{p=0}\xi_i\xi_j = \Phi'(u)\xi_i^2 \geq 0.
+	\end{equation*}
+
+	In the general porous medium equation
+	\begin{equation*}
+		A(x,t,u,p) = -f(x,t) - 
+	\end{equation*}
+\end{enumerate}
 \end{appendices}
@@
 \newpage
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{project_bibliography.bib}

### 2014-09-29 stuff_somewhat_organised.tex
Getting OK along with Ladyzhenskaya.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Notation and important spaces}
+Throughout this note $\Omega \subset \mathbb{R}^d$ will be a bounded domain, and $\partial \Omega$ will be its boundary.
+Furthermore we define $Q_T = \{ (x,t): x \in \Omega, t\in [0,T] \}$, and $\Gamma_T$ is the parabolic boundary, i.e.
+$\Gamma_T = \{(x,t): x \in \partial \Omega, t \in [0,T]\} \bigcup \{(x,t): x \in \Omega, t=0\}$.
+
+\subsection{Function spaces}
+Most, if not all, of the notation concerning function spaces will follow the notation in \citep{evans} (see in particular Ch. 5).
+
+To start off $C^k(U)$ is the set of all functions that are $k$ times continuously differentiable in $U \subset \mathbb{R}^n$. A norm for continuous functions is
+\begin{equation*}
+	||u||_{C(\bar{U})} = \underset{x\in U}{\text{sup}}|u(x)|.
+\end{equation*}
+Let now $0 < \gamma \leq 1$.
+\begin{mydef}[Hölder continuous]
+The $\gamma^{th}$-Hölder seminorm of $u: U \to \mathbb{R}$ is
+	\begin{equation*}
+	|u|_{C^{0,\gamma}(\bar{U}))} = \underset{\underset{x \neq y}{x,y \in U}}{\text{sup}} \left\{\frac{|u(x)-u(y)|}{|x-y|^\gamma} \right\}
+	\end{equation*}
+and the $\gamma^{th}$-Hölder norm is
+\begin{equation*}
+||u||_{C^{0,\gamma}} = ||u||_{C(\bar{U})} + |u|_{C^{0,\gamma}}.
+\end{equation*}
+\end{mydef}
+We continue by defining the Hölder spaces:
+\begin{mydef}[Hölder space]
+The Hölder space $C^{k,\gamma}(\bar{U})$ consists of all functions $u \in C^k(\bar{U})$ for which the norm
+\begin{equation*}
+ ||u||_{C^{k,\gamma}(\bar{U})} = \sum_{|\alpha| \leq k}||D^\alpha u||_{C(\bar{U})} + \sum_{|\alpha| = k} |D^\alpha u|_{C^{0,\gamma}(\bar{U})}
+\end{equation*}
+is finite.
+\end{mydef}
+%%%%%%%%%%%%%%%%%%
+%		B
+%%%%%%%%%%%%%%%%%%
 \section{Passing derivative inside the integral}
@@
 To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.
-
-%%%%%%%%%%%%%%%%%%
-%		B
-%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%
+%		C
+%%%%%%%%%%%%%%%%%%%
 \section{Some major theorems}
@@
 		\begin{cases}
-			\nu\xi^2 \leq \frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2, \quad \nu > 0 \\
+			\nu\xi^2 \leq \sum_{i,j=1}^d\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2 \\
 			\sum_{i=1}^d \left(|a_i| + |\frac{\partial a_i}{\partial u}|\right)(1+|p|) + \sum_{i,j=1}^d |\frac{\partial a_i}{\partial x_j}| + |a| \leq \mu (1 + |p|)^2. 		
@@
 
-	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a H\H{o}lder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a Hölder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
 
@@
 
-\subsection{This existence result applied to our problem}
+\subsection{This existence result applied to the GPME}
 The general porous medium equation we are concerned with can be written
@@
 \begin{equation}
-a_i(x,t,u,\nabla u) = \Phi'(u) u_{x_i}, \quad a(x,t,u,\nabla) = -f(x,t).
+a_i(x,t,u,\nabla u) = \Phi'(u) u_{x_i}, \quad a(x,t,u,\nabla u) = -f(x,t).
 \end{equation}
@@
 	\begin{equation*}
-		A(x,t,u,p) = -f(x,t) - 
+		A(x,t,u,p) = -f(x,t) - \sum_{i=1}^d \Phi''(u)p_i,
 	\end{equation*}
+	which means $A(x,t,u,0) = -f(x,t)$ (Also see that we need $\Phi \in C^2(\mathbb{R})$). Thus, according to (\ref{exist_cond1}) we need constants $b_1$ and $b_2$ so that
+	\begin{equation*}
+		f(x,t)u \leq b_1 u^2 + b_2.
+	\end{equation*}
+	We are able to choose $b_1$ and $b_2$ if, for example, $f(x,t)$ is bounded in $\overline{Q}_T$.
+
+	\item We need $a_i(x,t,u,p)$ and $a(x,t,u,p)$ to continuous.
+This translates to requiring that $\Phi'(u)$ and $f(x,t)$ are continuous.
+In addition $a_i(x,t,u,p)$ needs to be differentiable with respect to $x$, $t$, $u$ and $p$, which in our case means that $\Phi''(u)$ needs to be continuous.
+
+	Considering the first inequality in (\ref{exist_cond3}) we have
+	\begin{equation*}
+		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2.
+	\end{equation*}
+	Assuming that $\Phi'(u)$ is strictly positive and continuous for $|u|\leq M$ we can set
+	\begin{equation}
+	0 < \nu = \text{inf}_{|u| \leq M}\Phi'(u) < \text{sup}_{|u| \leq M}\Phi'(u) \leq \mu.
+	\end{equation}
+
+	After establishing that
+	\begin{equation*}
+		\begin{cases}
+			a_i(x,t,u,p) &= \Phi'(u)p_i \\
+			\frac{\partial a_i(x,t,u,p)}{\partial u} &= \Phi''(u)p_i \\
+			\frac{\partial a_i(x,t,u,p)}{\partial x_j} &= 0,
+		\end{cases}	
+	\end{equation*}
+	we put it into the left hand side of the second inequality of (\ref{exist_cond3}) as
+	\begin{align*}
+	&\sum_{i=1}^d\left( |a_i| + \left| \frac{\partial a_i}{\partial u}\right| \right)(1+|p|) + \sum_{i,j}^d\left| \frac{\partial a_i}{\partial x_j} \right| + |a| \\
+	&= \sum_{i=1}^d\left( |\Phi'(u)| + |\Phi''(u)| \right)|p_i|(1+|p|) + |f(x,t)| \\
+	&= (|\Phi'(u)| + |\Phi''(u)|)(1+|p|)\sum_{i=1}^d|p_i| + |f(x,t)|.
+	\end{align*}
+	By the equivalence of $l_p$-norms in finite dimensions $\sum_i |p_i| \leq C|p|$. Furthermore, we assume $\Phi''(u)$ to be continuous for $|u|\leq M$, then
+	\begin{equation*}
+	(|\Phi'(u)| + |\Phi''(u)|)(1+|p|)\sum_{i=1}^d|p_i| + |f(x,t)| \leq K(|p| + |p|^2) + |f(x,t)|,
+	\end{equation*}
+	where $K = C\cdot \text{sup}_{|u|\leq M}(|\Phi'(u)| + |\Phi''(u)|)$. Now we are almost done. All that remains is noticing that
+	\begin{align*}
+	K(|p| + |p|^2) + |f(x,t)| &\leq K(|p| + |p|^2) + ||f||_{\infty}(1+|p|) \\
+	&\leq \text{max}\{ K, ||f||_\infty \} (1+|p|)^2.
+	\end{align*}
+	So we can set $\mu = \text{max}\{K, ||f||_\infty, \text{sup}_{|u|\leq M}\Phi'(u) \}$, and both inequalities in (\ref{exist_cond3}) are satisfied.
+
+	\item To reiterate, we need the functions
+	\begin{equation*}
+		\begin{cases}
+			a_i(x,t,u,p) &= \Phi'(u)p_i \\
+			a(x,t,u,p) &= -f(x,t) \\
+			\frac{\partial a_i(x,t,u,p)}{\partial p_j} &= \delta_{ij}\Phi'(u) \\
+			\frac{\partial a_i(x,t,u,p)}{\partial u} &= \Phi''(u)p_i \\
+			\frac{\partial a_i(x,t,u,p)}{\partial x_j} &= 0
+		\end{cases}
+	\end{equation*}
+	to be Hölder continuous in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
+If we choose $\beta = 1$ (i.e.
+Lipschitz continuous for all variables except $t$) the only additional assumption we need to make on $\Phi$ is that $\Phi^{(3)}(u)$ is bounded for $|u| \leq M$.
+The additional assumptions we need to make on $f$ is that it needs to be Lipschitz continuous with respect to $x$ and that
+	\begin{equation*}
+	|f(x,t) - f(x,s)| \leq C|t-s|^\frac{1}{2}
+	\end{equation*}
+	for some constant $C$.
+
 \end{enumerate}

### 2014-09-29 stuff_somewhat_organised.tex
Done with you, Ladyzhenskaya!

@@
 \newtheorem{proposition}{Proposition}[section]
+\newtheorem{cor}{Corollary}[section]
 
@@
 	\end{equation}
+	on $\partial \Omega \times \{t=0\}$.
 
-	\item $S \in H^{2+\beta}$.
+	\item $\partial \Omega \in C^{2+\beta}$\footnote{I can't seem to find a definition of this sort of boundary in \citep{ladyzhenskaya}.
+However, \citep{evans} has something vaguely familiar, but here integer values of the exponent is assumed.}.
 \end{enumerate}
@@
 \end{theorem}
+
+\setcounter{rem}{0}
+\begin{rem}
+\label{rem:lady_notation}
+By the function space $H^{l, l/2}$, Ladyzhenskaya et.
+al means the Banach space of functions $u$ that are continuous in $\bar{Q}_T$.
+So are all partial derivatives of the form $\partial_t^r D^\alpha u$, with $2r+|\alpha| <l$.
+The norm, they define
+\begin{equation*}
+	|u|_{Q_T}^{(l)} = \langle u \rangle^{(l)}_{Q_T} + \sum_{j=0}^{[l]}\langle u \rangle^{(j)}_{Q_T},
+\end{equation*}
+with
+\begin{align*}
+\langle u \rangle^{(j)}_{Q_T} &= \sum_{2r+|\alpha|=j} ||\partial_t^r D^\alpha u||_{C(\bar{Q}_T)} \\
+\langle u \rangle^{(l)}_{Q_T} &= \langle u \rangle^{(l)}_{x,Q_T} + \langle u \rangle^{(l/2)}_{t,Q_T} \\
+\langle u \rangle^{(l)}_{x,Q_T} &= \sum_{2r+|\alpha|=[l]} |\partial_t^r D^{\alpha}u|_{C^{0,l-[l]}(\bar{Q}_T)} \\
+ \langle u \rangle^{(l/2)}_{t,Q_T} &= \sum_{0 < l - 2r -\alpha < 2} |\partial_t^r D^\alpha u|_{C^{0,(l-2r-s)/2}(\bar{Q}_T)}
+\end{align*}
+with the Hölder semi-norm with respect to $x$ and $t$ respectively in the last two definitions\footnote{Yikes.}.
+\end{rem}
+
+\begin{rem}
+The  $\varphi$ in (\ref{exist_cond4}) is required to satisfy
+\begin{equation*}
+\left( \int_0^T \left(\int_\Omega |\varphi(x,t)|^q dx\right)^\frac{r}{q} dt \right)^\frac{1}{r} < \infty,
+\end{equation*}
+i.e. $\varphi \in L^r(0,T: L^q(\Omega))$, where $q$ and $r$ satisfy
+\begin{equation*}
+\frac{1}{r} + \frac{d}{2q} = 1 - x_1
+\end{equation*}
+and
+\begin{equation*}
+	\begin{cases}
+		q\in \left[\frac{d}{2(1-x_1)},\infty\right], &r\in \left[\frac{1}{1-x_1},\infty \right], 0<x_1<1, \quad \text{ for } d \geq 2 \\
+		q \in [1, \infty], &r \in \left[\frac{1}{1-x_1},\frac{2}{1-2x_1}\right], 0<x_1<\frac{1}{2}, \quad \text{ for } n=1
+	\end{cases}
+\end{equation*}
+\end{rem}
 
@@
 	for some constant $C$.
+Note that for bounded domains, Lipschitz continuity implies Hölder continuity with lower exponent.
+So we could make the kind of a fortiori assumption that $f$ is Lipschitz continuous with respect to time.
+Or even that $f_t(x,t)$ is bounded.
+
+	\item For this condition we see that it seems even more natural to impose that $f$ is Lipschitz continuous in $t$, and that the domain is bounded.
+I.e.
+that $T<\infty$ and $\Omega$ is bounded.
+Then all the previous assumptions we've made on $\Phi$ and $f$ will ensure that this condition holds.
+
+	\item We of course have
+	\begin{equation*}
+		\begin{cases}
+		\Psi(x,t) &= 0, \quad (x,t) \in \partial \Omega \times [0,T] \\
+		\Psi(x,0) &= u_0(x), \quad x\in \Omega 
+		\end{cases}
+	\end{equation*}
+	and so this condition isn't too hard to handle\footnote{I think...}.
+First off, we should require that $u_0$ vanish at the boundary, and that it is sufficiently smooth.
+To be more precise, $u_0$ should be in $C^2_c(\Omega)$.
+The condition (\ref{exist_cond5}) holds trivially, because  $\Psi\big|_{\partial \Omega \times \{t=0\}} = 0$.
+
+	\item In this condition we can do nothing more than assume sufficient smoothness of the boundary.
+\end{enumerate}
+
+It seems only appropriate that we summarise this somehow. A nice little corollary tailored for our purposes is just what we need now.
+
+\begin{cor}
+Assume the following conditions are satisfied:
+	\begin{enumerate}[a)]
+		\item 	$\Phi: \mathbb{R} \to \mathbb{R}$ is in $C^2(\mathbb{R})$, strictly increasing, and $\Phi$ and its subsequent derivatives are all Lipschitz.
+
+		\item $f = f(x,t)$ is $C^1(Q_T)$, bounded and Lipschitz in both its variables.
+
+		\item $u_0$ is $C^2(\Omega)$ and $u_0$ and its derivatives vanish near the boundary $\partial \Omega$.
+
+		\item $\partial \Omega$ is $C^{2+\beta}$-smooth.
 
 	\end{enumerate}
+Then (\ref{HDP}) has a unique solution $u\in C^{2,1}(\bar{Q}_T)$ for $T<\infty$. Moreover, this solution has derivatives $u_{xt}$ in $L^2(Q_T)$.
+\end{cor}
 \end{appendices}

### 2014-10-07 stuff_somewhat_organised.tex
Må begynne å forme eksistensbeviset til å ta med L^1-kontraksjon.

@@
 \end{cor}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		COMPACTNESS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Compactness argument}
+Here I will simply state the Rellich-Kondrachov Compactness theorem as it is presented in \citep{evans}, mostly for my own ease of reference. For more details, please cf. Chapter 5 ibid.
+
+\begin{mydef}
+Let $X$ and $Y$ be Banach spaces with $X \subset Y$. We say that $X$ is \textbf{compactly embedded} in $Y$, written
+\begin{equation*}
+X \subset \subset Y,
+\end{equation*}
+provided 
+\begin{enumerate}[i)]
+	\item $||u||_Y \leq ||u||_X$ for every $u \in X$, for some constant $C$, and
+
+	\item each bounded sequence in $X$ is precompact in $Y$.
+\end{enumerate}
+\end{mydef}
+
+With this definition in mind we have the following theorem:
+\begin{theorem}[Rellich-Kondrachov Compactness Theorem]
+Assume $U$ is an open, bounded subset of $\mathbb{R}^n$ and $\partial U$ is $C^1$.
+Suppose $1\leq p < n$. Then
+\begin{equation}
+\label{Rellich}
+W^{1,p}(U) \subset \subset L^q(U)
+\end{equation}
+for each $1\leq q < p^*$, where $p^* = \frac{np}{n-p}$ is the Sobolev conjugate of $p$.
+\end{theorem}
+\setcounter{rem}{0}
+\begin{rem}
+If $p=2$, the we have
+\begin{equation*}
+H^1(U) \subset \subset L^q(U)
+\end{equation*}
+for each $1\leq q < p^*$.
+\end{rem}
+\begin{rem}
+Since $p^* > p$ the result is valid for $q=p$. This actually holds for all $1\leq p \leq \infty$, even when $p > n$.
+\end{rem}
+\begin{rem}
+We also have 
+\begin{equation*}
+W^{1,p}_0(U) \subset \subset L^p(U)
+\end{equation*}
+even when the assumption that $\partial U$ is $C^1$ is lifted.
+\end{rem}
+
 \end{appendices}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-10-14 stuff_somewhat_organised.tex
Begynt å skrive på eksistensbeviset.

@@
 \newtheorem{cor}{Corollary}[section]
+\newtheorem{lemma}{Lemma}[section]
 
@@
 	\Psi(s) = \int_0^s \Phi(u) ds.
-\end{equation*}
+\end{equation*},
+and we define the function space $L_\Psi(\Omega) = \{ u\in L^1(\Omega): \Psi(u)\in L^1(\Omega)\}$.
 With this in mind we can define energy solutions in the following way:
 \begin{mydef}[Energy solution]
-We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L^1(\Omega)$ and $\Psi(u_0) \in L^1(\Omega)$, and the energy inequality
+We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L_\Psi(\Omega)$, and the energy inequality
 \begin{equation}
@@
 Lastly, because of the homogeneous Dirichlet conditions, we use the Poincaré inequality and set $c$ so that
-\begin{equation*}
+\begin{equation}
+\label{using_Poincare}
 \iint_{Q_T} f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt,
-\end{equation*}
+\end{equation}
 and the final inequality becomes
@@
 \end{obs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			EXISTENCE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Existence}
+Now we jump in with trying to prove existence of signed, weak energy solutions.
+Following closely the proof provided in \citep{vazquez2007porous}, but now lifting the assumption that $\Phi$ is strictly increasing, and rather having that it is only nondecreasing.
+Another useful addition to proof will be that we will also incorporate the $L^1$-contractivity result.
+
+The proof will use an approximate problem which admits a unique solution from theorem \ref{thm:classical_existence}, and then employing the Rellich compactness argument to get a limit which hopefully will be a weak energy solution.
+
+In the following we will assume $u_0 \in L_\Psi(\Omega)$ and $f\in L^p(\Omega)$ with $p = \frac{2d}{d+2}$ if $d \geq 3$, or for some $p>1$ if $d=1,2$\footnote{This choice of value for $p$, I can only say is a mystery for me at this moment, but it seems to be related to the Sobolev conjugate.
+Let's just stay curious and excited for now, shall we?}.
+
+The main theorem reads:
+\begin{theorem}
+\label{thm:weak_existence}
+Assume $u_0 \in L_\Psi(\Omega)$ and $f \in L^p (\Omega)$.
+Then the homogeneous, general porous medium equation (\ref{HDP}) has a weak solution defined in an infinite time interval, $T=\infty$.
+We have $u \in L^\infty(0,T:L_\Psi(\Omega))$ and $\Phi(u) \in L^2(0,T:H_0^1(\Omega))$, and the energy inequality (\ref{energy_ineq}) holds.
+\end{theorem}
+
+We will not prove this in one big chunk, but rather split it off into smaller lemmas, and as already stated, some attention will also be paid to the $L^1$-contractivity.
+\subsection*{Preliminaries}
+To set ourselves up in a position where we can make use of theorem \ref{thm:classical_existence}, or rather corollary \ref{cor:GPME_existence}, we need to approximate $\Phi$, $u_0$, and $f$.
+
+We approximate $\Phi$ by the smooth approximations
+\begin{align*}
+\Phi_n(s) &= \left( \Phi(s) + \frac{s}{n} \right)*\eta_{\frac{1}{n}} \\
+	&= \int_{\mathbb{R}}\left(\Phi(y) + \frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy \\
+	&= \int_{\mathbb{R}}\left(\Phi(s-y) + \frac{s-y}{n}\right)\eta_{\frac{1}{n}}(y)dy
+\end{align*}
+where $\eta$ is the standard mollifier.
+We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$.
+We also ask that $|u_{0,n}| \leq $min$\{n,u_0\}$.
+
+Apparently, also according to \citep{vazquez2007porous}, we also approximate $f$ by a sequnce of functions $f_n$ that converges to $f$ in $L^p(Q_T)$ for all\footnote{Not sure if \textit{sic}...} $p<\infty$, and is so that $|f_n| \leq f$ for all $n$.
+
+Our first lemma then reads
+\begin{lemma}
+Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$, and $\partial_t f$ are bounded, $\partial \Omega \in C^{2+\alpha}$, and $\Phi$ is locally lipschitz continuous.
+\end{lemma}
+
+\begin{proof}
+
+\begin{description}
+	\item[Setting up an approximate problem:] We fix $T<\infty$ and consider the problem
+		\begin{equation*}
+			\begin{cases}
+			\partial_t u_n &= \Delta\Phi_n(u_n) + f_n, \quad \text{ in } Q_T \\
+			u_n(x,0) &= u_{0,n}(x),	\quad \text{ on } \overline{\Omega} \\
+			u_n(x,t) &= 0, \quad \text{ on }  \partial \Omega \times (0,T).
+			\end{cases}
+		\end{equation*}			
+	By virtue of theorem \ref{thm:classical_existence}, this approximate problem has a unique solution $u_n \in C^{2,1}(\overline{Q}_T)$.
+
+	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, multiply the GPME by $w_n$ and integrate over $Q_T$, which results in
+	\begin{equation*}
+	\iint_{Q_T}w_n\partial_t u_n dxdt = \iint_{Q_T}w_n\Delta w_n dxdt + \iint_{Q_T}f_n w_n dxdt.
+	\end{equation*}
+	Now we do exactly as we did the section on weak energy solutions and do integration by parts on the first term on the right hand side.
+We also notice that $w_n \partial_t u_n = \partial_t \Psi_n(u_n)$.
+Thus,
+	\begin{equation*}
+	\int_\Omega \Psi(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
+	\end{equation*}
+	Considering the second term on the right hand side we have
+	\begin{equation*}
+	\iint_{Q_T}f_n w_n dxdt \leq C\iint_{Q_T}f_n^2 dxdt + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2dxdt,
+	\end{equation*}
+	after exactly the same argument as we did with (\ref{using_Poincare}). After putting it back
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
+	\end{equation*}
+	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
+	\begin{equation*}
+	\iint_{Q_T}f_n^2dxdt \leq \iint_{Q_T} f^2 dxdt,
+	\end{equation*}
+	by our assumption on the approximation. In addition
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx = \int_\Omega \left[ \int_0^{u_{0,n}(x)} \int_\mathbb{R} \left(\Phi(y)+\frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy ds \right] dx,
+	\end{equation*}
+	and $\eta_{\frac{1}{n}}(s-\cdot)$ has support in $[s-\frac{1}{n}, s + \frac{1}{n}]$. Therefore, by the monotonicity of $\Phi$, 
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega \left[ \int_0^{u_{0,n}(x)}\Phi \left(s+\frac{1}{n} \right)ds + \int_0^{u_{0,n}}\frac{s+\frac{1}{n}}{n}ds \right] dx,
+	\end{equation*}
+	which after a variable transformation yields
+	\begin{align*}
+	\int_\Omega \Psi_n(u_{0,n})dx &\leq \int_\Omega \left[ \int_{\frac{1}{n} }^{u_{0,n}(x) + \frac{1}{n} } \Phi(s)ds + \frac{u_{0,n}(x)^2}{2n} + \frac{u_{0,n}(x)}{n^2} \right] dx \\
+	&\leq \int_\Omega \left[ \Psi\left(u_{0,n} +\frac{1}{n}\right) - \Psi\left(\frac{1}{n}\right) + \frac{1}{2n}\left(u_{0,n} + \frac{1}{n}\right)^2 \right] dx.
+	\end{align*}
+	Using now that $|u_{0,n}| \leq u_0$ and that $\Omega$ is a bounded set, we get a bound on this integral independent of $n$. And so $\iint_{Q_T} |\nabla w_n|^2 dxdt$ has a bound independent of $n$.
+\end{description}
+
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \begin{appendices}
@@
 \begin{cor}
+\label{cor:GPME_existence}
 Assume the following conditions are satisfied:
@@
 \end{cor}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{theorem}[Rellich-Kondrachov Compactness Theorem]
+\label{thm:Rellich}
 Assume $U$ is an open, bounded subset of $\mathbb{R}^n$ and $\partial U$ is $C^1$.

### 2014-10-15 stuff_somewhat_organised.tex
Fortsatt møkk.

@@
 	\item[Setting up an approximate problem:] We fix $T<\infty$ and consider the problem
-		\begin{equation*}
+		\begin{equation}
+		\label{approximate_problem}
 			\begin{cases}
@@
 			\end{cases}
-		\end{equation*}			
+		\end{equation}			
 	By virtue of theorem \ref{thm:classical_existence}, this approximate problem has a unique solution $u_n \in C^{2,1}(\overline{Q}_T)$.
@@
 	Using now that $|u_{0,n}| \leq u_0$ and that $\Omega$ is a bounded set, we get a bound on this integral independent of $n$. And so $\iint_{Q_T} |\nabla w_n|^2 dxdt$ has a bound independent of $n$.
+
+	\item[Control of the temporal derivative:] Now we let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 1$.
+If we multiply (\ref{approximate_problem}) by $\zeta \partial_tw_n$ and integrate over $Q_T$ we get
+	\begin{equation}
+	\label{temporal_bound_start}
+	\iint_{Q_T}\zeta \Phi'_n(u_n)|\partial_t u_n|^2 dxdt = \iint_{Q_T} \left\{ \zeta \partial_t w_n \Delta w_n + \zeta \partial_t w_n f_n \right\} dxdt.
+	\end{equation}
+	Let's start by considering the first term on the right hand side. By the product rule for the divergence
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \int_0^T \zeta \int_\Omega \left\{ \nabla \cdot (\partial_t w_n \nabla w_n) - (\partial_t \nabla w_n) \cdot \nabla w_n \right\} dx dt.
+	\end{equation*}
+	So after using the divergence theorem together with the homogeneous boundary data, as well as noticing that $(\partial_t \nabla w_n) \cdot \nabla w_n = \frac{1}{2}\partial_t |\nabla w_n|^2$, we see that
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla w_n|^2 dxdt.
+	\end{equation*}
+	Integrating by parts in the temporal dimension, we end up with
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla w_n|^2 dxdt - \frac{1}{2}\int_\Omega \left\{ |\nabla w_n(T)|^2 - |\nabla w_n(0)|^2 \right\} dx.
+	\end{equation*}
+	A similar inetgration by parts in the temporal dimension of the last term on the right hand side in (\ref{temporal_bound_start}) yields
+	\begin{equation*}
+	\iint_{Q_T} \zeta f_n \partial_t w_n dxdt = -\iint_{Q_T} \partial_t (\zeta f_n) w_n dxdt + \int_\Omega \left\{ f_n(T)w_n(T) - f_n(0)w_n(0) \right \} dx.
+	\end{equation*}
+	For the last term in this integral we can do the same trick as we did previously for the energy estimate.
+We use Cauchy-Schwarz and the inequality $\sqrt{ab} \leq \frac{c^2}{4}a + \frac{1}{c^2}b$.
+Then, after using a Poincaré inequality we can choose $c$ so that the integrals of $|\nabla w_n|^2$ at the temporal endpoints are cancelled.
+In toto we end up with
+	\begin{align*}
+	\iint_{Q_T} \zeta \Phi'_n(u_n) |\partial_t u_n|^2 dxdt &\leq \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
+	&+ \frac{C}{2}\int_\Omega \left\{ f_n^2(T) - f_n^2(0) \right\} dx	\\
+	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
+	&+ C \iint_{Q_T} f_n\partial_t f_n dxdt.
+	\end{align*}
+	Thus, by our assumption that $f$ and $\partial_t f$ are bounded, and our previous energy bound, the left hand side is bounded independent of $n$.
+
+	In particular, we can choose $\zeta = 1$\footnote{Yikes, sorry about the kind of a fortiori argument, those are always a bit of a headache.}, and we get a bound on $\Phi'_n(u_n)|\partial_t u_n|^2$ in $L^1(Q_T)$.
+See now that $|\partial_t w_n	|^2 = \Phi'_n(u_n)^2|\partial_t u_n|^2$.
+And so, beacuse $\Phi'(u)$ is bounded for all $|u| \leq C$, we have that $\Phi'_n(u_n)$ is uniformly bounded, our latest integral bound gives us that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T)$.
+
+	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.
+
+	\item[Convergence of $u_n$:] Recall that we defined $w_n = \Phi_n(u_n)$
 \end{description}

### 2014-10-15 trygve_b_written_assignment2.tex
Blæ

\documentclass[11pt, a4paper]{article}
\usepackage{mathptmx}
\usepackage{mathtools}
\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsthm}
\usepackage{remreset}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\usepackage{lmodern}
\usepackage{setspace}

\begin{document}
\onehalfspacing

\title{Written assignment 2 in SPRÅK3501}
\author{Trygve Bærland}
\maketitle

\section*{Before We Begin}
The following text will try to analyse the IMRaD structure of the paper "Entropy solution theory for fractional degenrate convecion-diffusion equation" by Simone Cifani and Espen Jakobsen, \citep{Cifani}.

\section*{Introduction}
The paper starts off by introducing a new kind of partial differential equation (PDE), containing both a convective- and, more relevant and interesting, an anomalous diffusion term. Although a new type of problem, the paper does a fair job of presenting the natural progression from which this new PDE emerges. For instance the convective term, and in the grander scheme of things, hyperbolic conservation laws as well as diffusion equations, fractional or otherwise, are mentioned and a sufficient amount of references are provided. In addition, some applications are mentioned.

The paper proceeds with a longer discussion of what will follow. Namedropping some heavyweight theorems like Kruzkov's entropy condition and uniqueness of solutions satisfying it. For a reader to some extent familiar with this theory, the strategy of the paper seems at least reasonable.

The introduction section ends with a shorter section-for-section summary of what you're about to read.

\section*{Method}
The material and methods section consists of sections 2, 3 and the first of section 4 in the paper. In section 2 the  definition of weak entropy solutions and some basic estimates and results are provided. In section 3 the more complicated (and beautiful) proof of $L^1$-contraction\footnote{In the most basic sense, means that solutions doesn't blow up as time goes on.} and, as a consequence, uniqueness of solutions are presented. This work is reminiscent of Kruzkov's work, and appreciators of his work will have an easier time following along in this section.

The first part of section 4 introduces the numerical method, the centerpiece of the paper, and follows up with some derivations of its properties. Properties of the nice sort, so that  conditions on convergence can be placed\footnote{A numerical method is usually specified by some grid size. Convergence means that when this grid size goes to zero (from discrete to continuous) we end up with something nice.}.

\section*{Results}
This lays the foundation nicely for the back-end of section 4, where the main result is stated. When convergence is proved and some estimates of numerical solution provided, a compactness theorem is used to guarantee that some subsequence of the numerical converges. The $L^1$-contractivity then ensures that the numerical method converges and in fact converges to a weak entropy condition. This gives existence of a unique solution to the PDE introduced in the paper. Existence is of course paramount if further analysis on this type of PDE should be at all interesting.

\section*{and Discussion}
Here comes the tricky part of alligning the paper with IMRaD structure. The paper seems quite content on letting the main result, beautifully named Theorem 4.7, speak for itself, and so no proper broadening of focus on that front is happening. However, the paper soldiers on in section 5 by discussing a different non-local operator (replacing the fractional diffusion term) and restating some of the minor results in this setting. Thus hinting at potential further work.

In section 6 a connection to another type of PDE, the Hamilton-Jacobi-Bellman equation, is established. I guess this can be viewed as making the main PDE's niche a bit broader, and is so a fitting contribution to a broadening of focus.

The last part of the paper can hardly be said fill any other function than to give the reader some grasp one what a solution should look like. That's no small function to fill, but it doesn't really point in any direction for further research, so may not be a good fit for the discussion segment of the paper.

\section*{Last thoughts}
The above analysis shows a good fit with the IMRaD model. Worth noting is that the method section plays more a role of setting up basic results to be used for the main results, which is kind of in line with theory sections of research papers in more applied fields.

In addition the discussion segment is much more interested in suggesting further work rather than restating the purpose of the paper and what was achieved. It seems to be done this way to let the proofs speak as much as possible for themselves, and not resort to something that may be perceived by the reader as last minute hand-waving. As far as my reading of mathematical papers is concerned, this is not an unusual strategy.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\bibliographystyle{plain}
\bibliography{project_bibliography.bib}
\end{document}

### 2014-10-20 stuff_somewhat_organised.tex
Blæ
Framgang. Endelig!

@@
 
-	\item[Convergence of $u_n$:] Recall that we defined $w_n = \Phi_n(u_n)$
+	\item[Convergence of $u_n$:] Recall that we defined $w_n = \Phi_n(u_n)$. Consider now
+	\begin{equation*}
+	\partial_t (u_{n} - u_{m}) = \Delta (w_{n} - w_{m}) + (f_{n}-f_{m}).
+	\end{equation*}
+	We will now do quite the same as we did when the $L^1$-contracivity for classical solutions: Let $p: \mathbb{R} \to [0,1]$ be a smooth approximation of the heaviside function, and multiply the above equation by $p(w_{n}-w_{m})$.
+Integrating over $\Omega$ and using integration by parts results in
+	\begin{align*}
+	\int_\Omega \partial_t(u_n - u_m)p(w_n-w_m)dx &= -\int_\Omega p'(w_n-w_m)|\nabla(w_n-w_m)|^2dx + \int_\Omega (f_n-f_m)p(w_n-w_m)dx \\
+	&\leq \int_\Omega (f_n-f_m)_+ dx.
+	\end{align*}
+	This last step us justified in that for all $n$ we have $w_n \in H^1(\Omega)$ for  every $t \in [0,T]$.
+Letting $p$ tend towards the heaviside function and integrating over the time interval $[0,t]$ we end up with
+	\begin{equation*}
+	\int_\Omega (u_n - u_m)_+(t) dx \leq \int_\Omega (u_{0,n} - u_{0,m})dx + \int_0^t\int_\Omega (f_n - f_m)_+ dxds,
+	\end{equation*}
+	and as a consequence
+	\begin{equation*}
+	||(u_n - u_m)(t)||_{L^1(\Omega)} \leq ||u_{0,n} - u_{0,m}||_{L^1(\Omega)} + ||f_n-f_m||_{L^1(Q_t)}.
+	\end{equation*}
+	Integrating over time yet again and using that $Q_T$ is bounded we deduce that $\{u_n\}$ is a Cauchy sequence in $L^1(Q_T)$, and hence converges to some $u$ in $L^1$.
+
+	\item[Showing that $w=\Phi(u)$:]
+
 \end{description}

### 2014-10-24 stuff_somewhat_organised.tex
Får vel organisere stuffet litt bedre.

@@
 	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.
+The energy estimate continues to hold in the limit as
+	\begin{equation}
+	\iint_{Q_T}|\nabla w|^2 dxdt \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}fw dxdt
+	\end{equation}
 
@@
 
-	\item[Showing that $w=\Phi(u)$:]
+	\item[Showing that $w=\Phi(u)$:] By the triangle inequality we split $|\Phi(u)-w|$ into
+	\begin{equation*}
+	|\Phi(u) - w| \leq |\Phi(u) - \Phi(u_{n_j})| + |\Phi(u_{n_j}) - \Phi_{n_j}(u_{n_j})| + |w_{n_j}-w|. 
+	\end{equation*}
+	Then, integration over $Q_T$ gives
+	\begin{align*}
+	\iint_{Q_T}|\Phi(u)-w|dxdt &\leq \iint_{Q_T}|\Phi(u)-\Phi(u_{n_j})|dxdt \\
+	&+ \iint_{Q_T}|\Phi(u_{n_j})-\Phi_{n_j}(u_{n_j})|dxdt \\
+	&+ \iint_{Q_T}|w_{n_j} - w|dxdt.
+	\end{align*}
+	The first term can be made arbitrarily small by the $L^1$-convergence of $\{u_n\}$ together with $\Phi$ being locally Lipschitz.
+The last term is controlled by the $L^2$-convergence of $\{w_{n_j}\}$ and that $Q_T$ is bounded.
+So we need to consider the middle term.
+We start off with
+	\begin{align*}
+	|\Phi(u_{n_j}) - \Phi_{n_j}(u_{n_j})| &= \left| \Phi(u_{n_j}) - \int_{\mathbb{R}}\left\{ \Phi(u_{n_j}-y) + \frac{u_{n_j}-y}{n_j} \right\} \eta_{n_j}(y)dy  \right| \\
+	&= \left|\int_\mathbb{R}\left\{\Phi(u_{n_j})-\Phi(u_{n_j}-y)-\frac{u_{n_j}-y}{n_j} \right\} \eta_{n_j}(y)dy \right| \\
+	&\leq \int_\mathbb{R}\left\{ |\Phi(u_{n_j})-\Phi(u_{n_j}-y)|+\frac{|u_{n_j}-y|}{n_j}\right\} \eta_{n_j}(y)dy.
+	\end{align*}
+	Since $\Phi$ is locally Lipschitz we get that for any $\epsilon >0$
+	\begin{align*}
+	|\Phi(u_{n_j}) - \Phi_{n_j}(u_{n_j})| &\leq \int_\mathbb{R}\left\{ L_{\Phi}|y|+\frac{|u_{n_j}-y|}{n_j}\right\} \eta_{n_j}(y)dy \\
+	&< L_{\Phi}\epsilon + \frac{|u_{n_j}|}{n_j}+\epsilon
+	\end{align*}
+	for sufficiently large $n_j$. Here $L_\Phi$ is a Lipschitz constant for $\Phi$. Thus, we can make the bounds on all three terms arbitrarily small, and we are forced to conclude that 
+	\begin{equation}
+	\iint_{Q_T}|\Phi(u)-w|dxdt = 0,
+	\end{equation}	 
+	which means that $\Phi(u) = w$ a.e.
 
+	\item[$u$ is a weak solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}(\Omega))$\footnote{Actually, this may not be as easy to see as I've stated here.
+Need to use yet another estimate to show this.}.
+So what's left is to show that
+	\begin{equation*}
+	\iint_{Q_T}\left\{ \nabla\Phi(u) \cdot \nabla \eta - u\partial_t \eta - f\eta \right\}dxdt - \int_\Omega u_0\eta\big|_{t=0}dx = 0
+	\end{equation*}
+	for any $\eta \in C^1(\overline{Q}_T)$ that vanish on $\partial \Omega \times [0,T)$ and for $t=T$.
 \end{description}

### 2014-10-27 draft_project.tex
Begynt å skrive på utkast da veit du.

\documentclass[11pt, a4paper]{article}
\usepackage{mathptmx}
\usepackage{mathtools}
\usepackage{amssymb}
%\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsthm}
\usepackage{remreset}
\usepackage[utf8x]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage[numbers]{natbib}

\usepackage{lmodern}

\begin{document}
\title{Draft for project}
\author{Trygve Bærland}
\maketitle
\abstract{For now, heavily reliant on \citep{vazquez2007porous}.}

% My text categories:
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{cor}{Corollary}[section]
\newtheorem{lemma}{Lemma}[section]

\theoremstyle{definition}
\newtheorem{mydef}{Definition}[section]
\newtheorem{example}{Example}[section]

%\theoremstyle{plain}
\newtheorem{obs}{Observation}
\newtheorem{rem}{Remark}

% Reset numbering for each section
\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Let $\Omega \subset \mathbb{R}^d$ be an open, bounded, and simply connected domain. Then the filtration, or general porous medium equation is

\begin{equation}
\label{GPME}
	\partial_t u = \Delta \Phi(u) + f,
\end{equation}

 where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. For now we assume that $\Phi$ is continuous and nondecreasing.

\subsection{Problem statement}
I will consider on the following Dirichlet problem:
\begin{equation}
\label{HDP}
	\begin{cases}
		\partial_t u = \Delta \Phi(u) + f, \quad \text{ in } Q_T \\
		u(x,0) = u_0(x), \quad \text{ in } \Omega \\
		u(x,t) = 0, \quad \text{ on } \partial\Omega \times [0,T].
	\end{cases}
\end{equation}
Here $Q_T = \Omega \times (0,T]$, where $T$ may very well be infinite. Furthermore we denote by $\Gamma_T = \overline{Q}_T\backslash Q_T$ the parabolic boundary.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				CLASSICAL SOLUTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Classical solutions}
In this section it is helpful to reformulate (\ref{HDP}) as 
\begin{equation}
	\begin{cases}
		\partial_t u + Lu &= f, \quad \text{in } Q_T \\
		u(x,0) &= u_0(x), \quad \text{in } \Omega \\
		u &= 0, \quad \text{on } \partial \Omega \times [0,T]
	\end{cases}
\end{equation}
where $L$ is a differential operator that can be written in the divergence form
\begin{equation}
Lu = -\sum_{i=1}^d \partial_{x_i}(a^i(x,t,u,\nabla u)) + a(x,t,u,\nabla u).
\end{equation}

The reason for this reformulation is that many of the results presented in this section supposes a particular condition on the coefficients $a^i(x,t,u,p)$. The condition is that there are constants $0 < \nu < \mu < \infty $ so that
\begin{equation}
\label{uniform_parabolicity}
\nu |\xi|^2 \leq \sum_{i,j=1}^d \frac{\partial a^i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu |\xi|^2 
\end{equation}
for every $\xi \in \mathbb{R}^d$. If this condition is satisfied we say that the operator $\partial_t + L$ is \textbf{uniformly parabolic}.

In our setting it's easy enough to check that
\begin{equation*}
a^i(x,t,u,p) = \Phi'(u)p_i,
\end{equation*}
and so (\ref{uniform_parabolicity}) translates to
\begin{equation}
\label{uniform_parabGPME}
\nu \leq \Phi'(u) \leq \mu.
\end{equation}
We will in this section assume this to be true. I.e. that $\Phi'(u)$ is bounded and strictly positive.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%			MAXIMUM PRINCIPLE:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Maximum principle}
The first main estimate we'll deal with is a $L^\infty$ bound on a classical solution. To that end, the following strong maximum principle will be helpful (cf. \citep[p. 396]{evans}).

\begin{theorem}[Strong maximum principle]
\begin{enumerate}[i)]
	Suppose $\Omega$ is connected, and $u\in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$, then:
	\item If
	\begin{equation*}
		\partial_tu + Lu \leq 0, \quad \text{ in } Q_T, 
	\end{equation*}
	and $u$ attains its maximum over $\overline{Q}_T$ at point $(x_0,t_0)\in Q_T$, then
	$u$ is constant on $Q_{t_0}$.

	\item Analagously, if
	\begin{equation*}
		\partial_tu + Lu \geq 0, \quad \text{ in } Q_T, 
	\end{equation*}
	and $u$ attains its minimum over $\overline{Q}_T$ at a points  $(x_0,t_0) \in Q_T$, then $u$ is constant on $Q_{t_0}$.
\end{enumerate}
\end{theorem}

Using this theorem we can prove the comparison principle:
\begin{lemma}[Comparison principle]
\label{lemma:comparison}
Let $u,v \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two solutions of (\ref{HDP}) with initial data $u_0$, $v_0$ and loading $f$, $\tilde{f}$ respectively. Further, assume that $v_0 \geq u_0$ in $\Omega$ and  $\tilde{f} \geq f$ in $Q_T$. Then either $u < v$ in $Q_T$ or $u=v$.
\end{lemma}
\begin{proof}
We set $w=v-u$ and see that $w$ then solves
\begin{align*}
\partial_t w &= \Delta(\Phi(v) - \Phi(u)) + (\tilde{f}-f) \\
			&= \Delta(\Phi(w+u) - \Phi(v-w)) + (\tilde{f}-f).  
\end{align*}
and $w(x,0) = v_0(x) - u_0(x)$ as well as satisfies the homogeneous Dirichlet boundary condition. We need to check that the problem satisfies (\ref{uniform_parabolicity}), and to that end we notice that
\begin{equation*}
\Delta(\Phi(w+u) - \Phi(v-w)) = \nabla \cdot \left(\Phi'(w+u)(\nabla w + \nabla u) - \Phi'(v-w)(\nabla v - \nabla w) \right).
\end{equation*}
Treating $u$ and $v$ as given parameters of the IVBP we get
\begin{equation*}
a^i = (\Phi'(w+u) + \Phi'(v-w))\partial_{x_i}w,
\end{equation*}
and since (\ref{uniform_parabGPME}) is satisfied the problem is uniformly parabolic.
We have
\begin{equation*}
\partial_tw - \Delta(\Phi(w+u) - \Phi(v-w)) = \tilde{f}-f \geq 0 
\end{equation*}
and we can use the second part of the strong maximum principle to deduce that
\begin{equation*}
w \geq \underset{\overline{Q_T}}{\mathrm{min}}w = \underset{\Gamma_T}{\mathrm{min}}w.
\end{equation*}
By the initial- and boundary data of $w$ we see that
\begin{equation*}
\underset{\Gamma_T}{\mathrm{min}}w = 0,
\end{equation*}
and so
\begin{equation*}
w \geq 0 \quad \Rightarrow  \quad v \geq u.
\end{equation*}

We conclude the proof by seeing that if $u=v$ at some points in $Q_T$ the strong maximum principle implies that $u=v$ everywhere. 
\end{proof}

\setcounter{rem}{0}
\begin{rem}
We could improve somewhat on this result by having $v \geq u$ on $\partial \Omega \times [0,T]$. All the steps in the proof works, in particular
\begin{equation*}
\underset{\Gamma_T}{\mathrm{min}}w \geq 0
\end{equation*} 
still holds.
\end{rem}

Let's now use this lemma to get an $L^\infty$-bound on classical solutions.
\begin{lemma}
If $u \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ is a solution of (\ref{HDP}), and $u_0$ is bounded in $\Omega$ and $f$ bounded in $Q_T$, then
	\begin{equation}
		\label{infinity_bound}
		||u||_{L^\infty(Q_T)} \leq ||u_0||_{L^\infty(\Omega)} + T||f||_{L^\infty(Q_T)}.
	\end{equation}
\end{lemma}

\begin{proof}
We start by defnining $M_1 = \mathrm{max}\{0, \mathrm{sup}_\Omega(u_0) \}$, and $N_1 = \mathrm{max}\{0, \mathrm{sup}_{Q_T}(f) \}$. With $v(x,t) = M_1 + N_1t$, it solves
\begin{equation*}
\begin{cases}
	\partial_t v &= \Delta\Phi(v) +N_1 \quad \text{in } Q_T\\
	v(x,0) &= M_1 \quad \text{in } \Omega \\
	v(x,t) &= M_1 + N_1t \quad \text{on } \partial \Omega \times [0,T].
\end{cases}
\end{equation*}
Since $u_0 \leq M_1$ and $f\leq N_1$ we can use the comparison principle to conclude that
\begin{equation*}
u(x,t) \leq M_1 + N_1t
\end{equation*}
in $Q_T$.

Similarly we define $M_2 = \mathrm{min}\{ 0, \mathrm{inf}_\Omega(u_0) \}$, and $N_2 = \mathrm{min}\{ 0, \mathrm{inf}_{Q_T}(f) \}$, to get the lower bound
\begin{equation*}
u(x,t) \geq M_2 + N_2t.
\end{equation*}

Because
\begin{equation*}
||u_0||_{L^\infty(\Omega)} = \mathrm{max}\{ \mathrm{sup}_\Omega(u_0), -\mathrm{inf}_\Omega (u_0)\} = \mathrm{max}\{|M_1|,|M_2|\},
\end{equation*}
and similarly for $f$, our two bounds implies that
\begin{equation*}
|u(x,t)| \leq ||u_0||_{L^\infty(\Omega)} + t||f||_{L^\infty(Q_T)},
\end{equation*}
which  is what we wanted to prove.

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				L^1-CONTRACTIVITY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$L^1$-contractivity}
In this section we let $u,\hat{u} \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two smooth solutions of the homogeneous Dirichlet problem (\ref{HDP}) with initial data $u_0$, $\hat{u}_0$ and loading $f$, $\hat{f}$ respectively. To reach our goal of deriving stability of solutions in $L^1$ we start off with the following lemma, from which the main result will be an almost immediate consequence.

\begin{lemma}
For $\tau, t \in [0,T]$ the inequality 
\begin{equation}
\label{l1_contr_part1}
\int_{\Omega}(u(t)-\hat{u}(t))_+dx \leq \int_{\Omega}(u(\tau)-\hat{u}(\tau))_+dx + \int_\tau^t\int_{\Omega}(f-\hat{f})_+dxdt.
\end{equation}
is satisfied.
\end{lemma}

\begin{proof}
Let $p: \mathbb{R} \to \mathbb{R}$ be a $C^1$ function satisfying $p(s) = 0$ for $s \leq 0$, $p'(s) \geq 0$ for all $s\in \mathbb{R}$, and $0 \leq p(s) \leq 1$ for $s > 0$. Define now $w = \Phi(u) - \Phi(\hat{u})$, and multiply $p(w)$ with the difference of (\ref{GPME}) for $u$ and $\hat{u}$ to get
\begin{equation*}
\partial_t(u-\hat{u})p(w) = p(w)\Delta w + p(w)f.
\end{equation*}
Integrating over $\Omega$, and using integration by parts on the first part on the right hand side yields
\begin{align*}
\int_{\Omega}\partial_t(u-\hat{u})p(w)dx &= -\int_{\Omega}p'(w)|\nabla w|^2dx + \int_{\Omega}p(w)(f-\hat{f}) dx \\
	&\leq \int_{\Omega}p(w)(f-\hat{f}) dx \\
	&\leq \int_{\Omega}(f-\hat{f})_+ dx,
\end{align*}
where the last step follows from the fact that $0 \leq p(w) \leq 1$. Here $(\cdot)_+ = \mathrm{max}\{\cdot, 0\}$.
Now, let $p$ converge to the Heaviside function $H(w)$. Then, it is worth noticing that $H(w) = H(u-\hat{u})$, because of the strict monotonicity of $\Phi$. Also see that $\partial_t(u-\hat{u})_+ = \partial_t(u-\hat{u})H(u-\hat{u})$. Thus
\begin{equation*}
\partial_t \int_{\Omega}(u-\hat{u})_+dx \leq \int_{\Omega}(f-\hat{f})_+ dx,
\end{equation*}
and integrating in time from $\tau$ to $t$ yields
\begin{equation*}
\int_{\Omega}(u(t)-\hat{u}(t))_+dx \leq \int_{\Omega}(u(\tau)-\hat{u}(\tau))_+dx + \int_\tau^t\int_{\Omega}(f-\hat{f})_+dxdt.
\end{equation*}
\end{proof}

\begin{cor}[$L^1$-contractivity]
For two smooth solutions, $u$ and $\hat{u}$ of the homoegenous Dirichlet problem (\ref{HDP}) with different initial data and loading, the $L^1$-estimate
\begin{equation}
\label{l1_contractivity}
||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||f-\hat{f}||_{L^1(Q_t)}
\end{equation}
holds for every $t\in [0,T]$.
\end{cor}

\begin{proof}
Setting $\tau = 0$ we have from the previous lemma that
\begin{equation*}
\int_\Omega  (u(t)-\hat{u}(t))_+dx \leq \int_\Omega (u_0 - \hat{u}_0)_+dx + \int_0^t \int_\Omega (f-\hat{f})_+ dxdt,
\end{equation*}
and by interchanging $u$ and $\hat{u}$ we also have 
\begin{equation*}
\int_\Omega  (\hat{u}(t)-u(t))_+dx \leq \int_\Omega (\hat{u}_0 - u_0)_+dx + \int_0^t \int_\Omega (\hat{f}-f)_+ dxdt.
\end{equation*}

Since $|a| = (a)_+ + (-a)_+$, the sum of these inequalities yields the desired result.
\end{proof}

\setcounter{obs}{0}
\begin{obs}

\end{obs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				WEAK SOLUTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Weak solutions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{plainnat}
\bibliography{project_bibliography.bib}
\end{document}

### 2014-10-27 draft_project.tex
Fått organisert det meste ganske fint.

@@
 \begin{obs}
+From this corollary, we get out immediately that (\ref{HDP}) has at most one solution in $C^{2,1}(Q_T)\cap C(\overline{Q}_T)$.
+\end{obs}
 
+\subsection{Control of the spatial derivative}
+This bound follows nicely the $L^1$-contractivity in that its derivation hinges on a clever choice of function to multiply (\ref{GPME}) with.
+The bound on the spatial derivative is summarised in the following lemma.
+
+\begin{lemma}
+For a solution $u\in C^{2,1}(Q_T) \cap C(\overline{Q}_T)$ of (\ref{HDP})
+\begin{equation}
+\label{spatial_derivative_bound}
+\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+We start off by multiplying (\ref{GPME}) with $\Phi(u)$ to get
+\begin{equation*}
+\Phi(u)\partial_t u = \Phi(u)\Delta \Phi(u) + \Phi(u)f,
+\end{equation*}
+and we notice that $\Phi(u)\partial_t u = \partial_t \Psi(u)$. That means when we integrate over $Q_T$ we have
+\begin{equation*}
+\iint_{Q_T} \partial_t \Psi(u)dxdt = \int_\Omega \Psi(u(T))dx - \int_\Omega \Psi(u_0)dx.
+\end{equation*}
+On the diffusive term we can use integration by parts, so
+\begin{equation*}
+\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_0^T \int_{\partial\Omega} \Phi(u)\nabla \Phi(u) \cdot \hat{n}dS,
+\end{equation*}
+where $\hat{n}$ is the outward unit normal. By the Dirichlet condition
+\begin{equation*}
+\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt,
+\end{equation*}
+and notice that this step would have been valid for homogeneous Neumann condition as well. In toto 
+\begin{equation*}
+\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt.
+\end{equation*}
+\end{proof}
+\setcounter{obs}{0}
+
+\begin{obs}
+We can go even further and deal with the last term on the right hand side: Assuming $f,\Phi(u) \in L^2(Q_T)$, then
+\begin{equation*}
+\iint_{Q_T} f\Phi(u)dxdt \leq \left(\iint_{Q_T} f^2 dxdt\right)^\frac{1}{2}\left(\iint_{Q_T} \Phi(u)^2 dxdt\right)^\frac{1}{2},
+\end{equation*}
+by Cauchy-Schwarz'. With the inequality $\sqrt{ab} \leq \frac{1}{4c}a + cb$ for $c>0$
+\begin{equation*}
+\iint_{Q_T} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\iint_{Q_T}\Phi(u)^2dxdt.
+\end{equation*}
+Lastly, because of the homogeneous Dirichlet conditions, we use the Poincaré inequality and set $c$ so that
+\begin{equation}
+\label{using_Poincare}
+\iint_{Q_T} f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt,
+\end{equation}
+and the final inequality becomes
+\begin{equation}
+\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
+\end{equation}
 \end{obs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				EXISTENCE:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Existence}
+Now we move on to tackle one of the central questions with regards to the well-posedness of (\ref{HDP}), viz.
+existence, and in particular what sort of assumptions we need to put on $u_0$, $f$ and $\Phi$ to be guaranteed that a solution exists.
+
+We will make good use of an admittedly quite harrowing theorem presented in \citep{ladyzhenskaya}.
+This theorem is quite general in its formulation and our job here will mainly be to translate all the conditions to the general porous medium equation, but before delving into this mammoth, let's set the stage, and introduce some notation used by Ladyzhenskaya et.
+al.
+
+\subsubsection{Preliminaries}
+
+As in the section on the maximum principle it will be useful to recast our PDE to the form
+\begin{equation}
+\label{lady_parabolic_eq}
+	u_t - \sum_{i=1}^d\frac{d}{dx_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
+\end{equation}
+in $Q_T$. In addition we formulate the initial value and boundary as
+\begin{equation}
+\label{lady_bc}
+	u\big|_{\Gamma_T} = \psi\big|_{\Gamma_T}
+\end{equation}
+for some known function $\psi$.
+
+Furthermore, we define
+\begin{equation*}
+A(x,t,u,\nabla u) = a(x,t,u,\nabla u) - \sum_{i=1}^d \left[ \frac{\partial a_i(x,t,u,\nabla u)}{\partial u} + \frac{\partial a_i(x,t,u,\nabla u)}{\partial x_i} \right]
+\end{equation*}
+
+By the function space $H^{l, l/2}$, we mean the Banach space of functions $u$ that are continuous in $\bar{Q}_T$.
+So are all partial derivatives of the form $\partial_t^r D^\alpha u$, with $2r+|\alpha| <l$.
+The norm is given as
+\begin{equation*}
+	|u|_{Q_T}^{(l)} = \langle u \rangle^{(l)}_{Q_T} + \sum_{j=0}^{[l]}\langle u \rangle^{(j)}_{Q_T},
+\end{equation*}
+with
+\begin{align*}
+\langle u \rangle^{(j)}_{Q_T} &= \sum_{2r+|\alpha|=j} ||\partial_t^r D^\alpha u||_{C(\bar{Q}_T)} \\
+\langle u \rangle^{(l)}_{Q_T} &= \langle u \rangle^{(l)}_{x,Q_T} + \langle u \rangle^{(l/2)}_{t,Q_T} \\
+\langle u \rangle^{(l)}_{x,Q_T} &= \sum_{2r+|\alpha|=[l]} |\partial_t^r D^{\alpha}u|_{C^{0,l-[l]}(\bar{Q}_T)} \\
+ \langle u \rangle^{(l/2)}_{t,Q_T} &= \sum_{0 < l - 2r -\alpha < 2} |\partial_t^r D^\alpha u|_{C^{0,(l-2r-s)/2}(\bar{Q}_T)},
+\end{align*}
+with the Hölder semi-norm with respect to $x$ and $t$ respectively in the last two definitions.
+
+\begin{rem}
+
+\end{rem}
+
+\subsubsection{The big, general existence theorem}
+We should now will at least partly prepared for the big existence theorem. It is presented immediately below, almost verbatim from \citep[ Theorem 6.1, p. 452]{ladyzhenskaya}.
+
+\begin{theorem}[Existence of classical solutions]
+\label{thm:classical_existence}
+Suppose that the following conditions hold.
+\begin{enumerate}[a)]
+	\item For $(x,t) \in \overline{Q}_T$ 
+	\begin{equation}
+		\label{exist_cond1}
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \Bigg|_{p=0} \geq 0, \quad A(x,t,u,0)u \geq -b_1 u^2 - b2
+	\end{equation}
+	 holds for arbitrary $u$ and $\xi = (\xi_1, \xi_2, \ldots, \xi_d)$.
+
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and arbitrary $p$ the functions $a_i(x,t,u,p)$ and $a(x,t,u,p)$ are continuous, the $a_i(x,t,u,p)$ are differentiable with respect to $x$, $u$ and $p$ and the following inequalities are satisfied
+	\begin{equation}
+	\label{exist_cond3}
+		\begin{cases}
+			\nu\xi^2 \leq \sum_{i,j=1}^d\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2 \\
+			\sum_{i=1}^d \left(|a_i| + |\frac{\partial a_i}{\partial u}|\right)(1+|p|) + \sum_{i,j=1}^d |\frac{\partial a_i}{\partial x_j}| + |a| \leq \mu (1 + |p|)^2. 		
+		\end{cases}
+	\end{equation}
+	where $\nu$ and $\mu$ are positive numbers.
+
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a Hölder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
+
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$ the function $a(x,t,u,p)$ has the partial derivatives $\frac{\partial a}{\partial p_j}$ and $\frac{\partial a}{\partial u}$ and the functions $a_i$ and $a$ satisfy
+	\begin{equation}
+	\label{exist_cond4}
+	\begin{split}
+		&\Bigg| \frac{\partial a_i(x,t,u,p)}{\partial u}, \frac{a_i(x,t+h,u,p) - 		a_i(x,t,u,p)}{h}, \\
+		&\frac{\partial a}{\partial p}, \frac{\partial a}{\partial u}, \frac{a(x,t+h,u,p) - a(x,t,u,p)}{h} \Bigg| \leq \varphi(x,t).
+	\end{split}.
+	\end{equation}
+	Here $\varphi$ is required to satisfy
+	\begin{equation*}
+	\left( \int_0^T \left(\int_\Omega |\varphi(x,t)|^q dx\right)^\frac{r}{q} dt 			\right)^\frac{1}{r} < \infty,
+	\end{equation*}
+	i.e. $\varphi \in L^r(0,T: L^q(\Omega))$, where $q$ and $r$ satisfy
+	\begin{equation*}
+	\frac{1}{r} + \frac{d}{2q} = 1 - x_1
+	\end{equation*}
+	and
+	\begin{equation*}
+	\begin{cases}
+		q\in \left[\frac{d}{2(1-x_1)},\infty\right], &r\in \left[\frac{1}{1-x_1},\infty \right], 0<x_1<1, \quad \text{ for } d \geq 2 \\
+		q \in [1, \infty], &r \in \left[\frac{1}{1-x_1},\frac{2}{1-2x_1}\right], 0<x_1<\frac{1}{2}, \quad \text{ for } n=1
+	\end{cases}
+\end{equation*}
+
+	\item $\psi(x,t) \in H^{2+\beta, 1+\beta/2}(\overline{Q}_T)$ and satisfy
+	\begin{equation}
+	\label{exist_cond5}
+	\psi_t - \frac{d}{dx_i}a_i(x,t,\psi,\psi_x) + a(x,t,\psi,\psi_x) = 0.
+	\end{equation}
+	on $\partial \Omega \times \{t=0\}$.
+
+	\item $\partial \Omega \in C^{2+\beta}$\footnote{I can't seem to find a definition of this sort of boundary in \citep{ladyzhenskaya}.
+However, \citep{evans} has something vaguely familiar, but here integer values of the exponent is assumed.}.
+\end{enumerate}
+
+Under these conditions there exists a unique solution of problem (\ref{lady_parabolic_eq})  with boundary condition (\ref{lady_bc}) from the class $H^{2+\beta, 1+\beta/2}(\overline{Q}_T)$.
+Moreover, this solution has derivatives $u_{xt}$ from $L^2(\overline{Q}_T)$.
+\end{theorem}
+
+\subsubsection{From general to specific: Existence for the GPME}
+The general porous medium equation we are concerned with can be written
+\begin{equation*}
+u_t - \nabla \cdot (\nabla \Phi(u) ) - f(x,t) = 0,
+\end{equation*}
+which is of the form (\ref{lady_parabolic_eq}) with
+\begin{equation}
+a_i(x,t,u,\nabla u) = \Phi'(u) u_{x_i}, \quad a(x,t,u,\nabla u) = -f(x,t).
+\end{equation}
+
+Let's go trhough each condition in theorem \ref{thm:classical_existence} to see what assumptions we must make to have a classical solution.
+
+\begin{enumerate}[a)]
+	\item We consider fullfilling (\ref{exist_cond1}). We have
+	\begin{equation*}
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j} = \delta_{ij} \Phi'(u),
+	\end{equation*}
+	and so, since $\Phi'(u) \geq 0$ is assumed,
+	\begin{equation*}
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j}\Bigg|_{p=0}\xi_i\xi_j = \Phi'(u)\xi_i^2 \geq 0.
+	\end{equation*}
+
+	In the general porous medium equation
+	\begin{equation*}
+		A(x,t,u,p) = -f(x,t) - \sum_{i=1}^d \Phi''(u)p_i,
+	\end{equation*}
+	which means $A(x,t,u,0) = -f(x,t)$ (Also see that we need $\Phi \in C^2(\mathbb{R})$). Thus, according to (\ref{exist_cond1}) we need constants $b_1$ and $b_2$ so that
+	\begin{equation*}
+		f(x,t)u \leq b_1 u^2 + b_2.
+	\end{equation*}
+	We are able to choose $b_1$ and $b_2$ if, for example, $f(x,t)$ is bounded in $\overline{Q}_T$.
+
+	\item We need $a_i(x,t,u,p)$ and $a(x,t,u,p)$ to be continuous.
+This translates to requiring that $\Phi'(u)$ and $f(x,t)$ are continuous.
+In addition $a_i(x,t,u,p)$ needs to be differentiable with respect to $x$, $t$, $u$ and $p$, which in our case means that $\Phi''(u)$ needs to be continuous.
+
+	Considering the first inequality in (\ref{exist_cond3}) we have
+	\begin{equation*}
+		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2.
+	\end{equation*}
+	Assuming that $\Phi'(u)$ is strictly positive and continuous for $|u|\leq M$ we can set
+	\begin{equation}
+	0 < \nu = \text{inf}_{|u| \leq M}\Phi'(u) < \text{sup}_{|u| \leq M}\Phi'(u) \leq \mu.
+	\end{equation}
+
+	After establishing that
+	\begin{equation*}
+		\begin{cases}
+			a_i(x,t,u,p) &= \Phi'(u)p_i \\
+			\frac{\partial a_i(x,t,u,p)}{\partial u} &= \Phi''(u)p_i \\
+			\frac{\partial a_i(x,t,u,p)}{\partial x_j} &= 0,
+		\end{cases}	
+	\end{equation*}
+	we put it into the left hand side of the second inequality of (\ref{exist_cond3}) as
+	\begin{align*}
+	&\sum_{i=1}^d\left( |a_i| + \left| \frac{\partial a_i}{\partial u}\right| \right)(1+|p|) + \sum_{i,j}^d\left| \frac{\partial a_i}{\partial x_j} \right| + |a| \\
+	&= \sum_{i=1}^d\left( |\Phi'(u)| + |\Phi''(u)| \right)|p_i|(1+|p|) + |f(x,t)| \\
+	&= (|\Phi'(u)| + |\Phi''(u)|)(1+|p|)\sum_{i=1}^d|p_i| + |f(x,t)|.
+	\end{align*}
+	By the equivalence of $l_p$-norms in finite dimensions $\sum_i |p_i| \leq C|p|$. Furthermore, we assume $\Phi''(u)$ to be continuous for $|u|\leq M$, then
+	\begin{equation*}
+	(|\Phi'(u)| + |\Phi''(u)|)(1+|p|)\sum_{i=1}^d|p_i| + |f(x,t)| \leq K(|p| + |p|^2) + |f(x,t)|,
+	\end{equation*}
+	where $K = C\cdot \text{sup}_{|u|\leq M}(|\Phi'(u)| + |\Phi''(u)|)$. Now we are almost done. All that remains is noticing that
+	\begin{align*}
+	K(|p| + |p|^2) + |f(x,t)| &\leq K(|p| + |p|^2) + ||f||_{\infty}(1+|p|) \\
+	&\leq \text{max}\{ K, ||f||_\infty \} (1+|p|)^2.
+	\end{align*}
+	So we can set $\mu = \text{max}\{K, ||f||_\infty, \text{sup}_{|u|\leq M}\Phi'(u) \}$, and both inequalities in (\ref{exist_cond3}) are satisfied.
+
+	\item To reiterate, we need the functions
+	\begin{equation*}
+		\begin{cases}
+			a_i(x,t,u,p) &= \Phi'(u)p_i \\
+			a(x,t,u,p) &= -f(x,t) \\
+			\frac{\partial a_i(x,t,u,p)}{\partial p_j} &= \delta_{ij}\Phi'(u) \\
+			\frac{\partial a_i(x,t,u,p)}{\partial u} &= \Phi''(u)p_i \\
+			\frac{\partial a_i(x,t,u,p)}{\partial x_j} &= 0
+		\end{cases}
+	\end{equation*}
+	to be Hölder continuous in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
+If we choose $\beta = 1$ (i.e.
+Lipschitz continuous for all variables except $t$) the only additional assumption we need to make on $\Phi$ is that $\Phi^{(3)}(u)$ is bounded for $|u| \leq M$, which means that $\Phi \in W^{3,\infty}(\mathbb{R})$.
+The additional assumptions we need to make on $f$ is that it needs to be Lipschitz continuous with respect to $x$ and that
+	\begin{equation*}
+	|f(x,t) - f(x,s)| \leq C|t-s|^\frac{1}{2}
+	\end{equation*}
+	for some constant $C$.
+Note that for bounded domains, Lipschitz continuity implies Hölder continuity with lower exponent.
+So we could make the kind of a fortiori assumption that $f$ is Lipschitz continuous with respect to time.
+Or even that $f_t(x,t)$ is bounded.
+
+	\item For this condition we see that it seems even more natural to impose that $f$ is Lipschitz continuous in $t$, and that the domain is bounded.
+I.e.
+that $T<\infty$ and $\Omega$ is bounded.
+Then all the previous assumptions we've made on $\Phi$ and $f$ will ensure that this condition holds.
+
+	\item We of course have
+	\begin{equation*}
+		\begin{cases}
+		\Psi(x,t) &= 0, \quad (x,t) \in \partial \Omega \times [0,T] \\
+		\Psi(x,0) &= u_0(x), \quad x\in \Omega 
+		\end{cases}
+	\end{equation*}
+	and so this condition isn't too hard to handle\footnote{I think...}.
+First off, we should require that $u_0$ vanish at the boundary, and that it is sufficiently smooth.
+To be more precise, $u_0$, $u'_0$ and $u''_0$ are all continuous and are zero at the boundary.
+The condition (\ref{exist_cond5}) holds trivially, because  $\Psi\big|_{\partial \Omega \times \{t=0\}} = 0$.
+
+	\item In this condition we can do nothing more than assume sufficient smoothness of the boundary.
+\end{enumerate}
+
+It seems only appropriate that we summarise this somehow. A nice little corollary tailored for our purposes is just what we need now.
+
+\begin{cor}
+\label{cor:GPME_existence}
+Assume the following conditions are satisfied:
+	\begin{enumerate}[a)]
+		\item 	$\Phi: \mathbb{R} \to \mathbb{R}$ is in $C^2(\mathbb{R})$, strictly increasing, and $\Phi$, $\Phi'$ and $\Phi''$ are all Lipschitz continuous.
+
+		\item $f = f(x,t)$ is $C^1(Q_T)$, bounded and Lipschitz in both its variables.
+
+		\item $u_0$ is in $C^2_c(\Omega)$; $u_0$ and its derivatives vanish near the boundary $\partial \Omega$.
+
+		\item $\partial \Omega$ is $C^{2+\beta}$-smooth.
+
+	\end{enumerate}
+Then (\ref{HDP}) has a unique solution $u\in C^{2,1}(\bar{Q}_T)$ for $T<\infty$. Moreover, this solution has derivatives $u_{xt}$ in $L^2(Q_T)$.
+\end{cor}
+
+We see that when these assumptions are fulfilled, the homogeneous Dirichlet problem is well posed, since uniqueness and stability are ensured by $L^1$-contractivity.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Weak solutions}
+In the previous sections we saw what assumptions needs to be made for the homogeneous Dirichlet problem to be well posed.
+Allthough a very nice result, the assumptions on the data are far too strict.
+Especially degenerate problems, where $\Phi$ is only increasing and not stricly so, are not valid for this existence result.
+In addition the assumptions on smoothness are often violated in applications.
+This heuristic will now lead us into a discussion of weak solutions, a more general sense of solution.
 
+In this section we will aim to prove well-posedness of weak solutions, and what sort of assumptions we'll need to put on the data to ensure it, well-posedness that is.
+Again, this follows \citep[Ch.
+5]{vazquez2007porous} quite closely.
+However, the proofs are worked out in greater detail than presented there, and we will not assume that $\Phi$ is strictly increasing, but rather try to handle the degenerate case.
+
+Let's just jump off with the definition of weak solutions that we will be using in this text.
+\begin{mydef}[Weak solutions]
+A locally integrable function $u$ defined in $Q_T$ is said to be a \textbf{weak solution} of (\ref{HDP}) if
+\begin{enumerate}[i)]
+	\item $u \in L^1(Q_T)$ and $\Phi(u) \in L^1(0,T : W_0^{1,1}(\Omega))$\footnote{$f:\Omega \to \mathbb{R}$ is an element of $W^{k,p}(\Omega)$ if all weak derivatives with $|\alpha| \leq k$ exists and are in $L^p(\Omega)$.
+$W_0^{k,p}$ is the closure of $C^\infty_c(\Omega)$ in $W^{k,p}(\Omega)$.};
+	\item $u$ satisfies
+		\begin{equation}
+		\label{weak}
+		\iint_{Q_T} \{\nabla\Phi(u)\cdot \nabla\eta - u\partial_t \eta \}dxdt = \int_\Omega u_0(x)\eta(x,0)dx + \iint_{Q_T}f\eta dxdt
+		\end{equation}
+for any $\eta \in C^1(\overline{Q}_T)$ that vanishes on $\partial \Omega \times [0,T)$ and for $t=T$.
+\end{enumerate}
+\end{mydef}
+
+\setcounter{obs}{0}
+\begin{obs}
+With $u_0 \in L^1(\Omega)$ and $f\in L^1(Q_T)$, all the integrals in (\ref{weak}) make sense.
+\end{obs}
+\begin{obs}
+Classical solutions are also weak solutions.
+This is fairly straight forward to see.
+Let $u$ be a smooth solutions and multiply (\ref{GPME}) with a test function $\eta$.
+Then, when integrating over $Q_T$
+\begin{equation*}
+\iint_{Q_T}\partial_t u \eta dxdt = \iint_{Q_T}\Delta\Phi(u) \eta + f\eta dxdt.
+\end{equation*}
+Using integration by parts in time on the left hand side and in space on the first term on the right hand side yields
+\begin{equation*}
+\int_\Omega u\eta dx \Bigg|_{t=0}^T - \iint_{Q_T}u\partial_t \eta dxdt = -\iint_{Q_T}\nabla \Phi(u) \cdot \nabla \eta dxdt + \iint_{Q_T}f\eta dxdt,
+\end{equation*}
+and now all that remains is rearranging the terms to get (\ref{weak}).
+\end{obs}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				UNIQUENESS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Uniqueness}
+
+\begin{theorem}[Uniqueness]
+	Assuming in addition that $u \in L^2(Q_T)$ and $\Phi(u) \in L^2(0,T : H_0^1(\Omega))$, (\ref{HDP}) has at most one weak solution.
+\end{theorem}
+
+\begin{proof}
+This is a pretty neat proof using a smart choice of $\eta$.
+So let's assume $u_1$ and $u_2$ are weak solutions.
+Then, when putting $u_1$ and $u_2$ into (\ref{weak}) and subtracting one from the other, we get
+\begin{equation}
+\label{weak_diff}
+\iint_{Q_T}\nabla(\Phi(u_2) - \Phi(u_1)) \cdot \nabla \eta - (u_2 - u_1)\partial_t \eta dxdt = 0.
+\end{equation}
+Now the inspired move\footnote{Of course, this isn't my proof so that sort of horn-tooting is in good taste.} is choosing
+\begin{equation*}
+\eta(x,t) = \begin{cases}
+		\int_t^T(\Phi(u_2) - \Phi(u_1))ds, \quad &\text{ if } 0 < t < T \\
+		0 \quad &\text{ if } t\geq T.
+	\end{cases}
+\end{equation*}
+We then have
+\begin{equation*}
+\begin{cases}
+	\partial_t \eta &= -(\Phi(u_2) - \Phi(u_1) ) \\
+	\nabla \eta &= \int_t^T\nabla (\Phi(u_2) - \Phi(u_1))ds,
+\end{cases}
+\end{equation*}
+where the time derivation is valid using the First Fundamentel Theorem of Calculus and that $\Phi(u_i) \in L^1(0,T : W_0^{1,1}(\Omega))$ by the definition of weak soultion.
+For the validity of the spatial derivative, confer appendix \ref{sec:derivative}.
+
+When putting these derivatives into the above equality we end up with
+\begin{equation}
+\label{unique}
+\begin{aligned}
+	&\iint_{Q_T}(\Phi(u_2) - \Phi(u_1))(u_2 - u_1)dxdt \\ 
+	&+ \iint_{Q_T}\nabla(\Phi(u_2(t)) - \Phi(u_1(t))) \cdot \left(\int_t^T 					\nabla(\Phi(u_2(s)) - \Phi(u_1(s))ds\right)dtdx = 0.
+\end{aligned}
+\end{equation}
+Let's take these in order:
+\begin{enumerate}[i)]
+	\item In the first integral we notice that $u_2 > u_1 \Rightarrow \Phi(u_2) \geq \Phi(u_1)$ and vice versa, so this integral is nonnegative.
+
+	\item For the second integral it is helpful to first only consider integration of the temporal dimensions, leaving us with
+	\begin{align*}
+	&\int_0^T\int_t^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dsdt \\
+	&= \int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds.
+	\end{align*}
+	Due to the symmetry about the line $s=t$, we have
+	\begin{align*}
+	&\int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
+	&= \frac{1}{2}\int_0^T \int_0^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
+	&= \frac{1}{2}\left( \int_0^T \nabla(\Phi(u_2)-\Phi(u_1))dt\right)^2,
+	\end{align*}
+	which is also nonnegative, and therefore the second integral in (\ref{unique}) must also be nonnegative.
+\end{enumerate}
+From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies, by the first integral that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e.
+in $Q_T$.
+Actually, we have that $\Phi(u_2) - \Phi(u_1) = 0$ a.e., because wherever $u_2 = u_1$ it is trivially true, and wherever $ u_2 \neq u_1$ it holds from the first integral being zero.
+Thus, $ \nabla (\Phi(u_2) - \Phi(u_1) ) = 0$ a.e.
+and putting this into (\ref{weak_diff}) we get that
+\begin{equation*}
+\iint_{Q_T}(u_2 - u_1)\partial_t \eta dx dt = 0.
+\end{equation*}
+This should hold for any test function $\eta$, and so the weak derivative of $u_2 - u_1$ with respect to time is zero.
+Because $u_2$ and $u_1$ have identical initial condition $u_0$ we conclude that $u_2 = u_1$.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			EXISTENCE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Existence}
+Now we jump in with trying to prove existence of signed, weak energy solutions.
+Following closely the proof provided in \citep{vazquez2007porous}, but now lifting the assumption that $\Phi$ is strictly increasing, and rather having that it is only nondecreasing.
+Another useful addition to proof will be that we will also incorporate the $L^1$-contractivity result.
+
+The proof will use an approximate problem which admits a unique solution from theorem \ref{thm:classical_existence}, and then employing the Rellich compactness argument (cf.
+appendix \ref{sec:compactness} to get a limit which hopefully will be a weak energy solution.
+
+In the following we will assume $u_0 \in L_\Psi(\Omega)$ and $f\in L^p(\Omega)$ with $p = \frac{2d}{d+2}$ if $d \geq 3$, or for some $p>1$ if $d=1,2$\footnote{This choice of value for $p$, I can only say is a mystery for me at this moment, but it seems to be related to the Sobolev conjugate.
+Let's just stay curious and excited for now, shall we?}.
+
+The main theorem reads:
+\begin{theorem}
+\label{thm:weak_existence}
+Assume $u_0 \in L_\Psi(\Omega)$ and $f \in L^p (\Omega)$.
+Then the homogeneous, general porous medium equation (\ref{HDP}) has a weak solution defined in an infinite time interval, $T=\infty$.
+We have $u \in L^\infty(0,T:L_\Psi(\Omega))$ and $\Phi(u) \in L^2(0,T:H_0^1(\Omega))$, and the energy inequality (\ref{energy_ineq}) holds.
+\end{theorem}
+
+We will not prove this in one big chunk, but rather split it off into smaller lemmas, and as already stated, some attention will also be paid to the $L^1$-contractivity.
+\subsection*{Preliminaries}
+To set ourselves up in a position where we can make use of theorem \ref{thm:classical_existence}, or rather corollary \ref{cor:GPME_existence}, we need to approximate $\Phi$, $u_0$, and $f$.
+
+We approximate $\Phi$ by the smooth approximations
+\begin{align*}
+\Phi_n(s) &= \left( \Phi(s) + \frac{s}{n} \right)*\eta_{\frac{1}{n}} \\
+	&= \int_{\mathbb{R}}\left(\Phi(y) + \frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy \\
+	&= \int_{\mathbb{R}}\left(\Phi(s-y) + \frac{s-y}{n}\right)\eta_{\frac{1}{n}}(y)dy
+\end{align*}
+where $\eta$ is the standard mollifier.
+We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$.
+We also ask that $|u_{0,n}| \leq $min$\{n,u_0\}$.
+
+Apparently, also according to \citep{vazquez2007porous}, we also approximate $f$ by a sequnce of functions $f_n$ that converges to $f$ in $L^p(Q_T)$ for all\footnote{Not sure if \textit{sic}...} $p<\infty$, and is so that $|f_n| \leq f$ for all $n$.
+
+Our first lemma then reads
+\begin{lemma}
+Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$, and $\partial_t f$ are bounded, $\partial \Omega \in C^{2+\alpha}$, and $\Phi$ is locally lipschitz continuous.
+\end{lemma}
+
+\begin{proof}
+
+\begin{description}
+	\item[Setting up an approximate problem:] We fix $T<\infty$ and consider the problem
+		\begin{equation}
+		\label{approximate_problem}
+			\begin{cases}
+			\partial_t u_n &= \Delta\Phi_n(u_n) + f_n, \quad \text{ in } Q_T \\
+			u_n(x,0) &= u_{0,n}(x),	\quad \text{ on } \overline{\Omega} \\
+			u_n(x,t) &= 0, \quad \text{ on }  \partial \Omega \times (0,T).
+			\end{cases}
+		\end{equation}			
+	By virtue of theorem \ref{thm:classical_existence}, this approximate problem has a unique solution $u_n \in C^{2,1}(\overline{Q}_T)$. In addition we can from the maximum principle see that
+	\begin{align*}
+	||u_n||_{L^\infty(Q_T)} &\leq ||u_{0,n}||_{L^\infty(\Omega)} + T||f_n||_{L^\infty(Q_T)} \\
+	&\leq ||u_0||_{L^\infty(\Omega)} + T||f||_{L^\infty(Q_T)} = C.
+	\end{align*}
+	A bound independent of $n$.
+
+	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, and do exactly as when deriving (\ref{spatial_derivative_bound}) to get 
+	\begin{equation*}
+	\int_\Omega \Psi(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
+	\end{equation*}
+	Considering the second term on the right hand side we have
+	\begin{equation*}
+	\iint_{Q_T}f_n w_n dxdt \leq C\iint_{Q_T}f_n^2 dxdt + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2dxdt,
+	\end{equation*}
+	after exactly the same argument as we did with (\ref{using_Poincare}). After putting it back
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
+	\end{equation*}
+	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
+	\begin{equation*}
+	\iint_{Q_T}f_n^2dxdt \leq \iint_{Q_T} f^2 dxdt,
+	\end{equation*}
+	by our assumption on the approximation. In addition
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx = \int_\Omega \left[ \int_0^{u_{0,n}(x)} \int_\mathbb{R} \left(\Phi(y)+\frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy ds \right] dx,
+	\end{equation*}
+	and $\eta_{\frac{1}{n}}(s-\cdot)$ has support in $[s-\frac{1}{n}, s + \frac{1}{n}]$. Therefore, by the monotonicity of $\Phi$, 
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega \left[ \int_0^{u_{0,n}(x)}\Phi \left(s+\frac{1}{n} \right)ds + \int_0^{u_{0,n}}\frac{s+\frac{1}{n}}{n}ds \right] dx,
+	\end{equation*}
+	which after a variable transformation yields
+	\begin{align*}
+	\int_\Omega \Psi_n(u_{0,n})dx &\leq \int_\Omega \left[ \int_{\frac{1}{n} }^{u_{0,n}(x) + \frac{1}{n} } \Phi(s)ds + \frac{u_{0,n}(x)^2}{2n} + \frac{u_{0,n}(x)}{n^2} \right] dx \\
+	&\leq \int_\Omega \left[ \Psi\left(u_{0,n} +\frac{1}{n}\right) - \Psi\left(\frac{1}{n}\right) + \frac{1}{2n}\left(u_{0,n} + \frac{1}{n}\right)^2 \right] dx.
+	\end{align*}
+	Using now that $|u_{0,n}| \leq u_0$ and that $\Omega$ is a bounded set, we get a bound on this integral independent of $n$. And so $\iint_{Q_T} |\nabla w_n|^2 dxdt$ has a bound independent of $n$.
+
+	\item[Control of the temporal derivative:] Now we let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 1$.
+If we multiply (\ref{approximate_problem}) by $\zeta \partial_tw_n$ and integrate over $Q_T$ we get
+	\begin{equation}
+	\label{temporal_bound_start}
+	\iint_{Q_T}\zeta \Phi'_n(u_n)|\partial_t u_n|^2 dxdt = \iint_{Q_T} \left\{ \zeta \partial_t w_n \Delta w_n + \zeta \partial_t w_n f_n \right\} dxdt.
+	\end{equation}
+	Let's start by considering the first term on the right hand side. By the product rule for the divergence
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \int_0^T \zeta \int_\Omega \left\{ \nabla \cdot (\partial_t w_n \nabla w_n) - (\partial_t \nabla w_n) \cdot \nabla w_n \right\} dx dt.
+	\end{equation*}
+	So after using the divergence theorem together with the homogeneous boundary data, as well as noticing that $(\partial_t \nabla w_n) \cdot \nabla w_n = \frac{1}{2}\partial_t |\nabla w_n|^2$, we see that
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla w_n|^2 dxdt.
+	\end{equation*}
+	Integrating by parts in the temporal dimension, we end up with
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla w_n|^2 dxdt - \frac{1}{2}\int_\Omega \left\{ |\nabla w_n(T)|^2 - |\nabla w_n(0)|^2 \right\} dx.
+	\end{equation*}
+	A similar inetgration by parts in the temporal dimension of the last term on the right hand side in (\ref{temporal_bound_start}) yields
+	\begin{equation*}
+	\iint_{Q_T} \zeta f_n \partial_t w_n dxdt = -\iint_{Q_T} \partial_t (\zeta f_n) w_n dxdt + \int_\Omega \left\{ f_n(T)w_n(T) - f_n(0)w_n(0) \right \} dx.
+	\end{equation*}
+	For the last term in this integral we can do the same trick as we did previously for the energy estimate.
+We use Cauchy-Schwarz and the inequality $\sqrt{ab} \leq \frac{c^2}{4}a + \frac{1}{c^2}b$.
+Then, after using a Poincaré inequality we can choose $c$ so that the integrals of $|\nabla w_n|^2$ at the temporal endpoints are cancelled.
+In toto we end up with
+	\begin{align*}
+	\iint_{Q_T} \zeta \Phi'_n(u_n) |\partial_t u_n|^2 dxdt &\leq \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
+	&+ \frac{C}{2}\int_\Omega \left\{ f_n^2(T) - f_n^2(0) \right\} dx	\\
+	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
+	&+ C \iint_{Q_T} f_n\partial_t f_n dxdt.
+	\end{align*}
+	Thus, by our assumption that $f$ and $\partial_t f$ are bounded, and our previous energy bound, the left hand side is bounded independent of $n$.
+
+	In particular, we can choose $\zeta = 1$\footnote{Yikes, sorry about the kind of a fortiori argument, those are always a bit of a headache.}, and we get a bound on $\Phi'_n(u_n)|\partial_t u_n|^2$ in $L^1(Q_T)$.
+See now that $|\partial_t w_n	|^2 = \Phi'_n(u_n)^2|\partial_t u_n|^2$.
+And so, beacuse $\Phi'(u)$ is bounded for all $|u| \leq C$, we have that $\Phi'_n(u_n)$ is uniformly bounded, our latest integral bound gives us that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T)$.
+
+	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.
+The energy estimate continues to hold in the limit as
+	\begin{equation}
+	\iint_{Q_T}|\nabla w|^2 dxdt \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}fw dxdt.
+	\end{equation}
+	Notice that since $w \in L^2(Q_T)$, we can from this inequality conclude that $w \in H^1(Q_T)$.
+
+	\item[Convergence of $u_n$:] Recall that we defined $w_n = \Phi_n(u_n)$. Consider now
+	\begin{equation*}
+	\partial_t (u_{n} - u_{m}) = \Delta (w_{n} - w_{m}) + (f_{n}-f_{m}).
+	\end{equation*}
+	We will now do quite the same as we did when the $L^1$-contracivity for classical solutions: Let $p: \mathbb{R} \to [0,1]$ be a smooth approximation of the heaviside function, and multiply the above equation by $p(w_{n}-w_{m})$.
+Integrating over $\Omega$ and using integration by parts results in
+	\begin{align*}
+	\int_\Omega \partial_t(u_n - u_m)p(w_n-w_m)dx &= -\int_\Omega p'(w_n-w_m)|\nabla(w_n-w_m)|^2dx + \int_\Omega (f_n-f_m)p(w_n-w_m)dx \\
+	&\leq \int_\Omega (f_n-f_m)_+ dx.
+	\end{align*}
+	This last step us justified in that for all $n$ we have $w_n \in H^1(\Omega)$ for  every $t \in [0,T]$.
+Letting $p$ tend towards the heaviside function and integrating over the time interval $[0,t]$ we end up with
+	\begin{equation*}
+	\int_\Omega (u_n - u_m)_+(t) dx \leq \int_\Omega (u_{0,n} - u_{0,m})_+dx + \int_0^t\int_\Omega (f_n - f_m)_+ dxds,
+	\end{equation*}
+	and as a consequence
+	\begin{equation*}
+	||(u_n - u_m)(t)||_{L^1(\Omega)} \leq ||u_{0,n} - u_{0,m}||_{L^1(\Omega)} + ||f_n-f_m||_{L^1(Q_t)}.
+	\end{equation*}
+	Integrating over time yet again and using that $Q_T$ is bounded we deduce that $\{u_n\}$ is a Cauchy sequence in $L^1(Q_T)$, and hence converges to some $u$ in $L^1$.
+
+	\item[Showing that $w=\Phi(u)$:] It is sensible to break this part into two similar steps.
+First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges points wise to $\Phi(u_k)$.
+Let now $\psi$ be a function in $L^1(Q_T)$ with compact support.
+We want to show that
+	\begin{equation*}
+	\iint_{Q_T} \Phi_n(u_k) \psi dxdt \to \iint_{Q_T}\Phi(u_k)\psi dxdt.
+	\end{equation*}
+	This is accomplished using the Dominated Convergence Theorem (DCT). So we note that since $|u_k| \leq C$, 
+	\begin{align*}
+    |\Phi_n(u_k)| &\leq \int_\mathbb{R} \left| \Phi(u_k-y) + \frac{u_k-y}{n}\right|\eta_{\frac{1}{n}}(y)dy \\
+    &\leq \underset{|s|\leq C+1/n}{sup}\left| \Phi(s) + \frac{s}{n}\right| < \infty,
+	\end{align*}
+	due to the support of $\eta_{\frac{1}{n}}$ being contained in $\left[ -\frac{1}{n}, \frac{1}{n}\right]$.
+Thus we set $M = \mathrm{sup}_{|s|\leq C+1}\left|\Phi(s) + s\right|$.
+Then $|\Phi_n(u_k)\psi| \leq M|\psi| \in L^1(Q_T)$, and we can use the DCT to establish that the proposed limit holds.
+
+	An almost identical argument is valid for showing that
+	\begin{equation*}
+	\iint_{Q_T}\Phi(u_n)\psi dxdt \to \iint_{Q_T}\Phi(u)\psi dxdt,
+	\end{equation*}		
+	only now using $M = \mathrm{sup}_{|s|\leq C}|\Phi(s)|$. Thus, we can construct a diagonal argument for the sequence $\Phi_n(u_n)$ to get that
+	\begin{equation}
+	\iint_{Q_T} w\psi dxdt = \lim_{n_j \to \infty} \iint_{Q_T}\Phi_{n_j}(u_{n_j})\psi dxdt = \iint_{Q_T} \Phi(u) \psi dxdt.
+	\end{equation}
+	Seeing as $\psi$ was arbitrary we get that $\Phi(u) = w$ almost everywhere.
+
+	\item[$u$ is a weak solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}(\Omega))$\footnote{Actually, this may not be as easy to see as I've stated here.
+Need to use yet another estimate to show this.}.
+So what's left is to show that
+	\begin{equation*}
+	\iint_{Q_T}\left\{ \nabla\Phi(u) \cdot \nabla \eta - u\partial_t \eta - f\eta \right\}dxdt - \int_\Omega u_0\eta\big|_{t=0}dx = 0
+	\end{equation*}
+	for any $\eta \in C^1(\overline{Q}_T)$ that vanish on $\partial \Omega \times [0,T)$ and for $t=T$.
+\end{description}
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				APPENDICES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{appendix}
+\section{Passing derivative inside the integral}
+\label{sec:derivative}
+
+We are now concern with whether
+\begin{equation}
+\label{diff_int}
+	\nabla \int_t^T \varphi(x,s)ds = \int_t^T \nabla\varphi(x,s)ds
+\end{equation}
+holds or not for $\varphi \in L^2(0,T:H_0^1 (\Omega))$. 
+For simplicity we now only consider one spatial dimension.
+
+To begin with, assume that $\psi \in C^{\infty}_c(\Omega)$ and $\eta \in L^2(0,T: H_0^1(\Omega))\cap C^\infty_c(Q_T)$, then we have that
+\begin{align*}
+\int_{\Omega}\psi \partial_x\left(\int_t^T \eta(x,s) ds\right)dx &= \int_{\Omega}\psi \lim_{h \to 0}\left(\int_t^T \frac{\eta(x+h,s)-\eta(x,s)}{h} ds\right)dx\\
+&= \int_{\Omega}\psi \lim_{h \to 0}\left(\int_t^T \eta_h(x,s) ds\right)dx.
+\end{align*}
+
+Assuming that $\partial_x \eta(x,s)$ is bounded, we can use the mean value theorem to state that $|\eta_h| \leq  ||\partial_x \eta||_\infty$.
+We also have that $\eta_h(x,s) \to \partial_x \eta(x,s)$ pointwise, and so we're in a position to use the Dominated Convergence theorem to conclude that
+\begin{equation}
+\label{results_diff_first}
+\int_{\Omega}\psi \partial_x\left(\int_t^T \eta(x,s) ds\right)dx = \int_{\Omega}\psi \left(\int_t^T \partial_x\eta(x,s) ds\right)dx.
+\end{equation}
+
+To extend the result to $L^2(0,T:H_0^1 (\Omega))$ we use that $C_c^\infty$ is dense in this space.
+So let $\{\psi_n\},\{\varphi_n\}$ be two sequence converging to $\psi$ and $\varphi$ in $L^2(\Omega)$ and $L^2(0,T:H_0^1(\Omega))$ respectively.
+Considering the left hand side of (\ref{results_diff_first}), we get
+\begin{align*}
+&\left|\int_{\Omega}\psi \partial_x \left( \int_t^T\varphi ds \right)dx - \int_{\Omega}\psi_n \partial_x \left( \int_t^T \varphi_n ds \right) dx \right| \\
+&\leq  \left| \int_{\Omega} \psi \partial_x \left(\int_t^T \varphi - \varphi_n ds\right)dx \right| + \left| \int_{\Omega}(\psi - \psi_n)\partial_x\left(\int_t^T \varphi_n ds\right) dx \right| \\
+&\leq ||\psi||_{L^2(\Omega)}|(\varphi -\varphi_n)|_{L^2(H_0^1)} + ||\psi-\psi_n||_{L^2}| \varphi_n |_{L^2(H_0^1)} \\
+&\leq ||\psi||_{L^2(\Omega)}||(\varphi -\varphi_n)||_{L^2(H_0^1)} + ||\psi-\psi_n||_{L^2}|| \varphi_n ||_{L^2(H_0^1)} \\
+&\to 0,
+\end{align*}
+after using the triangle- and Cauchy-Schwarz' inequality as well as the assumptions on convergence.
+
+An exactly similar approach can be done to the right hand side, and so passing the limit in (\ref{results_diff_first}) we get
+\begin{equation}
+\label{result_diff_final}
+\int_\Omega \psi \partial_x\left(\int_t^T \varphi(x,s)ds\right)dx = \int_\Omega \psi \left( \int_t^T \partial_x \varphi(x,s)ds \right) dx.
+\end{equation}
+
+To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		COMPACTNESS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Compactness argument}
+\label{sec:compactness}
+Here I will simply state the Rellich-Kondrachov Compactness theorem as it is presented in \citep{evans}, mostly for ease of reference. For more details, please cf. Chapter 5 ibid.
+
+\begin{mydef}
+Let $X$ and $Y$ be Banach spaces with $X \subset Y$. We say that $X$ is \textbf{compactly embedded} in $Y$, written
+\begin{equation*}
+X \subset \subset Y,
+\end{equation*}
+provided 
+\begin{enumerate}[i)]
+	\item $||u||_Y \leq ||u||_X$ for every $u \in X$, for some constant $C$, and
+
+	\item each bounded sequence in $X$ is precompact in $Y$.
+\end{enumerate}
+\end{mydef}
+
+With this definition in mind we have the following theorem:
+\begin{theorem}[Rellich-Kondrachov Compactness Theorem]
+\label{thm:Rellich}
+Assume $U$ is an open, bounded subset of $\mathbb{R}^n$ and $\partial U$ is $C^1$.
+Suppose $1\leq p < n$. Then
+\begin{equation}
+\label{Rellich}
+W^{1,p}(U) \subset \subset L^q(U)
+\end{equation}
+for each $1\leq q < p^*$, where $p^* = \frac{np}{n-p}$ is the Sobolev conjugate of $p$.
+\end{theorem}
+\setcounter{rem}{0}
+\begin{rem}
+If $p=2$, the we have
+\begin{equation*}
+H^1(U) \subset \subset L^q(U)
+\end{equation*}
+for each $1\leq q < p^*$.
+\end{rem}
+\begin{rem}
+Since $p^* > p$ the result is valid for $q=p$. This actually holds for all $1\leq p \leq \infty$, even when $p > n$.
+\end{rem}
+\begin{rem}
+We also have 
+\begin{equation*}
+W^{1,p}_0(U) \subset \subset L^p(U)
+\end{equation*}
+even when the assumption that $\partial U$ is $C^1$ is lifted.
+\end{rem}
+
+\end{appendix}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-10-28 draft_project.tex
Skrevet litt mer.

@@
 This bound follows nicely the $L^1$-contractivity in that its derivation hinges on a clever choice of function to multiply (\ref{GPME}) with.
-The bound on the spatial derivative is summarised in the following lemma.
+Before proceeding, we define  $\Psi$ as the primitive of $\Phi$ with $\Psi(0) = 0$, i.e.
+\begin{equation}
+\label{phi_primitive}
+	\Psi(s) = \int_0^s \Phi(u) ds,
+\end{equation}
+
+The bound on the spatial derivative is then summarised in the following lemma.
 
@@
 \end{obs}
+
+\subsection{Control of the temporal derivative}
+A similar, but perhaps a bit more involved argument can be used to make an estimate the temporal derivative.
+
+Let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 1$. If we multiply (\ref{GPME}) by $\zeta \partial_t\Phi(u)$ and integrate over $Q_T$ we get
+	\begin{equation}
+	\label{temporal_bound_start}
+	\iint_{Q_T}\zeta \Phi'(u)|\partial_t u|^2 dxdt = \iint_{Q_T} \left\{ \zeta \partial_t \Phi(u) \Delta \Phi(u)  + \zeta \partial_t \Phi(u) f \right\} dxdt.
+	\end{equation}
+	Let's start by considering the first term on the right hand side. By the product rule for the divergence
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = \int_0^T \zeta \int_\Omega \left\{ \nabla \cdot (\partial_t \Phi(u) \nabla \Phi(u)) - (\partial_t \nabla \Phi(u)) \cdot \nabla \Phi(u) \right\} dx dt.
+	\end{equation*}
+	So after using the divergence theorem together with the homogeneous boundary data, as well as noticing that $(\partial_t \nabla \Phi(u)) \cdot \nabla \Phi(u) = \frac{1}{2}\partial_t |\nabla \Phi(u)|^2$, we see that
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla \Phi(u)|^2 dxdt.
+	\end{equation*}
+	Integrating by parts in the temporal dimension, we end up with
+	\begin{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla \Phi(u)|^2 dxdt - \frac{1}{2}\int_\Omega \left\{ |\nabla \Phi(u(T))|^2 - |\nabla \Phi(u_0)|^2 \right\} dx.
+	\end{equation*}
+	A similar inetgration by parts in the temporal dimension of the last term on the right hand side in (\ref{temporal_bound_start}) yields
+	\begin{equation*}
+	\iint_{Q_T} \zeta f \partial_t \Phi(u) dxdt = -\iint_{Q_T} \partial_t (\zeta f) \Phi(u) dxdt + \int_\Omega \left\{ f(T)\Phi(u(T)) - f(0)\Phi(u_0) \right\} dx.
+	\end{equation*}
+	For the last term in this integral we can do the same trick as we did previously for the energy estimate.
+We use Cauchy-Schwarz and the inequality $\sqrt{ab} \leq \frac{c^2}{4}a + \frac{1}{c^2}b$.
+Then, after using a Poincaré inequality we can choose $c$ so that the integrals of $|\nabla \Phi(u)|^2$ at the temporal endpoints are cancelled.
+In toto we end up with
+	\begin{align*}
+	\iint_{Q_T} \zeta \Phi'(u) |\partial_t u|^2 dxdt &\leq \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla \Phi(u)|^2 - \partial_t(\zeta f) \Phi(u) \right\} dxdt \\
+	&+ \frac{C}{2}\int_\Omega \left\{ f^2(T) - f^2(0) \right\} dx	\\
+	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla \Phi(u)|^2 - \partial_t(\zeta f) \Phi(u) \right\} dxdt \\
+	&+ C \iint_{Q_T} f\partial_t f dxdt.
+	\end{align*}
+
+A particular choice for $\zeta$, that's of interest is $\zeta(t) = 1$. Then we end up with the estimate
+\begin{equation}
+\label{temporal_bound}
+\iint_{Q_T} \Phi'(u) |\partial_t u|^2 dxdt \leq \iint_{Q_T}\left\{ -\partial_t f \Phi(u)   +Cf\partial_tf \right\}dxdt, 
+\end{equation}
+and in addition if $\Phi'(u)$ is bounded over all relevant values of $u$, e.g. given my the $L^\infty$-bound, then what we have here is an $L^2$-estimate of $\partial_t \Phi(u)$.
 
@@
 with the Hölder semi-norm with respect to $x$ and $t$ respectively in the last two definitions.
-
-\begin{rem}
-
-\end{rem}
 
@@
 \begin{theorem}[Uniqueness]
+\label{thm:uniqueness}
 	Assuming in addition that $u \in L^2(Q_T)$ and $\Phi(u) \in L^2(0,T : H_0^1(\Omega))$, (\ref{HDP}) has at most one weak solution.
@@
 \subsection{Existence}
+As the assumptions in theorem \ref{thm:uniqueness} may hint at, some additional assumptions on $u$ and $\Phi(u)$ needs to be put to ensure that the homogeneous Dirichlet problem is well posed in the weak setting.
+There are some alternatives, and of course, any further analysis will be informed what sort of additional condition we want a weak solution $u$ to fulfill.
+The one we will be using here is guided by the notion that in a physical system the energy should be controlled, and is therefore called a weak energy solution.
+
+Recall our definition of $\Psi$ in (\ref{phi_primitive}) as the primitive of $\Phi$,
+and we define the function space $L_\Psi(\Omega) = \{ u\in L^1(\Omega): \Psi(u)\in L^1(\Omega)\}$.
+With this in mind we can define energy solutions in the following way:
+\begin{mydef}[Energy solution]
+We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L_\Psi(\Omega)$, and the energy inequality
+\begin{equation}
+\label{energy_ineq}
+\iint_{Q_T} |\nabla \Phi(u)|^2 dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}f\Phi(u)dxdt
+\end{equation}
+holds.
+\end{mydef}
+\setcounter{obs}{0}
+\begin{obs}
+If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as with the energy identity in (\ref{spatial_derivative_bound}) to get that $\Phi(u) \in L^2(0,T: H_0^1(\Omega))$.
+\end{obs}
+
 Now we jump in with trying to prove existence of signed, weak energy solutions.
 Following closely the proof provided in \citep{vazquez2007porous}, but now lifting the assumption that $\Phi$ is strictly increasing, and rather having that it is only nondecreasing.
-Another useful addition to proof will be that we will also incorporate the $L^1$-contractivity result.
+Another useful addition to proof will be that we will also incorporate a $L^1$-contractivity result.
 
@@
 We will not prove this in one big chunk, but rather split it off into smaller lemmas, and as already stated, some attention will also be paid to the $L^1$-contractivity.
-\subsection*{Preliminaries}
+\subsubsection{Preliminaries}
 To set ourselves up in a position where we can make use of theorem \ref{thm:classical_existence}, or rather corollary \ref{cor:GPME_existence}, we need to approximate $\Phi$, $u_0$, and $f$.
@@
 
+\subsubsection{$u_0$, $f$ and $\partial_t f$ bounded}
 Our first lemma then reads
@@
 	\begin{equation*}
-	\int_\Omega \Psi(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
+	\int_\Omega \Psi_n(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
 	\end{equation*}
@@
 	\begin{equation*}
-	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
+	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
 	\end{equation*}
@@
 	for any $\eta \in C^1(\overline{Q}_T)$ that vanish on $\partial \Omega \times [0,T)$ and for $t=T$.
+Seeing as every $u_n$ is a weak solution to the approximate (\ref{approximate_problem}) we can subtract it from the integral above to get
+	\begin{align*}
+	&\iint_{Q_T}\left\{ \nabla\Phi(u) \cdot \nabla \eta - u\partial_t \eta - f\eta \right\}dxdt - \int_\Omega u_0\eta\big|_{t=0}dx \\
+	= &\iint_{Q_T}\left\{ \nabla(\Phi(u)-w_n) \cdot \nabla \eta - (u-u_n)\partial_t \eta - (f-f_n)\eta \right\}dxdt - \int_\Omega (u_0-u_{0,n})\eta\big|_{t=0}dx.
+	\end{align*}
+
+	All the terms but the last are controlled by the convergences of $u_n$, $u_{0,n}$, and $f_n$.  	
 \end{description}

### 2014-10-29 draft_project.tex
Ting er dritt, ting er bra. Vætta faen!

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			SPATIAL DER. BOUND
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Control of the spatial derivative}
@@
 \end{obs}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				TEMPORAL DER. BOUND
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Control of the temporal derivative}
@@
 \end{equation}
-and in addition if $\Phi'(u)$ is bounded over all relevant values of $u$, e.g. given my the $L^\infty$-bound, then what we have here is an $L^2$-estimate of $\partial_t \Phi(u)$.
+and in addition if $\Phi'(u)$ is bounded over all relevant values of $u$, e.g. given by the $L^\infty$-bound, then what we have here is an $L^2$-estimate of $\partial_t \Phi(u)$.
 
@@
 
-	\item[Control of the temporal derivative:] Now we let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 1$.
-If we multiply (\ref{approximate_problem}) by $\zeta \partial_tw_n$ and integrate over $Q_T$ we get
-	\begin{equation}
-	\label{temporal_bound_start}
-	\iint_{Q_T}\zeta \Phi'_n(u_n)|\partial_t u_n|^2 dxdt = \iint_{Q_T} \left\{ \zeta \partial_t w_n \Delta w_n + \zeta \partial_t w_n f_n \right\} dxdt.
-	\end{equation}
-	Let's start by considering the first term on the right hand side. By the product rule for the divergence
-	\begin{equation*}
-	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \int_0^T \zeta \int_\Omega \left\{ \nabla \cdot (\partial_t w_n \nabla w_n) - (\partial_t \nabla w_n) \cdot \nabla w_n \right\} dx dt.
-	\end{equation*}
-	So after using the divergence theorem together with the homogeneous boundary data, as well as noticing that $(\partial_t \nabla w_n) \cdot \nabla w_n = \frac{1}{2}\partial_t |\nabla w_n|^2$, we see that
-	\begin{equation*}
-	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla w_n|^2 dxdt.
-	\end{equation*}
-	Integrating by parts in the temporal dimension, we end up with
-	\begin{equation*}
-	\int_0^T \zeta \int_\Omega \partial_t w_n \Delta w_n dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla w_n|^2 dxdt - \frac{1}{2}\int_\Omega \left\{ |\nabla w_n(T)|^2 - |\nabla w_n(0)|^2 \right\} dx.
-	\end{equation*}
-	A similar inetgration by parts in the temporal dimension of the last term on the right hand side in (\ref{temporal_bound_start}) yields
-	\begin{equation*}
-	\iint_{Q_T} \zeta f_n \partial_t w_n dxdt = -\iint_{Q_T} \partial_t (\zeta f_n) w_n dxdt + \int_\Omega \left\{ f_n(T)w_n(T) - f_n(0)w_n(0) \right \} dx.
-	\end{equation*}
-	For the last term in this integral we can do the same trick as we did previously for the energy estimate.
-We use Cauchy-Schwarz and the inequality $\sqrt{ab} \leq \frac{c^2}{4}a + \frac{1}{c^2}b$.
-Then, after using a Poincaré inequality we can choose $c$ so that the integrals of $|\nabla w_n|^2$ at the temporal endpoints are cancelled.
-In toto we end up with
-	\begin{align*}
-	\iint_{Q_T} \zeta \Phi'_n(u_n) |\partial_t u_n|^2 dxdt &\leq \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
-	&+ \frac{C}{2}\int_\Omega \left\{ f_n^2(T) - f_n^2(0) \right\} dx	\\
-	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt \\
-	&+ C \iint_{Q_T} f_n\partial_t f_n dxdt.
-	\end{align*}
-	Thus, by our assumption that $f$ and $\partial_t f$ are bounded, and our previous energy bound, the left hand side is bounded independent of $n$.
-
-	In particular, we can choose $\zeta = 1$\footnote{Yikes, sorry about the kind of a fortiori argument, those are always a bit of a headache.}, and we get a bound on $\Phi'_n(u_n)|\partial_t u_n|^2$ in $L^1(Q_T)$.
-See now that $|\partial_t w_n	|^2 = \Phi'_n(u_n)^2|\partial_t u_n|^2$.
-And so, beacuse $\Phi'(u)$ is bounded for all $|u| \leq C$, we have that $\Phi'_n(u_n)$ is uniformly bounded, our latest integral bound gives us that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T)$.
-
-	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.
+	\item[Control of the temporal derivative:] The derivation of (\ref{temporal_bound}) holds up in this case and we have
+	\begin{equation*}
+	\iint_{Q_T} \Phi'_n(u_n)|\partial_t u_n|^2 dxdt \leq \iint_{Q_T} \left\{ -\partial_t f_n \Phi_n(u_n) + Cf_n\partial_tf_n \right\} dxdt.
+	\end{equation*}
+	Just to reiterate, $C$ is here the constant given by Poincaré inequality, and is as such only dependent on $\Omega$.
+
+	Now, since we have assumed $\Phi$ to be locally Lipschitz, $|\Phi_n'(u_n)| \leq K < \infty$ over the relevant values of $u_n$, we notice that $|\partial_t w_n|^2 \leq K|\Phi'_n(u_n) (\partial_t u_n)^2|$.
+We have assumed both $f$ and $\partial_t f$ to be bounded, so we can put a uniform bound on the right hand side, independent of $n$.
+We conclude that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T)$.
+
+	\item[Using a compactness argument:]From the two previous parts we have that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.
 The energy estimate continues to hold in the limit as
@@
 
-	\item[Convergence of $u_n$:] Recall that we defined $w_n = \Phi_n(u_n)$. Consider now
-	\begin{equation*}
-	\partial_t (u_{n} - u_{m}) = \Delta (w_{n} - w_{m}) + (f_{n}-f_{m}).
-	\end{equation*}
-	We will now do quite the same as we did when the $L^1$-contracivity for classical solutions: Let $p: \mathbb{R} \to [0,1]$ be a smooth approximation of the heaviside function, and multiply the above equation by $p(w_{n}-w_{m})$.
-Integrating over $\Omega$ and using integration by parts results in
-	\begin{align*}
-	\int_\Omega \partial_t(u_n - u_m)p(w_n-w_m)dx &= -\int_\Omega p'(w_n-w_m)|\nabla(w_n-w_m)|^2dx + \int_\Omega (f_n-f_m)p(w_n-w_m)dx \\
-	&\leq \int_\Omega (f_n-f_m)_+ dx.
-	\end{align*}
-	This last step us justified in that for all $n$ we have $w_n \in H^1(\Omega)$ for  every $t \in [0,T]$.
-Letting $p$ tend towards the heaviside function and integrating over the time interval $[0,t]$ we end up with
-	\begin{equation*}
-	\int_\Omega (u_n - u_m)_+(t) dx \leq \int_\Omega (u_{0,n} - u_{0,m})_+dx + \int_0^t\int_\Omega (f_n - f_m)_+ dxds,
-	\end{equation*}
-	and as a consequence
-	\begin{equation*}
-	||(u_n - u_m)(t)||_{L^1(\Omega)} \leq ||u_{0,n} - u_{0,m}||_{L^1(\Omega)} + ||f_n-f_m||_{L^1(Q_t)}.
-	\end{equation*}
-	Integrating over time yet again and using that $Q_T$ is bounded we deduce that $\{u_n\}$ is a Cauchy sequence in $L^1(Q_T)$, and hence converges to some $u$ in $L^1$.
+	\item[Convergence of $u_{n_j}$:] Since all $u_{n_j}$ are classical solutions, they're also weak solutions.
+Therefore, when putting $u_{n_j}$ and $u_{n_k}$ into (\ref{weak}) and taking their difference,
+	\begin{align*}
+	-\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt &= -\iint_{Q_T}\nabla(w_{n_j} - w_{n_k})\cdot \nabla \eta dxdt \\
+	&+ \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0}dx \\
+	&+ \iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt 
+	\end{align*}	 
+	pops out. Restricting ourselves to only $\eta \in C^\infty_c(Q_T)$, and doing integration by parts on the term involving $w$, yields
+	\begin{equation*}
+	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| \leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| +  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|,
+	\end{equation*}
+	where the term concerning the initial data has dropped out following that $\eta \big|_{t=0} = 0$.
+The first and the last term can both be made arbitrarily small by the convergence of $w_{n_j}$ and $f_n$ respectively.
+And so $\partial_t u_{n_j}$ in the weak sense is a Cauchy sequence in $L^1_{loc}(Q_T)$, and since $Q_T$ is bounded, also in $L^1(Q_T)$.
 
@@
 
-	\item[$u$ is a weak solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}(\Omega))$\footnote{Actually, this may not be as easy to see as I've stated here.
+	Lastly, they're weak derivatives also agree, since
+	\begin{equation*}
+	\iint_{Q_T}\nabla(\Phi(u) - w) \cdot \psi dxdt = -\iint_{Q_T}(\Phi(u)-w)\nabla \cdot \psi dxdt = 0 
+	\end{equation*}
+	for every test function $\psi$.
+	 And so the energy inequality (\ref{energy_ineq}) continues to hold as
+	\begin{equation}
+	\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \int_{Q_T} f\Phi(u)dxdt.
+	\end{equation}
+
+	\item[$u$ is a weak energy solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}(\Omega))$\footnote{Actually, this may not be as easy to see as I've stated here.
 Need to use yet another estimate to show this.}.
 So what's left is to show that
-	\begin{equation*}
+	\begin{equation}
+	\label{claim_weak_solution}
 	\iint_{Q_T}\left\{ \nabla\Phi(u) \cdot \nabla \eta - u\partial_t \eta - f\eta \right\}dxdt - \int_\Omega u_0\eta\big|_{t=0}dx = 0
-	\end{equation*}
+	\end{equation}
 	for any $\eta \in C^1(\overline{Q}_T)$ that vanish on $\partial \Omega \times [0,T)$ and for $t=T$.
@@
 
-	All the terms but the last are controlled by the convergences of $u_n$, $u_{0,n}$, and $f_n$.  	
+	All the terms are controlled by the convergences of $w_n$, $u_n$, $u_{0,n}$, as long as the limit is taken along the subsequence for which we know $w_n$ converges.
+Thus, (\ref{claim_weak_solution}) holds, and $u$ is a weak energy solution.
+
+	We have from before that $u\in L^1(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique.
+
+	\item[Considering the $L^1$-contractivity:] Let now $\hat{u}$ be the weak energy solution to some auxiliary problem with intial value $\hat{u}_0$ and loading $\hat{f}$.
+We also let $\hat{u}_n$ be a sequence of approximations similarly constructed as those for $u$.
+We go by way of first showing that
+	\begin{equation}
+	\label{weak_solutions_l1_start}
+	\int_\Omega(u(t)-\hat{u}(t))_+dx \leq \int_\Omega (u_0 + \hat{u}_0)_+dx + \int_0^t \int_\Omega (f- \hat{f})_+ dxdt. 
+	\end{equation}
+	With that in mind it's worth noting that for $\int_\Omega (\cdot)_+dx$ the triangle inequality is valid, so
+	\begin{align*}
+	\int_\Omega (u(t) - \hat{u}(t))_+dx &\leq \int_\Omega(u(t) - u_n(t))_+dx + \int_\Omega (u_n(t) - \hat{u}_n(t))_+dx \\
+	&+ \int_\Omega(\hat{u}_n - \hat{u})_+dx.
+	\end{align*}
+	The first and last term we can make arbitrarily small, and for the middle term we use the $L^1$-contractivity for smooth solutions. Then, for every $\epsilon > 0$
+	\begin{equation*}
+	\int_\Omega (u(t) - \hat{u}(t))_+dx < \epsilon + \int_\Omega(u_{0,n} + \hat{u}_{0,n})_+ dx + \int_0^t \int_\Omega (f_n - \hat{f}_n)_+dxdt,
+	\end{equation*}
+	for sufficiently large $n$. When using the triangle inequality again
+	\begin{align*}
+	\int_\Omega (u(t) - \hat{u}(t))_+dx &< \epsilon + \int_\Omega(u_{0,n} - u_0)_+dx + \int_\Omega(u_0 - \hat{u}_0)_+dx \\
+	&+ \int_\Omega (\hat{u}_0 - \hat{u}_{0,n})_+dx + \int_0^t \int_\Omega(f_n - f)_+dxdt\\
+	&+ \int_0^t(f-\hat{f})_+dxdt + \int_0^t\int_\Omega (\hat{f}-\hat{f}_n)_+ dxdt.
+	\end{align*}	
+	All the term involving $n$ in the integrand can now be made arbitrarily small, so for sufficiently large $n$
+	\begin{equation*}
+	\int_\Omega (u(t) - \hat{u}(t))_+dx < 2\epsilon +\int_\Omega(u_0 - \hat{u}_0)_+dx + \int_0^t \int_\Omega (f-\hat{f})dxdt.
+	\end{equation*}					
+	Since this should hold for every $\epsilon >0 $, we must have that (\ref{weak_solutions_l1_start}) is satisfied.
+
+	From (\ref{weak_solutions_l1_start}), we do as for (\ref{l1_contractivity}), and get
+	\begin{equation*}
+	||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||f-\hat{f}||_{L^1(Q_t)}
+	\end{equation*}
 \end{description}

### 2014-10-31 draft_project.tex
Er det fiksa, er det lov å spørre seg.

@@
 	\end{align*}	 
-	pops out. Restricting ourselves to only $\eta \in C^\infty_c(Q_T)$, and doing integration by parts on the term involving $w$, yields
-	\begin{equation*}
-	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| \leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| +  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|,
-	\end{equation*}
-	where the term concerning the initial data has dropped out following that $\eta \big|_{t=0} = 0$.
-The first and the last term can both be made arbitrarily small by the convergence of $w_{n_j}$ and $f_n$ respectively.
+	pops out. Restricting ourselves to only $\eta \in C^\infty(Q_T)$ that vanish on $\partial \Omega \times [0,T]$ and for $t=T$, and doing integration by parts on the term involving $w$, yields
+	\begin{align*}
+	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| &\leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| \\
+	&+ \bigg| \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0} dx \bigg| \\
+	 &+  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|.
+	\end{align*}
+	 All terms can be made arbitrarily small by the convergences of $w_{n_j}$, $u_{0,n}$ and $f_n$ respectively.
 And so $\partial_t u_{n_j}$ in the weak sense is a Cauchy sequence in $L^1_{loc}(Q_T)$, and since $Q_T$ is bounded, also in $L^1(Q_T)$.
+By the completeness of $L^1(Q_T)$, it must also converge.
+The primitive of this limit is then determined up to a constant independent of $t$.
+However, the limit is completely determined when taking into account the initial data.
+
+	 To see this we call $v$ the weak time derivative of the limit of $u_{n_j}$, and $g$ its primitive. That is, for every $\eta \in C^\infty_c (Q_T)$ we have
+	 \begin{equation*}
+	 \iint_{Q_T} g\partial_t\eta dxdt = -\iint_{Q_T}v\eta dxdt.
+	 \end{equation*}
+	 In addition we impose the condition that
+	 \begin{equation*}
+	 \lim_{\epsilon \to 0} \iint_{Q_T}g \eta_\epsilon dxdt = \frac{1}{2}\int_\Omega u_0dx,
+	 \end{equation*}
+	 where $\eta_\epsilon$ is here the standard mollifier with respect to only the temporal dimension.
+Note that the factor $\frac{1}{2}$ comes from the mollifier being symmetric about the origin and we only integrate over positive values of $t$.
+With these two conditions $g$ can be uniquely determined.
+So $u_{n_j}$ converges in $L^1(Q_T)$ and we call the limit $u$.
 
 	\item[Showing that $w=\Phi(u)$:] It is sensible to break this part into two similar steps.
-First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges points wise to $\Phi(u_k)$.
+First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges pointwise to $\Phi(u_k)$.
 Let now $\psi$ be a function in $L^1(Q_T)$ with compact support.
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				BIBLIOGRAPHY
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\bibliographystyle{plainnat}
+\bibliography{project_bibliography.bib}
 
@@
 \end{appendix}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%				BIBLIOGRAPHY
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\bibliographystyle{plainnat}
-\bibliography{project_bibliography.bib}
 \end{document}

### 2014-11-03 draft_project.tex
....

@@
 
-We approximate $\Phi$ by the smooth approximations
-\begin{align*}
-\Phi_n(s) &= \left( \Phi(s) + \frac{s}{n} \right)*\eta_{\frac{1}{n}} \\
-	&= \int_{\mathbb{R}}\left(\Phi(y) + \frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy \\
-	&= \int_{\mathbb{R}}\left(\Phi(s-y) + \frac{s-y}{n}\right)\eta_{\frac{1}{n}}(y)dy
-\end{align*}
-where $\eta$ is the standard mollifier.
-We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$.
-We also ask that $|u_{0,n}| \leq $min$\{n,u_0\}$.
+We approximate $\Phi$ by the smooth approximations. To ensure suffient smoothness we define
+\begin{equation*}
+\Phi_n'(s) = \left( \Phi' + \frac{1}{n}\right)*\varphi_{\frac{1}{n}},
+\end{equation*}
+where $\varphi_{\frac{1}{n}}(s) = n\varphi\left( \frac{s}{n} \right)$ and $\varphi$ is the standard mollifier. Then, we can approximate $\Phi$ as
+\begin{align*}
+\Phi_n(u) &= \int_0^u \int_\mathbb{R}\left( \Phi'(s-y) + \frac{1}{n}\right)\varphi_{\frac{1}{n}}(y)dyds \\
+&= \int_\mathbb{R}\varphi_{\frac{1}{n}}(y) \int_0^u \left( \Phi'(s-y) + \frac{1}{n}\right)dsdy \\
+&= \int_\mathbb{R}\varphi_{\frac{1}{n}}(y) \left( \Phi(u-y) - \Phi(-y) + \frac{u}{n}\right)dy \\
+&= \Phi * \varphi_{\frac{1}{n}}(u) - \Phi * \varphi_{\frac{1}{n}}(0) + \frac{u}{n}.
+\end{align*}
+
+We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$. We also ask that $|u_{0,n}| \leq $min$\{n,u_0\}$.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			PROPERTIES OF THE APPROXIMATIONS:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Properties of the approximate nonlinearities}
+Let's discuss some of the properties of the sequence of approximations to the nonlinearity $\Phi$. To reiterate we defined
+\begin{equation*}
+\Phi_n(s) = \int_\mathbb{R}\left( \Phi(u-y) + \frac{u-y}{n}\right) \eta_{\frac{1}{n}}(y)dy
+\end{equation*}
+
 \end{appendix}

### 2014-11-04 draft_project.tex
Ferdig med bla bla bla.

@@
 \end{align*}
+Further discussion of $\Phi$ and its sequence of approximations has been relegated to appendix \ref{app:Phi} for sake of continuity.
 
@@
 \section{Properties of the approximate nonlinearities}
+\label{app:Phi}
 Let's discuss some of the properties of the sequence of approximations to the nonlinearity $\Phi$. To reiterate we defined
 \begin{equation*}
-\Phi_n(s) = \int_\mathbb{R}\left( \Phi(u-y) + \frac{u-y}{n}\right) \eta_{\frac{1}{n}}(y)dy
-\end{equation*}
+\Phi_n(u) = (\Phi * \varphi_{\frac{1}{n}})(u) - (\Phi * \varphi_{\frac{1}{n}})(0) + \frac{u}{n}.
+\end{equation*}
+It is obvious that $\Phi_n$ is infintely differentiable for each $n$, as well as $\Phi_n'(u) \geq \frac{1}{n}$. In addition the construction is so that $\Phi_n(0) = 0$.
+
+The first property we'll consider is summarised in the following proposition.
+\begin{proposition}
+If $\Phi$ is locally Lipschitz continuous, then $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
+\end{proposition}
+\begin{proof}
+The proof is done by getting out a crude, but sufficient estimate on the pointwise difference of $\Phi$ with its approximation. For any $u \in \mathbb{R}$, we have
+\begin{align*}
+|\Phi_n(u) - \Phi(u)| &= \left| \frac{u}{n} + \int_\mathbb{R}\Phi(u-y)\varphi_{\frac{1}{n}}(y)dy - \int_\mathbb{R}\Phi(y)\varphi_{\frac{1}{n}}(-y)dy - \Phi(u)\right| \\
+& \leq \frac{|u|}{n} + \int_\mathbb{R}\left| \Phi(u-y) - \Phi(u) - \Phi(y)\right| \varphi_{\frac{1}{n}}(y) dy \\
+& \leq \frac{|u|}{n} + \underset{y\in[-\frac{1}{n},\frac{1}{n}]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| + \mathrm{max}\{|\Phi (1/n) |,|\Phi(-1/n)| \}.
+\end{align*}
+Let now $K \subset \mathbb{R}$ be any compact set, and let $L_K$ be a Lipschitz constant for $\Phi$ over $K$. We then have for any $u \in K$ that
+\begin{equation*}
+|\Phi_n(u) - \Phi(u)| \leq \frac{1}{n}\left( L_K + \mathrm{sup}_{s \in K}|s| \right) + \mathrm{max}\{|\Phi (1/n) |,|\Phi(-1/n)| \}.
+\end{equation*}
+Since $K$ is bounded and $\Phi$ is continuous with $\Phi(0) = 0$ we have a bound independent of $u$, and therefore the convergence is uniform in $K$.
+\end{proof}
+
+In the remainder of this section we'll assume that $\Phi$ is continuous and strictly increasing, and that $\Phi( \pm \infty) = \pm \infty$.
+Then it is obvious that both $\Phi$ is both one-to-one and onto, and so has an inverse $\Phi^{-1}$.
+
+\begin{proposition}
+$\Phi^{-1}$ is strictly increasing, and continuous.
+\end{proposition}
+\begin{proof}
+Let's first prove that it's strictly increasing, which is easy.
+Take $y_1 < y_2$, and let $x_1$ and $x_2$ be so that $\Phi(x_i) = y_i$ for $i=1,2$.
+Then, because $\Phi$ is strictly increasing, we have $x_1 < x_2$.
+Which is the same as saying that
+\begin{equation*}
+y_1 < y_2 \quad \Rightarrow \quad \Phi^{-1}(y_1) < \Phi^{-1}(y_2),
+\end{equation*}
+i.e. $\Phi^{-1}$ is stricly increasing.
+
+Moving along, let $y \in \mathbb{R}$ and $x$ be so that $\Phi(x) = y$.
+Take any $\epsilon > 0$, and consider the interval $(x-\epsilon, x + \epsilon)$.
+We have that $(\Phi^{-1}(x-\epsilon), \Phi^{-1}(x+\epsilon))$ is non-empty because $\Phi^{-1}$ is strictly increasing, and $y$ is an element.
+Take now $\delta = \mathrm{min}\{ |y-\Phi^{-1}(x\pm\epsilon)|\} >0$, then for any $\tilde{y} \in (y-\delta, y + \delta)$ we have
+\begin{equation*}
+\tilde{y} > y-\delta \Rightarrow \Phi^{-1}(\tilde{y}) > \Phi^{-1}(y-\delta) \geq x-\epsilon
+\end{equation*}
+and
+\begin{equation*}
+\tilde{y} < y+\delta \Rightarrow \Phi^{-1}(\tilde{y}) < \Phi^{-1}(y+\delta) \leq x+\epsilon,
+\end{equation*}
+by using that $\Phi^{-1}$ is strictly increasing, as well as $\Phi(x-\epsilon) \leq y-\delta$ and $\Phi(x+\epsilon) \geq y + \delta$. This shows that $\Phi^{-1}$ is continuous.
+\end{proof}
+
+This result is also valid for $\Phi_n$ for every $n \in \mathbb{N}$, beacause they are all continuous and stricly increasing. We then have the following helpful result.
+
+\begin{proposition}
+$\Phi_n^{-1}$ converges pointwise to $\Phi^{-1}$.
+\end{proposition}
+
+\begin{proof}
+We need to consider $|\Phi_n^{-1}(y) - \Phi^{-1}(y)| = |x_n - x|$.
+Define $y_n = \Phi(x_n)$, then if we can show that $y_n \to y$ we can use the coninuity of $\Phi^{-1}$  to show that $x_n = \Phi^{-1}(y_n) \to \Phi^{-1}(y) = x$, and we would be done.
+It is now useful to see that
+\begin{align*}
+|y-y_n| &= |\Phi(x) - \Phi(x_n)| \\
+	&= |\Phi_n(x_n) - \Phi(x_n)|
+\end{align*}
+and hence we are in a nice position to use that $\Phi_n$ converges uniformly on compact sets, if we can show that $x_n$ is a bounded sequence. To that end we let $x_1<x$ be so that
+\begin{equation*}
+\Phi(x_1) = \Phi(x) -1
+\end{equation*}
+and similarly $x_2 > x$ by
+\begin{equation*}
+\Phi(x_2) = \Phi(x) +1.
+\end{equation*}
+Since $\Phi_n$ converges uniformly on $[x_1, x_2]$, there is an $N \in \mathbb{N}$ so that
+\begin{equation*}
+|\Phi_n(x) - \Phi(x)| < 1
+\end{equation*} 
+for every $x \in [x_1, x_2]$ and $n \geq N$. So take any $n \geq N$ and see that
+\begin{equation*}
+\Phi_n(x_2) \geq \Phi(x_2) - 1 = \Phi(x),
+\end{equation*}
+which by the strict monotonicity of $\Phi_n$ means that $x_n \leq x_2$.
+A similar argument yields $x_n \geq x_1$, and so we have that for every $n \geq N$ that $x_n \in [x_1, x_2]$.
+This means that $x_n$ is a bounded sequence, and hence we can use the unform convergence of $\Phi_n$ on compact sets to conclude that $y_n$ converges to $y$.
+Finally we have that
+\begin{equation*}
+x_n = \Phi_n^{-1} (y) = \Phi^{-1}(y_n) \overset{y_n\to y}{\to} \Phi^{-1}(y) = x
+\end{equation*}
+\end{proof}
+
+We can go even a step further with the last result of this section. It will require a bit more involved argument, but will operate on some familiar ideas from our latest proof.
+
+\begin{proposition}
+$\Phi_n^{-1}$ converges to $\Phi^{-1}$ uniformly on compact sets.
+\end{proposition}
+
+\begin{proof}
+Let $K \subset \mathbb{R}$ be a compact set, and fix $\epsilon > 0$. Our aim will be to establish that there is $N \in \mathbb{N}$ so that 
+\begin{equation*}
+|x-x_n| = |\Phi^{-1}(y) - \Phi_n^{-1}(y)| < \epsilon
+\end{equation*}
+for every $y \in K$ and $n \geq N$.
+
+Define $\tilde{K} = \Phi^{-1}(K)$ which is compact since $\Phi^{-1}$ is continuous. We will want to consider
+\begin{equation*}
+\Phi(x+\epsilon) - \Phi(x) > 0
+\end{equation*}
+for $x \in \tilde{K}$, so let $L$ be a Lipschitz constant for $\Phi$ over $\tilde{K}+[0,\epsilon]$. Our first claim is that
+\begin{equation*}
+\mathrm{inf}_{x \in \tilde{K}} \Phi(x+\epsilon) - \Phi(x) > 0.
+\end{equation*}
+It is obvious that the infimum is nonnegative, so we need to show that it is not zero. Assume to the contrary that for every $n \in \mathbb{N}$ there is an $x_n$ so that
+\begin{equation*}
+0 < \Phi(x_n + \epsilon) - \Phi(x_n) < \frac{1}{n}
+\end{equation*}
+which yields a sequence $(x_n)_n$ in $\tilde{K}$. Since $\tilde{K}$ is compact we have a subsequence $(x_{n_j})_j$ that converges to some $ \tilde{x} \in \tilde{K}$. But then
+\begin{align*}
+|\Phi(\tilde{x} + \epsilon) - \Phi(\tilde{x})| & \leq |\Phi(\tilde{x}+\epsilon) - \Phi(x_{n_j} + \epsilon)| + |\Phi(x_{n_j}+\epsilon) - \Phi(x_{n_j})| \\
+&+ |\Phi(x_{n_j}) - \Phi(\tilde{x})| \\
+&\leq 2L|\tilde{x}-x_{n_j}| + \frac{1}{n_j},
+\end{align*}
+Which can be made arbitrarily small.
+Hence, $\Phi(\tilde{x}+\epsilon) - \Phi(\tilde{x}) = 0$, which is in stark contrast to $\Phi$ being strictly increasing.
+This proves our claim and we can with some confidence say that there is a $\delta_+>0$ so that $\Phi(x+\epsilon) - \Phi(x) \geq \delta_+$ for every $x \in \tilde{K}$.
+
+We can do quite a similar argument on
+\begin{equation*}
+\Phi(x) - \Phi(x-\epsilon) > 0,
+\end{equation*}
+to establish a $\delta_- > 0$ so that $\Phi(x) - \Phi(x-\epsilon) \geq \delta_-$ for every $x\in \tilde{K}$.
+
+Let now $\delta = \mathrm{min}\{\delta_+, \delta_- \}>0$, and there is by the uniform convergence of $\Phi_n$ an $N \in \mathbb{N}$ so that
+\begin{equation*}
+|\Phi_n(x) - \Phi(x)| < \delta,
+\end{equation*}
+for every $x \in \tilde{K}+[\epsilon, \epsilon]$ and $n \geq N$. Take now any $y \in K$ and let $x$ and $x_n$ be so that
+\begin{equation*}
+\Phi(x) = \Phi_n(x_n) = y.
+\end{equation*}
+See now that
+\begin{align*}
+\Phi_n(x+\epsilon) &> \Phi(x+\epsilon) -\delta \\
+&\geq    \Phi(x+\epsilon) -\delta_+ \\
+&\geq \Phi(x+\epsilon) - (\Phi(x+\epsilon) - \Phi(x)) \\
+&= \Phi(x).
+\end{align*}
+So we have $\Phi_n(x+\epsilon) < y$, which implies that $x_n < x+\epsilon$ since $\Phi_n$ is strictly increasing. Quite similarly we can establish that
+\begin{align*}
+\Phi_n(x-\epsilon) &< \Phi(x-\epsilon) + \delta \\
+&\leq \Phi(x-\epsilon) + \delta_- \\
+&\leq \Phi(x-\epsilon) + (\Phi(x) - \Phi(x-\epsilon)) \\
+&= \Phi(x),
+\end{align*}
+which implies that $x_n > x-\epsilon$. In toto we have that whenever $n\geq N$
+\begin{equation*}
+|\Phi^{-1}(y) - \Phi_n^{-1}(y)| = |x - x_n| < \epsilon
+\end{equation*}
+for every $y \in K$, which is exactly what we wanted to prove.
+
+\end{proof}
 

### 2014-11-12 draft_project.tex
...

@@
 
+\subsection{Basic sets and notation}
+Before delving into the actual the actual analysis of our problem, let's just get assure ourselves that we're on the same page when it comes to notation of various sets and function spaces.
+
+The begin, we let $\Omega \subset \mathbb{R}^d$ be an open, bounded and simply connected set, with boundary $\partial \Omega$.
+This will denote our spatial domain, and so we let write $Q_T = \Omega \times (0,T]$ to mean the space-time cylinder up to a time $T$, which can be both finite or infinite, and it will be stated clearly when we need to assume $T < \infty$.
+The last set pertaining to the space-time domain we'll need is the parabolic boundary $\Gamma_T = (\partial \Omega \times [0,T]) \cup (\Omega\times \{t=0\})$.
+
+Most, if not all, of the notation concerning function spaces will follow the notation in \citep{evans} (see in particular Ch. 5).
+
 \subsection{Problem statement}
-I will consider on the following Dirichlet problem:
+We will consider on the following Dirichlet problem:
 \begin{equation}
@@
 \end{equation}
-
-The reason for this reformulation is that many of the results presented in this section supposes a particular condition on the coefficients $a^i(x,t,u,p)$.
-The condition is that there are constants $0 < \nu < \mu < \infty $ so that
+We will need to assume that $a^i$ for every $i$ as well as $a$ are continuous functions with respect to all variables.
+
+In addition we assume that there are constants $0 < \nu < \mu < \infty $ so that
 \begin{equation}
@@
 \end{equation}
-We will in this section assume this to be true. I.e. that $\Phi'(u)$ is bounded and strictly positive.
+We will in this section assume this to be true. I.e. that $\Phi'(u)$ is bounded from above as well as away from zero.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{lemma:comparison}
-Let $u,v \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two solutions of (\ref{HDP}) with initial data $u_0$, $v_0$ and loading $f$, $\tilde{f}$ respectively.
-Further, assume that $v_0 \geq u_0$ in $\Omega$ and  $\tilde{f} \geq f$ in $Q_T$.
-Then either $u < v$ in $Q_T$ or $u=v$.
+Let $\Phi \in C^2(\mathbb{R})$ and satisfy (\ref{uniform_parabGPME}), and let $u,v \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two solutions of the General Porous Medium Equation (\ref{GPME}) in $Q_T$ with initial data $u_0$, $v_0$, loading $f$, $\tilde{f}$ respectively as well as prescribed Dirchlet data on the boundary.
+Further, assume that $v\big|_{\Gamma_T} \geq u\big|_{\Gamma_T}$, and  $\tilde{f} \geq f$ in $Q_T$.
+Then $u \leq v$ in $Q_T$.
 \end{lemma}
 \begin{proof}
-We set $w=v-u$ and see that $w$ then solves
+The strategy will be to set $w = v-u$ and derive a initial- and boundary value problem that  $w$ solves. First off, we see that
 \begin{align*}
 \partial_t w &= \Delta(\Phi(v) - \Phi(u)) + (\tilde{f}-f) \\
-			&= \Delta(\Phi(w+u) - \Phi(v-w)) + (\tilde{f}-f).  
-\end{align*}
-and $w(x,0) = v_0(x) - u_0(x)$ as well as satisfies the homogeneous Dirichlet boundary condition.
-We need to check that the problem satisfies (\ref{uniform_parabolicity}), and to that end we notice that
-\begin{equation*}
-\Delta(\Phi(w+u) - \Phi(v-w)) = \nabla \cdot \left(\Phi'(w+u)(\nabla w + \nabla u) - \Phi'(v-w)(\nabla v - \nabla w) \right).
-\end{equation*}
-Treating $u$ and $v$ as given parameters of the IVBP we get
-\begin{equation*}
-a^i = (\Phi'(w+u) + \Phi'(v-w))\partial_{x_i}w,
-\end{equation*}
-and since (\ref{uniform_parabGPME}) is satisfied the problem is uniformly parabolic.
-We have
-\begin{equation*}
-\partial_tw - \Delta(\Phi(w+u) - \Phi(v-w)) = \tilde{f}-f \geq 0 
-\end{equation*}
-and we can use the second part of the strong maximum principle to deduce that
-\begin{equation*}
-w \geq \underset{\overline{Q_T}}{\mathrm{min}}w = \underset{\Gamma_T}{\mathrm{min}}w.
-\end{equation*}
-By the initial- and boundary data of $w$ we see that
-\begin{equation*}
-\underset{\Gamma_T}{\mathrm{min}}w = 0,
-\end{equation*}
-and so
-\begin{equation*}
-w \geq 0 \quad \Rightarrow  \quad v \geq u.
-\end{equation*}
-
-We conclude the proof by seeing that if $u=v$ at some points in $Q_T$ the strong maximum principle implies that $u=v$ everywhere. 
+&= \Delta ( \Phi(w+u) - \Phi(v-w) ) + (\tilde{f}-f)
+\end{align*}
+So, when treating $u$ and $v$ as parameters, we can formulate the problem
+\begin{equation}
+\begin{cases}
+\partial_t w &= \Delta ( \Phi(w+u) - \Phi(v-w) ) + (\tilde{f}-f), \quad \text{ in } Q_T \\
+w(x,0) &= v_0(x) - u_0(x), \quad \text{ in } \Omega \\
+w(x,t) &= v(x,t) - u(x,t), \quad \text{ on } \partial \Omega \times [0,T].
+\end{cases}
+\end{equation}
+Now we want to use the strong maximum principle, so we should find out what $a^i$ and $a$ are. We have that
+\begin{align*}
+\Delta ( \Phi(w+u) - \Phi(v-w) )&= \sum_{i=1}^d \partial_{x_i}\left(\Phi'(w+u)(\partial_{x_i}w + \partial_{x_i}u) - \Phi'(v-w)(\partial_{x_i}v-\partial_{x_i}w) \right),
+\end{align*} 
+and seeing as $u$ and $v$ should be considered parameters to this problem we can establish that
+\begin{equation*}
+\begin{cases}
+a^i(x,t,w,p) &= (\Phi'(w+u) + \Phi'(v-w))p_i \\
+a(x,t,w,p) &= \sum_{i=1}^d \partial_{x_i}\left( \Phi'(u+w)\partial_{x_i}u - \Phi'(v-w)\partial_{x_i}v\right).
+\end{cases}
+\end{equation*}
+The $a^i$'s are continuous from the assumptions on $\Phi$, and in addition it satisfies (\ref{uniform_parabGPME}) inherited from $\Phi$.
+The $a$ is continuous since both $u$ and $v$ are in $C^{2,1}(Q_T)$ and $\Phi \in C^2(\mathbb{R})$.
+
+We can thus use the maximum principle together with $\tilde{f}-f \geq 0$ to deduce that
+\begin{equation*}
+w \geq \mathrm{min}_{\overline{Q}_T}w = \mathrm{min}_{\Gamma_T}w.
+\end{equation*}
+By assumption $\mathrm{min}_{\Gamma_T}w \geq 0$, so $v \geq u$. We conclude the proof that seeing that if $u=v$ at some internal point $(x_0,t_0) \in Q_T$, then $u=v$ in $Q_{t_0}$.
 \end{proof}
-
-\setcounter{rem}{0}
-\begin{rem}
-We could improve somewhat on this result by having $v \geq u$ on $\partial \Omega \times [0,T]$. All the steps in the proof works, in particular
-\begin{equation*}
-\underset{\Gamma_T}{\mathrm{min}}w \geq 0
-\end{equation*} 
-still holds.
-\end{rem}
 
@@
 \begin{lemma}
+Assume $\Phi \in C^2(\mathbb{R})$ and satisfy (\ref{uniform_parabGPME}).
 If $u \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ is a solution of (\ref{HDP}), and $u_0$ is bounded in $\Omega$ and $f$ bounded in $Q_T$, then
@@
 \begin{proof}
-We start by defnining $M_1 = \mathrm{max}\{0, \mathrm{sup}_\Omega(u_0) \}$, and $N_1 = \mathrm{max}\{0, \mathrm{sup}_{Q_T}(f) \}$. With $v(x,t) = M_1 + N_1t$, it solves
+We start by defnining $M_1 = ||u_0^+||_{L^\infty(\Omega)} $, and $N_1 = ||f^+||_{L^\infty(Q_T)}$, where $(\cdot)^+ = \mathrm{max} \{ 0,\cdot \}$. With $v(x,t) = M_1 + N_1t$, it solves
 \begin{equation*}
@@
 
-Similarly we define $M_2 = \mathrm{min}\{ 0, \mathrm{inf}_\Omega(u_0) \}$, and $N_2 = \mathrm{min}\{ 0, \mathrm{inf}_{Q_T}(f) \}$, to get the lower bound
+Similarly we define $M_2 = -||u_0^-||_{L^\infty(\Omega)}$, and $N_2 = -||f^-||_{L^\infty(Q_T)}$.
+To avoid any possible confusion, here $(\cdot)^- = \mathrm{min}\{0, \cdot \}$.
+We use the same reasoning to get the lower bound
 \begin{equation*}
@@
 \begin{equation*}
-||u_0||_{L^\infty(\Omega)} = \mathrm{max}\{ \mathrm{sup}_\Omega(u_0), -\mathrm{inf}_\Omega (u_0)\} = \mathrm{max}\{|M_1|,|M_2|\},
+||u_0||_{L^\infty(\Omega)} = \mathrm{max}\{ ||u_0^+||_{L^\infty(\Omega)}, ||u_0^-||_{L^\infty(\Omega)} \} = \mathrm{max}\{|M_1|,|M_2|\},
 \end{equation*}
@@
 5]{vazquez2007porous} quite closely.
-However, the proofs are worked out in greater detail than presented there, and we will not assume that $\Phi$ is strictly increasing, but rather try to handle the degenerate case.
+However, the proofs are worked out in greater detail than presented there.
+We will, unless stated otherwise, assume that $\Phi$ is an increasing function, and not only stricly increasing.
 
@@
 Now we jump in with trying to prove existence of signed, weak energy solutions.
-Following closely the proof provided in \citep{vazquez2007porous}, but now lifting the assumption that $\Phi$ is strictly increasing, and rather having that it is only nondecreasing.
-Another useful addition to proof will be that we will also incorporate a $L^1$-contractivity result.
-
-The proof will use an approximate problem which admits a unique solution from theorem \ref{thm:classical_existence}, and then employing the Rellich compactness argument (cf.
-appendix \ref{sec:compactness} to get a limit which hopefully will be a weak energy solution.
+Following closely the proof provided in \citep{vazquez2007porous}.
+We will first prove existence of weak energy solutions under the assumption that $\Phi$ is strictly increasing, and then extend the result to the case of $\Phi$ being nondecreasing.
+Another useful addition to the proof will be that we will also incorporate a $L^1$-contractivity result.
+
+The proof will use an approximate problem which admits a unique solution from theorem \ref{thm:classical_existence}, and then employ the Rellich compactness argument (cf.
+appendix \ref{sec:compactness}) to get a limit which hopefully will be a weak energy solution.
 
@@
 
-We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$. We also ask that $|u_{0,n}| \leq $min$\{n,u_0\}$.
-
-Apparently, also according to \citep{vazquez2007porous}, we also approximate $f$ by a sequnce of functions $f_n$ that converges to $f$ in $L^p(Q_T)$ for all\footnote{Not sure if \textit{sic}...} $p<\infty$, and is so that $|f_n| \leq f$ for all $n$.
+We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$. We also ask that $|u_{0,n}| \leq $min$\{n,|u_0|\}$.
+
+Apparently, also according to \citep{vazquez2007porous}, we also approximate $f$ by a sequnce of functions $f_n$ that converges to $f$ in $L^p(Q_T)$ for all\footnote{Not sure if \textit{sic}...} $p<\infty$, and is so that $|f_n| \leq |f|$ for all $n$.
 
@@
 	after exactly the same argument as we did with (\ref{using_Poincare}). After putting it back
-	\begin{equation*}
+	\begin{equation}
+	\label{exist_proof_spatial}
 	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
-	\end{equation*}
+	\end{equation}
 	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
@@
 	\end{equation*}
-	by our assumption on the approximation. In addition
-	\begin{equation*}
-	\int_\Omega \Psi_n(u_{0,n})dx = \int_\Omega \left[ \int_0^{u_{0,n}(x)} \int_\mathbb{R} \left(\Phi(y)+\frac{y}{n}\right)\eta_{\frac{1}{n}}(s-y)dy ds \right] dx,
-	\end{equation*}
-	and $\eta_{\frac{1}{n}}(s-\cdot)$ has support in $[s-\frac{1}{n}, s + \frac{1}{n}]$. Therefore, by the monotonicity of $\Phi$, 
-	\begin{equation*}
-	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega \left[ \int_0^{u_{0,n}(x)}\Phi \left(s+\frac{1}{n} \right)ds + \int_0^{u_{0,n}}\frac{s+\frac{1}{n}}{n}ds \right] dx,
-	\end{equation*}
-	which after a variable transformation yields
-	\begin{align*}
-	\int_\Omega \Psi_n(u_{0,n})dx &\leq \int_\Omega \left[ \int_{\frac{1}{n} }^{u_{0,n}(x) + \frac{1}{n} } \Phi(s)ds + \frac{u_{0,n}(x)^2}{2n} + \frac{u_{0,n}(x)}{n^2} \right] dx \\
-	&\leq \int_\Omega \left[ \Psi\left(u_{0,n} +\frac{1}{n}\right) - \Psi\left(\frac{1}{n}\right) + \frac{1}{2n}\left(u_{0,n} + \frac{1}{n}\right)^2 \right] dx.
-	\end{align*}
-	Using now that $|u_{0,n}| \leq u_0$ and that $\Omega$ is a bounded set, we get a bound on this integral independent of $n$. And so $\iint_{Q_T} |\nabla w_n|^2 dxdt$ has a bound independent of $n$.
+	by our assumption on the approximation.
+
+	For the $\Psi$-term on the right hand side we start by recalling that we define
+	\begin{equation*}
+	\Psi_n(u) = \int_0^{u}\Phi_n(s)ds,
+	\end{equation*}
+	from which it is to see that $\Psi_n(u) \leq 0$ for every $u \in \mathbb{R}$. It is also very much worthwhile to see that because $\Phi_n$ is monotone for every $n$ we have the estimate
+	\begin{equation*}
+	|\Psi_n(u)| \leq |\Phi_n(u)u|.
+	\end{equation*}
+	This leads to
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega |\Phi_n(u_{0,n})u_{0,n}|dx	
+	\end{equation*}
+	Using now that $|u_{0,n}| \leq u_0$ and that $\Phi_n$ is monotone we can remove some of the dependence on $n$ as
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega |\Phi_n(u_{0})u_{0}|dx.
+	\end{equation*}
+	Now we do as in appendix \ref{app:Phi} to get a bound in $\Phi_n$ in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
+	\begin{align*}
+	|\Phi_n(u) - \Phi(u)| &= \left|\frac{u}{n} + \int_\mathbb{R}\left( \Phi(u-y) - \Phi(u) - \Phi(y)\right)\varphi_{\frac{1}{n}}(y)dy \right| \\
+	&\leq \frac{|u|}{n} + \underset{y\in [-1/n, 1/n]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| + \mathrm{max}\{|\Phi(-1/n)|, |\Phi(1/n)|\} \\
+	&\leq |u| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\},
+	\end{align*}
+	where we have used that $\mathrm{supp}(\varphi_{\frac{1}{n}})\subset [-1/n, 1/n]$ as well as that $\Phi$ is monotone. This, when considering $u_0$, we have
+	\begin{align*}
+	|\Phi_n(u_0)| &\leq |\Phi(u_0)| + |u_0| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u_0-y) - \Phi(u_0)| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
+	&= K.
+	\end{align*}
+	All terms are bounded since $u_0$ is bounded, and so we get the crude, but sufficient estimate
+	\begin{equation*}
+	\int_\Omega \Psi_n(u_{0,n})dx \leq K ||u_0||_{L^1(\Omega)},
+	\end{equation*}
+	which is finite from $u_0 \in L^1(\Omega)$.
+Most importantly, this shows that the left hand side of (\ref{exist_proof_spatial}) is bounded independently of $n$, which immediately implies that $\nabla w_n$ is a bounded sequence in $L^2(Q_T)$.
 

### 2014-11-12 draft_project.tex
Skrevet enda litt mer.

@@
 \begin{lemma}
+\label{lem:existence_part1}
 Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$, and $\partial_t f$ are bounded, $\partial \Omega \in C^{2+\alpha}$, and $\Phi$ is locally lipschitz continuous.
@@
 
-	\item[Convergence of $u_{n_j}$:] Since all $u_{n_j}$ are classical solutions, they're also weak solutions.
-Therefore, when putting $u_{n_j}$ and $u_{n_k}$ into (\ref{weak}) and taking their difference,
-	\begin{align*}
-	-\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt &= -\iint_{Q_T}\nabla(w_{n_j} - w_{n_k})\cdot \nabla \eta dxdt \\
-	&+ \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0}dx \\
-	&+ \iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt 
-	\end{align*}	 
-	pops out. Restricting ourselves to only $\eta \in C^\infty(Q_T)$ that vanish on $\partial \Omega \times [0,T]$ and for $t=T$, and doing integration by parts on the term involving $w$, yields
-	\begin{align*}
-	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| &\leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| \\
-	&+ \bigg| \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0} dx \bigg| \\
-	 &+  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|.
-	\end{align*}
-	 All terms can be made arbitrarily small by the convergences of $w_{n_j}$, $u_{0,n}$ and $f_n$ respectively.
-And so $\partial_t u_{n_j}$ in the weak sense is a Cauchy sequence in $L^1_{loc}(Q_T)$, and since $Q_T$ is bounded, also in $L^1(Q_T)$.
-By the completeness of $L^1(Q_T)$, it must also converge.
-The primitive of this limit is then determined up to a constant independent of $t$.
-However, the limit is completely determined when taking into account the initial data.
-
-	 To see this we call $v$ the weak time derivative of the limit of $u_{n_j}$, and $g$ its primitive. That is, for every $\eta \in C^\infty_c (Q_T)$ we have
-	 \begin{equation*}
-	 \iint_{Q_T} g\partial_t\eta dxdt = -\iint_{Q_T}v\eta dxdt.
-	 \end{equation*}
-	 In addition we impose the condition that
-	 \begin{equation*}
-	 \lim_{\epsilon \to 0} \iint_{Q_T}g \eta_\epsilon dxdt = \frac{1}{2}\int_\Omega u_0dx,
-	 \end{equation*}
-	 where $\eta_\epsilon$ is here the standard mollifier with respect to only the temporal dimension.
-Note that the factor $\frac{1}{2}$ comes from the mollifier being symmetric about the origin and we only integrate over positive values of $t$.
-With these two conditions $g$ can be uniquely determined.
-So $u_{n_j}$ converges in $L^1(Q_T)$ and we call the limit $u$.
-
-	\item[Showing that $w=\Phi(u)$:] It is sensible to break this part into two similar steps.
-First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges pointwise to $\Phi(u_k)$.
-Let now $\psi$ be a function in $L^1(Q_T)$ with compact support.
-We want to show that
-	\begin{equation*}
-	\iint_{Q_T} \Phi_n(u_k) \psi dxdt \to \iint_{Q_T}\Phi(u_k)\psi dxdt.
-	\end{equation*}
-	This is accomplished using the Dominated Convergence Theorem (DCT). So we note that since $|u_k| \leq C$, 
-	\begin{align*}
-    |\Phi_n(u_k)| &\leq \int_\mathbb{R} \left| \Phi(u_k-y) + \frac{u_k-y}{n}\right|\eta_{\frac{1}{n}}(y)dy \\
-    &\leq \underset{|s|\leq C+1/n}{sup}\left| \Phi(s) + \frac{s}{n}\right| < \infty,
-	\end{align*}
-	due to the support of $\eta_{\frac{1}{n}}$ being contained in $\left[ -\frac{1}{n}, \frac{1}{n}\right]$.
-Thus we set $M = \mathrm{sup}_{|s|\leq C+1}\left|\Phi(s) + s\right|$.
-Then $|\Phi_n(u_k)\psi| \leq M|\psi| \in L^1(Q_T)$, and we can use the DCT to establish that the proposed limit holds.
-
-	An almost identical argument is valid for showing that
-	\begin{equation*}
-	\iint_{Q_T}\Phi(u_n)\psi dxdt \to \iint_{Q_T}\Phi(u)\psi dxdt,
-	\end{equation*}		
-	only now using $M = \mathrm{sup}_{|s|\leq C}|\Phi(s)|$. Thus, we can construct a diagonal argument for the sequence $\Phi_n(u_n)$ to get that
-	\begin{equation}
-	\iint_{Q_T} w\psi dxdt = \lim_{n_j \to \infty} \iint_{Q_T}\Phi_{n_j}(u_{n_j})\psi dxdt = \iint_{Q_T} \Phi(u) \psi dxdt.
-	\end{equation}
-	Seeing as $\psi$ was arbitrary we get that $\Phi(u) = w$ almost everywhere.
-
-	Lastly, they're weak derivatives also agree, since
-	\begin{equation*}
-	\iint_{Q_T}\nabla(\Phi(u) - w) \cdot \psi dxdt = -\iint_{Q_T}(\Phi(u)-w)\nabla \cdot \psi dxdt = 0 
-	\end{equation*}
-	for every test function $\psi$.
-	 And so the energy inequality (\ref{energy_ineq}) continues to hold as
-	\begin{equation}
-	\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \int_{Q_T} f\Phi(u)dxdt.
-	\end{equation}
+	\item[Convergence of $u_{n_j}$:] Both $\Phi$ and its approximations $\Phi_n$ all admit a continuous inverse, and so
+	\begin{equation*}
+	u_{n_j} = \Phi_{n_j}^{-1}(w_{n_j}).
+	\end{equation*}
+	We now simply have by the triangle inequality
+	\begin{align*}
+	|u_{n_j} - \Phi^{-1}(w)| &= |\Phi_{n_j}^{-1}(w_{n_j}) - \Phi^{-1}(w)| \\
+		&\leq |\Phi_{n_j}^{-1}(w_{n_j}) - \Phi^{-1}(w_{n_j})| + |\Phi^{-1}(w_{n_j}) - \Phi^{-1}(w)|.
+	\end{align*}
+	 We have that $w_{n_j}$ is a bounded sequence, seeing as $u_{n_j}$ is bounded.
+Hence we can use proposition \ref{prop:inverse_uniform} to make the first term in the above inequality arbitrarily small.
+The second term is controlled by the observation that since $w_{n_j}$ converges to $w$ in $L^2(Q_T)$, the convergence is also pointwise, and the continuity of $\Phi^{-1}$.
+That means that
+	 \begin{equation*}
+	 u_{n_j} \to u = \Phi^{-1}(w)
+	 \end{equation*}
+	 pointwise. We immediately see that $\Phi(u) = w$.
+
+	 More importantly, since we have the uniform bound $u_{n_j} \leq M$ in $Q_T$ we can use the Dominated Convergence Theorem to state that $u_{n_j} \to u$ in $L^1(Q_T)$.
 
@@
 
+\end{proof}
+
+\subsubsection{$\Phi$ no longer locally Lipschitz}
+We proceed by generalising the result of \ref{thm:weak_existence} to the case when $\Phi$ is no longer locally Lipschitz.
+
+\begin{lemma}
+Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$ and $\partial_t f$ are bounded.
+\end{lemma}
+
+\begin{proof}
+We begin this proof in the exact same manner as with the proof of lemma \ref{lem:existence_part1}, by setting up an approximate problem using $\Phi_n$, $u_{0,n}$ and $f_n$ as smooth approximations which yields a sequence of classical solutions $u_n$.
+We again define $w_n = \Phi_n(u_n)$.
+
+Looking back at the proof for lemma \ref{lem:existence_part1} the only part where we actually needed $\Phi$ to be locally Lipschitz was in controlling the temporal derivative of $\Phi_n(u_n)$ in $L^2(Q_T)$.
+This means we can in this case no longer say that $w_n$ is a bounded sequence in $H^1(Q_T)$.
+
+The strategy for showing that $u_n$ converges to a weak solution will be similar to that of lemma \ref{lem:existence_part1}, only now we will use the Rellich-Kondrachov Compactness Theorem on another sequence than $w_n$.
+I.e.
+we need a bounded sequence in $H^1(Q_T)$.
+To that end we define for $u \in \mathbb{R}$
+\begin{equation}
+Z_n(u) = \int_0^u \mathrm{min}\{1, \Phi_n'(s)\} ds,
+\end{equation}
+which is easily seen to be globally Lipschitz. In addition $Z_n'(u) \leq 1$ and $Z_n'(u) \leq \Phi_n(u)$.
+
+We then go on to define
+\begin{equation}
+z_n(x,t) = Z_n(u_n(x,t)).
+\end{equation}
+
+See now that
+\begin{align*}
+\nabla z_n &= Z_n'(u_n)\nabla u_n \\
+	&\leq \Phi_n'(u_n)\nabla u_n \\
+	&= \nabla \Phi_n(u_n) \\
+	&= \nabla w_n,
+\end{align*}
+which means that $|\nabla z_n|^2 \leq |\nabla w_n|^2$ in all of $Q_T$.
 \end{proof}
@@
 \begin{proposition}
+\label{prop:inverse_uniform}
 $\Phi_n^{-1}$ converges to $\Phi^{-1}$ uniformly on compact sets.
@@
 for every $y \in K$, which is exactly what we wanted to prove.
-
+\end{proof}
+
+Looking back at this proof, the only things we needed were that $\Phi$ is strictly increasing and continuous, and is locally Lipschitz, and that $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
+So we can generalise our result in the following lemma.
+
+\begin{lemma}
+\label{lem:Inverse_uniform_general}
+Let $f: \mathbb{R} \to \mathbb{R}$ be a strictly monotone, continuous function, and let $\{f_n\}$ be a family of strictly monotone, continuous functions that converge to $f$ uniformly on compact sets.
+Then $f_n^{-1}$ converges to $f^{-1}$ uniformly on compact sets.
+\end{lemma}
+
+\begin{proof}
+The proof is identical to that of proposition \ref{prop:inverse_uniform} with only minor alterations in notation.
 \end{proof}

### 2014-11-12 stuff_somewhat_organised.tex
Begynt å skrive på utkast da veit du.
Skrevet enda litt mer.

@@
 
+\section{CLIPBOARD}
+Since all $u_{n_j}$ are classical solutions, they're also weak solutions. Therefore, when putting $u_{n_j}$ and $u_{n_k}$ into (\ref{weak}) and taking their difference, 
+	\begin{align*}
+	-\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt &= -\iint_{Q_T}\nabla(w_{n_j} - w_{n_k})\cdot \nabla \eta dxdt \\
+	&+ \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0}dx \\
+	&+ \iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt 
+	\end{align*}	 
+	pops out. Restricting ourselves to only $\eta \in C^\infty(Q_T)$ that vanish on $\partial \Omega \times [0,T]$ and for $t=T$, and doing integration by parts on the term involving $w$, yields
+	\begin{align*}
+	\bigg|\iint_{Q_T}(u_{n_j} - u_{n_k})\partial_t \eta dxdt \bigg| &\leq \bigg|\iint_{Q_T} (w_{n_j} - w_{n_k})\Delta\eta dxdt \bigg| \\
+	&+ \bigg| \int_\Omega (u_{0,n_j} - u_{0,n_k})\eta\big|_{t=0} dx \bigg| \\
+	 &+  \bigg|\iint_{Q_T}(f_{n_j} - f_{n_k})\eta dxdt\bigg|.
+	\end{align*}
+	 All terms can be made arbitrarily small by the convergences of $w_{n_j}$, $u_{0,n}$ and $f_n$ respectively.
+And so $\partial_t u_{n_j}$ in the weak sense is a Cauchy sequence in $L^1_{loc}(Q_T)$, and since $Q_T$ is bounded, also in $L^1(Q_T)$.
+By the completeness of $L^1(Q_T)$, it must also converge.
+The primitive of this limit is then determined up to a constant independent of $t$.
+However, the limit is completely determined when taking into account the initial data.
+
+	 To see this we call $v$ the weak time derivative of the limit of $u_{n_j}$, and $g$ its primitive. That is, for every $\eta \in C^\infty_c (Q_T)$ we have
+	 \begin{equation*}
+	 \iint_{Q_T} g\partial_t\eta dxdt = -\iint_{Q_T}v\eta dxdt.
+	 \end{equation*}
+	 In addition we impose the condition that
+	 \begin{equation*}
+	 \lim_{\epsilon \to 0} \iint_{Q_T}g \eta_\epsilon dxdt = \frac{1}{2}\int_\Omega u_0dx,
+	 \end{equation*}
+	 where $\eta_\epsilon$ is here the standard mollifier with respect to only the temporal dimension.
+Note that the factor $\frac{1}{2}$ comes from the mollifier being symmetric about the origin and we only integrate over positive values of $t$.
+With these two conditions $g$ can be uniquely determined.
+So $u_{n_j}$ converges in $L^1(Q_T)$ and we call the limit $u$.
+
+\subsection{part II}
+
+	\item[Showing that $w=\Phi(u)$:] It is sensible to break this part into two similar steps.
+First, fix $k \in \mathbb{N}$ and consider the sequence $\Phi_n(u_k)$, which converges pointwise to $\Phi(u_k)$.
+Let now $\psi$ be a function in $L^1(Q_T)$ with compact support.
+We want to show that
+	\begin{equation*}
+	\iint_{Q_T} \Phi_n(u_k) \psi dxdt \to \iint_{Q_T}\Phi(u_k)\psi dxdt.
+	\end{equation*}
+	This is accomplished using the Dominated Convergence Theorem (DCT). So we note that since $|u_k| \leq C$, 
+	\begin{align*}
+    |\Phi_n(u_k)| &\leq \int_\mathbb{R} \left| \Phi(u_k-y) + \frac{u_k-y}{n}\right|\eta_{\frac{1}{n}}(y)dy \\
+    &\leq \underset{|s|\leq C+1/n}{sup}\left| \Phi(s) + \frac{s}{n}\right| < \infty,
+	\end{align*}
+	due to the support of $\eta_{\frac{1}{n}}$ being contained in $\left[ -\frac{1}{n}, \frac{1}{n}\right]$.
+Thus we set $M = \mathrm{sup}_{|s|\leq C+1}\left|\Phi(s) + s\right|$.
+Then $|\Phi_n(u_k)\psi| \leq M|\psi| \in L^1(Q_T)$, and we can use the DCT to establish that the proposed limit holds.
+
+	An almost identical argument is valid for showing that
+	\begin{equation*}
+	\iint_{Q_T}\Phi(u_n)\psi dxdt \to \iint_{Q_T}\Phi(u)\psi dxdt,
+	\end{equation*}		
+	only now using $M = \mathrm{sup}_{|s|\leq C}|\Phi(s)|$. Thus, we can construct a diagonal argument for the sequence $\Phi_n(u_n)$ to get that
+	\begin{equation}
+	\iint_{Q_T} w\psi dxdt = \lim_{n_j \to \infty} \iint_{Q_T}\Phi_{n_j}(u_{n_j})\psi dxdt = \iint_{Q_T} \Phi(u) \psi dxdt.
+	\end{equation}
+	Seeing as $\psi$ was arbitrary we get that $\Phi(u) = w$ almost everywhere.
+
+	Lastly, they're weak derivatives also agree, since
+	\begin{equation*}
+	\iint_{Q_T}\nabla(\Phi(u) - w) \cdot \psi dxdt = -\iint_{Q_T}(\Phi(u)-w)\nabla \cdot \psi dxdt = 0 
+	\end{equation*}
+	for every test function $\psi$.
+	 And so the energy inequality (\ref{energy_ineq}) continues to hold as
+	\begin{equation}
+	\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \int_{Q_T} f\Phi(u)dxdt.
+	\end{equation}
+
 \end{appendices}

### 2014-11-13 trygve_b_written_assignment3.tex
Oppgave 3 i SPRÅK3501.

\documentclass[11pt, a4paper]{article}
\usepackage{mathptmx}
\usepackage{mathtools}
\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsthm}
\usepackage{remreset}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\usepackage{lmodern}
\usepackage{setspace}

\begin{document}
\onehalfspacing

\title{Written assignment 3 in SPRÅK3501}
\author{Trygve Bærland}
\maketitle

\section*{Abstract for my project.}
This project is an exposition of the General Porous Medium Equation, which contains both the porous medium equation and the heat equation as special cases as well as the Stefan problem when considering the degenerate case. The first part is devoted to presenting some theory on classical solution with attention paid to important estimates. The comparison principle and $L^1$-contractivity, as well as estimates on both the spatial and temporal derivatives are derived. Concluding the discussion of classical solutions is an existence result under quite strict assumptions on the initial data, loading and nonlinearity.

 The theory is then extended to a weak setting, and a definition of weak solutions is provided. Again, proving well posedness will be the main focus, and to that end the concept of weak energy solutions is introduced. In this framework existence, uniqueness and stability is proved, and attention is paid to showing that the estimates for classical solutions are inherited by weak solutions. This is first done for the nondegenerate case, and the project report concludes by extending the well posedness results to the degenerate case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	BIBLIOGRAPHY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\bibliographystyle{plain}
\bibliography{project_bibliography.bib}
\end{document}

### 2014-11-17 draft_project.tex
BLÆHBLÆBLÆBLÆBLÆBLÆBLÆBLÆgit add .git add .

@@
 	\begin{equation*}
+	\label{exist_proof_temporal}
 	\iint_{Q_T} \Phi'_n(u_n)|\partial_t u_n|^2 dxdt \leq \iint_{Q_T} \left\{ -\partial_t f_n \Phi_n(u_n) + Cf_n\partial_tf_n \right\} dxdt.
@@
 \end{align*}
-which means that $|\nabla z_n|^2 \leq |\nabla w_n|^2$ in all of $Q_T$.
+which means that $|\nabla z_n|^2 \leq |\nabla w_n|^2$ in all of $Q_T$. As a trivial consequence of this
+\begin{equation*}
+\iint_{Q_T}|\nabla z_n|^2dxdt \leq \iint_{Q_T}|\nabla w_n|^2dxdt.
+\end{equation*}
+
+Seeing as estimate (\ref{exist_proof_spatial}), we can argue exactly as we did in the previous proof to say that $\nabla z_n$ is uniformly bounded in $L^2(Q_T)$.
+Similarly we have the two inequalities
+\begin{equation*}
+|\partial_t z_n | \leq |\partial_t u_n|, \quad \text{ and} \quad |\partial_t z_n| \leq |\Phi_n'(u_n) \partial_t u_n|,
+\end{equation*}
+and as a consequence
+\begin{equation*}
+\iint_{Q_T}|\partial_t z_n|^2 dxdt \leq \iint_{Q_T} |\Phi_n'(u_n)|\cdot |\partial_t u_n|^2dxdt.
+\end{equation*}
+The estimate (\ref{exist_proof_temporal}) holds in this case as well, and by the assumptions on $f$ and its approximations we also have a uniform bound of $\partial_t z_n$ in $L^2(Q_T)$.
+Hence $z_n$ is a bounded sequence in $H^1(Q_T)$, and we can utilize the Rellich-Kondrachov Compactness Theorem (theorem \ref{Rellich}) again to conclude that there is a subsequence $\{z_{n_j}\}$ converging to some $z$ in $L^2(Q_T)$.
 \end{proof}

### 2014-11-20 trygve_b_written_assignment4.tex
Started writing on written assignment 4.

\documentclass[11pt, a4paper]{article}
\usepackage{mathptmx}
\usepackage{mathtools}
\usepackage{amssymb}
%\usepackage{amsfonts}
%\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsthm}
\usepackage{remreset}
\usepackage[utf8]{inputenc}

\usepackage{lmodern}

\begin{document}

\title{Written assignment 4 in SPRÅK3501}
\author{Trygve Bærland}
\maketitle
\section*{Introduction:}
In my project I will consider a generalisation of the Porous Medium Equation, and specifically try to construct a numerical method that converges to a, in some sense, unique solution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%			FIRST ARTICLE:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{First item:}
\subsection{Summary:}
\cite{Cifani} presents a numerical method for solving a convection-diffusion equation with fractional, nonlinear diffusion. The article starts off by setting up a problem formulation, then introduce an entropy condition that ensures uniqueness of solutions that are bounded and integrable. After presenting a numerical method and proving that it converges to the entropy solution, the authors show that the numerical solutions also converge to a function of bounded variation, and hence they prove existence of solutions with bounded variation.

\subsection{Critique:}
The article is quite impressive in that it introduces a new class of partial differential equations, and establishes existence, uniqueness and stability of solutions. However, it seems to me that the numerical method presented only works on simple problems, in the sense that if the domain cannot easily be made into a nice grid the implementation will be almost impossible.

\subsection{Reflections:}
Although this article tackles a class of partial differential equations that easily are much harder to analyse than what I'm setting out to tackle, the overall strategy to get a new sense of existence is very similar to what I aim to do in my work, and hence is a quite useful article. Also, the numerical method used here is quite different from the one I will be using.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%			SECOND ARTICLE:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\section{Second item:}
\subsection{Summary:}
In \cite{Schochet} scalar hyperbolic conservation laws are considered. While not using novel numerical method on this class of partial differential equations the author is able to further the field by deriving a rate of convergence for the spectral- and pseudospectral methods.

\subsection{Critique:}
The article assumes quite a bit of knowledge on the reader. E.g. extensive knowledge of Fourier analysis and certain convergence results in this field is assumed. This makes it a tough read. Luckily, in between paragraphs heavy on mathematical notation, the author is mostly very considerate and provides good discussions.

\subsection{Reflections:}
Again, the family of equations considered are different from the ones I will be considering, but in contrast to \cite{Cifani}, the methods of analysis doesn't carry over as well as I'd hoped. The numerical method is quite similar to the one I will be using, and that is the main reason for this article's relevance to my work, however there are some key differences that I'm not yet sure of whether are significant or not.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%			THIRD ARTICLE:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Third item}
\subsection{Summary:}
The monograph \cite{vazquez2007porous} handles, as its name suggests, the mathematical theory pertaining to the Porous Medium Equation and some of its most notable variants and generalisations. Of particular interest are the first five chapters. The first chapter is a short introduction to the field, presenting a quite broad overview and mentioning some of the more peculiar hallmarks of solutions of the porous medium equation. The second chapter is mostly spent deriving the partial differential equation from physical principles and assumptions. It's first with the third chapter that the more mathematical juicy stuff enters, and a whole bunch of important estimates and other results are presented in quick succesion. The fourth chapter is a sort of resting chapter, mainly concerned with specific examples of solutions, giving the reader at least a feel what to expect in subsequent analysis about e.g. boundedness or smoothness of solutions.

All these four chapters are more or less relevant for a close reading of the fifth chapter concerning weak solutions and the existence and uniqueness of such.

\subsection{Critique:}
The chapter progression is well thought out and pedagogical, and in the third chapter in particular the presentation is excellent. In this chapter most proofs and derivations are carefully plotted out, and most, if not all, concerns the reader might have were addressed.

However, all this changes in the fifth chapter, which is by far the most relevant to my work. In the proofs in this chapter many results from preceeding chapters are used implicitly, which demands a lot of the reader's recollection. It also makes this chapter almost impossible to read by itself, and suggests the book more be used for thorough readings rather than as a handy reference work. The sudden vanishing of careful exposition also raises questions about who the intended reader should be. The first chapters suggest someone at my level, with some graduate courses in analysis and partial differential equations, but then the reader is assumed to be not only acquainted, but familiar with Sobolev equalities and embeddings, as well as other mainstay techniques of more advanced PDE theory.

\subsection{Reflections:}
Although a lot of eyebrows might, more or less justifiably, be raised at the transition in exposition, it is without a question a useful opportunity to get first hand experience with some important techniques in PDE theory. It is because of this opportunity that much of project is spent in laying many of the book's proofs out in more detail. In doing so \cite{vazquez2007porous} has become a sort of centerpiece for my project.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%			FOURTH ARTICLE:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fourth item}
\subsection{Summary:}
The book "Partial Differential Equations" (\cite{evans}) stands as a monument in PDE theory (with that title, you can't aim for anything less). The most pertinent chapters to my work is chapter 5, concerning Sobolev spaces and -equalities, and chapter 7 about second  order parabolic equation, of which the general porous medium equation is an example.

The first part of chapter 5 is mostly a list of definitions of important function spaces and other analytic tools that will become useful. Then the reader is exposed to some results with a flavour of functional analysis. E.g. that any function satisfying certain conditions about its summability can be approximated by infinitely smooth and bounded functions. A most useful, and not at all trivial result.

After this we are prepared to tackle Sobolev inequalities, stating vaguely that if a function is in some space we can also deduce some other spaces it's in. The last really important result of this chapter is then the Sobolev embedding theorem, that goes even further in saying that a bounded sequence in some function space has a convergent subsequence in another. This results is of utmost importance in an existence proof in \cite{vazquez2007porous}.

The second chapter of relevance for my project is, as previously stated, chapter 7. It is not as important and far reaching as chapter 5, and the only part of any concern to us is the discussion on maximum principles, which were only briefly presented in \cite{vazquez2007porous}. This is a hallmark of parabolic equations and says something to the extent of solutions attain there extrema at the boundary, and not the interior.

\subsection{Critique:}
The parts of the book considered here held a high technical standard, but all proofs were carefully laid out, so albeit a challenging read it is definitely rewarding. In addition the interstitial discussions were for the most part good at motivating what was to follow and how to use what we've already been through.

Another thing worth mentioning is that both chapters could be read as stand alone chapters, and almost all terminology used in the chapter was introduced there. This hints at that the book can be used for easy reference. A definite positive.

On the other hand, the notation is a bit of hassle, and it's reasonable to assume that many readers will need some time getting used to it. Especially when it comes to differential operator.

\subsection{Reflections:}
The chapter on Sobolev spaces has, apart from being useful to my project at the moment, been a real treat to have knowledge about. The results presented there have far reaching consequences and I've already made some use of it in other courses I'm taking this semester. Point being that the semester project may prove to be an even more rewarding learning experience than first anticipated, not as niche.

For the most part I had a very pleasant experience with this book, and I understand why I see it in so many professor offices.

Notational friction not withstanding the pages are easy on the eye, which had a positive effect on my patience when reading. I haven't even thought to consider the visual aspect of a text in the  foregoing items, which should only support its excellence in this case.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%			FIFTH ARTICLE:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fifth item}
\subsection{Summary:}
The book "Linear and Quasilinear Equations of Parabolic Type" (\cite{ladyzhenskaya}) gives an extensive presentation of the theory on parabolic PDEs, but my work has lead me to only consider chapter 5. on "Quasi-linear equations with principal part in divergence form". And even more in particular a theorem on the existence of classical solutions. However, this theorem is so involved that a more thorough reading of this chapter is required.

The chapter starts with introducing the general equation in question and also the concept of weak solutions. Even though some estimates on weak solutions are presented, the following sections assumes continuously differentiable solutions, relegating us to the realm of classical solutions.

All subsequent estimates and small results, including some bounds on the spatial derivative  and smoothness of solutions, lead up to main part relevant for my project: Theorem 6.1. This theorem says that under quite strict and numerous assumptions, the considered equation has a smooth solution. This is not to say that it's not an impressive result, which it is.

\subsection{Critique:}
As opposed to the presentation in \cite{evans}, the parts of \cite{ladyzhenskaya} here considered were not self contained, and required reading at least the introduction of the book where most of the notation was established. In addition, said notation did not follow western conventions making it all very confusing. This isn't to say that the western way is the right way, only that it was difficult for a non-initiated.

The chapter also relied on results established in previous parts of the books, but luckily sufficient references were given, making it less of a challenge to navigate the book.

As both the main- and chapter title suggests, the contents were highly technical, and expect a similar high level of mathematical maturity. A level I must admit to not having at the moment.

\subsection{Reflection:}
A frustrating read, to say the least, but fortunately my main objective was acquiring Theorem 6.1 and massaging into the equation I'm considering. This sort of superficial reading is undoubtedly reflected in the above summary.

Even for the superficial reading and that much of the stuff went over my head, I feel I can  make a comment on the overall structure of the book, which to me felt far too involved. There is a loose rule in mathematical writing that you need to periodically remind the reader of certain main results that you still plan on using, or haven't outplayed their part (cf. for example \cite{halmos1970write}). This is violated in both \cite{ladyzhenskaya} and \cite{vazquez2007porous}, and has the biproduct of making the overall structure of the book more complex and involved than it needed to be.

\newpage
\bibliographystyle{plain}
\bibliography{project_bibliography.bib}
\end{document}

### 2014-11-20 trygve_b_written_assignment4.tex
Bare en artikkel igjen nå.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			SIXTH ARTICLE:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Sixth item:}
+\subsection{Summary:}
+"Nonlinear integro-differential Equation" (\cite{davidsen2013nonlinear}) is the master thesis of Stein-Olav Davidsen.
+Here he proposes a numerical method for solving the same type of problem as was analysed in \cite{Cifani}, but he uses the more advanced Spectral method aand shows convergence of this method to the weak solution.
+
+The thesis starts off with a short introduction of the equation before delving into a sufficient description of the numerical method.
+It is a spectral method with a Fourier basis, i.e.
+doing a sort of wave decomposition approach.
+For stability he uses the popular spectral vaninishing viscosity by introducing diffusion only on the highest frequencies, so that the method is less prone to undesirable oscillations.
+
+The entire third part of the thesis is devoted to showing convergence of the numerical method, and starts by introducing a compactness theorem (similar to the Sobolev embedding theorem presented in \cite{evans}) which will we be used.
+But before making use of the compactness argument a lot of estimates must be established, and so a lot of space in the third part is devoted to this.
+
+The remainder of the thesis addresses several difficulties with implementing the method and gives some examples of numerical solutions.
+
+\subsection{Critique:}
+Especially the third part, concerning the convergence result, is nicely set up with introducing the main theorem in the offset, which motivates everything to come. A smart move, in my opinion.
+
+It was also a good idea to spend a lot of time on implementation concerns, increasing the chances of reproducability.
+As does the numerical examples, which also corresponds nicely with those provided in \cite{Cifani}.
+
+\subsection{Reflections:}
+All in all I'm impressed with the thesis.
+Maybe a bit short on some of the proofs, but it's already very heavy on mathematical notation, so any more detailed proofs would only make too strenuous to read.
+Seeing as Stein-Olav had the same supervisor as I'm currently working for/under/with I recognize alot of the structural suggestions I've received in this thesis, and it seems to work well in this case.
+
+I'm not too fond of the Fourier basis, since it's not flexible when it comes to domain.
+It pretty much has to be a rectangular domain when using Fourier basis.
+So a possible advancement would be a change of basis to Chebyshev or Legendre, which are more flexible, but not as easy to stabilise as Fourier using spectral vanishing viscosity.
+
+Even though my own project this semester has drifted a bit away from numerical considerations, I'm certain I will put more emphasis on it in this spring's master's writing, so a possible thesis could be to consider other bases.
 \newpage

### 2014-11-23 draft_project.tex
Finished appendix on the approximate nonlinearities.

@@
 \section{Properties of the approximate nonlinearities}
+\subsection{Properties of $\Phi$ and its approximations}
 \label{app:Phi}
@@
 \begin{proposition}
-If $\Phi$ is locally Lipschitz continuous, then $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
+If $\Phi$ is continuous, $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
 \end{proposition}
 \begin{proof}
-The proof is done by getting out a crude, but sufficient estimate on the pointwise difference of $\Phi$ with its approximation. For any $u \in \mathbb{R}$, we have
-\begin{align*}
-|\Phi_n(u) - \Phi(u)| &= \left| \frac{u}{n} + \int_\mathbb{R}\Phi(u-y)\varphi_{\frac{1}{n}}(y)dy - \int_\mathbb{R}\Phi(y)\varphi_{\frac{1}{n}}(-y)dy - \Phi(u)\right| \\
-& \leq \frac{|u|}{n} + \int_\mathbb{R}\left| \Phi(u-y) - \Phi(u) - \Phi(y)\right| \varphi_{\frac{1}{n}}(y) dy \\
-& \leq \frac{|u|}{n} + \underset{y\in[-\frac{1}{n},\frac{1}{n}]}{\mathrm{sup}}|\Phi(u-y) - \Phi(u)| + \mathrm{max}\{|\Phi (1/n) |,|\Phi(-1/n)| \}.
-\end{align*}
-Let now $K \subset \mathbb{R}$ be any compact set, and let $L_K$ be a Lipschitz constant for $\Phi$ over $K$. We then have for any $u \in K$ that
-\begin{equation*}
-|\Phi_n(u) - \Phi(u)| \leq \frac{1}{n}\left( L_K + \mathrm{sup}_{s \in K}|s| \right) + \mathrm{max}\{|\Phi (1/n) |,|\Phi(-1/n)| \}.
-\end{equation*}
-Since $K$ is bounded and $\Phi$ is continuous with $\Phi(0) = 0$ we have a bound independent of $u$, and therefore the convergence is uniform in $K$.
+This follows almost immediately from part iii) of theorem 7 of appendix C in \citep{evans}, which states that if $\Phi$ is continuous, then $\Phi * \varphi_{\frac{1}{n}}$ converges uniformly to $\Phi$ on compact sets.
+So let $K\subset \mathbb{R}$ be a compact set, and fix $\epsilon < 0$.
+Then there is an $N_1 \in \mathbb{N}$ so that
+\begin{equation*}
+\underset{x\in K}{\mathrm{sup}}|\Phi * \varphi_{\frac{1}{n}}(x) - \Phi(x)| < \frac{\epsilon}{3},
+\end{equation*} 
+whenever $n \geq N_1$. Similarly we have an $N_2 \in \mathbb{N}$, so that 
+\begin{equation*}
+|\Phi * \varphi_{\frac{1}{n}}(0) - \Phi(0)| < \frac{\epsilon}{3},
+\end{equation*}
+for every $n \geq N_2$. Lastly, since $K$ is compact, there is an $N_3 \in \mathbb{N}$ so that
+\begin{equation*}
+\underset{x\in K}{\mathrm{sup}}\frac{|x|}{n} < \frac{\epsilon}{3},
+\end{equation*}
+whenever $n \geq N_3$.
+
+Now we set $N = \mathrm{max}\{N_1,N_2,N_3\}$, and see that
+\begin{align*}
+\underset{x\in K}{\mathrm{sup}}|\Phi_n(x) - \Phi(x)| &\leq  \underset{x\in K}{\mathrm{sup}}|\Phi * \varphi_{\frac{1}{n}}(x) - \Phi(x)| + |\Phi * \varphi_{\frac{1}{n}}(0) - \Phi(0)| + \underset{x\in K}{\mathrm{sup}}\frac{|x|}{n} \\
+&< \frac{\epsilon}{3} + \frac{\epsilon}{3} + \frac{\epsilon}{3} \\
+&= \epsilon,
+\end{align*}
+for every $n \geq N$, which proves the proposition.
 \end{proof}
@@
 
+\subsection{Properties of $Z$ and its approximations}
+In this section we assume $\Phi$ to be absolutely continuous, i.e.
+\begin{equation*}
+\Phi(u) = \int_0^u \Phi'(s)ds,
+\end{equation*}
+and $\Phi' \in L^1_{loc}(\mathbb{R})$. We also assume $\Phi$ to be strictly increasing and  $\Phi(\pm \infty) = \pm \infty$.
+
+We define 
+\begin{equation}
+Z(u) = \int_0^u \mathrm{min}\{1, \Phi'(s)\} ds,
+\end{equation}
+and similarly
+\begin{equation}
+Z_n(u) = \int_0^u\mathrm{min}\{1, \Phi_n'(s)\}ds.
+\end{equation}
+
+As in the previous section we'll establish that $Z_n$ converges to $Z$ uniformly on compact sets, and continue on with the inverses and a similar convergence results for them.
+We'll start off with the following proposition:
+
+\begin{proposition}
+$Z_n$ converges pointwise to $Z$.
+\end{proposition}
+\begin{proof}
+A useful identity to have in mind at this point is
+\begin{equation*}
+\mathrm{min}\{a,b\} = \frac{a+b}{2} - \frac{|a-b|}{2},
+\end{equation*}
+which makes
+\begin{align*}
+|\mathrm{min}\{1,a\} - \mathrm{min}\{1,b\}| &= \left| \frac{1+a}{2} -\frac{1+b}{2} + \frac{|1-b|}{2} - \frac{|1-a|}{2}\right| \\
+&\leq \frac{1}{2}|a-b| + \frac{1}{2}\big| |1-b| - |1-a| \big| \\
+&\leq \frac{1}{2}|a-b| + \frac{1}{2}|a-b| \\
+&= |a-b|.
+\end{align*}
+
+For any $u \in \mathbb{R}$ we then have
+\begin{align*}
+|Z_n(u) - Z(u)| &\leq \int_0^{|u|} |\mathrm{min}\{1,\Phi'_n(s)\} - \mathrm{min}\{1,\Phi'(s)\}|ds \\
+&\leq \int_0^{|u|} |\Phi'_n(s)-\Phi'(s)|ds,
+\end{align*}
+by using the above derived inequality. Following the definition of $Phi_n$, its derivative is
+\begin{equation*}
+\Phi'_n(s) = \Phi' * \varphi_{\frac{1}{n}}(s) + \frac{1}{n},
+\end{equation*}
+and so
+\begin{equation*}
+|Z_n(u) - Z(u)| \leq \int_0^{|u|}|\Phi'*\varphi_{\frac{1}{n}}(s) - \Phi'(s)|ds + \frac{|u|}{n}.
+\end{equation*}
+We have of course complete control of the latter of these terms by making $n$ sufficiently large.
+For the first term we use part iv) of theorem 7 of appendix C in \citep{evans}, to state that $\Phi'*\varphi_{\frac{1}{n}}$ converges to $\Phi$ in $L^1_{loc}(\mathbb{R})$.
+With this we deduce that $Z_n$ converges pointwise to $Z$.
+\end{proof}
+
+Next we will prove that $Z_n$ converges to $Z$ uniformly on compact sets, but for this we need the Arzela-Ascoli theorem, presented below for ease of reference, (cf.
+e.g.
+\citep[p 718]{evans}).
+This theorem hinges on the concept of equicontinuity, for which a definition is presented directly below.
+\begin{mydef}
+A sequence $(f_n)$ of continuous, real-valued functions defined on an interval $[a,b]$ is said to be \textbf{equicontinuous} if for every $\epsilon >0$ there is a $\delta >0 $, depending only on $\epsilon$, so that for $x,y \in [a,b]$
+\begin{equation*}
+|x-y| < \delta \Rightarrow |f_n(x) - f_n(y)| < \epsilon
+\end{equation*}
+for every $n \in \mathbb{N}$.
+\end{mydef}
+We are now prepared for the Arzela-Ascoli theorem.
+\begin{theorem}[Arzela-Ascoli]
+\label{thm:Ascoli}
+A bounded, equicontinuous sequence, $(f_n)$, of continuous, real-valued functions has a subsequence which converges uniformly.
+\end{theorem}
+
+Using this powerful theorem we can prove the following:
+\begin{proposition}
+\label{prop:Z_uniform_convergence}
+$Z_n$ converges to $Z$ uniformly on compact sets.
+\end{proposition}
+\begin{proof}
+The proof will be done by contradiction.
+Take $K \subset \mathbb{R}$ to be a compact set, and consider a closed interval of the form $[-M,M]$, with $M$ so large as to contain $K$.
+Obviously, $Z_n$ is a bounded sequence, with
+\begin{equation*}
+|Z_n(x)| \leq M.
+\end{equation*}
+In addition, the sequence is equicontinuous, since all $Z_n$'s are globally Lipschitz continuous with the same Lipschitz constant $1$.
+
+We can from this conclude that $(Z_n)$ has a subsequence that converges uniformly on $[-M,M]$, and that the limit is $Z$, using theorem \ref{thm:Ascoli} and that $Z_n$ converges pointwise to $Z$.
+We can, with and identitical argument say that any subsequence of $(Z_n)$ also contains a subsequence converging uniformly to $Z$.
+
+Suppose now that $(Z_n)$ does not converge to $Z$ uniformly on $[-M,M]$. Then there is an $\epsilon > 0$ so that for every $k \in \mathbb{N}$ there is an $n \geq k$ so that
+\begin{equation*}
+\underset{x\in[-M,M]}{\mathrm{sup}}|Z_n(x) - Z(x)| \geq \epsilon.
+\end{equation*}
+From this we can construct a subsequence $(Z_{n_k})$ so that
+\begin{equation*}
+\underset{x\in[-M,M]}{\mathrm{sup}}|Z_{n_k}(x) - Z(x)| \geq \epsilon,
+\end{equation*}
+for every $k$, but this is in clear contradiction with the fact that $(Z_{n_k})$ must have a subsequence converging uniformly to $Z$.
+Hence we can conclude that $(Z_n)$ converges uniformly to $Z$ on $[-M,M]$, and as a consequence also on $K$.
+\end{proof}
+
+We'll continue on with the last result of this section.
+\begin{proposition}
+\label{prop:Zinv_uniform_convergence}
+With $\Phi$ strictly increasing, $Z$ is strictly increasing, and thus permits and inverse. Furthermore $Z_n^{-1}$ converges to $Z^{-1}$ uniformly on compact sets.
+\end{proposition}
+\begin{proof}
+ We note that $Z_n' \geq \frac{1}{n}$, and is thus stricly increasing, permitting a continuous inverse $Z_n^{-1}$.
+
+That $Z$ is also strictly increasing follows from that $\Phi$ is strictly increasing. Indeed, suppose $t<u$ and see that
+\begin{equation*}
+Z(u) - Z(t) = \int_t^u \mathrm{min}\{1,\Phi'(s)\}ds \geq 0.
+\end{equation*}
+The only way this can be $0$ is if $\Phi' = 0$ a.e.
+everywhere on $(t,u)$, but if that were the case then $\Phi(u) = \Phi(t)$, in contradiction with $\Phi$ being strictly increasing.
+So $Z$ is strictly increasing, and has continuous and strictly increasing inverse $Z^{-1}$.
+
+We have from proposition \ref{prop:Z_uniform_convergence} that $Z_n$ converges uniformly to $Z$ on compact sets, and so we can simply use lemma \ref{lem:Inverse_uniform_general} to conclude that $Z_n^{-1}$ converges uniformly to $Z^{-1}$ on compact sets.
+\end{proof}
+
 \end{appendix}

### 2014-11-23 trygve_b_written_assignment4.tex
Finished appendix on the approximate nonlinearities.

@@
 Even though my own project this semester has drifted a bit away from numerical considerations, I'm certain I will put more emphasis on it in this spring's master's writing, so a possible thesis could be to consider other bases.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			SEVENTH ARTICLE:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Seventh item}
+\subsection{Summary:}
+As the title of \cite{benilan1981continuous}, "The Continuous Dependence on $\varphi$ of Solutions of $u_t - \Delta\varphi(u) = 0$, suggests, this paper establishes a stability result on the nonlinearity for that type of equation, which is just the homogeneous general porous medium equation.
+The paper starts in good Imrad fashion to present the state of the field and what advances has been made similar to theirs, as well as discussing why the strides made in this paper are valuable.
+
+The main results of the paper is introduced already in the introduction, and with presents all challenges which needs to be overcome what's to follow.
+In particular a somewhat arbitrary-looking identity  concerning the inverse of the nonlinearity needs to be shown, and extra concerns needs to be addressed when the dimension of the problem exceeds 2.
+In this case the function space where a solution may reside needs to be restricted.
+
+This leads to introducing the concept of maximal monotone graph, since the inverse of the nonlinearity $\varphi$ may be a set-function, and not just a regular function.
+In this setting existence of a unique weak solution is proved.
+
+The remainder of the paper is spent on proving minor results building up to the main theorem, and concludes with some related proposition to be used for future reference.
+
+\subsection{Critique:}
+Although a sound strategy to introduce the main result early in the paper, sufficient care was not given when motivating every part result.
+Making it rather confusing at times, but blame can also be placed on me for not having sufficient mathematical maturity.
+
+Indeed, the mathematical knowledge expected of the reader in this paper will indubitably cast any critique I may impart in a bad light, but in any case there are structural issues here that I feel competent enough to address.
+The previously mentioned confusion arises from such structural acrobatics as putting a proof of a minor result in the middle of a larger proof, and have almost no interstitial discussions.
+Especially the latter of these editorial decisions makes the paper extremely difficult to read.
+With no discernible "narrative"\footnote{Running thread, or whatever the english translation of the norwegian idiom "rød tråd" is.} the writer seems to expect a whole lot on the reader's concentration, focus, and ability to maintain both.
+
+\subsection{Reflections:}
+My project needs a stability result on the nonlinearity to be able to extend the existence result from $\varphi$ strictly increasing to only nondecreasing.
+However, the case studied in this paper is the Cauchy problem (on the entirity of $\mathbb{R}^n$) rather than on a bounded domain, which is the problem I'm studying.
+Due to the mathematical sophistication I have a hard time saying whether I will be able to use these results, or something similar, to what I'm dealing with.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				BIBLIOGRAPHY:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2014-11-25 trygve_b_written_assignment4.tex
Changed title

@@
 
-\title{Written assignment 4 in SPRÅK3501}
+\title{A Noncomprehensive Annotated Bibliography for Analysing the General Porous Medium Equation}
 \author{Trygve Bærland}
@@
 Especially the latter of these editorial decisions makes the paper extremely difficult to read.
-With no discernible "narrative"\footnote{Running thread, or whatever the english translation of the norwegian idiom "rød tråd" is.} the writer seems to expect a whole lot on the reader's concentration, focus, and ability to maintain both.
+With no discernible running theme the writer seems to expect a whole lot on the reader's concentration, focus, and ability to maintain both.
 

### 2014-11-25 draft_project.tex
KOM IGJEN NÅ!

@@
 Hence $z_n$ is a bounded sequence in $H^1(Q_T)$, and we can utilize the Rellich-Kondrachov Compactness Theorem (theorem \ref{Rellich}) again to conclude that there is a subsequence $\{z_{n_j}\}$ converging to some $z$ in $L^2(Q_T)$.
+
+Now we obviously have $u_{n_j} = Z_{n_j}^{-1}(z_{n_j})$, and so
+\begin{align*}
+|u_{n_j} - Z^{-1}(z)| &= |Z_{n_j}^{-1}(z_{n_j}) - Z^{-1}(z)| \\
+&\leq |Z_{n_j}^{-1}(z_{n_j}) - Z^{-1}(z_{n_j})| + |Z^{-1}(z_{n_j})- Z^{-1}(z)|.
+\end{align*}
+The sequence $(z_{n_j})$ converges pointwise to $z$ as well as being uniformly bounded 
+since $|z_{n_j}| \leq |u_{n_j}| \leq M$.
+And so the first term on the right hand side in the above inequality is controlled by $Z_n^{-1}$ converging uniformly to $Z^{-1}$ on compact sets, as shown in proposition \ref{prop:Zinv_uniform_convergence}.
+The second term tends to zero since $z_{n_j}$ converges pointwise to $z$ and $Z^{-1}$ is continuous.
+
+We define $u=Z^{-1}(z)$ as the pointwise limit of $u_{n_j}$, and note as in the previous proof that $u_{n_j}$ also converges to $u$ in $L^1(Q_T)$.
 \end{proof}
@@
 \end{align*}
-by using the above derived inequality. Following the definition of $Phi_n$, its derivative is
+by using the above derived inequality. Following the definition of $\Phi_n$, its derivative is
 \begin{equation*}
@@
 \label{prop:Zinv_uniform_convergence}
-With $\Phi$ strictly increasing, $Z$ is strictly increasing, and thus permits and inverse. Furthermore $Z_n^{-1}$ converges to $Z^{-1}$ uniformly on compact sets.
+With $\Phi$ strictly increasing and continuos, $Z$ is strictly increasing and continuous, and thus permits a strictly increasing and continuous inverse.
+Furthermore $Z_n^{-1}$ converges to $Z^{-1}$ uniformly on compact sets.
 \end{proposition}
@@
 everywhere on $(t,u)$, but if that were the case then $\Phi(u) = \Phi(t)$, in contradiction with $\Phi$ being strictly increasing.
-So $Z$ is strictly increasing, and has continuous and strictly increasing inverse $Z^{-1}$.
+So $Z$ is strictly increasing, and has a continuous and strictly increasing inverse $Z^{-1}$.
 

### 2014-12-10 draft_project.tex
Enda et bevis doone.

@@
 \begin{lemma}
+\label{lem:l1_stability_classical}
 For $\tau, t \in [0,T]$ the inequality 
@@
 \begin{cor}[$L^1$-contractivity]
+\label{cor:l1-contractivity_classical}
 For two smooth solutions, $u$ and $\hat{u}$ of the homoegenous Dirichlet problem (\ref{HDP}) with different initial data and loading, the $L^1$-estimate
@@
 	We have from before that $u\in L^1(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique.
-
-	\item[Considering the $L^1$-contractivity:] Let now $\hat{u}$ be the weak energy solution to some auxiliary problem with intial value $\hat{u}_0$ and loading $\hat{f}$.
-We also let $\hat{u}_n$ be a sequence of approximations similarly constructed as those for $u$.
-We go by way of first showing that
-	\begin{equation}
-	\label{weak_solutions_l1_start}
-	\int_\Omega(u(t)-\hat{u}(t))_+dx \leq \int_\Omega (u_0 + \hat{u}_0)_+dx + \int_0^t \int_\Omega (f- \hat{f})_+ dxdt. 
-	\end{equation}
-	With that in mind it's worth noting that for $\int_\Omega (\cdot)_+dx$ the triangle inequality is valid, so
-	\begin{align*}
-	\int_\Omega (u(t) - \hat{u}(t))_+dx &\leq \int_\Omega(u(t) - u_n(t))_+dx + \int_\Omega (u_n(t) - \hat{u}_n(t))_+dx \\
-	&+ \int_\Omega(\hat{u}_n - \hat{u})_+dx.
-	\end{align*}
-	The first and last term we can make arbitrarily small, and for the middle term we use the $L^1$-contractivity for smooth solutions. Then, for every $\epsilon > 0$
-	\begin{equation*}
-	\int_\Omega (u(t) - \hat{u}(t))_+dx < \epsilon + \int_\Omega(u_{0,n} + \hat{u}_{0,n})_+ dx + \int_0^t \int_\Omega (f_n - \hat{f}_n)_+dxdt,
-	\end{equation*}
-	for sufficiently large $n$. When using the triangle inequality again
-	\begin{align*}
-	\int_\Omega (u(t) - \hat{u}(t))_+dx &< \epsilon + \int_\Omega(u_{0,n} - u_0)_+dx + \int_\Omega(u_0 - \hat{u}_0)_+dx \\
-	&+ \int_\Omega (\hat{u}_0 - \hat{u}_{0,n})_+dx + \int_0^t \int_\Omega(f_n - f)_+dxdt\\
-	&+ \int_0^t(f-\hat{f})_+dxdt + \int_0^t\int_\Omega (\hat{f}-\hat{f}_n)_+ dxdt.
-	\end{align*}	
-	All the term involving $n$ in the integrand can now be made arbitrarily small, so for sufficiently large $n$
-	\begin{equation*}
-	\int_\Omega (u(t) - \hat{u}(t))_+dx < 2\epsilon +\int_\Omega(u_0 - \hat{u}_0)_+dx + \int_0^t \int_\Omega (f-\hat{f})dxdt.
-	\end{equation*}					
-	Since this should hold for every $\epsilon >0 $, we must have that (\ref{weak_solutions_l1_start}) is satisfied.
-
-	From (\ref{weak_solutions_l1_start}), we do as for (\ref{l1_contractivity}), and get
-	\begin{equation*}
-	||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||f-\hat{f}||_{L^1(Q_t)}
-	\end{equation*}
+In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak energy energy solution, and so the uniqueness precludes any other accumulation point than $u$.
+I.e.
+the whole sequence $(u_n)$ converges to $u$.
+
 \end{description}
@@
 \begin{lemma}
+\label{lem:weak_existence_part2}
 Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$ and $\partial_t f$ are bounded.
@@
 We define $u=Z^{-1}(z)$ as the pointwise limit of $u_{n_j}$, and note as in the previous proof that $u_{n_j}$ also converges to $u$ in $L^1(Q_T)$.
+
+Similarly we can show that $w_{n_j}$ converges to $w=\Phi(u)$ and that $w \in L^2(Q_T)$.
+In addition, from a previous argument $\nabla w_n$ is bounded in $L^2$ independent of $n$, and so we conclude that $w \in H^1(Q_T)$.
+
+From this point on, proving that $u$ is a weak energy solution is identical to the last part of the proof of lemma \ref{lem:existence_part1}.
+\end{proof}
+
+We will continue on with lifting more of the assumptions, in particular those on $f$ and $u_0$, but first an intermediate result is needed.
+The result is simply the $L^1$-stability presented in lemma \ref{lem:l1_stability_classical} only now for weak solutions.
+
+\begin{lemma}
+\label{lem:l1_stability_weak}
+Let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$. They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively. Then the inequality
+\begin{equation}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + \int_0^t||f-\hat{f}||_{L^1(\Omega)}
+\end{equation}
+for almost every $t\in [0,T]$.
+\end{lemma}
+
+\begin{proof}
+Let $\Phi_n$ be the approximations of $\Phi$, $u_{0,n}$ and $\hat{u}_{0,n}$ be approximations of $u_0$ and $\hat{u}_{0,n}$ to the initial data, converging in $L^1$.
+Furthermore, let $f_n$ and $\hat{f}_n$ be approximations of $f$ and $\hat{f}$ converging in $L^2(Q_T)$, and so also in $L^1(Q_T)$ since $Q_T$ is bounded.
+All the above approximations are as already presented in the foregoing proofs.
+Hence we have a sequence of classical solutions $u_n$ and $\hat{u}_n$ that converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
+
+We now use the triangle inequality for
+\begin{equation*}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u(t) - u_n(t)||_{L^1(\Omega)} + ||u_n(t) - \hat{u}_n(t)||_{L^1(\Omega)} + ||\hat{u}_n(t) - \hat{u}(t)||_{L^1(\Omega)}.
+\end{equation*}
+The first and last term on the right hand side are easily controlled by the convergence of $u_n$ and $\hat{u}_n$.
+As for the middle term we use corollary \ref{cor:l1-contractivity_classical}, and so for any $\epsilon > 0$,
+\begin{equation*}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq \epsilon + ||u_{0,n} - \hat{u}_{0,n}||_{L^1(\Omega)} + ||f_n - \hat{f}_n||_{L^1(Q_t)}
+\end{equation*}
+for sufficiently large $n$.
+Using the triangle inequality another time yields
+\begin{align*}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} &\leq \epsilon + ||u_{0,n} - u_0||_{L^1(\Omega)} + ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||\hat{u}_0 -\hat{u}_{0,n}||_{L^1(\Omega)} \\
+&+ ||f_n - f||_{L^1(Q_t)} + ||f - \hat{f}||_{L^1(Q_t)} + ||\hat{f}-\hat{f}_n||_{L^1(Q_t)}.
+\end{align*}
+Lastly, we have from the various convergences that for sufficiently large $n$  
+\begin{equation*}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq 2\epsilon + ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||f - \hat{f}||_{L^1(Q_t)}, 
+\end{equation*}
+and since $\epsilon$ was arbitrary this concludes the proof.
+\end{proof}
+
+\subsubsection{Removing the assumptions on $f$ and $u_0$}
+Now we try to generalise to the case when $f$ and/or $u_0$ are not bounded, but still require $f \in L^2(Q_T)$ and $u_0 \in L_{\Psi}(\Omega)$.
+
+\begin{lemma}
+Theorem \ref{thm:weak_existence} holds when $\Phi$ is strictly increasing and absolutely continuous.
+\end{lemma}
+\begin{proof}
+
+\begin{description}
+\item[Finding a candidate for a solution:]
+Let $(u_{0,n})$ be sequence of bounded functions converging to $u_0$ in $L_{\Psi}(\Omega)$, and $(f_n)$ a sequence of bounded functions converging to $f$ in $L^2(Q_T)$, as well as $\partial_t f_n$ being bounded in $Q_T$ for each $n$.
+It will also be useful to assume $|u_{0,n}| \leq |u_0|$ and $|f_n| \leq |f|$ for all $n$.
+
+Using lemma \ref{lem:weak_existence_part2} we get a sequence of weak energy solutions, $(u_n)$. Notice now that we have discarded any approximations of $\Phi$. By lemma \ref{lem:l1_stability_weak}
+\begin{equation*}
+||u_n(t) - u_m(t)||_{L^1(\Omega)} \leq ||u_{0,n} - u_{0,m}||_{L^1(\Omega)} + ||f_n - f_m||_{L^1(Q_T)}
+\end{equation*}
+for almost every $t \in [0,T]$, and so $(u_n)$ is a Cauchy sequence in $L^\infty(0,T: L^1(\Omega))$, guaranteeing a limit $u \in L^\infty(0,T: L^1(\Omega))$.
+The convergence happens also in $L^1(Q_T)$, since
+\begin{equation*}
+||u - u_n||_{L^1(Q_T)} \leq T\underset{t \in [0,T]}{\mathrm{sup}}||u(t) - u_n(t)||_{L^1(\Omega)}.
+\end{equation*}
+
+\item[$\Phi(u)$ is in $L^2(Q_T)$:]
+We also have pointwise convergence almost everywhere along a subsequence, so $\Phi(u_n)$ converges to $\Phi(u)$ almost everywhere in $Q_T$. Seeing as all $u_n$ are weak energy solutions we have
+\begin{equation*}
+\iint_{Q_T}|\nabla \Phi(u_n)|^2dxdt + \int_\Omega \Psi(u_n(T)) dxdt \leq \int_\Omega \Psi(u_{0,n}) dx + \iint_{Q_T} f_n \Phi(u_n)dxdt,
+\end{equation*}
+and we do as always to get
+\begin{equation*}
+\iint_{Q_T}|\nabla \Phi(u_n)|^2dxdt + 2\int_\Omega \Psi(u_n(T)) dxdt \leq 2\int_\Omega \Psi(u_{0,n}) dx + C\iint_{Q_T} f_n^2 dxdt.
+\end{equation*}
+From our assumptions on the apprxoimations we thus have that $\Phi(u_n)$ is a bounded sequence in $L^2(0,T: H^1(\Omega))$.
+As such we can by Banach-Alaoglu deduce $\Phi(u_n)$ has a subsequence $\Phi(u_{n_k})$ that converges weakly to some  $v$ in $L^2(Q_T)$.
+Suppose now that $v \neq \Phi(u)$ on  a set of positive measure.
+Without loss of generality we can for some $\delta > 0$ define $E = \{ (x,t) \in Q_T: v \geq \Phi(u) + \delta\}$.
+Fix now $\epsilon$, then by Egorov's theorem (cf.
+e.g.
+\citep[p.
+120]{weiss1999course}) there is a measurable set $B \subset E$ over which $\Phi(u_n)$ converges uniformly to $\Phi(u)$, with $B$ having positive measure.
+Therefore,
+\begin{equation*}
+\big|\iint_{B}\Phi(u_n) - \Phi(u) dxdt \big| \leq \epsilon |B|  
+\end{equation*}
+for sufficiently large $n$. Since $\epsilon$ was arbitrary it follows that
+\begin{equation*}
+\iint_B \Phi(u_n) dxdt \to \iint_B \Phi(u) dxdt.
+\end{equation*}
+However, the characteristic function of $B$, $\chi_B$, is in $L^2(Q_T)$, and so by the weak convergence of $\Phi(u_{n_k})$ to $v$ we have
+\begin{align*}
+\iint_{B} \Phi(u_{n_k})dxdt & \to \iint_{B} v dxdt \\
+& \geq \iint_{B} \Phi(u)dxdt + \delta|B|,
+\end{align*}
+which is a contradiction, and we conclude that $v=\Phi(u)$ almost everywhere, and in particular $\Phi(u) \in L^2(Q_T)$.
+Notice also that this argument holds for every subsequence of $\Phi(u_n)$, which means that every subsequence of $\Phi(u_n)$ has a subsequence converging weakly to $\Phi(u)$, and so $\Phi(u_n)$ converges weakly to $\Phi(u)$.
+
+\item[$\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$:]
+Now we claim that $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$ in $L^2(Q_T)$.
+Firstly, since $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, we can by the Banach-Alaoglu theorem together with $L^2(Q_T)$ being a Hilbert space deduce that some subsequence of $\nabla \Phi(u_n)$ converges weakly to some $v$ in $L^2(Q_T)$.
+
+Let now $\psi \in C_0^\infty(Q_T)$ and fix $\epsilon > 0$.
+Since $Q_T$ is bounded we can use Egorov's theorem (cf.
+e.g.
+\citep[p.
+120]{weiss1999course}), to deduce that there is a set $E \subset Q_T$ with $|Q_T \setminus E| < \epsilon^2$ so that $\Phi(u_n)$ converges uniformly to $\Phi(u)$ in $E$.
+Hence, we have
+\begin{equation}
+\label{phi_distribution_convergence}
+\iint_{Q_T}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt = \iint_{E}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt + \iint_{Q_T \setminus E}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt.
+\end{equation}
+The first integral is controlled by the uniform convergence of $\Phi(u_n)$ on $E$. For the latter integral, use of Cauchy-Schwartz yields
+\begin{align*}
+\iint_{Q_T \setminus E}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt &\leq ||\Phi(u_n) - \Phi(u)||_{L^2(Q_T)}||\nabla \cdot \psi||_{L^2(Q_T\setminus E)} \\
+&\leq (||\Phi(u_n)||_{L^2(Q_T)} + ||\Phi(u)||_{L^2(Q_T)})||\nabla \cdot \psi ||_{L^\infty(Q_T)}|Q_T\setminus E|^\frac{1}{2},
+\end{align*}
+and here we use that $\Phi(u_n)$ is uniformly bounded in $L^2(Q_T)$ and that $\Phi(u) \in L^2(Q_T)$.
+So we can make both integrals on the right hand side  in \ref{phi_distribution_convergence} arbitrarily small, and conclude that
+\begin{equation*}
+\iint_{Q_T}\Phi(u_n)\nabla \cdot \psi dxdt \to \iint_{Q_T} \Phi(u) \nabla \cdot \psi dxdt.
+\end{equation*}
+
+Since this argument holds for all $\psi \in C_0^\infty (Q_T)$ we can conclude that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
+Also we have that weak convergence in $L^2(Q_T)$ implies distributional convergence, so $v= \nabla \Phi(u)$.
+
+This argument holds for every subsequence of $\nabla \Phi(u_n)$.
+I.e.
+every subsequence of $\nabla \Phi(u_n)$ has a subsequence that converges weakly to $\nabla \Phi(u)$ which implies that $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$ in $L^2(Q_T)$.
+
+\item[$u$ is a weak solution:]
+We have established that $u \in L^1(Q_T)$, and $\Phi(u) \in L^2(0,T: H^1(\Omega)) \subset L^1(0,T: W^{1,1}(\Omega))$, and so all that remains is to consider the convergence of
+\begin{equation}
+\iint_{Q_T} \{ \nabla\Phi(u_n) \cdot \nabla \eta - u_n \partial_t \eta \} dxdt = \int_\Omega u_{0,n}\eta\big|_{t=0}dx + \iint_{Q_T} f_n \eta dxdt,
+\end{equation}
+which holds for each $n$ and every $\eta \in C^1(\overline{Q}_T)$.
+But this is easily seen to hold in the limit by the weak convergence of $\nabla \Phi(u_n)$ in $L^2(Q_T)$, the convergence of $u_n$ and $u_{0,n}$ in $L^1(Q_T)$ and $L^1(\Omega)$, and the convergence of $f_n$ in $L^2(Q_T)$.
+
+\item[Establishing the energy inequality:]
+By the continuity of $\Psi$, we have that $\Psi(u_n(T))$ converges almost everywhere to $\Psi(u(T))$, and so by Fatou's Lemma (cf. \citep[p. 126]{weiss1999course}) 
+\begin{equation*}
+\int_\Omega \Psi(u(T))dx \leq \underset{n \to \infty}{\mathrm{liminf}}\int_\Omega \Psi(u_n(T))dx. 
+\end{equation*}
+
+In addition, the mapping $I[u] = ||\nabla u||_{L^2(Q_T)}$ is convex, and therefore weakly lower semicontinuous \citep[p. 468]{evans}, which means that
+\begin{equation*}
+\iint_{Q_T} |\nabla \Phi(u) |^2 dxdt \leq  \underset{n \to \infty}{\mathrm{liminf}} \iint_{Q_T} |\nabla \Phi(u_n)|^2 dxdt.
+\end{equation*}
+
+Putting, these two things together we can establish that
+\begin{align*}
+\iint_{Q_T} |\nabla \Phi(u) |^2 dxdt + \int_\Omega \Psi(u(T))dx &\leq \underset{n \to \infty}{\mathrm{liminf}} \iint_{Q_T} |\nabla \Phi(u_n)|^2 dxdt + \underset{n \to \infty}{\mathrm{liminf}}\int_\Omega \Psi(u_n(T))dx \\
+&\leq \underset{n \to \infty}{\mathrm{liminf}} \left[ \iint_{Q_T} |\nabla \Phi(u_n)|^2 dxdt + \int_\Omega \Psi(u_n(T))dx \right] \\
+&\leq \underset{n \to \infty}{\mathrm{liminf}}\left[ \int_\Omega \Psi(u_{0,n}) + \iint_{Q_T}f_n \Phi(u_n)dxdt \right] \\
+&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt,
+\end{align*}
+where we have used that the $u_n$ satisfies the energy inequality. This completes the proof.
+
+\end{description}
 \end{proof}

### 2014-12-12 draft_project.tex
Skrevet massemassemasse.

@@
 
+%Assumptions:
+\newtheorem{assumption}{Assumption}
+
 \theoremstyle{definition}
 \newtheorem{mydef}{Definition}[section]
-\newtheorem{example}{Example}[section]
+\newtheorem{example}{Example}%[section]
 
@@
 
- where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\phi: \mathbb{R} \to \mathbb{R}$. For now we assume that $\Phi$ is continuous and nondecreasing.
+ where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\Phi: \mathbb{R} \to \mathbb{R}$.
+
+The PDE (\ref{GPME}) encompasses some noteworthy special cases:
+\begin{example}[PME]
+When $\Phi(u) = u^m$ for $m>1$, (\ref{GPME}) is the Porous Medium Equation (PME), whose name is derived from its main application: Describing gas concentration flow in porous media, like rock.
+To allow for solutions with changing signs, one has $\Phi(u) = |u|^{m-1}u$.
+Notice that this choice of $\Phi$ is strictly increasing and locally Lipschitz continuous.
+\end{example}
+
+\begin{example}[FDE]
+With the same choice of $\Phi(u) = |u|^{m-1}u$, only now with $0<m<1$ yields the so-called Fast Diffusion Equation (FDE).
+$\Phi$ is still strictly increasing, but no longer locally Lipschitz continuous.
+\end{example}
+
+\begin{example}[Stefan problem]
+The Stefan problem can be posed with $\Phi(u) = (u-1)_+$, which is used to describe temperature distribution in a system with a phase transitions.
+E.g.
+melting an ice cube in a glass of water.
+Here $\Phi$ is no longer strictly increasing, which constitutes a degenerate problem.
+\end{example}
 
 \subsection{Basic sets and notation}
-Before delving into the actual the actual analysis of our problem, let's just get assure ourselves that we're on the same page when it comes to notation of various sets and function spaces.
+Before delving into the actual analysis of our problem, let's just assure ourselves that we're on the same page when it comes to notation of various sets and function spaces.
 
@@
 
-Most, if not all, of the notation concerning function spaces will follow the notation in \citep{evans} (see in particular Ch. 5).
+Most, if not all, of the notation concerning function spaces will follow the notation in \citep{evans} (see in particular Ch.
+5).
+In the following let $U$ be an open subset of $\mathbb{R}^d$, then we will denote by $C(U)$ the space of bounded and continuous functions with norm
+\begin{equation*}
+||u||_{C(U)} = \underset{x \in U}{\mathrm{sup}}|u(x)|.
+\end{equation*}
+Further, with $0< \gamma \leq 1$ we define the Hölder seminorm as
+\begin{equation*}
+|u|_{C^{0,\gamma}(U)} = \underset{x,y \in U, x\neq y}{\mathrm{sup}}\frac{|u(x)-u(y)|}{|x-y|^\gamma}
+\end{equation*}
+which enables the Hölder space $C^{0,\gamma}(U)$, with norm
+\begin{equation*}
+||u||_{C^{0,\gamma}(U)} = ||u||_{C(U)} + |u|_{C^{0,\gamma}(U)}.
+\end{equation*}
+
+With $C^k(U)$ being the $k$ times continuously differentiable functions in $U$, we define the Hölder space $C^{k,\gamma}(U)$ to be all $u \in C^{k}(U)$ si that the norm
+\begin{equation*}
+||u||_{C^{k,\gamma}(U)} = \sum_{|\alpha| \leq k} ||D^\alpha u||_{C^(U)} + \sum_{|\alpha| = k} |D^\alpha u |_{C^{0,\gamma}},
+\end{equation*}
+where we have adopted the multiindex notation of \citep{evans}.
+In addition we say that the boundary $U$, $\partial U$, is $C^{k, \alpha}$ if for every point on $\partial U$ there is a neighbourhood over which $\partial U$ describes the graph of a $C^{k,\alpha}$ function in $d-1$ coordinates, \citep{gilbarg2001elliptic}.
+
+Seeing as we're considering a time-dependent problem, different assumptions on the smoothness of a functions in space and time will emerge, and as such function spaces that reflect this are necessary.
+The spaces $C^k_r(U)$ are the $k$-times continuously differentiable in space and $r$ times continuously differentiable in time.
+Meaning that if $u \in C^k_r(U)$, then $\partial_t^m D^\alpha u$ exists and is bounded and continuous in $U$ for all $m \leq r$ and all multiindices $\alpha$ so that $|\alpha| \leq k$.
+
+We will also need to consider the spaces of strongly summable functions. Let $X$ be a normed space and $1\leq p < \infty$, then $u \in L^p(0,T:X)$ if
+\begin{equation*}
+||u||_{L^p(0,T:X)} = \left( \int_0^T ||u(t)||_X^p dt \right)^\frac{1}{p}
+\end{equation*} 
+is finite. This of course has the natural extension to $p=\infty$ with norm
+\begin{equation*}
+||u||_{L^\infty(0,T:X)} = \mathrm{ess \; sup}_{0\leq t \leq T} ||u(t)||_X.
+\end{equation*}
+
+The last function space we'll pay particular attention to in this section is the Hölder space $H^{l, l/2}(Q_T)$ \citep{ladyzhenskaya}, which consists of all $u$ that are continuous as well as $\partial_t^rD^\alpha u$ are continuous for all $r$ and $\alpha$ so that $2r + |\alpha| <l$.
+The norm is given as
+\begin{equation*}
+	||u||_{H^{l,l/2}(Q_T)} = \langle u \rangle^{(l)}_{Q_T} + \sum_{j=0}^{[l]}\langle u \rangle^{(j)}_{Q_T},
+\end{equation*}
+with
+\begin{align*}
+\langle u \rangle^{(j)}_{Q_T} &= \sum_{2r+|\alpha|=j} ||\partial_t^r D^\alpha u||_{C(\bar{Q}_T)} \\
+\langle u \rangle^{(l)}_{Q_T} &= \langle u \rangle^{(l)}_{x,Q_T} + \langle u \rangle^{(l/2)}_{t,Q_T} \\
+\langle u \rangle^{(l)}_{x,Q_T} &= \sum_{2r+|\alpha|=[l]} |\partial_t^r D^{\alpha}u|_{C^{0,l-[l]}_x(\bar{Q}_T)} \\
+ \langle u \rangle^{(l/2)}_{t,Q_T} &= \sum_{0 < l - 2r -|\alpha| < 2} |\partial_t^r D^\alpha u|_{C^{0,(l-2r-s)/2}_t(\bar{Q}_T)},
+\end{align*}
+with the Hölder semi-norm with respect to $x$ and $t$ respectively in the last two definitions being 
+\begin{align*}
+|u|_{C_x^{0,\rho}(Q_T)} &= \underset{\overset{(x,t),(y,t)\in Q_T}{x\neq y}}{\mathrm{sup}} \frac{|u(x,t) - u(y,t)|}{|x-y|^\rho} \\
+|u|_{C_t^{0,\rho}(Q_T)} &= \underset{\overset{(x,t),(x,s)\in Q_T}{t\neq s}}{\mathrm{sup}}\frac{|u(x,t) - u(x,s)|}{|t-s|^\rho},
+\end{align*}
+for $0 < \rho \leq 1$.
+
+Luckily this norm will not be of the most importance in what is to follow, but some acquaintance with it is useful.
 
@@
 	\begin{cases}
-		\partial_t u = \Delta \Phi(u) + f, \quad \text{ in } Q_T \\
-		u(x,0) = u_0(x), \quad \text{ in } \Omega \\
-		u(x,t) = 0, \quad \text{ on } \partial\Omega \times [0,T].
+		\partial_t u &= \Delta \Phi(u) + f, \quad \text{ in } Q_T \\
+		u(x,0) &= u_0(x), \quad \text{ in } \Omega \\
+		u(x,t) &= 0, \quad \text{ on } \partial\Omega \times [0,T].
 	\end{cases}
@@
 Here $Q_T = \Omega \times (0,T]$, where $T$ may very well be infinite. Furthermore we denote by $\Gamma_T = \overline{Q}_T\backslash Q_T$ the parabolic boundary.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		ASSUMPTIONS CAN POSSIBLY GO HERE???
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Classical solutions}
+The strictest sense in which we can have a solution of (\ref{HDP}) is that there is a $u \in C^2_1(Q_T)\cap C(\overline{Q}_T)$ for which $u\big|_{t=0} = u_0$,  $u\big|_{\partial\Omega \times [0,T]} = 0$, and the equality
+\begin{equation*}
+\partial_t u = \Delta \Phi(u) + f
+\end{equation*}
+holds everywhere in $Q_T$.
+This means we must also impose that $\Phi \in C^2(\mathbb{R})$ and that $f$ is continuous.
+If $u \in C^2_1(Q_T)$, $\Phi$ and $f$ satisfy this we call $u$ a classical solution of (\ref{HDP}).
+
 In this section it is helpful to reformulate (\ref{HDP}) as 
 \begin{equation}
+\label{general_parabolic_problem}
 	\begin{cases}
@@
 \begin{equation}
-Lu = -\sum_{i=1}^d \partial_{x_i}(a^i(x,t,u,\nabla u)) + a(x,t,u,\nabla u).
-\end{equation}
-We will need to assume that $a^i$ for every $i$ as well as $a$ are continuous functions with respect to all variables.
+Lu = -\sum_{i=1}^d \partial_{x_i}(a^i(x,t,u,\nabla u)) + a(x,t,u,\nabla u),
+\end{equation}
+where the functions $a^i$ and $a$ are given and continuous with respect to all variables.
 
@@
 
-In our setting it's easy enough to check that
+With the special case
 \begin{equation*}
@@
 \end{equation*}
+(\ref{general_parabolic_problem}) reduces to the homogeneous Dirichlet (\ref{HDP}),
 and so (\ref{uniform_parabolicity}) translates to
@@
 \label{uniform_parabGPME}
-\nu \leq \Phi'(u) \leq \mu.
-\end{equation}
+\nu \leq \Phi'(u) \leq \mu,
+\end{equation}
+for (\ref{HDP}) to be uniformly parabolic.
 We will in this section assume this to be true. I.e. that $\Phi'(u)$ is bounded from above as well as away from zero.
@@
 \begin{enumerate}[i)]
-	Suppose $\Omega$ is connected, and $u\in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$, then:
+	Suppose $\Omega$ is connected, and $u\in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$, and $\partial_t + L$ is uniformly parabolic, then:
 	\item If
@@
 Let's now use this lemma to get an $L^\infty$-bound on classical solutions.
-\begin{lemma}
+\begin{cor}
+\label{cor:Linf_bound_classical}
 Assume $\Phi \in C^2(\mathbb{R})$ and satisfy (\ref{uniform_parabGPME}).
@@
 	\end{equation}
-\end{lemma}
+\end{cor}
 
@@
 \label{lem:l1_stability_classical}
-For $\tau, t \in [0,T]$ the inequality 
+Let $u, \hat{u} \in C^2_1(Q_T)\cap C(\overline{Q}_T)$, be two classical solutions of the homogeneous Dirichlet problem (\ref{HDP}), with initial data $u_0$ and $\hat{u}_0$ as well as loading $f$ and $\hat{f}$, respectively.
+Assume further that $\Phi$ is strictly increasing, and $\Phi(0)=0$.
+Then, for $\tau, t \in [0,T]$, the inequality
 \begin{equation}
@@
 Define now $w = \Phi(u) - \Phi(\hat{u})$, and multiply $p(w)$ with the difference of (\ref{GPME}) for $u$ and $\hat{u}$ to get
-\begin{equation*}
+\begin{equation}
+\label{l1_stab_step1}
 \partial_t(u-\hat{u})p(w) = p(w)\Delta w + p(w)f.
-\end{equation*}
+\end{equation}
 Integrating over $\Omega$, and using integration by parts on the first part on the right hand side yields
+\begin{equation*}
+\int_\Omega p(w)\Delta w dx = -\int_\Omega p'(w)|\nabla w|^2dx + \int_{\partial \Omega}p(w)\nabla w \cdot \hat{n} dS,
+\end{equation*}
+where $\hat{n}$ is the unit normal vector pointing out of $\Omega$.
+The boundary integral term vanishes since $w\big|_{\partial \Omega} = 0$ and $p(0)=0$.
+Thus integration over $\Omega$ in (\ref{l1_stab_step1}) yields
 \begin{align*}
@@
 where the last step follows from the fact that $0 \leq p(w) \leq 1$. Here $(\cdot)_+ = \mathrm{max}\{\cdot, 0\}$.
-Now, let $p$ converge to the Heaviside function $H(w)$.
-Then, it is worth noticing that $H(w) = H(u-\hat{u})$, because of the strict monotonicity of $\Phi$.
-Also see that $\partial_t(u-\hat{u})_+ = \partial_t(u-\hat{u})H(u-\hat{u})$.
+Now, let $p$ converge pointwise to the positive sign function $\mathrm{sign}_0^+$ defined
+\begin{equation*}
+\mathrm{sign}^+_0(s) = \begin{cases}
+1&, \quad \text{for } s>0 \\
+0&, \quad \text{for } s\leq 0.
+\end{cases}
+\end{equation*}
+In the convergence of $p$, the integrand $\partial_t(u-\hat{u})p(w)$ is dominated by $\partial_t (u - \hat{u}) \mathrm{sign}_0^+(w)$ which is integrable from the continuity requirements, and so the Dominated Convergence Theorem implies that
+\begin{equation*}
+\int_\Omega \partial_t(u-\hat{u})p(w) dx \to \int_\Omega \partial_t (u - \hat{u}) \mathrm{sign}_0^+(w)dx.
+\end{equation*}
+
+Notice now that $\mathrm{sign}_0^+(u-\hat{u}) = \mathrm{sign}_0^+(\Phi(u) - \Phi(\hat{u}))$ because of the assumption that $\Phi$ is strictly increasing.
+In addition we have $\partial_t (u-\hat{u})_+ = \mathrm{sign}_0^+ \partial_t (u - \hat{u})$, in the weak derivative sense.
 Thus
+\begin{equation*}
+\int_\Omega \partial_t(u-\hat{u})p(w) dx \to \int_\Omega \partial_t (u-\hat{u})_+ dx,
+\end{equation*}
+which implies that
 \begin{equation*}
@@
 \label{cor:l1-contractivity_classical}
-For two smooth solutions, $u$ and $\hat{u}$ of the homoegenous Dirichlet problem (\ref{HDP}) with different initial data and loading, the $L^1$-estimate
+Under the same assumption as lemma \ref{lem:l1_stability_classical}
 \begin{equation}
@@
 \end{proof}
-
-\setcounter{obs}{0}
-\begin{obs}
-From this corollary, we get out immediately that (\ref{HDP}) has at most one solution in $C^{2,1}(Q_T)\cap C(\overline{Q}_T)$.
-\end{obs}
+An obvious consequence of lemma \ref{cor:l1-contractivity_classical} is uniqueness of classical solutions.
+\begin{cor}
+If $\Phi$ is strictly and $f$ is continuous, then the homogeneous Dirichlet problem (\ref{HDP}) has at most on solution in $C^2_1(Q_T)\cap C(\overline{Q}_T)$.
+\end{cor}
+
+\begin{proof}
+Assume $u$ and $v$ are two classical solutions of (\ref{HDP}) with the same initial data $u_0$, then corollary \ref{cor:l1-contractivity_classical} implies that
+\begin{equation*}
+||u(t)-v(t)||_{L^1(\Omega)} \leq 0
+\end{equation*}
+for all $t \in [0,T]$, which means that $u=v$ almost everywhere. Since both solutions are continuous we conclude that $u=v$ everywhere in $\overline{Q}_T$.
+\end{proof}
 
@@
 \begin{lemma}
-For a solution $u\in C^{2,1}(Q_T) \cap C(\overline{Q}_T)$ of (\ref{HDP})
+\label{lem:Energy_equality_classical}
+For a classical solution $u\in C^{2,1}(Q_T) \cap C(\overline{Q}_T)$ of (\ref{HDP})
 \begin{equation}
@@
 
-\begin{obs}
-We can go even further and deal with the last term on the right hand side: Assuming $f,\Phi(u) \in L^2(Q_T)$, then
-\begin{equation*}
-\iint_{Q_T} f\Phi(u)dxdt \leq \left(\iint_{Q_T} f^2 dxdt\right)^\frac{1}{2}\left(\iint_{Q_T} \Phi(u)^2 dxdt\right)^\frac{1}{2},
-\end{equation*}
-by Cauchy-Schwarz'. With the inequality $\sqrt{ab} \leq \frac{1}{4c}a + cb$ for $c>0$
-\begin{equation*}
-\iint_{Q_T} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\iint_{Q_T}\Phi(u)^2dxdt.
-\end{equation*}
-Lastly, because of the homogeneous Dirichlet conditions, we use the Poincaré inequality and set $c$ so that
-\begin{equation}
-\label{using_Poincare}
-\iint_{Q_T} f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt,
-\end{equation}
-and the final inequality becomes
-\begin{equation}
+We can go even further and deal with the last term on the right hand side of (\ref{spatial_derivative_bound}):
+
+\begin{cor}
+\label{cor:spatial_bound_w_poincare}
+In addition to the assumptions under lemma \ref{lem:Energy_equality_classical}, assume $f,\Phi(u) \in L^2(Q_T)$, then
+\begin{equation}
+\label{spatial_derivative_bound_w_poincare}
 \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
 \end{equation}
-\end{obs}
+for some $C$ dependent only on $\Omega$ and the number of spatial dimensions $d$.
+\end{cor}
+
+\begin{proof}
+For the term involving $f$ in (\ref{spatial_derivative_bound}) we use the inequality $ab \leq \frac{a^2}{4c} + cb^2$ for any reals $a$ and $b$, and any positive $c$, to get
+\begin{equation*}
+\iint_{Q_T}f\Phi(u) dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\iint_{Q_T}\Phi(u)^2 dxdt.
+\end{equation*}
+
+On the latter of the right hand terms we can for each $t \in [0,T]$ use the Poincaré inequality
+\begin{equation*}
+\int_\Omega \Phi(u)^2 dx \leq \tilde{C}\int_\Omega |\nabla \Phi(u) |^2 dx,
+\end{equation*}
+where $\tilde{C}>0$ depends only on $\Omega$ and $d$. We then have
+\begin{equation*}
+\iint_{Q_T} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\tilde{C}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt. 
+\end{equation*}
+
+We set now $c = \frac{1}{2\tilde{C}}$, and $C= \frac{\tilde{C}}{2}$, which results in
+\begin{equation*}
+\iint_{Q_T}f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt.
+\end{equation*}
+Putting this back into (\ref{spatial_derivative_bound}) we get
+\begin{equation}
+\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
+\end{equation}
+\end{proof}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 1$. If we multiply (\ref{GPME}) by $\zeta \partial_t\Phi(u)$ and integrate over $Q_T$ we get
+\begin{lemma}
+\label{lem:temporal_bound_classical}
+Let $u\in C^2_1(Q_T) \cap C(\overline{Q}_T)$ be a classical solution of (\ref{HDP}), where $f$ and $\partial_tf$ are continuous as well as $\Phi \in C^2(\mathbb{R})$.
+Further, let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 0$.
+Then
+\begin{equation}
+\label{temporal_bound_classical}
+\iint_{Q_T} \zeta \Phi'(u) |\partial_t u|^2 dxdt = \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla \Phi(u)|^2 - \partial_t(\zeta f) \Phi(u) \right\} dxdt.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+
+ If we multiply (\ref{GPME}) by $\zeta \partial_t\Phi(u)$ and integrate over $Q_T$ we get
 	\begin{equation}
@@
 	\begin{equation*}
-	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla \Phi(u)|^2 dxdt.
+	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T}\frac{\zeta}{2}\partial_t |\nabla \Phi(u)|^2 dxdt,
 	\end{equation*}
@@
 	\begin{equation*}
-	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla \Phi(u)|^2 dxdt - \frac{1}{2}\int_\Omega \left\{ |\nabla \Phi(u(T))|^2 - |\nabla \Phi(u_0)|^2 \right\} dx.
-	\end{equation*}
+	\int_0^T \zeta \int_\Omega \partial_t \Phi(u) \Delta \Phi(u) dxdt = \iint_{Q_T} \frac{\partial_t \zeta}{2} |\nabla \Phi(u)|^2 dxdt,
+	\end{equation*}
+	where the temporal end point integrals vanish since $\zeta(0) = \zeta(T) = 0$.
 	A similar inetgration by parts in the temporal dimension of the last term on the right hand side in (\ref{temporal_bound_start}) yields
 	\begin{equation*}
-	\iint_{Q_T} \zeta f \partial_t \Phi(u) dxdt = -\iint_{Q_T} \partial_t (\zeta f) \Phi(u) dxdt + \int_\Omega \left\{ f(T)\Phi(u(T)) - f(0)\Phi(u_0) \right\} dx.
-	\end{equation*}
-	For the last term in this integral we can do the same trick as we did previously for the energy estimate.
-We use Cauchy-Schwarz and the inequality $\sqrt{ab} \leq \frac{c^2}{4}a + \frac{1}{c^2}b$.
-Then, after using a Poincaré inequality we can choose $c$ so that the integrals of $|\nabla \Phi(u)|^2$ at the temporal endpoints are cancelled.
-In toto we end up with
-	\begin{align*}
-	\iint_{Q_T} \zeta \Phi'(u) |\partial_t u|^2 dxdt &\leq \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla \Phi(u)|^2 - \partial_t(\zeta f) \Phi(u) \right\} dxdt \\
-	&+ \frac{C}{2}\int_\Omega \left\{ f^2(T) - f^2(0) \right\} dx	\\
-	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla \Phi(u)|^2 - \partial_t(\zeta f) \Phi(u) \right\} dxdt \\
-	&+ C \iint_{Q_T} f\partial_t f dxdt.
-	\end{align*}
-
-A particular choice for $\zeta$, that's of interest is $\zeta(t) = 1$. Then we end up with the estimate
-\begin{equation}
-\label{temporal_bound}
-\iint_{Q_T} \Phi'(u) |\partial_t u|^2 dxdt \leq \iint_{Q_T}\left\{ -\partial_t f \Phi(u)   +Cf\partial_tf \right\}dxdt, 
-\end{equation}
-and in addition if $\Phi'(u)$ is bounded over all relevant values of $u$, e.g. given by the $L^\infty$-bound, then what we have here is an $L^2$-estimate of $\partial_t \Phi(u)$.
+	\iint_{Q_T} \zeta f \partial_t \Phi(u) dxdt = -\iint_{Q_T} \partial_t (\zeta f) \Phi(u) dxdt
+	\end{equation*}
+	where again we've made use of $\zeta(0) = \zeta(T) = 0$.
+	Putting all this back into (\ref{temporal_bound_start}) results in the desired equality 
+	\begin{equation}
+	\iint_{Q_T} \zeta \Phi'(u) |\partial_t u|^2 dxdt = \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla \Phi(u)|^2 - \partial_t(\zeta f) \Phi(u) \right\} dxdt.
+	\end{equation}
+\end{proof}
 
@@
 \begin{equation*}
-A(x,t,u,\nabla u) = a(x,t,u,\nabla u) - \sum_{i=1}^d \left[ \frac{\partial a_i(x,t,u,\nabla u)}{\partial u} + \frac{\partial a_i(x,t,u,\nabla u)}{\partial x_i} \right]
-\end{equation*}
-
-By the function space $H^{l, l/2}$, we mean the Banach space of functions $u$ that are continuous in $\bar{Q}_T$.
-So are all partial derivatives of the form $\partial_t^r D^\alpha u$, with $2r+|\alpha| <l$.
-The norm is given as
-\begin{equation*}
-	|u|_{Q_T}^{(l)} = \langle u \rangle^{(l)}_{Q_T} + \sum_{j=0}^{[l]}\langle u \rangle^{(j)}_{Q_T},
-\end{equation*}
-with
-\begin{align*}
-\langle u \rangle^{(j)}_{Q_T} &= \sum_{2r+|\alpha|=j} ||\partial_t^r D^\alpha u||_{C(\bar{Q}_T)} \\
-\langle u \rangle^{(l)}_{Q_T} &= \langle u \rangle^{(l)}_{x,Q_T} + \langle u \rangle^{(l/2)}_{t,Q_T} \\
-\langle u \rangle^{(l)}_{x,Q_T} &= \sum_{2r+|\alpha|=[l]} |\partial_t^r D^{\alpha}u|_{C^{0,l-[l]}(\bar{Q}_T)} \\
- \langle u \rangle^{(l/2)}_{t,Q_T} &= \sum_{0 < l - 2r -\alpha < 2} |\partial_t^r D^\alpha u|_{C^{0,(l-2r-s)/2}(\bar{Q}_T)},
-\end{align*}
-with the Hölder semi-norm with respect to $x$ and $t$ respectively in the last two definitions.
+A(x,t,u,\nabla u) = a(x,t,u,\nabla u) - \sum_{i=1}^d \left[ \frac{\partial a_i(x,t,u,\nabla u)}{\partial u}\partial_{x_i}u + \frac{\partial a_i(x,t,u,\nabla u)}{\partial x_i} \right]
+\end{equation*}
 
@@
 		\label{exist_cond1}
-		\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \Bigg|_{p=0} \geq 0, \quad A(x,t,u,0)u \geq -b_1 u^2 - b2
+		\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \Bigg|_{p=0} \geq 0, \quad A(x,t,u,0)u \geq -b_1 u^2 - b_2
 	\end{equation}
@@
 		\begin{cases}
-			\nu\xi^2 \leq \sum_{i,j=1}^d\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu \xi^2 \\
+			\nu|\xi|^2 \leq \sum_{i,j=1}^d\frac{\partial a_i(x,t,u,p)}{\partial p_j}\xi_i \xi_j \leq \mu |\xi|^2 \\
 			\sum_{i=1}^d \left(|a_i| + |\frac{\partial a_i}{\partial u}|\right)(1+|p|) + \sum_{i,j=1}^d |\frac{\partial a_i}{\partial x_j}| + |a| \leq \mu (1 + |p|)^2. 		
@@
 
-	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a Hölder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
+	\item For $(x,t) \in \overline{Q}_T$, $|u| \leq M$ and $|p| \leq M_1$, the functions $a_i$, $a$, $\frac{\partial a_i}{\partial p_j}$, $\frac{\partial a_i}{\partial u}$, and $\frac{\partial a_i}{\partial x_i}$ are continuous functions satisfying a Hölder condition in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively, for some $\beta \in (0,1]$.
 
@@
 	\begin{split}
-		&\Bigg| \frac{\partial a_i(x,t,u,p)}{\partial u}, \frac{a_i(x,t+h,u,p) - 		a_i(x,t,u,p)}{h}, \\
-		&\frac{\partial a}{\partial p}, \frac{\partial a}{\partial u}, \frac{a(x,t+h,u,p) - a(x,t,u,p)}{h} \Bigg| \leq \varphi(x,t).
+		&\Bigg| \frac{\partial a_i(x,t,u,p)}{\partial u}\Bigg|, \Bigg|\frac{a_i(x,t+h,u,p) - 		a_i(x,t,u,p)}{h}\Bigg|, \\
+		&\Bigg|\frac{\partial a}{\partial p}\Bigg|, \Bigg|\frac{\partial a}{\partial u}\Bigg|, \Bigg|\frac{a(x,t+h,u,p) - a(x,t,u,p)}{h} \Bigg| \leq \varphi(x,t).
 	\end{split}.
@@
 	\label{exist_cond5}
-	\psi_t - \frac{d}{dx_i}a_i(x,t,\psi,\psi_x) + a(x,t,\psi,\psi_x) = 0.
+	\psi_t - \frac{d}{dx_i}a_i(x,t,\psi,\nabla\psi) + a(x,t,\psi,\nabla\psi) = 0.
 	\end{equation}
@@
 
-	\item $\partial \Omega \in C^{2+\beta}$\footnote{I can't seem to find a definition of this sort of boundary in \citep{ladyzhenskaya}.
-However, \citep{evans} has something vaguely familiar, but here integer values of the exponent is assumed.}.
+	\item $\partial \Omega \in C^{2,\beta}$.
 \end{enumerate}
@@
 Under these conditions there exists a unique solution of problem (\ref{lady_parabolic_eq})  with boundary condition (\ref{lady_bc}) from the class $H^{2+\beta, 1+\beta/2}(\overline{Q}_T)$.
-Moreover, this solution has derivatives $u_{xt}$ from $L^2(\overline{Q}_T)$.
+Moreover, this solution has derivatives $\partial_t \nabla u$ from $L^2(\overline{Q}_T)$.
 \end{theorem}
@@
 \subsubsection{From general to specific: Existence for the GPME}
-The general porous medium equation we are concerned with can be written
+Now we'll consider theorem \ref{thm:classical_existence} in the setting of (\ref{HDP}) and under which conditions a solution is guaranteed to exist.
+The result is summarised in the following corollary.
+
+\begin{cor}
+\label{cor:GPME_existence}
+Assume the following conditions are satisfied:
+	\begin{enumerate}[a)]
+		\item 	$\Phi: \mathbb{R} \to \mathbb{R}$ is in $C^2(\mathbb{R})$, satisfies (\ref{uniform_parabGPME}), and $\Phi$, $\Phi'$ and $\Phi''$ are all Lipschitz continuous.
+
+		\item $f = f(x,t)$ is $C^1(Q_T)$, bounded and Lipschitz in both its variables.
+
+		\item $u_0$ is in $C^2_c(\Omega)$; $u_0\in C^2(\Omega)$ and has compact support.
+
+		\item $\partial \Omega$ is $C^{2+\beta}$-smooth.
+
+	\end{enumerate}
+Then (\ref{HDP}) has a unique solution $u\in C^{2}_1(Q_T)\cap C(\overline{Q}_T)$ for $T<\infty$. Moreover, this solution has derivatives $\partial_t \nabla u$ in $L^2(Q_T)$.
+\end{cor}
+
+\begin{proof}
+
+The general porous medium equation (\ref{GPME}) we are concerned with can be written
 \begin{equation*}
@@
 
-Let's go trhough each condition in theorem \ref{thm:classical_existence} to see what assumptions we must make to have a classical solution.
+Let's go through each condition in theorem \ref{thm:classical_existence} and verify that each are met.
 
@@
 	\end{equation*}
-	which means $A(x,t,u,0) = -f(x,t)$ (Also see that we need $\Phi \in C^2(\mathbb{R})$). Thus, according to (\ref{exist_cond1}) we need constants $b_1$ and $b_2$ so that
+	which means $A(x,t,u,0) = -f(x,t)$. Thus, according to (\ref{exist_cond1}) we need constants $b_1$ and $b_2$ so that
 	\begin{equation*}
@@
 	\end{equation*}
-	We are able to choose $b_1$ and $b_2$ if, for example, $f(x,t)$ is bounded in $\overline{Q}_T$.
+	We are able to choose $b_1$ and $b_2$ since $f$ is continuous and bounded in $\overline{Q}_T$.
 
@@
 	\begin{equation*}
-		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2.
-	\end{equation*}
-	Assuming that $\Phi'(u)$ is strictly positive and continuous for $|u|\leq M$ we can set
-	\begin{equation}
-	0 < \nu = \text{inf}_{|u| \leq M}\Phi'(u) < \text{sup}_{|u| \leq M}\Phi'(u) \leq \mu.
-	\end{equation}
+		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2,
+	\end{equation*}
+	which is satisfied because of (\ref{uniform_parabGPME}).
 
@@
 	to be Hölder continuous in $x$, $t$, $u$ and $p$ with exponents $\beta$, $\frac{\beta}{2}$, $\beta$ and $\beta$ respectively.
-If we choose $\beta = 1$ (i.e.
-Lipschitz continuous for all variables except $t$) the only additional assumption we need to make on $\Phi$ is that $\Phi^{(3)}(u)$ is bounded for $|u| \leq M$, which means that $\Phi \in W^{3,\infty}(\mathbb{R})$.
-The additional assumptions we need to make on $f$ is that it needs to be Lipschitz continuous with respect to $x$ and that
+This is satisfied for any $\beta \in (0,1]$ since $\Phi$, $\Phi'$, $\Phi''$ and $f$ are all assumed to be Lipschitz continuous.
+	With $\beta = 1$, the requirement of theorem \ref{thm:classical_existence} is that $f$ is Hölder continuous with exponent $1/2$ in time, i.e.
 	\begin{equation*}
@@
 	\end{equation*}
-	for some constant $C$.
-Note that for bounded domains, Lipschitz continuity implies Hölder continuity with lower exponent.
-So we could make the kind of a fortiori assumption that $f$ is Lipschitz continuous with respect to time.
-Or even that $f_t(x,t)$ is bounded.
-
-	\item For this condition we see that it seems even more natural to impose that $f$ is Lipschitz continuous in $t$, and that the domain is bounded.
-I.e.
-that $T<\infty$ and $\Omega$ is bounded.
-Then all the previous assumptions we've made on $\Phi$ and $f$ will ensure that this condition holds.
+	for some constant $C$. Note that for bounded domains, Lipschitz continuity implies Hölder continuity with lower exponent. Therefore, this is satisfied with $f$ Lipschitz in time.
+
+	\item This condition holds from $\frac{\partial a_i}{\partial u}$, $\frac{\partial a}{\partial t}$ (the rest of the expressions in the condition are zero), and since we're considering $Q_T$, with $T$ finite, constants are integrable.
 
@@
 	\end{equation*}
-	and so this condition isn't too hard to handle\footnote{I think...}.
+	and so this condition isn't too hard to handle.
 First off, we should require that $u_0$ vanish at the boundary, and that it is sufficiently smooth.
-To be more precise, $u_0$, $u'_0$ and $u''_0$ are all continuous and are zero at the boundary.
+To be more precise, $u_0$, $\nabla u_0$ and $\Delta u_0$ are all continuous and are zero at the boundary.
 The condition (\ref{exist_cond5}) holds trivially, because  $\Psi\big|_{\partial \Omega \times \{t=0\}} = 0$.
 
-	\item In this condition we can do nothing more than assume sufficient smoothness of the boundary.
+	\item This condition holds trivially.
 \end{enumerate}
-
-It seems only appropriate that we summarise this somehow. A nice little corollary tailored for our purposes is just what we need now.
-
-\begin{cor}
-\label{cor:GPME_existence}
-Assume the following conditions are satisfied:
-	\begin{enumerate}[a)]
-		\item 	$\Phi: \mathbb{R} \to \mathbb{R}$ is in $C^2(\mathbb{R})$, strictly increasing, and $\Phi$, $\Phi'$ and $\Phi''$ are all Lipschitz continuous.
-
-		\item $f = f(x,t)$ is $C^1(Q_T)$, bounded and Lipschitz in both its variables.
-
-		\item $u_0$ is in $C^2_c(\Omega)$; $u_0$ and its derivatives vanish near the boundary $\partial \Omega$.
-
-		\item $\partial \Omega$ is $C^{2+\beta}$-smooth.
-
-	\end{enumerate}
-Then (\ref{HDP}) has a unique solution $u\in C^{2,1}(\bar{Q}_T)$ for $T<\infty$. Moreover, this solution has derivatives $u_{xt}$ in $L^2(Q_T)$.
-\end{cor}
-
-We see that when these assumptions are fulfilled, the homogeneous Dirichlet problem is well posed, since uniqueness and stability are ensured by $L^1$-contractivity.
+All conditions of theorem (\ref{thm:classical_existence}) are met, which yields the conclusion that (\ref{HDP}) with the additional assumption of this corollary has a unique solution $u \in C^2_1(Q_T)\cap C(\overline{Q}_T)$.
+\end{proof}
+
+\setcounter{rem}{0}
+\begin{rem}
+We end this section on classical solutions with the remark that the assumptions in corollary \ref{cor:GPME_existence} is a subset of the assumptions for lemma \ref{cor:l1-contractivity_classical}.
+Therefore, two solutions $u$ and $\hat{u}$ aquired from corollary \ref{cor:GPME_existence} will also satisfy (\ref{l1_contractivity}), i.e.
+$L^1$-stability.
+Hence, The homogeneous Dirichlet problem (\ref{HDP}) with the assumptions in corollary \ref{cor:GPME_existence} is well-posed.
+\end{rem}
 
@@
 5]{vazquez2007porous} quite closely.
-However, the proofs are worked out in greater detail than presented there.
-We will, unless stated otherwise, assume that $\Phi$ is an increasing function, and not only stricly increasing.
+However, the proofs are worked out in much greater detail than presented there.
+We will, unless stated otherwise, assume that $\Phi$ is a strictly increasing function.
 
@@
 \end{equation}
-Now the inspired move\footnote{Of course, this isn't my proof so that sort of horn-tooting is in good taste.} is choosing
+Now the inspired move is choosing
 \begin{equation*}
@@
 This should hold for any test function $\eta$, and so the weak derivative of $u_2 - u_1$ with respect to time is zero.
-Because $u_2$ and $u_1$ have identical initial condition $u_0$ we conclude that $u_2 = u_1$.
+Because $u_2$ and $u_1$ have identical initial condition $u_0$ we conclude that $u_2 = u_1$ almost everywhere.
 \end{proof}
@@
 As the assumptions in theorem \ref{thm:uniqueness} may hint at, some additional assumptions on $u$ and $\Phi(u)$ needs to be put to ensure that the homogeneous Dirichlet problem is well posed in the weak setting.
-There are some alternatives, and of course, any further analysis will be informed what sort of additional condition we want a weak solution $u$ to fulfill.
+There are some alternatives, and of course, any further analysis will be informed by what sort of additional condition we want a weak solution $u$ to fulfill.
 The one we will be using here is guided by the notion that in a physical system the energy should be controlled, and is therefore called a weak energy solution.
@@
 \begin{obs}
-If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as with the energy identity in (\ref{spatial_derivative_bound}) to get that $\Phi(u) \in L^2(0,T: H_0^1(\Omega))$.
+If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as we did in deriving (\ref{spatial_derivative_bound_w_poincare}), to get that $\Phi(u) \in L^2(0,T: H^1_0(\Omega))$.
 \end{obs}
@@
 
-In the following we will assume $u_0 \in L_\Psi(\Omega)$ and $f\in L^p(\Omega)$ with $p = \frac{2d}{d+2}$ if $d \geq 3$, or for some $p>1$ if $d=1,2$\footnote{This choice of value for $p$, I can only say is a mystery for me at this moment, but it seems to be related to the Sobolev conjugate.
-Let's just stay curious and excited for now, shall we?}.
+In the following we will assume $u_0 \in L_\Psi(\Omega)$ and $f\in L^2(Q_T)$.
 
@@
 Assume $u_0 \in L_\Psi(\Omega)$ and $f \in L^p (\Omega)$.
-Then the homogeneous, general porous medium equation (\ref{HDP}) has a weak solution defined in an infinite time interval, $T=\infty$.
+Then the homogeneous, general porous medium equation (\ref{HDP}) has a weak solution defined in any finite time interval.
 We have $u \in L^\infty(0,T:L_\Psi(\Omega))$ and $\Phi(u) \in L^2(0,T:H_0^1(\Omega))$, and the energy inequality (\ref{energy_ineq}) holds.
@@
 \end{equation*}
-where $\varphi_{\frac{1}{n}}(s) = n\varphi\left( \frac{s}{n} \right)$ and $\varphi$ is the standard mollifier. Then, we can approximate $\Phi$ as
+where $\varphi_{\frac{1}{n}}(s) = n\varphi(ns)$ and $\varphi$ is the standard mollifier. Then, we can approximate $\Phi$ as
 \begin{align*}
@@
 
-We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$. We also ask that $|u_{0,n}| \leq $min$\{n,|u_0|\}$.
-
-Apparently, also according to \citep{vazquez2007porous}, we also approximate $f$ by a sequnce of functions $f_n$ that converges to $f$ in $L^p(Q_T)$ for all\footnote{Not sure if \textit{sic}...} $p<\infty$, and is so that $|f_n| \leq |f|$ for all $n$.
-
-\subsubsection{$u_0$, $f$ and $\partial_t f$ bounded}
+We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$. We also ask that $|u_{0,n}| \leq \mathrm{min}\{n,|u_0|\}$.
+This construction can be done as follows: First, define $\tilde{u}_n = \mathrm{max}\{ \mathrm{min}\{u_0, n\}, -n\}$, so $u_0$ is truncated at $\pm n$.
+Then let $(V_n)$ be a sequence of open subsets so that $V_n \subset V_{n+1}$ for all $n$ as well as $\cup_{n\in \mathbb{N}}V_n = \Omega$, and we require $\mathrm{dist}(V_n,\partial \Omega) \geq \frac{2}{n}$.
+Then we set $u_n = (\chi_{V_n}\tilde{u}_n)*\varphi_{\frac{1}{n}}$, where $\chi_{V_n}$ is the characteristic function for $V_n$ and $\varphi_{\frac{1}{n}}$ is the scaled standard mollifier in $\mathbb{R}^d$.
+The requirement on the distance between $V_n$ and $\partial \Omega$ we see is to ensure that $u_{0,n}$ and its derivatives vanish at the boundary.
+
+We also approximate $f$ by a sequence of $C^\infty(Q_T)$ functions $f_n$ that converge to $f$ in $L^2(Q_T)$, and is so that $|f_n| \leq |f|$ for all $n$.
+
+\subsubsection{$u_0$, $f$, $\partial_t f$ bounded and $\Phi$ locally Lipschitz}
 Our first lemma then reads
@@
 		\end{equation}			
-	By virtue of theorem \ref{thm:classical_existence}, this approximate problem has a unique solution $u_n \in C^{2,1}(\overline{Q}_T)$. In addition we can from the maximum principle see that
+	By virtue of corollary \ref{cor:GPME_existence} this approximate problem has a unique solution $u_n \in C^2_1(Q_T)\cap C(\overline{Q}_T)$.
+In addition we can from the corollary   \ref{cor:Linf_bound_classical} see that
 	\begin{align*}
 	||u_n||_{L^\infty(Q_T)} &\leq ||u_{0,n}||_{L^\infty(\Omega)} + T||f_n||_{L^\infty(Q_T)} \\
-	&\leq ||u_0||_{L^\infty(\Omega)} + T||f||_{L^\infty(Q_T)} = C.
+	&\leq ||u_0||_{L^\infty(\Omega)} + T||f||_{L^\infty(Q_T)} = M.
 	\end{align*}
@@
 
-	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, and do exactly as when deriving (\ref{spatial_derivative_bound}) to get 
-	\begin{equation*}
-	\int_\Omega \Psi_n(u_n(T))dx + \iint_{Q_T}|\nabla w_n|^2dxdt = \int_\Omega \Psi_n(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt.
-	\end{equation*}
-	Considering the second term on the right hand side we have
-	\begin{equation*}
-	\iint_{Q_T}f_n w_n dxdt \leq C\iint_{Q_T}f_n^2 dxdt + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2dxdt,
-	\end{equation*}
-	after exactly the same argument as we did with (\ref{using_Poincare}). After putting it back
+	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, and use (\ref{spatial_derivative_bound_w_poincare}) to get 
 	\begin{equation}
 	\label{exist_proof_spatial}
-	\int_\Omega \Psi_n(u_n(T))dx + \frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
-	\end{equation}
+	\frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dx  \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
+	\end{equation}
+	for each $n$.
+
 	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
@@
 	\end{equation*}
-	from which it is to see that $\Psi_n(u) \leq 0$ for every $u \in \mathbb{R}$. It is also very much worthwhile to see that because $\Phi_n$ is monotone for every $n$ we have the estimate
+	from which it is easy to see that $\Psi_n(u) \leq 0$ for every $u \in \mathbb{R}$. It is also very much worthwhile to see that because $\Phi_n$ is monotone for every $n$ we have the estimate
 	\begin{equation*}
@@
 	\end{equation*}
-	Now we do as in appendix \ref{app:Phi} to get a bound in $\Phi_n$ in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
+
+	Now we derive an estimate on $\Phi_n$ in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
 	\begin{align*}
@@
 	|\Phi_n(u_0)| &\leq |\Phi(u_0)| + |u_0| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u_0-y) - \Phi(u_0)| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
-	&= K.
-	\end{align*}
-	All terms are bounded since $u_0$ is bounded, and so we get the crude, but sufficient estimate
+	& \leq \underset{|s| \leq ||u_0||_\infty}{\mathrm{sup}}|\Phi(s)| + ||u_0||_{\infty}\\
+	& + \underset{\underset{y\in[-1/n,1/n]}{|s| \leq ||u_0||_{\infty}}}{\mathrm{sup}}|\Phi(s-y) - \Phi(s)| + \mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
+	&= K < \infty.
+	\end{align*}
+	All terms are bounded since $u_0$ is bounded, and so we finally get the estimate
 	\begin{equation*}
@@
 Most importantly, this shows that the left hand side of (\ref{exist_proof_spatial}) is bounded independently of $n$, which immediately implies that $\nabla w_n$ is a bounded sequence in $L^2(Q_T)$.
-
-	\item[Control of the temporal derivative:] The derivation of (\ref{temporal_bound}) holds up in this case and we have
-	\begin{equation*}
-	\label{exist_proof_temporal}
-	\iint_{Q_T} \Phi'_n(u_n)|\partial_t u_n|^2 dxdt \leq \iint_{Q_T} \left\{ -\partial_t f_n \Phi_n(u_n) + Cf_n\partial_tf_n \right\} dxdt.
-	\end{equation*}
-	Just to reiterate, $C$ is here the constant given by Poincaré inequality, and is as such only dependent on $\Omega$.
-
-	Now, since we have assumed $\Phi$ to be locally Lipschitz, $|\Phi_n'(u_n)| \leq K < \infty$ over the relevant values of $u_n$, we notice that $|\partial_t w_n|^2 \leq K|\Phi'_n(u_n) (\partial_t u_n)^2|$.
-We have assumed both $f$ and $\partial_t f$ to be bounded, so we can put a uniform bound on the right hand side, independent of $n$.
-We conclude that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T)$.
-
-	\item[Using a compactness argument:]From the two previous parts we have that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.
-The energy estimate continues to hold in the limit as
-	\begin{equation}
-	\iint_{Q_T}|\nabla w|^2 dxdt \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}fw dxdt.
-	\end{equation}
-	Notice that since $w \in L^2(Q_T)$, we can from this inequality conclude that $w \in H^1(Q_T)$.
+Notice also that from the Poincaré inequality,
+	\begin{equation*}
+	\iint_{Q_T}w_n^2 dxdt \leq C\iint_{Q_T} |\nabla w_n|^2dxdt,	
+	\end{equation*}
+	$w_n$ is also uniformly bounded in $L^2(Q_T)$.
+
+	\item[Control of the temporal derivative:] From lemma \ref{lem:temporal_bound_classical} we have for each $n$ and every cutoff function $\zeta\in C^1([0,T], [0,1])$
+	\begin{equation}
+	\iint_{Q_T} \zeta \Phi'_n(u_n) |\partial_t u_n|^2 dxdt = \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt.
+	\end{equation}
+
+	Take now $0<\tau < \frac{T}{2}$, and take $\zeta(t)=1$ for $t\in [\tau, T-\tau]$. We define $Q_T^\tau = \Omega \times (\tau, T - \tau)$, then
+	\begin{align*}
+	\iint_{Q_T^\tau}\Phi'_n(u_n)|\partial_t u_n|^2 dxdt & \leq \iint_{Q_T}\zeta\Phi'_n(u_n)|\partial_t u_n|^2 dxdt \\
+	&= \iint_{Q_T} \left\{ \frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t(\zeta f_n) w_n \right\} dxdt.
+	\end{align*}
+	From the uniform boundedness of $w_n$ and $\nabla w_n$ in $L^2(Q_T)$ as well as the boundedness of $\partial_t f$ enables us to deduce from the above inequality that $\Phi'_n(u_n)|\partial_t u_n|^2$ is uniformly bounded in $L^1(Q_T^\tau)$ for all $\tau > 0$.
+	Recall now that $|u_n| \leq M$ and $M$ is a constant independent of $n$, and so $[-M,M]$ is a compact subset of $\mathbb{R}$.
+By the local Lipschitz assumption on $\Phi$ there is a constant $L$, so that $\Phi'(s)\leq L$ for all $s\in [-M,M]$, and from the definition of $\Phi_n$ we then have that $\Phi'_n(s) \leq L + 1$ for all $s \in [-M,M]$ and all $n$.
+Hence $|\partial_t w_n|^2 \leq (L+1)\Phi'_n(u_n)|\partial_t u_n|^2$, and we have that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T^\tau)$.
+
+	\item[Using a compactness argument to get a weak limit of $w_n$:]From the two previous parts we have that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T^\tau)$ for $\tau >0$.
+The fact that we were only able to bound $\partial_t w_n$ in $L^2(Q_T^\tau)$ causes some problems in using the Rellich-Kondrachov theorem to get a converging subsequence of $w_n$.
+We'll remedy this by the following diagonal argument:
+	Let $(\tau_m)$ be a positive, decreasing sequence converging to $0$.
+	\begin{enumerate}[i)]
+	\item Consider $Q_T^{\tau_1}$.
+Then $w_n$ is bounded sequence in $H^1(Q_T^{\tau_1})$, and we use theorem \ref{Rellich} to get a subsequence $(w_{n_j}^1)$ that converges strongly to some $\tilde{w}_1$ in $L^2(Q_T^{\tau_1})$.
+
+	\item $w_{n_j}^1$ is uniformly bounded in $H^1(Q_T^{\tau_2})$, and we use theorem \ref{Rellich} again to get a subsequence $(w_{n_j}^2)$ that converges to $\tilde{w}_2$.
+We have that $\tilde{w}_2 = \tilde{w}_1$ in $L^2(Q_T^{\tau_1})$.
+
+	\item We proceed in this manner and for each $m \in \mathbb{R}$.
+$w_{n_j}^{m-1}$ is uniformly bounded in $H^1(Q_T^{\tau_m})$, so we use theorem \ref{Rellich} to get another subsequence $(w_{n_j}^m)$ that converges to $\tilde{w}_m$ in $L^2(Q_T^{\tau_m})$.
+
+	\item We define the subsequence $(w_{n_j})$ by $w_{n_j} = w_{n_j}^j$, which will converge to some $w$ in $L^2(Q_T^\tau)$ for every $\tau > 0$, and hence in $L^2_loc(Q_T)$.
+Without loss of generality we assume $w_{n_j}$ converges to $w$ almost everywhere in $Q_T$ (If not, take yet another subsequence so that it does).
+\end{enumerate}
+
+	To determine that $w_{n_j}$ converges weakly to $w$ in $L^2(Q_T)$ we first note that every subsequence of $w_{n_j}$ is bounded in $L^2(Q_T)$ and by Banach-Alaoglu's theorem and that $L^2(Q_T)$ is a Hilbert deduce that the subsequence has a subsequence that converges weakly to some $v$.
+If we can prove that $v=w$ in $L^2(Q_T)$, then $w_{n_j}$ converges weakly to $w$, since every subsequence has a weakly convergent subsequence with the same limit.
+
+	So assume that $v\neq w$, then there is an $\epsilon > 0$ and a subset $E\subset Q_T$ with positive measure where $|v-w| \geq \epsilon$. We can without loss of generality assume that $v > w$ in $E$.
+
+	By the pointwise convergence of $w_{n_j}$ to $w$ and Egorov's theorem \citep[p. 120]{weiss1999course}	
+	there is a measurable set $B\subset E$ with positive measure over which $w_{n_j}$ converges uniformly to $w$. Therefore, for any $\delta > 0$ and sufficiently large $n$,
+	\begin{equation*}
+	\iint_B |w_{n_j}-w|dxdt \leq \delta |B|,
+	\end{equation*}
+	where $|B|>0$ is the measure of $B$. We conclude that
+	\begin{equation*}
+	\iint_B w_{n_j}dxdt \to \iint_B wdxdt.
+	\end{equation*}
+
+	However, since $B$ is measurable the characteristic function $\chi_B \in L^2(Q_T)$, and by the weak convergence of $w_{n_j}$ to $v$ we have
+	\begin{equation*}
+	\iint_B w_{n_j}dxdt \to \iint_B vdxdt \geq \iint_B wdxdt + \epsilon|B|,
+	\end{equation*}
+	which is a contradiction. We conclude that $v=w$, and since this is true for any weakly convergent subsequence of $w_{n_j}$, this implies that $w_{n_j}$ converges weakly to $w$ in $L^2(Q_T)$.
 
@@
 \label{sec:derivative}
-
-We are now concern with whether
+In this section we prove the assertion made in the proof of theorem \ref{thm:uniqueness} regarding passing the derivative inside an integral.
+
+\begin{lemma}
+Let $\varphi \in L^2(0,T: H^1(\Omega))$, then 
 \begin{equation}
@@
 \end{equation}
-holds or not for $\varphi \in L^2(0,T:H_0^1 (\Omega))$. 
+weakly in $H^1_0(\Omega)$, meaning 
+\begin{equation*}
+\int_\Omega \psi \nabla \left(\int_t^T \varphi ds \right) dx = \int_\Omega \psi \left(\int_t^T \nabla \varphi ds \right) dx
+\end{equation*}
+for all $\psi \in H^1_0(\Omega)$.
+\end{lemma}
+
+\begin{proof}
+
 For simplicity we now only consider one spatial dimension.
@@
 To extend the result to $L^2(0,T:H_0^1 (\Omega))$ we use that $C_c^\infty$ is dense in this space.
-So let $\{\psi_n\},\{\varphi_n\}$ be two sequence converging to $\psi$ and $\varphi$ in $L^2(\Omega)$ and $L^2(0,T:H_0^1(\Omega))$ respectively.
+So let $\{\psi_n\},\{\varphi_n\}$ be two sequence converging to $\psi$ and $\varphi$ in $H^1_0(\Omega)$ and $L^2(0,T:H_0^1(\Omega))$ respectively.
 Considering the left hand side of (\ref{results_diff_first}), we get
@@
 &\left|\int_{\Omega}\psi \partial_x \left( \int_t^T\varphi ds \right)dx - \int_{\Omega}\psi_n \partial_x \left( \int_t^T \varphi_n ds \right) dx \right| \\
-&\leq  \left| \int_{\Omega} \psi \partial_x \left(\int_t^T \varphi - \varphi_n ds\right)dx \right| + \left| \int_{\Omega}(\psi - \psi_n)\partial_x\left(\int_t^T \varphi_n ds\right) dx \right| \\
-&\leq ||\psi||_{L^2(\Omega)}|(\varphi -\varphi_n)|_{L^2(H_0^1)} + ||\psi-\psi_n||_{L^2}| \varphi_n |_{L^2(H_0^1)} \\
-&\leq ||\psi||_{L^2(\Omega)}||(\varphi -\varphi_n)||_{L^2(H_0^1)} + ||\psi-\psi_n||_{L^2}|| \varphi_n ||_{L^2(H_0^1)} \\
-&\to 0,
-\end{align*}
-after using the triangle- and Cauchy-Schwarz' inequality as well as the assumptions on convergence.
-
-An exactly similar approach can be done to the right hand side, and so passing the limit in (\ref{results_diff_first}) we get
-\begin{equation}
-\label{result_diff_final}
-\int_\Omega \psi \partial_x\left(\int_t^T \varphi(x,s)ds\right)dx = \int_\Omega \psi \left( \int_t^T \partial_x \varphi(x,s)ds \right) dx.
-\end{equation}
-
+&\leq \underbrace{\left| \int_{\Omega} \psi \partial_x \left(\int_t^T \varphi - \varphi_n ds\right)dx \right| }_{I} + \underbrace{\left| \int_{\Omega}(\psi - \psi_n)\partial_x\left(\int_t^T \varphi_n ds\right) dx \right|}_{II}
+\end{align*}
+after adding and subtracting $\int_\Omega \psi \partial_x \left(\int_t^T \varphi_n ds\right)dx$.
+
+Let's go over these two integrals one at a time.
+\begin{enumerate}[I:]
+
+\item After using integration by parts and Cauchy-Schwarz, the first integrals is estimated as
+\begin{align*}
+\left| \int_{\Omega} \psi \partial_x \left(\int_t^T \varphi - \varphi_n ds\right)dx \right| &= \left| \int_\Omega (\partial_x \psi) \int_t^T\varphi - \varphi_n ds dx \right| \\
+&\leq ||\psi||_{H^1(\Omega)}\big|\big| \int_t^T \varphi - \varphi_n ds \big|\big|_{L^2(\Omega)}.
+\end{align*}
+For the latter of this factors we notice that since norms are convex we can use Jensen's inequality \citep[Theorem 2, p. 705]{evans} to get
+\begin{align*}
+\big|\big| \int_t^T \varphi - \varphi_n ds \big|\big|_{L^2(\Omega)} &\leq \int_t^T ||\varphi - \varphi_n||_{L^2(\Omega)}ds \\
+&\leq ||\varphi - \varphi_n||_{L^2(Q_T)} \\
+&\leq ||\varphi - \varphi_n||_{L^2(0,T: H^1(\Omega))},
+\end{align*}
+which we control by the convergence of $\varphi_n$ to $\varphi$.
+
+\item We do exactly the same steps as we did immediately above for I, but now convergence is controlled by the convergence of $\psi_n$ to $\psi$ in $H^1(\Omega)$.
+
+\end{enumerate}
+From the convergence of $I$ and $II$ we deduce that
+\begin{equation}
+\label{diff_results_LHS}
+\int_{\Omega}\psi \partial_x \left( \int_t^T\varphi ds \right)dx = \lim_{n\to \infty}\int_{\Omega}\psi_n \partial_x \left( \int_t^T \varphi_n ds \right) dx.
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+The right hand side can be handled identically, save for a detail.
+We do the same decomposition as
+\begin{align*}
+&\left| \int_\Omega \psi \left( \int_t^T \partial_x \varphi ds \right)dx - \int_\Omega \psi_n \left( \int_t^T \partial_x \varphi_n ds \right)dx \right| \\
+&\leq \underbrace{ \left| \psi \left( \int_t^T \partial_x (\varphi - \varphi_n)ds \right) dx\right|}_{I} + \underbrace{ \left| \int_\Omega (\psi - \psi_n) \left( \int_t^T \partial_x \varphi_n ds \right) dx \right|}_{II}.
+\end{align*}
+
+Again, let's take these term by term:
+
+\begin{enumerate}[I:]
+
+\item Using Cauchy-Schwarz immediately gives
+\begin{align*}
+\left| \psi \left( \int_t^T \partial_x (\varphi - \varphi_n)ds \right) dx\right| & \leq ||\psi||_{L^2(\Omega)} \big| \big| \int_t^T \partial_x(\varphi - \varphi_n) ds \big| \big|_{L^2(\Omega)} \\
+& \leq ||\psi||_{H^1(\Omega)}||\varphi - \varphi_n||_{L^2(0,T:H^1(\Omega))},
+\end{align*}
+where Jensen's inequality has been put to use yet another time. This is controlled by the convergence of $\varphi_n$ to $\varphi$ in $L^2(0,T: H^1(\Omega))$.
+
+\item The same steps as immediately above, only now convergence is controlled by the convergence of $\psi_n$ to $\psi$. 
+\end{enumerate}
+
+Hence we deduce that
+\begin{equation}
+\label{diff_results_RHS}
+\int_\Omega \psi \left( \int_t^T \partial_x \varphi ds \right)dx = \lim_{n \to \infty} \int_\Omega \psi_n \left( \int_t^T \partial_x \varphi_n ds \right)dx
+\end{equation}
+
+With (\ref{diff_results_RHS}) and (\ref{diff_results_LHS}) we get
+\begin{align*}
+\int_{\Omega}\psi \partial_x \left( \int_t^T\varphi ds \right)dx &= \lim_{n\to \infty}\int_{\Omega}\psi_n \partial_x \left( \int_t^T \varphi_n ds \right) dx \\
+&= \lim_{n \to \infty} \int_\Omega \psi_n \left( \int_t^T \partial_x \varphi_n ds \right)dx \\
+&= \int_\Omega \psi \left( \int_t^T \partial_x \varphi ds \right)dx,
+\end{align*}
+which is the final result for differentiation in one spatial dimension.
 To get the more general (\ref{diff_int}), we simply apply this result for each individual spatial dimension while keeping the others fixed.
+
+\end{proof}
 

### 2014-12-13 draft_project.tex
Fått skrevet litt mer, men fortsatt en del igjen å gjøre.

@@
 
-	\item We define the subsequence $(w_{n_j})$ by $w_{n_j} = w_{n_j}^j$, which will converge to some $w$ in $L^2(Q_T^\tau)$ for every $\tau > 0$, and hence in $L^2_loc(Q_T)$.
+	\item We define the subsequence $(w_{n_j})$ by $w_{n_j} = w_{n_j}^j$, which will converge to some $w$ in $L^2(Q_T^\tau)$ for every $\tau > 0$, and hence in $L^2_{loc}(Q_T)$.
 Without loss of generality we assume $w_{n_j}$ converges to $w$ almost everywhere in $Q_T$ (If not, take yet another subsequence so that it does).
@@
 
+	\item[$\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$:]
+	First off we note that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense. Indeed, the distributional gradient of $w_{n_j}$ is defined by
+	\begin{equation}
+	\iint_{Q_T}\nabla w_{n_j}\cdot \psi dxdt = -\iint_{Q_T} w_{n_j} \nabla \cdot \psi dxdt ,
+	\end{equation}
+	which is to hold for every $\psi \in C^\infty_c(Q_T)$. Since $w_{n_j}$ converges weakly to $w$
+	\begin{align*}
+	\iint_{Q_T}\nabla w_{n_j} \cdot \psi dxdt &= -\iint_{Q_T} w_{n_j} \nabla \cdot \psi dxdt \\
+	&\to -\iint_{Q_T} w \nabla \cdot \psi dxdt \\
+	&= \iint_{Q_T} \nabla w \cdot \psi dxdt,
+	\end{align*}
+	where the last inequality is by definition of the distributional derivative. From this we deduce that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense.
+
+	Notice now that since $\nabla w_{n_j}$ is a bounded sequence in $L^2(Q_T)$ we can use Banach-Alaoglu's to say that every subsequence of $\nabla w_{n_j}$ has a weakly converging subsequence converging to some limit $v$.
+Since weak convergence implies convergence in the distributional sense and distributional limits are unique, we have that $v=\nabla w$.
+	Thus $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
+
+	 Lastly, note that with $w, \nabla w \in L^2(Q_T)$, $w \in L^2(0,T: H^1(\Omega))$.
 	\item[Convergence of $u_{n_j}$:] Both $\Phi$ and its approximations $\Phi_n$ all admit a continuous inverse, and so
@@
 Hence we can use proposition \ref{prop:inverse_uniform} to make the first term in the above inequality arbitrarily small.
-The second term is controlled by the observation that since $w_{n_j}$ converges to $w$ in $L^2(Q_T)$, the convergence is also pointwise, and the continuity of $\Phi^{-1}$.
+The second term is controlled by the almost everywhere convergence of $w_{n_j}$ to $w$ and the continuity of $\Phi^{-1}$.
 That means that
@@
 	 \end{equation*}
-	 pointwise. We immediately see that $\Phi(u) = w$.
+	 almost everywhere. We immediately see that $\Phi(u) = w$.
 
 	 More importantly, since we have the uniform bound $u_{n_j} \leq M$ in $Q_T$ we can use the Dominated Convergence Theorem to state that $u_{n_j} \to u$ in $L^1(Q_T)$.
-
-	\item[$u$ is a weak energy solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}(\Omega))$\footnote{Actually, this may not be as easy to see as I've stated here.
-Need to use yet another estimate to show this.}.
+	 It is also easy to see that
+	 \begin{equation}
+	 ||u||_{L^2(Q_T)} \leq M||u||_{L^1(Q_T)},
+	 \end{equation}
+	 which means that $u \in L^2(Q_T)$.
+
+	\item[$u$ is a weak solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}_0(\Omega))\subset L^2(0,T: H^1_0(\Omega))$ since $\Omega$ is bounded.
 So what's left is to show that
@@
 	All the terms are controlled by the convergences of $w_n$, $u_n$, $u_{0,n}$, as long as the limit is taken along the subsequence for which we know $w_n$ converges.
-Thus, (\ref{claim_weak_solution}) holds, and $u$ is a weak energy solution.
-
-	We have from before that $u\in L^1(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique.
+Thus, (\ref{claim_weak_solution}) holds, and $u$ is a weak solution.
+
+	We have from before that $u\in L^2(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique.
 In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak energy energy solution, and so the uniqueness precludes any other accumulation point than $u$.
@@
 
+	\item[Fulfillment of the energy inequality:]
+	We note that $\Psi_n(u_n)$ converges almost everywhere to $\Psi(u)$, which is shown similarly to how we showed that $u_{n_j}$ converges almost everywhere to $u$. We use the triangle inequality as
+	\begin{equation}
+	|\Psi_n(u_n) - \Psi(u)| \leq |\Psi_n(u_n) - \Psi(u_n)| + |\Psi(u_n) + \Psi(u)|.
+	\end{equation}
+	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see proposition \ref{prop:Psi_uniform_convergence}) to control the first term.
+The second term is controlled by the almost everywhere convergence of $u_n$ to $u$ and the continuity of $\Psi$.
+By Fatou's lemma \citep[p.
+162]{weiss1999course} and that $\Psi_n(u_n)$ are all nonnegative
+	\begin{equation}
+	\int_\Omega \Psi(u(T)) dx \leq \liminf_{n \to \infty} \int_\Omega \Psi_n(u_n(T))dx.
+	\end{equation}
+
+	In addition, since $|\cdot|^2$ is convex and nonnegative, the functional $I[u]:= ||\nabla u||^2_{L^2(Q_T)}$ is weakly lower semicontinuous (cf.
+\citep[Theorem 1, p.
+468]{evans}).
+Then, since $w_n$ converges weakly to $w$ we have that
+	\begin{equation}
+	\iint_{Q_T}|\nabla w|^2 dxdt \leq \liminf_{n \to \infty} \iint_{Q_T} |\nabla w_n|^2 dxdt.
+	\end{equation}
+
+	Putting these two together and using a property of the limit inferior yields
+	\begin{align*}
+	\iint_{Q_T}|\nabla w|^2dxdt + \int_\Omega \Psi(u(T))dx &\leq \liminf_{n \to \infty} \iint_{Q_T} |\nabla w_n|^2 dxdt + \liminf_{n \to \infty} \int_\Omega \Psi_n(u_n(T))dx \\
+	&\leq \liminf_{n \to \infty} \left[ \iint_{Q_T} |\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dx \right].
+	\end{align*}
+
+	Recall now that by lemma \ref{lem:Energy_equality_classical} 
+	\begin{equation*}
+	\iint_{Q_T} |\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dxdt = \int_\Omega \Psi(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt,
+	\end{equation*}
+	for each $n$, and so
+	\begin{align*}
+	\iint_{Q_T}|\nabla w|^2dxdt + \int_\Omega \Psi(u(T))dx &\leq \liminf_{n \to \infty} \left[\int_\Omega \Psi(u_{0,n})dx + \iint_{Q_T}f_n w_n dxdt \right] \\
+	&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f w dxdt,
+	\end{align*}
+	where in the last step we've made use of that $u_{0,n}$ converges to $u_0$ in $L_{\Psi}(\Omega)$, $w_n$ converges weakly to $w$ and the convergence of $f_n$ to $f$, both in $L^2(Q_T)$.
+This shows that (\ref{energy_ineq}) is satisfied, making $u$ a weak energy solution.
 \end{description}
@@
 \label{lem:weak_existence_part2}
-Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$ and $\partial_t f$ are bounded.
+Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$ and $\partial_t f$ are bounded, but still strictly increasing.
 \end{lemma}
@@
 The strategy for showing that $u_n$ converges to a weak solution will be similar to that of lemma \ref{lem:existence_part1}, only now we will use the Rellich-Kondrachov Compactness Theorem on another sequence than $w_n$.
-I.e.
-we need a bounded sequence in $H^1(Q_T)$.
-To that end we define for $u \in \mathbb{R}$
 \begin{equation}
@@
 
-Seeing as estimate (\ref{exist_proof_spatial}), we can argue exactly as we did in the previous proof to say that $\nabla z_n$ is uniformly bounded in $L^2(Q_T)$.
+Considering (\ref{exist_proof_spatial}), we can argue exactly as we did in the previous proof to say that $\nabla z_n$ is uniformly bounded in $L^2(Q_T)$.
 Similarly we have the two inequalities
@@
 \end{equation*}
-The estimate (\ref{exist_proof_temporal}) holds in this case as well, and by the assumptions on $f$ and its approximations we also have a uniform bound of $\partial_t z_n$ in $L^2(Q_T)$.
-Hence $z_n$ is a bounded sequence in $H^1(Q_T)$, and we can utilize the Rellich-Kondrachov Compactness Theorem (theorem \ref{Rellich}) again to conclude that there is a subsequence $\{z_{n_j}\}$ converging to some $z$ in $L^2(Q_T)$.
+Doing the same as in the previous proof we deduce that $z_n$ is uniformly bounded in $H^1(Q_T^\tau)$, for all $\tau$, and after an identical diagonal argument as before $(z_n)$ contains a subsequence that converges almost everywhere to some $z$.
+The convergence happens also weakly in $L^2(Q_T)$.
+We denote this subsequence by $(z_{n_j})$.
 
@@
 
-Similarly we can show that $w_{n_j}$ converges to $w=\Phi(u)$ and that $w \in L^2(Q_T)$.
-In addition, from a previous argument $\nabla w_n$ is bounded in $L^2$ independent of $n$, and so we conclude that $w \in H^1(Q_T)$.
-
-From this point on, proving that $u$ is a weak energy solution is identical to the last part of the proof of lemma \ref{lem:existence_part1}.
+The rest of the proof is almost identical to that for lemma \ref{lem:existence_part1}.
+First, $w_{n_j}$ converges pointwise almost everywhere to some $w = \Phi(u)$, which follows from the fact that $\Phi_n$ converges uniformly to $\Phi$ on compact sets, and the continuity of $\Phi$.
+Since $w_n$ is bounded in $Q_T$ for all $n$ with uniform bound, we can use the dominated convergence theorem to deduce that $w \in L^2(Q_T)$.
+
+It follows that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense, and since $w_{n_j}$ is bounded in $L^2(Q_T)$ we can deduce that $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
+
+Lastly, establishing that $u$ is a weak solution and satisfies inequality (\ref{energy_ineq}) follows the exact same argument as in the proof of lemma \ref{lem:existence_part1}.
 \end{proof}
@@
 \item[$\Phi(u)$ is in $L^2(Q_T)$:]
-We also have pointwise convergence almost everywhere along a subsequence, so $\Phi(u_n)$ converges to $\Phi(u)$ almost everywhere in $Q_T$. Seeing as all $u_n$ are weak energy solutions we have
-\begin{equation*}
-\iint_{Q_T}|\nabla \Phi(u_n)|^2dxdt + \int_\Omega \Psi(u_n(T)) dxdt \leq \int_\Omega \Psi(u_{0,n}) dx + \iint_{Q_T} f_n \Phi(u_n)dxdt,
-\end{equation*}
-and we do as always to get
-\begin{equation*}
-\iint_{Q_T}|\nabla \Phi(u_n)|^2dxdt + 2\int_\Omega \Psi(u_n(T)) dxdt \leq 2\int_\Omega \Psi(u_{0,n}) dx + C\iint_{Q_T} f_n^2 dxdt.
-\end{equation*}
-From our assumptions on the apprxoimations we thus have that $\Phi(u_n)$ is a bounded sequence in $L^2(0,T: H^1(\Omega))$.
-As such we can by Banach-Alaoglu deduce $\Phi(u_n)$ has a subsequence $\Phi(u_{n_k})$ that converges weakly to some  $v$ in $L^2(Q_T)$.
-Suppose now that $v \neq \Phi(u)$ on  a set of positive measure.
-Without loss of generality we can for some $\delta > 0$ define $E = \{ (x,t) \in Q_T: v \geq \Phi(u) + \delta\}$.
-Fix now $\epsilon$, then by Egorov's theorem (cf.
-e.g.
-\citep[p.
-120]{weiss1999course}) there is a measurable set $B \subset E$ over which $\Phi(u_n)$ converges uniformly to $\Phi(u)$, with $B$ having positive measure.
-Therefore,
-\begin{equation*}
-\big|\iint_{B}\Phi(u_n) - \Phi(u) dxdt \big| \leq \epsilon |B|  
-\end{equation*}
-for sufficiently large $n$. Since $\epsilon$ was arbitrary it follows that
-\begin{equation*}
-\iint_B \Phi(u_n) dxdt \to \iint_B \Phi(u) dxdt.
-\end{equation*}
-However, the characteristic function of $B$, $\chi_B$, is in $L^2(Q_T)$, and so by the weak convergence of $\Phi(u_{n_k})$ to $v$ we have
-\begin{align*}
-\iint_{B} \Phi(u_{n_k})dxdt & \to \iint_{B} v dxdt \\
-& \geq \iint_{B} \Phi(u)dxdt + \delta|B|,
-\end{align*}
-which is a contradiction, and we conclude that $v=\Phi(u)$ almost everywhere, and in particular $\Phi(u) \in L^2(Q_T)$.
-Notice also that this argument holds for every subsequence of $\Phi(u_n)$, which means that every subsequence of $\Phi(u_n)$ has a subsequence converging weakly to $\Phi(u)$, and so $\Phi(u_n)$ converges weakly to $\Phi(u)$.
+This part of the proof will closely resemble the part of the proof for lemma \ref{lem:existence_part1}.
+See that since $\Phi$ is continuous, $\Phi(u_n)$ converges almost everywhere to $\Phi(u)$.
+With the energy inequality
+\begin{equation*}
+\iint_{Q_T} |\nabla w_n|^2dxdt + \int_{\Omega} \Psi(u_n(T))dxdt \leq \int_\Omega \Psi(u_{0,n})dx + \iint_{Q_T}f_n \Phi(u_n)dxdt
+\end{equation*}
+holding for each $n$ we can do the same trick as when deriving (\ref{spatial_derivative_bound_w_poincare}) for classical solutions to arrive at the estimate
+\begin{equation}
+\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u_n)|^2 dxdt + \int_\Omega \Psi(u_n(T))dx \leq \int_\Omega \Psi(u_{0,n})dx + C\iint_{Q_T}f_n^2dxdt,
+\end{equation}
+where $C$ is a constant independent of $n$.
+With the assumptions we've put on $f_n$ and $u_{0,n}$ we can conclude that $||f_n||_{L^2(Q_T)} \leq ||f||_{L^2(Q_T)}$ and $||\Psi(u_{0,n})||_{L^1(\Omega)} \leq ||\Psi(u_0)||_{L^1(\Omega)}$.
+This implies that $\nabla \Phi(u_n)$ is uniformly bounded in $L^2(Q_T)$, and as an extension $\Phi(u_n)$ is also bounded in $L^2(Q_T)$ from the Poincaré inequality.
+
+By Banach-Alaoglu every subsequence of $\Phi(u_n)$ has a weakly convergent subsequence, and by the pointwise convergence we can, after arguing as in the proof in lemma \ref{lem:existence_part1}, conclude that the weak limit is always $\Phi(u)$.
+This implies that $\Phi(u_n)$ converges weakly to $\Phi(u)$.
 
 \item[$\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$:]
-Now we claim that $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$ in $L^2(Q_T)$.
-Firstly, since $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, we can by the Banach-Alaoglu theorem together with $L^2(Q_T)$ being a Hilbert space deduce that some subsequence of $\nabla \Phi(u_n)$ converges weakly to some $v$ in $L^2(Q_T)$.
-
-Let now $\psi \in C_0^\infty(Q_T)$ and fix $\epsilon > 0$.
-Since $Q_T$ is bounded we can use Egorov's theorem (cf.
-e.g.
-\citep[p.
-120]{weiss1999course}), to deduce that there is a set $E \subset Q_T$ with $|Q_T \setminus E| < \epsilon^2$ so that $\Phi(u_n)$ converges uniformly to $\Phi(u)$ in $E$.
-Hence, we have
-\begin{equation}
-\label{phi_distribution_convergence}
-\iint_{Q_T}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt = \iint_{E}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt + \iint_{Q_T \setminus E}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt.
-\end{equation}
-The first integral is controlled by the uniform convergence of $\Phi(u_n)$ on $E$. For the latter integral, use of Cauchy-Schwartz yields
-\begin{align*}
-\iint_{Q_T \setminus E}(\Phi(u_n) - \Phi(u))\nabla \cdot \psi dxdt &\leq ||\Phi(u_n) - \Phi(u)||_{L^2(Q_T)}||\nabla \cdot \psi||_{L^2(Q_T\setminus E)} \\
-&\leq (||\Phi(u_n)||_{L^2(Q_T)} + ||\Phi(u)||_{L^2(Q_T)})||\nabla \cdot \psi ||_{L^\infty(Q_T)}|Q_T\setminus E|^\frac{1}{2},
-\end{align*}
-and here we use that $\Phi(u_n)$ is uniformly bounded in $L^2(Q_T)$ and that $\Phi(u) \in L^2(Q_T)$.
-So we can make both integrals on the right hand side  in \ref{phi_distribution_convergence} arbitrarily small, and conclude that
-\begin{equation*}
-\iint_{Q_T}\Phi(u_n)\nabla \cdot \psi dxdt \to \iint_{Q_T} \Phi(u) \nabla \cdot \psi dxdt.
-\end{equation*}
-
-Since this argument holds for all $\psi \in C_0^\infty (Q_T)$ we can conclude that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
-Also we have that weak convergence in $L^2(Q_T)$ implies distributional convergence, so $v= \nabla \Phi(u)$.
-
-This argument holds for every subsequence of $\nabla \Phi(u_n)$.
-I.e.
-every subsequence of $\nabla \Phi(u_n)$ has a subsequence that converges weakly to $\nabla \Phi(u)$ which implies that $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$ in $L^2(Q_T)$.
+The proof of this assertion is done by noticing from the weak convergence of $\Phi(u_n)$ we can as previously deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
+In addition $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, and so every subsequence has a weakly convergent subsequence.
+Arguing as before, the limit point is always $\nabla \Phi(u)$, and so $\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$.
 
 \item[$u$ is a weak solution:]
-We have established that $u \in L^1(Q_T)$, and $\Phi(u) \in L^2(0,T: H^1(\Omega)) \subset L^1(0,T: W^{1,1}(\Omega))$, and so all that remains is to consider the convergence of
-\begin{equation}
-\iint_{Q_T} \{ \nabla\Phi(u_n) \cdot \nabla \eta - u_n \partial_t \eta \} dxdt = \int_\Omega u_{0,n}\eta\big|_{t=0}dx + \iint_{Q_T} f_n \eta dxdt,
-\end{equation}
-which holds for each $n$ and every $\eta \in C^1(\overline{Q}_T)$.
-But this is easily seen to hold in the limit by the weak convergence of $\nabla \Phi(u_n)$ in $L^2(Q_T)$, the convergence of $u_n$ and $u_{0,n}$ in $L^1(Q_T)$ and $L^1(\Omega)$, and the convergence of $f_n$ in $L^2(Q_T)$.
-
-\item[Establishing the energy inequality:]
-By the continuity of $\Psi$, we have that $\Psi(u_n(T))$ converges almost everywhere to $\Psi(u(T))$, and so by Fatou's Lemma (cf. \citep[p. 126]{weiss1999course}) 
-\begin{equation*}
-\int_\Omega \Psi(u(T))dx \leq \underset{n \to \infty}{\mathrm{liminf}}\int_\Omega \Psi(u_n(T))dx. 
-\end{equation*}
-
-In addition, the mapping $I[u] = ||\nabla u||_{L^2(Q_T)}$ is convex, and therefore weakly lower semicontinuous \citep[p. 468]{evans}, which means that
-\begin{equation*}
-\iint_{Q_T} |\nabla \Phi(u) |^2 dxdt \leq  \underset{n \to \infty}{\mathrm{liminf}} \iint_{Q_T} |\nabla \Phi(u_n)|^2 dxdt.
-\end{equation*}
-
-Putting, these two things together we can establish that
-\begin{align*}
-\iint_{Q_T} |\nabla \Phi(u) |^2 dxdt + \int_\Omega \Psi(u(T))dx &\leq \underset{n \to \infty}{\mathrm{liminf}} \iint_{Q_T} |\nabla \Phi(u_n)|^2 dxdt + \underset{n \to \infty}{\mathrm{liminf}}\int_\Omega \Psi(u_n(T))dx \\
-&\leq \underset{n \to \infty}{\mathrm{liminf}} \left[ \iint_{Q_T} |\nabla \Phi(u_n)|^2 dxdt + \int_\Omega \Psi(u_n(T))dx \right] \\
-&\leq \underset{n \to \infty}{\mathrm{liminf}}\left[ \int_\Omega \Psi(u_{0,n}) + \iint_{Q_T}f_n \Phi(u_n)dxdt \right] \\
-&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt,
-\end{align*}
-where we have used that the $u_n$ satisfies the energy inequality. This completes the proof.
+With the various convergences shown above or given by assumption, showing that $u$ is a weak solution and satisfies the energy inequality (\ref{energy_ineq}) is done identically as in the proof of lemma \ref{lem:existence_part1}.
 
@@
 \end{proof}
+
+\subsubsection{No longer $C^{2,\alpha}$ boundary}
 
@@
 \begin{proposition}
+\label{prop:Phi_uniform_convergence}
 If $\Phi$ is continuous, $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
@@
 for every $n \geq N$, which proves the proposition.
+\end{proof}
+
+Another useful fact about our approximations is the following:
+
+\begin{proposition}
+\label{prop:Psi_uniform_convergence}
+$\Psi_n$ converges uniformly to $\Psi$ on compact sets.
+\end{proposition}
+\begin{proof}
+Let $K$ be a compact set in $\mathbb{R}$, and take $R$ to be so that $|u| \leq R$ for all $u \in K$. Fix $\epsilon > 0$, and see that for any $u\in K$
+\begin{align*}
+|\Psi_n(u) - \Psi(u)| &\leq \left|\int_0^u \Phi_n(s) - \Phi(s)ds \right| \\
+&\leq \int_0^u |\Phi_n(s) - \Phi(s)|ds.
+\end{align*}
+By proposition \ref{prop:Phi_uniform_convergence} we can take find an $N \in \mathbb{N}$ so that
+\begin{equation*}
+|\Phi_n(s) - \Phi(s)| < \frac{\epsilon}{R}
+\end{equation*}
+for all $n \geq N$ and $s \in [-R, R]$. Thus,
+\begin{align*}
+|\Psi_n(u) - \Psi(u)| &\leq \int_0^u |\Phi_n(s) - \Phi(s)|ds \\
+&< \frac{\epsilon}{R}|u| \leq \epsilon.
+\end{align*}
+With $\epsilon$ being arbitrary, this proves the assertion.
 \end{proof}

### 2014-12-14 draft_project.tex
Kom igjen nå, ikke mye igjen......

@@
 
-The begin, we let $\Omega \subset \mathbb{R}^d$ be an open, bounded and simply connected set, with boundary $\partial \Omega$.
-This will denote our spatial domain, and so we let write $Q_T = \Omega \times (0,T]$ to mean the space-time cylinder up to a time $T$, which can be both finite or infinite, and it will be stated clearly when we need to assume $T < \infty$.
+To begin with, we let $\Omega \subset \mathbb{R}^d$ be an open, bounded and simply connected set, with boundary $\partial \Omega$.
+This will denote our spatial domain, and so we let write $Q_T = \Omega \times (0,T]$ to mean the space-time cylinder up to a time $T$, which can be both finite or infinite, but throughout this text we will assume $T < \infty$.
+It will also be useful to define $Q_T^\tau = \Omega \times (\tau, T-\tau)$ for $0<\tau < \frac{T}{2}$.
 The last set pertaining to the space-time domain we'll need is the parabolic boundary $\Gamma_T = (\partial \Omega \times [0,T]) \cup (\Omega\times \{t=0\})$.
@@
 
-Now we jump in with trying to prove existence of signed, weak energy solutions.
-Following closely the proof provided in \citep{vazquez2007porous}.
-We will first prove existence of weak energy solutions under the assumption that $\Phi$ is strictly increasing, and then extend the result to the case of $\Phi$ being nondecreasing.
-Another useful addition to the proof will be that we will also incorporate a $L^1$-contractivity result.
+We will prove the existence of weak energy solutions for the homogeneous Dirichlet problem (\ref{HDP}) under the following assumptions:
+\begin{assumption}
+\label{ass:Phi_general}
+$\Phi$ is absolutely continuous and nondecreasing. $\Phi(0) = 0$ and $\Phi(\pm \infty) = \pm \infty$.
+\end{assumption}
+
+\begin{assumption}
+\label{ass:f}
+$f \in L^2(Q_T)$.
+\end{assumption}
+
+\begin{assumption}
+\label{ass:u_0}
+$u_0 \in L_{\Psi}(\Omega)$.
+\end{assumption}
+
+On our way to proving existence under these assumptions, we will also need some additional assumptions that will subsequently be lifted. These are:
+\begin{assumption}
+\label{ass:f_ft_u_0_bounded}
+$f$, $\partial_t f$ are bounded in $Q_T$, and $u_0$ is bounded in $\Omega$.
+\end{assumption}
+
+\begin{assumption}
+\label{ass:Phi_strictly_increasing}
+$\Phi$ is strictly increasing.
+\end{assumption}
+
+\begin{assumption}
+\label{ass:Phi_lipschitz}
+$\Phi$ is locally Lipschitz.
+\end{assumption}
+
+\begin{assumption}
+\label{ass:smooth_boundary}
+$\partial \Omega$ is $C^{2,\alpha}$ for some $\alpha \in (0,1)$.
+\end{assumption}
+
+Our main existence theorem reads:
+\begin{theorem}
+\label{thm:weak_existence}
+Under assumptions \ref{ass:Phi_general}-\ref{ass:u_0} the homogeneous Dirichlet problem (\ref{HDP}) has a weak solution, $u$, defined in any finite time interval.
+In addition $u \in L^\infty(0,T:L_\Psi(\Omega))$ and $\Phi(u) \in L^2(0,T:H_0^1(\Omega))$, and the energy inequality (\ref{energy_ineq}) holds.
+\end{theorem}
 
@@
 
-In the following we will assume $u_0 \in L_\Psi(\Omega)$ and $f\in L^2(Q_T)$.
-
-The main theorem reads:
-\begin{theorem}
-\label{thm:weak_existence}
-Assume $u_0 \in L_\Psi(\Omega)$ and $f \in L^p (\Omega)$.
-Then the homogeneous, general porous medium equation (\ref{HDP}) has a weak solution defined in any finite time interval.
-We have $u \in L^\infty(0,T:L_\Psi(\Omega))$ and $\Phi(u) \in L^2(0,T:H_0^1(\Omega))$, and the energy inequality (\ref{energy_ineq}) holds.
-\end{theorem}
-
 We will not prove this in one big chunk, but rather split it off into smaller lemmas, and as already stated, some attention will also be paid to the $L^1$-contractivity.
 \subsubsection{Preliminaries}
+\label{sec:approximations}
 To set ourselves up in a position where we can make use of theorem \ref{thm:classical_existence}, or rather corollary \ref{cor:GPME_existence}, we need to approximate $\Phi$, $u_0$, and $f$.
@@
 This construction can be done as follows: First, define $\tilde{u}_n = \mathrm{max}\{ \mathrm{min}\{u_0, n\}, -n\}$, so $u_0$ is truncated at $\pm n$.
-Then let $(V_n)$ be a sequence of open subsets so that $V_n \subset V_{n+1}$ for all $n$ as well as $\cup_{n\in \mathbb{N}}V_n = \Omega$, and we require $\mathrm{dist}(V_n,\partial \Omega) \geq \frac{2}{n}$.
-Then we set $u_n = (\chi_{V_n}\tilde{u}_n)*\varphi_{\frac{1}{n}}$, where $\chi_{V_n}$ is the characteristic function for $V_n$ and $\varphi_{\frac{1}{n}}$ is the scaled standard mollifier in $\mathbb{R}^d$.
+Then let $(V_n)$ be a sequence of simply connected, compact subsets so that $K_n \subset K_{n+1}$ for all $n$ as well as $\cup_{n\in \mathbb{N}}K_n = \Omega$, and we require $\mathrm{dist}(K_n,\partial \Omega) \geq \frac{2}{n}$.
+Then we set $u_{0,n}= (\chi_{K_n}\tilde{u}_n)*\varphi_{\frac{1}{n}}$, where $\chi_{K_n}$ is the characteristic function for $K_n$ and $\varphi_{\frac{1}{n}}$ is the scaled standard mollifier in $\mathbb{R}^d$.
 The requirement on the distance between $V_n$ and $\partial \Omega$ we see is to ensure that $u_{0,n}$ and its derivatives vanish at the boundary.
 
-We also approximate $f$ by a sequence of $C^\infty(Q_T)$ functions $f_n$ that converge to $f$ in $L^2(Q_T)$, and is so that $|f_n| \leq |f|$ for all $n$.
-
-\subsubsection{$u_0$, $f$, $\partial_t f$ bounded and $\Phi$ locally Lipschitz}
-Our first lemma then reads
-\begin{lemma}
-\label{lem:existence_part1}
-Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$, and $\partial_t f$ are bounded, $\partial \Omega \in C^{2+\alpha}$, and $\Phi$ is locally lipschitz continuous.
-\end{lemma}
-
-\begin{proof}
-
-\begin{description}
-	\item[Setting up an approximate problem:] We fix $T<\infty$ and consider the problem
+We also approximate $f$ by a sequence of $C^\infty(Q_T)$ functions $f_n$ that converge to $f$ in $L^2(Q_T)$, and is so that $|f_n| \leq \mathrm{min}\{n,|f|\}$ for all $n$.
+These approximations can be done in a similar manner to those for $u_0$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		PROOF OF EXISTENCE PART I:							  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{With all assumptions in place}
+The goal of this section will be to prove existence of a weak energy solution under all the assumptions \ref{ass:Phi_general}-\ref{ass:smooth_boundary}, but before doing that some preliminary facts should be established.
+
+\begin{proposition}
+\label{prop:classical_sols_seq}
+With assumptions \ref{ass:Phi_general}-\ref{ass:u_0}, \ref{ass:f_ft_u_0_bounded} and \ref{ass:smooth_boundary} as well as the approximations introduced in section \ref{sec:approximations}, we can identify a sequence $(u_n)$ of classical solutions of some homogeneous Dirichlet problems.
+Moreover, the sequence is uniformly bounded in $Q_T$ with some bound $M$.
+\end{proposition}
+
+\begin{proof}
+With the provided approximations, the problem
 \begin{equation}
@@
 \end{equation}
-	By virtue of corollary \ref{cor:GPME_existence} this approximate problem has a unique solution $u_n \in C^2_1(Q_T)\cap C(\overline{Q}_T)$.
+will for each $n$ permit a classical solution by corollary \ref{cor:GPME_existence}.
+Then we simply define the sequence $(u_n) \subset C^2_1(Q_T)\cap C(\overline{Q}_T)$ as $u_n$ being for each $n$ the unique classical solution of (\ref{approximate_problem}).
+
 In addition we can from the corollary   \ref{cor:Linf_bound_classical} see that
@@
 	A bound independent of $n$.  	
-
-	\item[Control of the spatial derivative:] Now we define $w_n = \Phi_n(u_n)$, and use (\ref{spatial_derivative_bound_w_poincare}) to get 
+\end{proof}
+
+Define now for each $n$ $w_n = \Phi_n(u_n)$. It's the sequence $(w_n)$ we will use the Rellich-Kondrachov compactness argument, which motivates the following two propositions.
+
+\begin{proposition}
+\label{prop:spatial_boundedness}
+With the same assumptions as in proposition \ref{prop:classical_sols_seq},
+the sequences $(w_n)$ and $(\nabla w_n)$ are uniformly bounded in $L^2(Q_T)$. In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$.
+\end{proposition}
+\begin{proof}
+Since $u_n$ are classical solutions, we use (\ref{spatial_derivative_bound_w_poincare}) to get that
 	\begin{equation}
 	\label{exist_proof_spatial}
-	\frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dx  \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt,
-	\end{equation}
-	for each $n$.
-
-	and so we're getting close to a uniform bound on $\nabla w_n$ in $L^2(Q_T)$. We notice that
+	\frac{1}{2}\iint_{Q_T}|\nabla w_n|^2 dxdt + \int_\Omega \Psi_n(u_n(T))dx  \leq \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt
+	\end{equation}
+	holds for each $n$.
+
+	All that remains is to bound the right hand side (\ref{exist_proof_spatial}) independent of $n$, and we're done.To that end we notice that
 	\begin{equation*}
@@
 	$w_n$ is also uniformly bounded in $L^2(Q_T)$.
-
-	\item[Control of the temporal derivative:] From lemma \ref{lem:temporal_bound_classical} we have for each $n$ and every cutoff function $\zeta\in C^1([0,T], [0,1])$
+\end{proof}
+
+\begin{proposition}
+\label{prop:temporal_bound}
+With the same assumptions as in proposition \ref{prop:classical_sols_seq}, the sequence $(\Phi'_n(u_n) |\partial_t u_n|^2)$ is uniformly bounded in $L^1(Q_T^\tau)$ for all $0 < \tau < \frac{T}{2}$.
+\end{proposition}
+
+\begin{proof}
+From lemma \ref{lem:temporal_bound_classical} we have for each $n$ and every cutoff function $\zeta\in C^1([0,T], [0,1])$
 	\begin{equation}
@@
 	\end{align*}
-	From the uniform boundedness of $w_n$ and $\nabla w_n$ in $L^2(Q_T)$ as well as the boundedness of $\partial_t f$ enables us to deduce from the above inequality that $\Phi'_n(u_n)|\partial_t u_n|^2$ is uniformly bounded in $L^1(Q_T^\tau)$ for all $\tau > 0$.
-	Recall now that $|u_n| \leq M$ and $M$ is a constant independent of $n$, and so $[-M,M]$ is a compact subset of $\mathbb{R}$.
-By the local Lipschitz assumption on $\Phi$ there is a constant $L$, so that $\Phi'(s)\leq L$ for all $s\in [-M,M]$, and from the definition of $\Phi_n$ we then have that $\Phi'_n(s) \leq L + 1$ for all $s \in [-M,M]$ and all $n$.
-Hence $|\partial_t w_n|^2 \leq (L+1)\Phi'_n(u_n)|\partial_t u_n|^2$, and we have that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T^\tau)$.
-
-	\item[Using a compactness argument to get a weak limit of $w_n$:]From the two previous parts we have that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T^\tau)$ for $\tau >0$.
+	From the uniform boundedness of $w_n$ and $\nabla w_n$ in $L^2(Q_T)$ as well as the boundedness of $\partial_t f$ enables us to deduce from the above inequality that $\Phi'_n(u_n)|\partial_t u_n|^2$ is uniformly bounded in $L^1(Q_T^\tau)$.
+\end{proof}
+
+with these facts in place, we are in a position where we can start deriving some limit points of the various sequences, and as such get a candidate for teh weak solution.
+
+\begin{proposition}
+\label{prop:weak_convergence_w_n}
+With the same assumptions as in proposition \ref{prop:classical_sols_seq},
+$w_n$ contains a subsequence $(w_{n_j})$ converging almost everywhere to some $w \in L^2(Q_T)$. The convergence happens also weakly in $L^2(Q_T)$.
+\end{proposition}
+
+\begin{proof}
+From proposition \ref{prop:spatial_boundedness} $w_n$ and $\nabla w_n$ are uniformly bounded in $L^2(Q_T)$.
+
+Notice that we have from proposition \ref{prop:classical_sols_seq} that $||u_n||_{L^\infty(Q_T)} \leq M$ for all $n$.
+By assumption $\Phi$ is locally Lipschitz, and so there is a constant $L$ so that $\Phi'(s) \leq L$ for all $s \in [-M, M]$, and from the definition of $\Phi_n$ we then have taht $\Phi'_n(s) \leq L+1$ for all $s\in [-M,M]$ and all $n$.
+Hence $|\partial_t w_n|^2 \leq  (L+1)\Phi'_n(u_n)|\partial_t u_n|^2$, and by proposition \ref{prop:temporal_bound} we have that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T^\tau)$ for $\tau > 0$.As a consequence $w_n$ is uniformly bounded in $H^1(Q_T^\tau)$, for all $\tau > 0$.
+
  The fact that we were only able to bound $\partial_t w_n$ in $L^2(Q_T^\tau)$ causes some problems in using the Rellich-Kondrachov theorem to get a converging subsequence of $w_n$.
@@
 	which is a contradiction. We conclude that $v=w$, and since this is true for any weakly convergent subsequence of $w_{n_j}$, this implies that $w_{n_j}$ converges weakly to $w$ in $L^2(Q_T)$.
-
-	\item[$\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$:]
+\end{proof}
+
+We can get a similar convergence result for $\nabla w_{n_j}$:
+\begin{proposition}
+\label{prop:gradw_weak_convergence}
+With the same assumptions as in proposition \ref{prop:classical_sols_seq},
+$\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
+\end{proposition}
+\begin{proof}
 First off we note that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense. Indeed, the distributional gradient of $w_{n_j}$ is defined by
@@
 	 Lastly, note that with $w, \nabla w \in L^2(Q_T)$, $w \in L^2(0,T: H^1(\Omega))$.
-	\item[Convergence of $u_{n_j}$:] Both $\Phi$ and its approximations $\Phi_n$ all admit a continuous inverse, and so
+\end{proof}
+
+With this list of propositions we are in a position to prove our first lemma, which reads
+\begin{lemma}
+\label{lem:existence_part1}
+Theorem \ref{thm:weak_existence} holds with the additional assumptions \ref{ass:f_ft_u_0_bounded} through \ref{ass:smooth_boundary}.
+\end{lemma}
+
+\begin{proof}
+With proposition \ref{prop:classical_sols_seq} we get a sequence of classical solutions $(u_n)$, uniformly bounded by some $M$.
+Propositions \ref{prop:weak_convergence_w_n} and \ref{prop:gradw_weak_convergence} provides subsequence of $w_n = \Phi_n(u_n)$, $(w_{n_j})$, that converges pointwise almost everywhere to some $w$.
+In addition $w_{n_j}$ and $\nabla w_{n_j}$ converges weakly in $L^2(Q_T)$ to $w$ and $\nabla w$ respectively.
+What remains to establish, is a candidate solution $u$, and show that this is a weak solution that satisfies (\ref{energy_ineq}).
+
+\begin{description}
+	\item[Convergence of $u_{n_j}$:] Both $\Phi$ and its approximations $\Phi_n$ all admit a continuous inverse (cf. appendix \ref{app:Phi}), and so
 	\begin{equation*}
@@
 	We have from before that $u\in L^2(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique.
-In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak energy energy solution, and so the uniqueness precludes any other accumulation point than $u$.
+In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak solution, and so the uniqueness in theorem \ref{thm:uniqueness} precludes any other accumulation point than $u$.
 I.e.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		PROOF OF EXISTENCE PART II:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsubsection{$\Phi$ no longer locally Lipschitz}
-We proceed by generalising the result of \ref{thm:weak_existence} to the case when $\Phi$ is no longer locally Lipschitz.
-
-\begin{lemma}
-\label{lem:weak_existence_part2}
-Theorem \ref{thm:weak_existence} holds with the additional assumption that $u_0$, $f$ and $\partial_t f$ are bounded, but still strictly increasing.
-\end{lemma}
-
-\begin{proof}
-We begin this proof in the exact same manner as with the proof of lemma \ref{lem:existence_part1}, by setting up an approximate problem using $\Phi_n$, $u_{0,n}$ and $f_n$ as smooth approximations which yields a sequence of classical solutions $u_n$.
-We again define $w_n = \Phi_n(u_n)$.
-
-Looking back at the proof for lemma \ref{lem:existence_part1} the only part where we actually needed $\Phi$ to be locally Lipschitz was in controlling the temporal derivative of $\Phi_n(u_n)$ in $L^2(Q_T)$.
-This means we can in this case no longer say that $w_n$ is a bounded sequence in $H^1(Q_T)$.
-
-The strategy for showing that $u_n$ converges to a weak solution will be similar to that of lemma \ref{lem:existence_part1}, only now we will use the Rellich-Kondrachov Compactness Theorem on another sequence than $w_n$.
+We proceed by generalising the result lemma \ref{lem:existence_part1} to the case when $\Phi$ is no longer locally Lipschitz, i.e. lifting assumption \ref{ass:Phi_lipschitz}.
+
+Looking back at the previous section, we see that the only place where we actually made use of $\Phi$ being locally Lipschitz, was in getting a uniform bound on $\partial_t w_n$ in $L^2(Q_T^\tau)$ by way of proposition \ref{prop:temporal_bound}.
+Because of this we'll take a small detour to find a sequence that enjoys the same uniform bounds as $w_n$ did in the previous section.
+
+To that end we define
 \begin{equation}
@@
 
-See now that
+The following proposition will establish that the sequence $(z_n)$ has the desired boundedness property.
+
+\begin{proposition}
+\label{prop:z_n_bounded_H1}
+With assumptions \ref{ass:Phi_general}-\ref{ass:u_0}, \ref{ass:f_ft_u_0_bounded} and \ref{ass:smooth_boundary}, the sequence $(z_n)$ is uniformly bounded in $H^1(Q_T^\tau)$ for $0<\tau < \frac{T}{2}$.
+\end{proposition}
+
+\begin{proof}
+See that
 \begin{align*}
@@
 \end{equation*}
-
-Considering (\ref{exist_proof_spatial}), we can argue exactly as we did in the previous proof to say that $\nabla z_n$ is uniformly bounded in $L^2(Q_T)$.
+Using proposition \ref{prop:spatial_boundedness} we conclude that both $z_n$ and $\nabla z_n$ are uniformly bounded in $L^2(Q_T)$.
+
 Similarly we have the two inequalities
@@
 \end{equation*}
-Doing the same as in the previous proof we deduce that $z_n$ is uniformly bounded in $H^1(Q_T^\tau)$, for all $\tau$, and after an identical diagonal argument as before $(z_n)$ contains a subsequence that converges almost everywhere to some $z$.
+With proposition \ref{prop:temporal_bound} $\partial_t z_n$ is uniformly bounded in $L^2(Q_T^\tau)$, and we conclude that $z_n$ is uniformly bounded in $H^1(Q_T^\tau)$.
+\end{proof}
+
+We are also able to establish some convergence results for $z_n$, summarised in propositions immediately below.
+
+\begin{proposition}
+\label{prop:z_n_weak_convergence}
+Under the same assumptions as proposition \ref{prop:z_n_bounded_H1}, $z_n$ contains a subsequence $(z_{n_j})$ that converges almost everywhere to some $z$.
 The convergence happens also weakly in $L^2(Q_T)$.
-We denote this subsequence by $(z_{n_j})$.
-
+Moreover, $\nabla z_{n_j}$ converges weakly to $\nabla z$.
+\end{proposition}
+
+\begin{proof}
+This proof is almost identical to the proof of proposition \ref{prop:weak_convergence_w_n} and \ref{prop:gradw_weak_convergence}: Using proposition \ref{prop:z_n_bounded_H1} and Rellich-Kondrachov we can construct the same type of diagonal argument to extract a subsequence $(z_{n_j})$ that converges almost everywhere to $z$.
+Since $z_n$ is a bounded sequence in $L^2(Q_T)$, a reflexive Hilbert space, every subsequence contains a weakly convergent subsequence.
+The same use of Egorov's theorem as in proposition \ref{prop:weak_convergence_w_n} establishes that $z_{n_j}$ converges weakly to $z$ in $L^2(Q_T)$.
+\end{proof}
+
+This enables to prove existence in a slightly more general setting.
+\begin{lemma}
+\label{lem:weak_existence_part2}
+Theorem \ref{thm:weak_existence} holds with the additional assumptions \ref{ass:f_ft_u_0_bounded}, \ref{ass:Phi_strictly_increasing} and \ref{ass:smooth_boundary}.
+\end{lemma}
+
+\begin{proof}
+We use proposition \ref{prop:classical_sols_seq} to get a sequence $(u_n)$ of classical soltutions, and we can use this sequence to define $(z_n)$.
+Further, proposition \ref{prop:z_n_weak_convergence} provides us with a subsequence $(z_{n_j})$ that converges almost everywhere to $z$.
 Now we obviously have $u_{n_j} = Z_{n_j}^{-1}(z_{n_j})$, and so
@@
 First, $w_{n_j}$ converges pointwise almost everywhere to some $w = \Phi(u)$, which follows from the fact that $\Phi_n$ converges uniformly to $\Phi$ on compact sets, and the continuity of $\Phi$.
-Since $w_n$ is bounded in $Q_T$ for all $n$ with uniform bound, we can use the dominated convergence theorem to deduce that $w \in L^2(Q_T)$.
+Since $w_{n}$ is bounded in $Q_T$ for all $n$ with uniform bound, we can use the dominated convergence theorem to deduce that  $w \in L^2(Q_T)$.
+
+Since $\nabla w_{n_j}$ is a bounded sequence in $L^2(Q_T)$, by proposition \ref{prop:spatial_boundedness}, we can argue as in proposition \ref{prop:gradw_weak_convergence} to deduce that $\nabla w_{n_j}$ converges weakly to $\nabla w$.
 
@@
 
-\begin{lemma}
-\label{lem:l1_stability_weak}
-Let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$. They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively. Then the inequality
+\begin{proposition}
+\label{prop:l1_stability_weak_part1}
+Assume the assumptions as in lemma \ref{lem:weak_existence_part2}, and let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
+They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively.
+Then the inequality
 \begin{equation}
@@
 for almost every $t\in [0,T]$.
-\end{lemma}
+\end{proposition}
 
@@
 All the above approximations are as already presented in the foregoing proofs.
-Hence we have a sequence of classical solutions $u_n$ and $\hat{u}_n$ that converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
+Hence we have by proposition \ref{prop:classical_sols_seq} sequences of classical solutions $u_n$ and $\hat{u}_n$.
+With the same argument as was done in lemma \ref{lem:weak_existence_part2}, these sequences converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
 
@@
 and since $\epsilon$ was arbitrary this concludes the proof.
+\end{proof}
+
+\subsubsection{No longer $C^{2,\alpha}$ boundary}
+Following suit from the previous section, we'll now aim to prove lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$.
+
+To that end, we take a sequence of simply connected compact sets $K_n \subset \Omega$ so that $K_n \subset K_{n+1}$ and $\cup_{n \in \mathbb{N}}K_n = \Omega$.
+Quite similarly to have we did when approximating $u_0$ in section \ref{sec:approximations}, but now with the additional asssumption that $\partial K_n$ is $C^{2,\alpha}$ smooth for each $n$.
+We'll also denote by $Q_n$ the time-space sylinder $K_n \times (0,T)$.
+
+Further, we take $\zeta_n$ to be cutoff functions with support in $K_n$, and go on to define $u_{0,n} = \zeta_n u_0$ and $f_n = \zeta_n f$.
+Of course the $\zeta_n$ should be approximations of the characteristic function of $K_n$, so that $u_{0,n} \to u_0$ in $L^1(\Omega)$ and $f_n \to f$ in $L^2(Q_T)$.
+The feasibility of these approximations can be found in \citep[Sec.
+5.3]{evans}.
+In this notational setting we'll continue with our generalisation.
+
+\begin{proposition}
+\label{prop:}
+\end{proposition}
+
+\begin{lemma}
+Theorem \ref{thm:weak_existence} holds with additional assumptions \ref{ass:f_ft_u_0_bounded} and \ref{ass:Phi_strictly_increasing}.
+\end{lemma}
+
+\begin{proof}
+To start, we set up for each $n$ the approximate problem
+\begin{equation}
+\begin{cases}
+\partial_t u_n &= \Delta \Phi(u_n) + f_n, \quad \text{in } Q_n \\
+u_n(x,0) &= u_{0,n}, \quad \text{in } K_n \\
+u_n &= 0, \quad \text{on } \partial K_n \times (0,T), 
+\end{cases}
+\end{equation}
+which has by lemma \ref{lem:weak_existence_part2} a weak energy solution. We'll denote by $u_n$ the weak solution extended by $0$ to be defined in all of $Q_T$.
+
 \end{proof}
@@
 \end{proof}
-
-\subsubsection{No longer $C^{2,\alpha}$ boundary}
 

### 2014-12-15 draft_project.tex
Kom igjen nå! Muligens bare korrektur igjen hergit status

@@
 With the same assumptions as in proposition \ref{prop:classical_sols_seq},
-the sequences $(w_n)$ and $(\nabla w_n)$ are uniformly bounded in $L^2(Q_T)$. In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$.
+the sequences $(w_n)$ and $(\nabla w_n)$ are uniformly bounded in $L^2(Q_T)$.
+In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$.
+Moreover, there is some $K >0$, depending only on $M$ and $\Phi$, so that
+\begin{equation}
+\label{gradwn_bound_uniform}
+||\nabla w_n||_{L^2(Q_T)} \leq K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}.
+\end{equation}
+for all $n$.
 \end{proposition}
@@
 	\begin{equation*}
-	|\Psi_n(u)| \leq |\Phi_n(u)u|.
+	|\Psi_n(u)| \geq |\Phi_n(u)u|.
 	\end{equation*}
@@
 The convergence happens also weakly in $L^2(Q_T)$.
-Moreover, $\nabla z_{n_j}$ converges weakly to $\nabla z$.
 \end{proposition}
@@
 
+To conclude this section, is a proposition on an estimate for $\partial_t z$ in $L^2(Q_T)$, which will prove useful in the coming section.
+
+\begin{proposition}
+\label{prop:z_t_estimate}
+Under the same assumptions as proposition \ref{prop:z_n_bounded_H1}, $\partial_t z_n$ converges weakly to $\partial_t z$ in $L^2(Q_T^\tau)$, for $0 < \tau < \frac{T}{2}$. Moreover, the esimate
+\begin{equation}
+\label{z_t_estimate}
+\iint_{Q_T^\tau} |\partial_t z|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}\right) + \iint_{Q_T}|\partial_t (f \zeta ) w| dxdt
+\end{equation}
+for $\tau >0$, where $\zeta=\zeta(t)$ is a smooth cutoff function with $\zeta(t)=1$ for $\tau \leq t \leq T-\tau$.
+
+\end{proposition}
+\begin{proof}
+That $\partial_t z_n$ converges weakly to $\partial_t z$ in follows by almost the exact same approach we used in proving proposition \ref{prop:gradw_weak_convergence}: First by noting that since $z_n$ converges weakly to $z$ in $L^2(Q_T)$, $\partial_t z_n$ must converge to $\partial_t z$ in the distributional sense.
+
+For every $\tau > 0$, $\partial_t z_n$ is a uniformly bounded sequence in $L^2(Q_T^\tau)$, and so we can use the same argument as in proposition \ref{prop:gradw_weak_convergence} to deduce that $\partial_t z_n$ converges weakly to $\partial_t z$ in $L^2(Q_T^\tau)$ for every $0 < \tau < \frac{T}{2}$.
+
+From norms being weakly lower semicontinuous
+\begin{equation}
+\iint_{Q_T^\tau} |\partial_t z|^2 dxdt \leq \liminf_{n \to \infty} \iint_{Q_T} |\partial_t z_n|^2 dxdt,
+\end{equation}
+and by proposition \ref{prop:temporal_bound}, we get that for any smooth cutoff function $\zeta$ with the above stated properties
+\begin{align*}
+\iint_{Q_T^\tau} |\partial_t z|^2 dxdt &\leq \liminf_{n \to \infty} \iint_{Q_T} \left\{\frac{\partial_t \zeta}{2}|\nabla w_n|^2 - \partial_t (\zeta f_n)\right\} dxdt \\
+&\leq \liminf_{n\to \infty}\iint_{Q_T} \left\{ \frac{|\partial_t \zeta|}{2}|\nabla w_n|^2dxdt + |\partial_t (f_n \zeta) |w_n| \right\}dxdt.
+\end{align*}
+A property of the limit inferior is that $\liminf(a_n + b_n) \leq \liminf a_n + \limsup b_n$ for any two real sequences $(a_n)$ and $(b_n)$. This is relevant in this setting because then
+\begin{equation}
+\label{z_t_L2_almost_there}
+\iint_{Q_T^\tau} |\partial_t z|^2 dxdt\leq \liminf_{n\to \infty} \iint_{Q_T}\frac{|\partial_t \zeta|}{2}|\nabla w_n|^2dxdt + \limsup_{n \to \infty} \iint_{Q_T}|\partial_t (f_n \zeta) w_n| dxdt.
+\end{equation}
+On the first term on the right hand side, we use the estimate (\ref{gradwn_bound_uniform}) provided by proposition \ref{prop:spatial_boundedness} to get
+\begin{equation*}
+\liminf_{n\to \infty} \iint_{Q_T}\frac{|\partial_t \zeta|}{2}|\nabla w_n|^2dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}\right).
+\end{equation*}
+
+For the second term, we only need to note that $\partial_t (f_n \zeta)$ converges pointwise to $\partial_t (f \zeta)$ and $w_n$ converges almost everywhere to $w$ Both are bounded sequences, and since we're on a bounded set, this permits us to use the dominated convergence theorem as
+\begin{equation*}
+\limsup_{n \to \infty} \iint_{Q_T}|\partial_t (f_n \zeta) w_n| dxdt = \iint_{Q_T}|\partial_t (f \zeta ) w| dxdt.
+\end{equation*}
+
+Putting these back into (\ref{z_t_L2_almost_there}), we get
+\begin{equation}
+\iint_{Q_T^\tau} |\partial_t z|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}\right) + \iint_{Q_T}|\partial_t (f_n \zeta) w_n| dxdt = \iint_{Q_T}|\partial_t (f \zeta ) w| dxdt.
+\end{equation}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%			PROOF OF EXISTENCE PART III:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsubsection{No longer $C^{2,\alpha}$ boundary}
@@
 To that end, we take a sequence of simply connected compact sets $K_n \subset \Omega$ so that $K_n \subset K_{n+1}$ and $\cup_{n \in \mathbb{N}}K_n = \Omega$.
-Quite similarly to have we did when approximating $u_0$ in section \ref{sec:approximations}, but now with the additional asssumption that $\partial K_n$ is $C^{2,\alpha}$ smooth for each $n$.
+Quite similarly to how we did when approximating $u_0$ in section \ref{sec:approximations}, but now with the additional asssumption that $\partial K_n$ is $C^{2,\alpha}$ smooth for each $n$.
 We'll also denote by $Q_n$ the time-space sylinder $K_n \times (0,T)$.
 
-Further, we take $\zeta_n$ to be cutoff functions with support in $K_n$, and go on to define $u_{0,n} = \zeta_n u_0$ and $f_n = \zeta_n f$.
-Of course the $\zeta_n$ should be approximations of the characteristic function of $K_n$, so that $u_{0,n} \to u_0$ in $L^1(\Omega)$ and $f_n \to f$ in $L^2(Q_T)$.
+We go on then to define $u_{0,n} = \chi_{K_n} u_0$ and $f_n = \chi_{K_n} f$.
+See then that $u_{0,n} \to u_0$ in $L^1(\Omega)$ and $f_n \to f$ in $L^2(Q_T)$.
 The feasibility of these approximations can be found in \citep[Sec.
@@
 \begin{proposition}
-\label{prop:}
+\label{prop:sequence_weak_solution_nonsmoothboundary}
+With assumptions \ref{ass:Phi_general}-\ref{ass:f_ft_u_0_bounded}, we can identify a sequence $u_n$ in $L^1(Q_T)$ that are weak energy solutions on $Q_n \subset Q_T$. 
 \end{proposition}
-
-\begin{lemma}
-Theorem \ref{thm:weak_existence} holds with additional assumptions \ref{ass:f_ft_u_0_bounded} and \ref{ass:Phi_strictly_increasing}.
-\end{lemma}
-
 \begin{proof}
@@
 which has by lemma \ref{lem:weak_existence_part2} a weak energy solution. We'll denote by $u_n$ the weak solution extended by $0$ to be defined in all of $Q_T$.
+\end{proof}
+
+Similar to the previous section, we will for this section define the sequences $w_n = \Phi(u_n)$ and
+\begin{equation}
+z_n(x,t) = Z(u(x,t)) = \int_0^{u_n(x,t)} \mathrm{min}\{1, \Phi'(s)\} ds,
+\end{equation}
+and we will in a little bit see that we can find a subsequence of $(z_n)$ that converges almost everwhere. But for this we'll need to establish some boundedness properties.
+
+\begin{proposition}
+\label{prop:w_n_nonsmooth_spatial_boundedness}
+With the same assumptions as proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}, the sequence $w_n$ is bounded in $L^2(0,T: H_0^1(\Omega))$.
+\end{proposition}
+\begin{proof}
+Notice that for each $n$, $w_n= |\nabla w_n|=0$ in $Q_T\setminus Q_n$ by the construction done in proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}, and so
+
+\begin{equation*}
+\iint_{Q_T} |\nabla w_n|^2dxdt + \int_\Omega \Psi(u_n(T)) = \iint_{Q_n}|\nabla w_n|^2dxdt + \int_{K_n} \Psi(u_n(T))dx.
+\end{equation*}
+For each $n$, $u_n$ is a weak energy solution in $Q_n$ and as satisfies \ref{energy_ineq}, giving
+\begin{align}
+\label{step_spatial_bound_z_nonsmooth_boundary}
+\iint_{Q_T} |\nabla w_n|^2dxdt + \int_\Omega \Psi(u_n(T)) &\leq \int_{K_n}\Psi(u_{0,n})dx + \iint_{Q_n}f_n w_n dxdt \nonumber \\
+&= \int_\Omega \Psi(u_{0,n})dx + \iint_{Q_T} f_n w_n dxdt \nonumber\\
+& \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f_n w_n dxdt,
+\end{align}
+where we've also made use of that $|u_{0,n}| \leq |u_0|$, as well as that $w_n$ and $u_{0,n}$ vanish outside of $Q_n$ and $K_n$ respectively.
+$w_n$ is in $L^2(0,T:H_0^1(\Omega)$ for each $n$, so use of the inequality $ab \leq \frac{a^2}{4c} + cb^2$ on the last term on the right hand side yields
+\begin{equation*}
+\iint_{Q_T} f_n w_n dxdt \leq \frac{1}{4c}\iint_{Q_T}f_n^2dxdt + c\iint_{Q_T} w_n^2 dxdt.
+\end{equation*}
+
+We use a Poincaré inequality, set $c$ as was done in corollary \ref{cor:spatial_bound_w_poincare} and notice that $f_n^2 \leq f^2$ in $Q_T$ to arrive at
+\begin{equation*}
+\iint_{Q_T} f_n w_n dxdt \leq C\iint_{Q_T} f^2dxdt + \frac{1}{2}\iint_{Q_T} |\nabla w_n|^2 dxdt,
+\end{equation*}
+where $C >0$ is a constant independent of $n$. When putting this back into (\ref{step_spatial_bound_z_nonsmooth_boundary}), the result is
+\begin{equation}
+\frac{1}{2}\iint_{Q_T} |\nabla w_n|^2 dxdt + \int_\Omega \Psi(u_n(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T} f^2dxdt,
+\end{equation}
+implying that $\nabla w_n$ is a bounded sequence in $L^2(Q_T)$. As a consequence of the Poincaré inequality
+\begin{equation*}
+\iint_{Q_T} w_n^2 dxdt \leq \tilde{C} \iint_{Q_T} |\nabla w_n|^2 dxdt,
+\end{equation*}
+making also $w_n$ a bounded sequence in $L^2(Q_T)$.
+
+\end{proof}
+
+\begin{proposition}
+\label{prop:z_n_bounded_in_H1}
+With the same assumptions as proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}, the sequence $z_n$ is bounded in $H^1(Q_T^\tau)$ for every $0 < \tau < \frac{T}{2}$.
+\end{proposition}
+
+\begin{proof}
+That $z_n$ is bounded in $L^2(0,T: H_0^1(\Omega))$ follows from the observation that $|\nabla z_n| \leq |\nabla w_n|$ almost everywhere and proposition \ref{prop:w_n_nonsmooth_spatial_boundedness}.
+We have for every $n$ that $z_n = 0$ in $Q_T\setminus Q_n$, and as a consequence $\partial_t z_n = 0$ also.
+Therefore
+\begin{equation*}
+\iint_{Q_T^\tau} |\partial_t z_n|^2 dxdt = \iint_{Q_n^\tau} |\partial_t z_n|^2 dxdt.
+\end{equation*}
+
+By proposition \ref{prop:z_t_estimate} we can use the estimate (\ref{z_t_estimate}) as
+\begin{equation}
+\label{z_n_bounded_in_H1_start}
+\iint_{Q_T^\tau} |\partial_t z_n|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_{0,n}||_{L^1(K_n)} + ||f_n||_{L^2(Q_n)}\right) + \iint_{Q_n}|\partial_t (f_n \zeta ) w_n| dxdt,
+\end{equation}
+where $\zeta = \zeta(t)$ is a smooth cutoff function from proposition \ref{prop:z_t_estimate}, which has a bounded derivative.
+
+First off, we see that $||u_{0,n}||_{L^1(K_n)} = ||u_{0,n}||_{L^1(\Omega)}$ and $||f_n||_{L^2(Q_n)} \leq ||f||_{L^2(Q_T)}$.
+For the second part on the right hand side of (\ref{z_n_bounded_in_H1_start}) we have that $w_n=0$ in $Q_T\setminus Q_n$, and so integration can be extended to all of $Q_T$.
+In addition $|\partial_t (f_n \zeta)| \leq ||\partial_t f||_{\infty} + ||f||_\infty ||\partial_t \zeta||_\infty$, which are all bounded, independent of $n$.
+Hence the right hand side of (\ref{z_n_bounded_in_H1_start}) is bounded independent of $n$.
+This, along with $z_n$ being bounded in $L^2(0,T: H^1_0(\Omega)$, proves the assertion.
+\end{proof}
+
+With that last proposition we are able to prove existence of weak energy solutions
+
+\begin{lemma}
+\label{lem:weak_existence_part3}
+Theorem \ref{thm:weak_existence} holds with additional assumptions \ref{ass:f_ft_u_0_bounded} and \ref{ass:Phi_strictly_increasing}.
+\end{lemma}
+
+\begin{proof}
+We start by constructing a sequence of weak solutions $(u_n)$ in $Q_n$ defined in $Q_T$ as done in proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}.
+With $z_n = Z(u_n)$ and $w_n = \Phi(u_n)$, $(z_n)$ is bounded in $H^1(Q_T^\tau)$ for every $0< \tau < \frac{T}{2}$ by proposition \ref{prop:z_n_bounded_in_H1}.
+A diagonal argument, as was done in the proof of \ref{prop:weak_convergence_w_n} to extract a subsequence of $(z_n)$ that converges pointwise almost everywhere to some $z$.
+With a pointwise limit for a subsequence $z_{n_j}$, the rest of the proof is identical to the proof of lemma \ref{lem:weak_existence_part2}.
+\end{proof}
+
+Before we move on to remove the assumption regarding the boundedness of $u_0$ and $f$ we need to ensure the $L^1$-contractivity result of proposition \ref{prop:l1_stability_weak_part1} still holds after passing to limit as we did in the proof of lemma \ref{lem:weak_existence_part3}, it will become useful in the coming section.
+
+\begin{proposition}
+\label{prop:l1_stability_weak_part2}
+With assumptions \ref{ass:Phi_general}-\ref{ass:Phi_strictly_increasing},  let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
+They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively.
+Then the inequality
+\begin{equation}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + \int_0^t||f-\hat{f}||_{L^1(\Omega)}
+\end{equation}
+holds for almost every $t\in [0,T]$.
+\end{proposition}
+
+\begin{proof}
+The proof follows closely that of proposition \ref{prop:l1_stability_weak_part1}.
+Indeed, we start by constructing sequences of weak solutions $u_n$ and $\hat{u}_n$ by proposition \ref{prop:sequence_weak_solution_nonsmoothboundary} that converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
+Fix $\epsilon > 0$, then with the triangle inequality
+\begin{align*}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} &\leq ||u(t) - u_n(t)||_{L^1(\Omega)} + ||u_n(t) - \hat{u}_n(t)||_{L^1(\Omega)} + ||\hat{u}_n(t) - \hat{u}(t)||_{L^1(\Omega)} \\
+&< \epsilon + ||u_n(t) - \hat{u}_n(t)||_{L^1(\Omega)},
+\end{align*}
+for sufficiently large $n$.
+Since both $u_n$ and $\hat{u}_n$ vanish on $Q_T\setminus Q_n$ the integration can be restricted to $K_n$ instead of $\Omega$, leaving us in a position to make use of proposition \ref{prop:l1_stability_weak_part1}, resulting in
+\begin{align*}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} &< \epsilon + ||u_{0,n} - \hat{u}_{0,n}||_{L^1(\Omega)} + ||f_n - \hat{f}_n||_{L^1(Q_T)} \\
+&\leq \epsilon + ||u_{0,n} - u_0||_{L^1(\Omega)} + ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||\hat{u}_0 - \hat{u}_{0,n}||_{L^1(\Omega)} \\
+&+ ||f_n - f||_{L^1(Q_T)} + ||f - \hat{f}||_{L^1(Q_T)} + ||\hat{f} - \hat{f}_n||_{L^1(Q_T)}.
+\end{align*}
+All terms involving $n$ we can control by the various convergences. Thus, when passing to the limit $n \to \infty$ we end up with
+\begin{equation}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + ||f - \hat{f}||_{L^1(Q_T)}.
+\end{equation}
 
@@
 \subsubsection{Removing the assumptions on $f$ and $u_0$}
-Now we try to generalise to the case when $f$ and/or $u_0$ are not bounded, but still require $f \in L^2(Q_T)$ and $u_0 \in L_{\Psi}(\Omega)$.
-
-\begin{lemma}
-Theorem \ref{thm:weak_existence} holds when $\Phi$ is strictly increasing and absolutely continuous.
-\end{lemma}
-\begin{proof}
+We've finally arrived at the last section, where we'll prove theorem \ref{thm:weak_existence} without the assumption \ref{ass:f_ft_u_0_bounded}, which have proved so very useful for us up to this point.
+Let's just get to it then.
+
+\begin{proof}[Proof of theorem \ref{thm:weak_existence}]
 
@@
 It will also be useful to assume $|u_{0,n}| \leq |u_0|$ and $|f_n| \leq |f|$ for all $n$.
-
-Using lemma \ref{lem:weak_existence_part2} we get a sequence of weak energy solutions, $(u_n)$. Notice now that we have discarded any approximations of $\Phi$. By lemma \ref{lem:l1_stability_weak}
+A way, to do this is first truncate $u_0$ and $f$ below and above by $-n$ and $n$, and then mollify.
+
+For example, for $f$ we define $\tilde{f}_n = \mathrm{max}\{ -n, \mathrm{\min}\{f,n\}\}$ and then $f_n = \tilde{f}_n * \varphi_{\frac{1}{n}}$, with $\varphi_{\frac{1}{n}}$ is the scaled standard mollifier in $\mathbb{R}^{d+1}$.
+The mollification is there to ensure that also $\partial_t f_n$ is bounded for each $n$.
+
+Using lemma \ref{lem:weak_existence_part3} we get a sequence of weak energy solutions, $(u_n)$. By lemma \ref{prop:l1_stability_weak_part2}
 \begin{equation*}
@@
 \end{equation*}
+From here on we may also assume that $u_n$ converges almost everywhere to $u$, because if not we can take a subsequence that does.
 
 \item[$\Phi(u)$ is in $L^2(Q_T)$:]
-This part of the proof will closely resemble the part of the proof for lemma \ref{lem:existence_part1}.
+This part of the proof will closely resemble the part of the proof for lemma \ref{prop:weak_convergence_w_n}.
 See that since $\Phi$ is continuous, $\Phi(u_n)$ converges almost everywhere to $\Phi(u)$.
@@
 
-By Banach-Alaoglu every subsequence of $\Phi(u_n)$ has a weakly convergent subsequence, and by the pointwise convergence we can, after arguing as in the proof in lemma \ref{lem:existence_part1}, conclude that the weak limit is always $\Phi(u)$.
+By Banach-Alaoglu every subsequence of $\Phi(u_n)$ has a weakly convergent subsequence, and by the pointwise convergence we can, after arguing as in the proof in lemma \ref{prop:weak_convergence_w_n}, conclude that the weak limit is always $\Phi(u)$.
 This implies that $\Phi(u_n)$ converges weakly to $\Phi(u)$.
@@
 \item[$\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$:]
-The proof of this assertion is done by noticing from the weak convergence of $\Phi(u_n)$ we can as previously deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
+The proof of this assertion is done, as in the proof of proposition \ref{prop:gradw_weak_convergence}, by noticing from the weak convergence of $\Phi(u_n)$ we can deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
 In addition $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, and so every subsequence has a weakly convergent subsequence.
@@
 With the various convergences shown above or given by assumption, showing that $u$ is a weak solution and satisfies the energy inequality (\ref{energy_ineq}) is done identically as in the proof of lemma \ref{lem:existence_part1}.
-
+The same is true for showing that $u$ satisfies the energy inequality (\ref{energy_ineq}).
 \end{description}
+\end{proof}
+
+For the sake of completeness, we'll end this project by ensuring that the $L^1$-contractivity still holds.
+
+\begin{lemma}
+\label{lem:l1_stability_weak_final}
+With assumptions \ref{ass:Phi_general}-\ref{ass:u_0},  let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
+They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively.
+Then the inequality
+\begin{equation}
+||u(t) - \hat{u}(t)||_{L^1(\Omega)} \leq ||u_0 - \hat{u}_0||_{L^1(\Omega)} + \int_0^t||f-\hat{f}||_{L^1(\Omega)}
+\end{equation}
+holds for almost every $t\in [0,T]$.
+\end{lemma}
+
+\begin{proof}
+The proof is identical to that of proposition \ref{prop:l1_stability_weak_part2}, only now the use of proposition \ref{prop:l1_stability_weak_part1} is exchanged with use of \ref{prop:l1_stability_weak_part2}.
 \end{proof}

### 2014-12-16 draft_project.tex
...

@@
 \usepackage{lmodern}
-
+\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
 \begin{document}
-\title{Draft for project}
-\author{Trygve Bærland}
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	TITLE PAGE:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagestyle{empty}
+\pagenumbering{roman}
+\begin{titlepage}
+\begin{center}
+
+% Upper part of the page. The '~' is needed because \\
+% only works if a paragraph has started.
+
+\textsc{\LARGE Norwegians University of Science and Technology}\\[1.5cm]
+
+\textsc{\Large TMA4500: Spesialisation project}\\[0.5cm]
+
+% Title
+\HRule \\[0.4cm]
+{ \huge \bfseries The general porous medium equation \\[0.4cm] }
+
+\HRule \\[1.5cm]
+
+% Author and supervisor
+\noindent
+\begin{minipage}{0.4\textwidth}
+\begin{flushleft} \large
+\emph{Author:}\\
+Trygve \textsc{Bærland}
+\end{flushleft}
+\end{minipage}%
+\begin{minipage}{0.4\textwidth}
+\begin{flushright} \large
+\emph{Supervisor:} \\
+Espen R. \textsc{Jakobsen}
+\end{flushright}
+\end{minipage}
+
+\vfill
+
+% Bottom of the page
+{\large \today}
+
+\end{center}
+\end{titlepage}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		END OF TITLE PAGE
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \abstract{For now, heavily reliant on \citep{vazquez2007porous}.}
 
+\newpage
+\tableofcontents
+\pagenumbering{arabic}
 % My text categories:
@@
 %Assumptions:
-\newtheorem{assumption}{Assumption}
+\newtheorem{assumption}{Assumption}[section]
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section{Introduction}
@@
 \section{Classical solutions}
+\subsection{Preliminaries and assumptions}
 The strictest sense in which we can have a solution of (\ref{HDP}) is that there is a $u \in C^2_1(Q_T)\cap C(\overline{Q}_T)$ for which $u\big|_{t=0} = u_0$,  $u\big|_{\partial\Omega \times [0,T]} = 0$, and the equality
@@
 \end{equation*}
-holds everywhere in $Q_T$.
-This means we must also impose that $\Phi \in C^2(\mathbb{R})$ and that $f$ is continuous.
-If $u \in C^2_1(Q_T)$, $\Phi$ and $f$ satisfy this we call $u$ a classical solution of (\ref{HDP}).
-
-In this section it is helpful to reformulate (\ref{HDP}) as 
+holds everywhere in $Q_T$, and we call such a solution $u$ a classical solution.
+
+In this section, when deriving various results pertaining to classical solutions, we will do so under various assumptions on $\Phi$, $u_0$ and $f$. These assumptions are listed immediately below.
+
+\begin{assumption}[Regularity of $\Phi$]
+\label{ass:classical_Phi_smooth}
+$\Phi \in C^2(\mathbb{R})$ and strictly increasing, as well as $\Phi(0) = 0$.
+\end{assumption}
+
+\begin{assumption}[Uniform parabolicity]
+\label{ass:classical_uniform_parabolicity}
+There exists constants $ 0 < \nu < \mu < \infty$ so that
+\begin{equation}
+\label{uniform_parabGPME}
+\nu \leq \Phi'(s) \leq \mu, \quad u \in \mathbb{R}
+\end{equation}
+holds for all $s \in \mathbb{R}$.
+\end{assumption}
+
+\begin{assumption}[Continuity of $f$]
+\label{ass:classical_f}
+$f$ is bounded and continuous in $\overline{Q}_T$.
+\end{assumption}
+
+\begin{assumption}[Continuity of $u_0$]
+\label{ass:classical_u_0}
+$u_0$ is bounded and continuous in $\overline{\Omega}$. In addition, 
+\begin{equation}
+u_0\big|_{\partial \Omega} = 0.
+\end{equation}
+\end{assumption}
+
+Most of the above assumptions are naturally motivated by the regularity restrictions on a classical solution.
+For example if $f$ was discontinuous somewhere in $Q_T$ this would lead to a discontinuity of the time derivative of a solution.
+
+The only one that may not be immediately clear is assumption \ref{ass:classical_uniform_parabolicity}, and to somewhat motivate this assumption it is useful to consider the more general parabolic Dirichlet problem
 \begin{equation}
@@
 \begin{equation}
+\label{divergence_operator}
 Lu = -\sum_{i=1}^d \partial_{x_i}(a^i(x,t,u,\nabla u)) + a(x,t,u,\nabla u),
@@
 
-In addition we assume that there are constants $0 < \nu < \mu < \infty $ so that
+Many results regarding problems of the type (\ref{general_parabolic_problem}) assumes there are constants $0 < \nu < \mu < \infty $ so that
 \begin{equation}
@@
 \end{equation}
-for every $\xi \in \mathbb{R}^d$. If this condition is satisfied we say that the operator $\partial_t + L$ is \textbf{uniformly parabolic}.
+for every $\xi \in \mathbb{R}^d$, all $(x,t) \in Q_T$ and all $u\in \mathbb{R}$. If this condition is satisfied we say that the operator $\partial_t + L$ is \textbf{uniformly parabolic}.
 
@@
 \end{equation*}
-(\ref{general_parabolic_problem}) reduces to the homogeneous Dirichlet (\ref{HDP}),
-and so (\ref{uniform_parabolicity}) translates to
-\begin{equation}
-\label{uniform_parabGPME}
-\nu \leq \Phi'(u) \leq \mu,
-\end{equation}
-for (\ref{HDP}) to be uniformly parabolic.
-We will in this section assume this to be true. I.e. that $\Phi'(u)$ is bounded from above as well as away from zero.
+(\ref{general_parabolic_problem}) reduces to the homogeneous Dirichlet problem (\ref{HDP}),
+and so (\ref{uniform_parabolicity}) translates to assumption \ref{ass:classical_uniform_parabolicity}.
+
+In this framework the remainder of this section considering classical solutions will be devoted to deriving various a priori estimates for classical solutions, and ending with a corollary stating sufficient conditions for existence of a classical solution to (\ref{HDP}).
+As we will see, these conditions are quite strict, leading us naturally to want to consider weak solutions, which the next section is devoted to.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{lemma:comparison}
-Let $\Phi \in C^2(\mathbb{R})$ and satisfy (\ref{uniform_parabGPME}), and let $u,v \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two solutions of the General Porous Medium Equation (\ref{GPME}) in $Q_T$ with initial data $u_0$, $v_0$, loading $f$, $\tilde{f}$ respectively as well as prescribed Dirchlet data on the boundary.
+Under assumptions \ref{ass:classical_Phi_smooth}-\ref{ass:classical_u_0}, let $u,v \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two solutions of the General Porous Medium Equation (\ref{GPME}) in $Q_T$ with initial data $u_0$, $v_0$, loading $f$, $\tilde{f}$ respectively as well as prescribed Dirchlet data on the boundary.
 Further, assume that $v\big|_{\Gamma_T} \geq u\big|_{\Gamma_T}$, and  $\tilde{f} \geq f$ in $Q_T$.
@@
 \label{cor:Linf_bound_classical}
-Assume $\Phi \in C^2(\mathbb{R})$ and satisfy (\ref{uniform_parabGPME}).
-If $u \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ is a solution of (\ref{HDP}), and $u_0$ is bounded in $\Omega$ and $f$ bounded in $Q_T$, then
+Under the same assumptions as Lemma \ref{lemma:comparison},  let $u \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be a classical solution of (\ref{HDP}), then
 	\begin{equation}
@@
 \subsection{$L^1$-contractivity}
-In this section we let $u,\hat{u} \in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$ be two smooth solutions of the homogeneous Dirichlet problem (\ref{HDP}) with initial data $u_0$, $\hat{u}_0$ and loading $f$, $\hat{f}$ respectively.
-To reach our goal of deriving stability of solutions in $L^1$ we start off with the following lemma, from which the main result will be an almost immediate consequence.
+Moving right along, the next a priori estimate up for consideration is one regarding stability in $L^\infty(0,T: L^1(\Omega))$.
+To reach our goal we start off with the following lemma, from which the main result will be an almost immediate consequence.
 
@@
 \label{lem:l1_stability_classical}
-Let $u, \hat{u} \in C^2_1(Q_T)\cap C(\overline{Q}_T)$, be two classical solutions of the homogeneous Dirichlet problem (\ref{HDP}), with initial data $u_0$ and $\hat{u}_0$ as well as loading $f$ and $\hat{f}$, respectively.
-Assume further that $\Phi$ is strictly increasing, and $\Phi(0)=0$.
+Under assumptions \ref{ass:classical_Phi_smooth}, \ref{ass:classical_f} and \ref{ass:classical_u_0}, let $u, \hat{u} \in C^2_1(Q_T)\cap C(\overline{Q}_T)$, be two classical solutions of the homogeneous Dirichlet problem (\ref{HDP}), with initial data $u_0$ and $\hat{u}_0$ as well as loading $f$ and $\hat{f}$, respectively.
 Then, for $\tau, t \in [0,T]$, the inequality
@@
 \label{l1_stab_step1}
-\partial_t(u-\hat{u})p(w) = p(w)\Delta w + p(w)f.
+\partial_t(u-\hat{u})p(w) = p(w)\Delta w + p(w)(f-\hat{f}).
 \end{equation}
@@
 where the last step follows from the fact that $0 \leq p(w) \leq 1$. Here $(\cdot)_+ = \mathrm{max}\{\cdot, 0\}$.
-Now, let $p$ converge pointwise to the positive sign function $\mathrm{sign}_0^+$ defined
+Now, let $p$ converge pointwise in an increasing fashion to the positive sign function $\mathrm{sign}_0^+$ defined
 \begin{equation*}
@@
 \end{equation*}
-In the convergence of $p$, the integrand $\partial_t(u-\hat{u})p(w)$ is dominated by $\partial_t (u - \hat{u}) \mathrm{sign}_0^+(w)$ which is integrable from the continuity requirements, and so the Dominated Convergence Theorem implies that
-\begin{equation*}
-\int_\Omega \partial_t(u-\hat{u})p(w) dx \to \int_\Omega \partial_t (u - \hat{u}) \mathrm{sign}_0^+(w)dx.
-\end{equation*}
+
+We need to ensure then that
+\begin{equation}
+\label{cool_use_of_MCT}
+\int_\Omega \partial_t (u - \hat{u}) p(w) dx \underset{n \to \infty}{\to} \int_\Omega \partial_t (u - \hat{u})\mathrm{sign}^+_0(w)dx.
+\end{equation}
+It is obvious that $\partial_t (u - \hat{u})p(w)$ converges pointwise to $\partial_t (u-\hat{u})\mathrm{sign}_0^+(w)$, and we proceed by defining the two sets
+\begin{equation*}
+\begin{cases}
+\Omega_+ &= \{ x \in \Omega: \partial_t (u - \hat{u}) \geq 0 \}, \text{ and} \\
+\Omega_- &=  \{ x \in \Omega: \partial_t (u - \hat{u}) < 0\} 
+\end{cases}
+\end{equation*}
+and split up the integral in following fashion,
+\begin{equation}
+\int_\Omega \partial_t (u - \hat{u}) p(w) dx = \int_{\Omega_+}\partial_t (u - \hat{u}) p(w)dx - \int_{\Omega_-} -\partial_t (u - \hat{u}) p(w)dx. 
+\end{equation}
+
+In both integrals the integrands are nonnegative and converge monotonically to $\pm \partial_t (u - \hat{u})\mathrm{sign}^+_0(w)$, and so use of the Monotone convergence theorem (cf.
+\citep[Thm.
+5.6, p.
+165]{weiss1999course}) to conclude that (\ref{cool_use_of_MCT}) is indeed valid.
 
 Notice now that $\mathrm{sign}_0^+(u-\hat{u}) = \mathrm{sign}_0^+(\Phi(u) - \Phi(\hat{u}))$ because of the assumption that $\Phi$ is strictly increasing.
-In addition we have $\partial_t (u-\hat{u})_+ = \mathrm{sign}_0^+ \partial_t (u - \hat{u})$, in the weak derivative sense.
+In addition we have $\partial_t (u-\hat{u})_+ = \mathrm{sign}_0^+(u-\hat{u}) \partial_t (u - \hat{u})$, in the weak derivative sense.
 Thus
@@
 \end{equation*}
-which implies that
-\begin{equation*}
-\partial_t \int_{\Omega}(u-\hat{u})_+dx \leq \int_{\Omega}(f-\hat{f})_+ dx,
-\end{equation*}
 and integrating in time from $\tau$ to $t$ yields
 \begin{equation*}
-\int_{\Omega}(u(t)-\hat{u}(t))_+dx \leq \int_{\Omega}(u(\tau)-\hat{u}(\tau))_+dx + \int_\tau^t\int_{\Omega}(f-\hat{f})_+dxdt.
-\end{equation*}
+\int_\tau^t \int_{\Omega}\partial_t(u(t)-\hat{u}(t))_+dx \leq \int_\tau^t\int_{\Omega}(f-\hat{f})_+dxdt.
+\end{equation*}
+
+Using Fubini's theorem to interchange the integration on the left hand side then finally results in
+\begin{equation}
+\int_\Omega (u(t) - \hat{u})_+ dx \leq \int_\Omega (u(\tau) - \hat{u}(\tau))_+ dx + int_\tau^t \int_\Omega (f-\hat{f})_+ dxdt.
+\end{equation}
 \end{proof}
@@
 \begin{cor}
-If $\Phi$ is strictly and $f$ is continuous, then the homogeneous Dirichlet problem (\ref{HDP}) has at most on solution in $C^2_1(Q_T)\cap C(\overline{Q}_T)$.
+Under the same assumptions as Lemma \ref{lem:l1_stability_classical}, then the homogeneous Dirichlet problem (\ref{HDP}) has at most on solution in $C^2_1(Q_T)\cap C(\overline{Q}_T)$.
 \end{cor}
@@
 \label{lem:Energy_equality_classical}
-For a classical solution $u\in C^{2,1}(Q_T) \cap C(\overline{Q}_T)$ of (\ref{HDP})
+With the same assumptions as Lemma \ref{lem:l1_stability_classical} we have for a classical solution $u\in C^{2,1}(Q_T) \cap C(\overline{Q}_T)$ of (\ref{HDP}) that
 \begin{equation}
 \label{spatial_derivative_bound}
-\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt.
-\end{equation}
+\iint_{Q_\tau} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(\tau))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_\tau} f\Phi(u)dxdt,
+\end{equation}
+for every $\tau \in [0,T]$.
 \end{lemma}
@@
 \end{equation*}
-and we notice that $\Phi(u)\partial_t u = \partial_t \Psi(u)$. That means when we integrate over $Q_T$ we have
-\begin{equation*}
-\iint_{Q_T} \partial_t \Psi(u)dxdt = \int_\Omega \Psi(u(T))dx - \int_\Omega \Psi(u_0)dx.
+and we notice that $\Phi(u)\partial_t u = \partial_t \Psi(u)$. That means when we integrate over $Q_t$ we have
+\begin{equation*}
+\iint_{Q_\tau} \partial_t \Psi(u)dxdt = \int_\Omega \Psi(u(\tau))dx - \int_\Omega \Psi(u_0)dx.
 \end{equation*}
@@
 \begin{equation*}
-\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_0^T \int_{\partial\Omega} \Phi(u)\nabla \Phi(u) \cdot \hat{n}dS,
+\iint_{Q_\tau}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_\tau} |\nabla \Phi(u)|^2dxdt + \int_0^\tau \int_{\partial\Omega} \Phi(u)\nabla \Phi(u) \cdot \hat{n}dS,
 \end{equation*}
@@
 \begin{equation*}
-\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt,
+\iint_{Q_\tau}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_\tau} |\nabla \Phi(u)|^2dxdt,
 \end{equation*}
@@
 \begin{equation*}
-\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt.
+\iint_{Q_\tau} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(\tau))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_\tau} f\Phi(u)dxdt.
 \end{equation*}
@@
 \begin{proof}
-For the term involving $f$ in (\ref{spatial_derivative_bound}) we use the inequality $ab \leq \frac{a^2}{4c} + cb^2$ for any reals $a$ and $b$, and any positive $c$, to get
+Set $\tau=T$ in (\ref{spatial_derivative_bound}), and for the term involving $f$ in (\ref{spatial_derivative_bound}) we use the inequality $ab \leq \frac{a^2}{4c} + cb^2$ for any reals $a$ and $b$, and any positive $c$, to get
 \begin{equation*}
@@
 \label{lem:temporal_bound_classical}
-Let $u\in C^2_1(Q_T) \cap C(\overline{Q}_T)$ be a classical solution of (\ref{HDP}), where $f$ and $\partial_tf$ are continuous as well as $\Phi \in C^2(\mathbb{R})$.
+Under the same assumptions as in Lemma \ref{lem:l1_stability_classical}, assume in addition that $\partial_t f$ is continuous.
+Let $u\in C^2_1(Q_T) \cap C(\overline{Q}_T)$ be a classical solution of (\ref{HDP}).
 Further, let $\zeta = \zeta(t)$ be a $C^1([0,T],[0,1])$ cutoff function so that $\zeta(0) = \zeta(T) = 0$.
@@
 Now we move on to tackle one of the central questions with regards to the well-posedness of (\ref{HDP}), viz.
-existence, and in particular what sort of assumptions we need to put on $u_0$, $f$ and $\Phi$ to be guaranteed that a solution exists.
+existence, and in particular what sort of assumptions we can put on $u_0$, $f$ and $\Phi$ to be guaranteed that a solution exists.
 
@@
 
-As in the section on the maximum principle it will be useful to recast our PDE to the form
+Recalling the divergence form (\ref{divergence_operator}) at the beginning of this section, it will be useful to consider a general parabolic equation of the form
 \begin{equation}
@@
 \begin{enumerate}[i)]
-	\item $u \in L^1(Q_T)$ and $\Phi(u) \in L^1(0,T : W_0^{1,1}(\Omega))$\footnote{$f:\Omega \to \mathbb{R}$ is an element of $W^{k,p}(\Omega)$ if all weak derivatives with $|\alpha| \leq k$ exists and are in $L^p(\Omega)$.
-$W_0^{k,p}$ is the closure of $C^\infty_c(\Omega)$ in $W^{k,p}(\Omega)$.};
+	\item $u \in L^1(Q_T)$ and $\Phi(u) \in L^1(0,T : W_0^{1,1}(\Omega))$;
 	\item $u$ satisfies
@@
 \subsection{Uniqueness}
-
+The first result we'll prove for weak solutions is uniqueness under some additional assumptions.
+The proof can be found in \citep{vazquez2007porous}, but here worked out in greater detail.
+The result is also somewhat improved upon by here admitting $\Phi$ to be nondecreasing, rather than strictly increasing.
 \begin{theorem}[Uniqueness]
@@
 \end{equation*}
-where the time derivation is valid using the First Fundamentel Theorem of Calculus and that $\Phi(u_i) \in L^1(0,T : W_0^{1,1}(\Omega))$ by the definition of weak soultion.
+where the temporal differentiation is valid using the First Fundamentel Theorem of Calculus and that $\Phi(u_i) \in L^1(0,T : W_0^{1,1}(\Omega))$ by the definition of weak soultion.
 For the validity of the spatial derivative, confer appendix \ref{sec:derivative}.
@@
 \begin{enumerate}[i)]
-	\item In the first integral we notice that $u_2 > u_1 \Rightarrow \Phi(u_2) \geq \Phi(u_1)$ and vice versa, so this integral is nonnegative.
+	\item In the first integral we notice that $u_2 \geq u_1 \Rightarrow \Phi(u_2) \geq \Phi(u_1)$ and vice versa, so this integral is nonnegative.
 
@@
 Recall our definition of $\Psi$ in (\ref{phi_primitive}) as the primitive of $\Phi$,
-and we define the function space $L_\Psi(\Omega) = \{ u\in L^1(\Omega): \Psi(u)\in L^1(\Omega)\}$.
+and we define the function space $L_\Psi(\Omega) = \{ u\in L^1(\Omega): \Psi(u)\in L^1(\Omega)\}$. This is with the norm
+\begin{equation}
+||u||_{L_\Psi (\Omega)} = ||u||_{L^1(\Omega)} + ||\Psi(u)||_{L^1(\Omega)}.
+\end{equation}
 With this in mind we can define energy solutions in the following way:
 \begin{mydef}[Energy solution]
-We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L_\Psi(\Omega)$, and the energy inequality
+We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, $u_0 \in L_\Psi(\Omega)$, and the energy inequality
 \begin{equation}
@@
 \label{ass:Phi_general}
-$\Phi$ is absolutely continuous and nondecreasing. $\Phi(0) = 0$ and $\Phi(\pm \infty) = \pm \infty$.
+$\Phi$ is absolutely continuous and strictly increasing. $\Phi(0) = 0$ and $\Phi(\pm \infty) = \pm \infty$.
 \end{assumption}
@@
 $f$, $\partial_t f$ are bounded in $Q_T$, and $u_0$ is bounded in $\Omega$.
-\end{assumption}
-
-\begin{assumption}
-\label{ass:Phi_strictly_increasing}
-$\Phi$ is strictly increasing.
 \end{assumption}
@@
 
-We also approximate $f$ by a sequence of $C^\infty(Q_T)$ functions $f_n$ that converge to $f$ in $L^2(Q_T)$, and is so that $|f_n| \leq \mathrm{min}\{n,|f|\}$ for all $n$.
-These approximations can be done in a similar manner to those for $u_0$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%		PROOF OF EXISTENCE PART I:							  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{With all assumptions in place}
-The goal of this section will be to prove existence of a weak energy solution under all the assumptions \ref{ass:Phi_general}-\ref{ass:smooth_boundary}, but before doing that some preliminary facts should be established.
-
-\begin{proposition}
-\label{prop:classical_sols_seq}
-With assumptions \ref{ass:Phi_general}-\ref{ass:u_0}, \ref{ass:f_ft_u_0_bounded} and \ref{ass:smooth_boundary} as well as the approximations introduced in section \ref{sec:approximations}, we can identify a sequence $(u_n)$ of classical solutions of some homogeneous Dirichlet problems.
-Moreover, the sequence is uniformly bounded in $Q_T$ with some bound $M$.
-\end{proposition}
-
-\begin{proof}
-With the provided approximations, the problem
+We define the approximations of $f$ in a similar manner: Let $\tilde{f}_n = \mathrm{max}\{ \mathrm{min}\{f,n \}, -n\}$, and then define $f_n = \tilde{f}_n * \varphi_{\frac{1}{n}}$.
+Notice that by Young's inequality $||f_n||_{L^2(Q_T)} \leq ||\tilde{f}_n||_{L^2(Q_T)} \leq ||f||_{L^2(Q_T)}$.
+
+With these approximations at hand we can define an approximate problem to (\ref{HDP}), by
  \begin{equation}
@@
 \end{equation}
+
+The main strategy in proving Theorem \ref{thm:weak_existence} is to show the right type of convergence for the solutions of (\ref{approximate_problem}). 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		PROOF OF EXISTENCE PART I:							  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{With all assumptions in place}
+The goal of this section will be to prove existence of a weak energy solution under all the assumptions \ref{ass:Phi_general}-\ref{ass:smooth_boundary}, but before doing that some preliminary facts should be established.
+
+\begin{lemma}
+\label{prop:classical_sols_seq}
+With assumptions \ref{ass:Phi_general}-\ref{ass:u_0}, \ref{ass:f_ft_u_0_bounded} and \ref{ass:smooth_boundary} as well as the approximations introduced in section \ref{sec:approximations}, we can identify a sequence $(u_n)$ of classical solutions of (\ref{approximate_problem}).
+Moreover, there is a constant $M>0$, so that $|u_n(x,t)| \leq M$ in all of $Q_T$ and for all $n$.
+\end{lemma}
+
+\begin{proof}
+With the provided approximations, the approximate problem 
 will for each $n$ permit a classical solution by corollary \ref{cor:GPME_existence}.
@@
 
-Define now for each $n$ $w_n = \Phi_n(u_n)$. It's the sequence $(w_n)$ we will use the Rellich-Kondrachov compactness argument, which motivates the following two propositions.
-
-\begin{proposition}
+Define now for each $n$ $w_n = \Phi_n(u_n)$. It's the sequence $(w_n)$ we will use the Rellich-Kondrachov compactness argument, which motivates the following two lemmas.
+
+\begin{lemma}
 \label{prop:spatial_boundedness}
@@
 In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$.
-Moreover, there is some $K >0$, depending only on $M$ and $\Phi$, so that
+Moreover, there is some $K >0$, depending only on $M$ from Lemma \ref{prop:classical_sols_seq} and $\Phi$, so that
 \begin{equation}
@@
 for all $n$.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 	\end{equation*}
-	from which it is easy to see that $\Psi_n(u) \leq 0$ for every $u \in \mathbb{R}$. It is also very much worthwhile to see that because $\Phi_n$ is monotone for every $n$ we have the estimate
-	\begin{equation*}
-	|\Psi_n(u)| \geq |\Phi_n(u)u|.
+	from which it is easy to see that $\Psi_n(u) \geq 0$ for every $u \in \mathbb{R}$. It is also very much worthwhile to see that because $\Phi_n$ is monotone for every $n$ we have the estimate
+	\begin{equation*}
+	|\Psi_n(u)| \leq |\Phi_n(u)u|.
 	\end{equation*}
@@
 	\end{equation*}
-	Using now that $|u_{0,n}| \leq u_0$ and that $\Phi_n$ is monotone we can remove some of the dependence on $n$ as
-	\begin{equation*}
-	\int_\Omega \Psi_n(u_{0,n})dx \leq \int_\Omega |\Phi_n(u_{0})u_{0}|dx.
-	\end{equation*}
-
-	Now we derive an estimate on $\Phi_n$ in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
+
+	Now we derive an estimate on the $\Phi_n$-part in terms of $\Phi$ and $u_0$. A crude estimate will be sufficient, and we have
 	\begin{align*}
@@
 	\end{align*}
-	where we have used that $\mathrm{supp}(\varphi_{\frac{1}{n}})\subset [-1/n, 1/n]$ as well as that $\Phi$ is monotone. This, when considering $u_0$, we have
-	\begin{align*}
-	|\Phi_n(u_0)| &\leq |\Phi(u_0)| + |u_0| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u_0-y) - \Phi(u_0)| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
+	where we have used that $\mathrm{supp}(\varphi_{\frac{1}{n}})\subset [-1/n, 1/n]$ as well as that $\Phi$ is monotone. This, when considering $u_{0,n}$, we have
+	\begin{align*}
+	|\Phi_n(u_{0,n})| &\leq |\Phi(u_{0,n})| + |u_{0,n}| + \underset{y\in [-1, 1]}{\mathrm{sup}}|\Phi(u_{0,n}-y) - \Phi(u_{0,n})| +\mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
 	& \leq \underset{|s| \leq ||u_0||_\infty}{\mathrm{sup}}|\Phi(s)| + ||u_0||_{\infty}\\
 	& + \underset{\underset{y\in[-1/n,1/n]}{|s| \leq ||u_0||_{\infty}}}{\mathrm{sup}}|\Phi(s-y) - \Phi(s)| + \mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
-	&= K < \infty.
-	\end{align*}
-	All terms are bounded since $u_0$ is bounded, and so we finally get the estimate
-	\begin{equation*}
-	\int_\Omega \Psi_n(u_{0,n})dx \leq K ||u_0||_{L^1(\Omega)},
-	\end{equation*}
+	&=: K < \infty.
+	\end{align*}
+	In the last step we also made repeated use of $|u_{0,n}| \leq ||u_0||_\infty$.
+	All terms are bounded since $u_0$ is bounded. When also using that $||u_{0,n}||_{L^1(\Omega)} \leq ||u_0||_{L^1(\Omega)}$ we finally get the estimate
+	\begin{align*}
+	\int_\Omega \Psi_n(u_{0,n})dx &\leq K ||u_{0,n}||_{L^1(\Omega)} \\
+	&\leq K ||u_0||_{L^1(\Omega)}
+	\end{align*}
 	which is finite from $u_0 \in L^1(\Omega)$.
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:temporal_bound}
-With the same assumptions as in proposition \ref{prop:classical_sols_seq}, the sequence $(\Phi'_n(u_n) |\partial_t u_n|^2)$ is uniformly bounded in $L^1(Q_T^\tau)$ for all $0 < \tau < \frac{T}{2}$.
-\end{proposition}
-
-\begin{proof}
-From lemma \ref{lem:temporal_bound_classical} we have for each $n$ and every cutoff function $\zeta\in C^1([0,T], [0,1])$
+With the same assumptions as in Lemma \ref{prop:classical_sols_seq}, the sequence $(\Phi'_n(u_n) |\partial_t u_n|^2)$ is uniformly bounded in $L^1(Q_T^\tau)$ for all $0 < \tau < \frac{T}{2}$.
+\end{lemma}
+
+\begin{proof}
+From Lemma \ref{lem:temporal_bound_classical} we have for each $n$ and every cutoff function $\zeta\in C^1([0,T], [0,1])$
 	\begin{equation}
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:weak_convergence_w_n}
@@
 $w_n$ contains a subsequence $(w_{n_j})$ converging almost everywhere to some $w \in L^2(Q_T)$. The convergence happens also weakly in $L^2(Q_T)$.
-\end{proposition}
-
-\begin{proof}
-From proposition \ref{prop:spatial_boundedness} $w_n$ and $\nabla w_n$ are uniformly bounded in $L^2(Q_T)$.
-
-Notice that we have from proposition \ref{prop:classical_sols_seq} that $||u_n||_{L^\infty(Q_T)} \leq M$ for all $n$.
+\end{lemma}
+
+\begin{proof}
+From Lemma \ref{prop:spatial_boundedness} $w_n$ and $\nabla w_n$ are uniformly bounded in $L^2(Q_T)$.
+
+Notice that we have from Lemma \ref{prop:classical_sols_seq} that $||u_n||_{L^\infty(Q_T)} \leq M$ for all $n$.
 By assumption $\Phi$ is locally Lipschitz, and so there is a constant $L$ so that $\Phi'(s) \leq L$ for all $s \in [-M, M]$, and from the definition of $\Phi_n$ we then have taht $\Phi'_n(s) \leq L+1$ for all $s\in [-M,M]$ and all $n$.
-Hence $|\partial_t w_n|^2 \leq  (L+1)\Phi'_n(u_n)|\partial_t u_n|^2$, and by proposition \ref{prop:temporal_bound} we have that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T^\tau)$ for $\tau > 0$.As a consequence $w_n$ is uniformly bounded in $H^1(Q_T^\tau)$, for all $\tau > 0$.
+Hence $|\partial_t w_n|^2 \leq  (L+1)\Phi'_n(u_n)|\partial_t u_n|^2$, and by Lemma \ref{prop:temporal_bound} we have that $\partial_t w_n$ is uniformly bounded in $L^2(Q_T^\tau)$ for $\tau > 0$.As a consequence $w_n$ is uniformly bounded in $H^1(Q_T^\tau)$, for all $\tau > 0$.
 
@@
 We can get a similar convergence result for $\nabla w_{n_j}$:
-\begin{proposition}
+\begin{lemma}
 \label{prop:gradw_weak_convergence}
@@
 $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 Since weak convergence implies convergence in the distributional sense and distributional limits are unique, we have that $v=\nabla w$.
-	Thus $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
+So every subsequence og $\nabla w_{n_j}$ has a subsequence that converges weakly to $\nabla w$, which implies that $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
 
@@
 \begin{proof}
-With proposition \ref{prop:classical_sols_seq} we get a sequence of classical solutions $(u_n)$, uniformly bounded by some $M$.
-Propositions \ref{prop:weak_convergence_w_n} and \ref{prop:gradw_weak_convergence} provides subsequence of $w_n = \Phi_n(u_n)$, $(w_{n_j})$, that converges pointwise almost everywhere to some $w$.
+With Lemma \ref{prop:classical_sols_seq} we get a sequence of classical solutions $(u_n)$, uniformly bounded by some $M$.
+Lemmas \ref{prop:weak_convergence_w_n} and \ref{prop:gradw_weak_convergence} provides a subsequence of $w_n = \Phi_n(u_n)$, $(w_{n_j})$, that converges pointwise almost everywhere to some $w$.
 In addition $w_{n_j}$ and $\nabla w_{n_j}$ converges weakly in $L^2(Q_T)$ to $w$ and $\nabla w$ respectively.
@@
 
-	Recall now that by lemma \ref{lem:Energy_equality_classical} 
+	Recall now that by Lemma \ref{lem:Energy_equality_classical} 
 	\begin{equation*}
@@
 \subsubsection{$\Phi$ no longer locally Lipschitz}
-We proceed by generalising the result lemma \ref{lem:existence_part1} to the case when $\Phi$ is no longer locally Lipschitz, i.e. lifting assumption \ref{ass:Phi_lipschitz}.
+We proceed by generalising Lemma \ref{lem:existence_part1} to the case when $\Phi$ is no longer locally Lipschitz, i.e. lifting assumption \ref{ass:Phi_lipschitz}.
 
@@
 
-The following proposition will establish that the sequence $(z_n)$ has the desired boundedness property.
+The following Lemma will establish that the sequence $(z_n)$ has the desired boundedness property.
 
@@
 \end{equation*}
-Using proposition \ref{prop:spatial_boundedness} we conclude that both $z_n$ and $\nabla z_n$ are uniformly bounded in $L^2(Q_T)$.
+Using Lemma \ref{prop:spatial_boundedness} we conclude that both $z_n$ and $\nabla z_n$ are uniformly bounded in $L^2(Q_T)$.
 
@@
 \end{equation*}
-With proposition \ref{prop:temporal_bound} $\partial_t z_n$ is uniformly bounded in $L^2(Q_T^\tau)$, and we conclude that $z_n$ is uniformly bounded in $H^1(Q_T^\tau)$.
-\end{proof}
-
-We are also able to establish some convergence results for $z_n$, summarised in propositions immediately below.
-
-\begin{proposition}
+With Lemma \ref{prop:temporal_bound} $\partial_t z_n$ is uniformly bounded in $L^2(Q_T^\tau)$, and we conclude that $z_n$ is uniformly bounded in $H^1(Q_T^\tau)$.
+\end{proof}
+
+We are also able to establish some convergence results for $z_n$, summarised in lemmas immediately below.
+
+\begin{lemma}
 \label{prop:z_n_weak_convergence}
@@
 The convergence happens also weakly in $L^2(Q_T)$.
-\end{proposition}
-
-\begin{proof}
-This proof is almost identical to the proof of proposition \ref{prop:weak_convergence_w_n} and \ref{prop:gradw_weak_convergence}: Using proposition \ref{prop:z_n_bounded_H1} and Rellich-Kondrachov we can construct the same type of diagonal argument to extract a subsequence $(z_{n_j})$ that converges almost everywhere to $z$.
+\end{lemma}
+
+\begin{proof}
+This proof is almost identical to the proofs of lemmas \ref{prop:weak_convergence_w_n} and \ref{prop:gradw_weak_convergence}: Using Lemma \ref{prop:z_n_bounded_H1} and Rellich-Kondrachov we can construct the same type of diagonal argument to extract a subsequence $(z_{n_j})$ that converges almost everywhere to $z$.
 Since $z_n$ is a bounded sequence in $L^2(Q_T)$, a reflexive Hilbert space, every subsequence contains a weakly convergent subsequence.
-The same use of Egorov's theorem as in proposition \ref{prop:weak_convergence_w_n} establishes that $z_{n_j}$ converges weakly to $z$ in $L^2(Q_T)$.
-\end{proof}
-
-This enables to prove existence in a slightly more general setting.
+The same use of Egorov's theorem as in Lemma \ref{prop:weak_convergence_w_n} establishes that $z_{n_j}$ converges weakly to $z$ in $L^2(Q_T)$.
+\end{proof}
+
+This enables us to prove existence in a slightly more general setting.
 \begin{lemma}
 \label{lem:weak_existence_part2}
-Theorem \ref{thm:weak_existence} holds with the additional assumptions \ref{ass:f_ft_u_0_bounded}, \ref{ass:Phi_strictly_increasing} and \ref{ass:smooth_boundary}.
+Theorem \ref{thm:weak_existence} holds with the additional assumptions \ref{ass:f_ft_u_0_bounded} and \ref{ass:smooth_boundary}.
 \end{lemma}
@@
 \begin{proof}
-We use proposition \ref{prop:classical_sols_seq} to get a sequence $(u_n)$ of classical soltutions, and we can use this sequence to define $(z_n)$.
-Further, proposition \ref{prop:z_n_weak_convergence} provides us with a subsequence $(z_{n_j})$ that converges almost everywhere to $z$.
+We use Lemma \ref{prop:classical_sols_seq} to get a sequence $(u_n)$ of classical soltutions, and we can use this sequence to define $(z_n)$.
+Further, Lemma \ref{prop:z_n_weak_convergence} provides us with a subsequence $(z_{n_j})$ that converges almost everywhere to $z$.
 Now we obviously have $u_{n_j} = Z_{n_j}^{-1}(z_{n_j})$, and so
@@
 since $|z_{n_j}| \leq |u_{n_j}| \leq M$.
-And so the first term on the right hand side in the above inequality is controlled by $Z_n^{-1}$ converging uniformly to $Z^{-1}$ on compact sets, as shown in proposition \ref{prop:Zinv_uniform_convergence}.
+And so the first term on the right hand side in the above inequality is controlled by $Z_n^{-1}$ converging uniformly to $Z^{-1}$ on compact sets, as shown in Lemma \ref{prop:Zinv_uniform_convergence}.
 The second term tends to zero since $z_{n_j}$ converges pointwise to $z$ and $Z^{-1}$ is continuous.
@@
 
-The rest of the proof is almost identical to that for lemma \ref{lem:existence_part1}.
+The rest of the proof is almost identical to that for Lemma \ref{lem:existence_part1}.
 First, $w_{n_j}$ converges pointwise almost everywhere to some $w = \Phi(u)$, which follows from the fact that $\Phi_n$ converges uniformly to $\Phi$ on compact sets, and the continuity of $\Phi$.
@@
 
-Since $\nabla w_{n_j}$ is a bounded sequence in $L^2(Q_T)$, by proposition \ref{prop:spatial_boundedness}, we can argue as in proposition \ref{prop:gradw_weak_convergence} to deduce that $\nabla w_{n_j}$ converges weakly to $\nabla w$.
-
-It follows that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense, and since $w_{n_j}$ is bounded in $L^2(Q_T)$ we can deduce that $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
-
-Lastly, establishing that $u$ is a weak solution and satisfies inequality (\ref{energy_ineq}) follows the exact same argument as in the proof of lemma \ref{lem:existence_part1}.
+Since $\nabla w_{n_j}$ is a bounded sequence in $L^2(Q_T)$, by Lemma \ref{prop:spatial_boundedness}, we can argue as in Lemma \ref{prop:gradw_weak_convergence} to deduce that $\nabla w_{n_j}$ converges weakly to $\nabla w$:
+
+It follows that $\nabla w_{n_j}$ converges to $\nabla w$ in the distributional sense, and since $w_{n_j}$ is bounded in $L^2(Q_T)$ we can deduce, by way of Banach-Alaoglu's and the uniqueness of distributional limits, that $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
+
+Lastly, establishing that $u$ is a weak solution and satisfies inequality (\ref{energy_ineq}) follows the exact same argument as in the proof of Lemma \ref{lem:existence_part1}.
 \end{proof}

### 2014-12-17 draft_project.tex
Bare innspurten igjen nå, er det ikke? Vetta faen, vil ha mølje.

@@
 \label{cor:spatial_bound_w_poincare}
-In addition to the assumptions under lemma \ref{lem:Energy_equality_classical}, assume $f,\Phi(u) \in L^2(Q_T)$, then
-\begin{equation}
-\label{spatial_derivative_bound_w_poincare}
-\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
+In addition to the assumptions under lemma \ref{lem:Energy_equality_classical}, assume $f,\Phi(u) \in L^2(Q_T)$, then for each $\tau \in [0,T]$
+\begin{equation}
+\label{spatial_derivative_bound_w_poaincare}
+\frac{1}{2}\iint_{Q_\tau}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(\tau))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_\tau}f^2dxdt.
 \end{equation}
@@
 \begin{proof}
-Set $\tau=T$ in (\ref{spatial_derivative_bound}), and for the term involving $f$ in (\ref{spatial_derivative_bound}) we use the inequality $ab \leq \frac{a^2}{4c} + cb^2$ for any reals $a$ and $b$, and any positive $c$, to get
-\begin{equation*}
-\iint_{Q_T}f\Phi(u) dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\iint_{Q_T}\Phi(u)^2 dxdt.
-\end{equation*}
-
-On the latter of the right hand terms we can for each $t \in [0,T]$ use the Poincaré inequality
+for the term involving $f$ in (\ref{spatial_derivative_bound}) we use the inequality $ab \leq \frac{a^2}{4c} + cb^2$ for any reals $a$ and $b$, and any positive $c$, to get
+\begin{equation*}
+\iint_{Q_\tau}f\Phi(u) dxdt \leq \frac{1}{4c}\iint_{Q_\tau}f^2dxdt + c\iint_{Q_\tau}\Phi(u)^2 dxdt.
+\end{equation*}
+
+On the latter of the right hand terms we can for each $t \in [0,\tau]$ use the Poincaré inequality
 \begin{equation*}
@@
 \begin{equation*}
-\iint_{Q_T} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\tilde{C}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt. 
+\iint_{Q_\tau} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_\tau}f^2dxdt + c\tilde{C}\iint_{Q_\tau}|\nabla \Phi(u)|^2dxdt. 
 \end{equation*}
@@
 \begin{equation*}
-\iint_{Q_T}f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt.
+\iint_{Q_\tau}f\Phi(u)dxdt \leq C\iint_{Q_\tau}f^2dxdt + \frac{1}{2}\iint_{Q_\tau}|\nabla \Phi(u)|^2dxdt.
 \end{equation*}
@@
 \begin{equation}
-\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
+\frac{1}{2}\iint_{Q_\tau}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(\tau))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_\tau}f^2dxdt.
 \end{equation}
@@
 
-We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$. We also ask that $|u_{0,n}| \leq \mathrm{min}\{n,|u_0|\}$.
+We also let $u_{0,n}\in C^\infty_c(\Omega)$ be a smooth approximation of $u_0$, and converging in $L_\Psi(\Omega)$.
 This construction can be done as follows: First, define $\tilde{u}_n = \mathrm{max}\{ \mathrm{min}\{u_0, n\}, -n\}$, so $u_0$ is truncated at $\pm n$.
@@
 The requirement on the distance between $V_n$ and $\partial \Omega$ we see is to ensure that $u_{0,n}$ and its derivatives vanish at the boundary.
+See that this way of approximating $u_0$ ensures that $||u_{0,n}||_{L^1(\Omega)} \leq ||u_0||_{L^1(\Omega)}$ as well as $||u_{0,n}||_{L^\infty(\Omega)} \leq ||u_0||_{L^\infty(\Omega)}$ for all $n$ by Young's inequality for convolutions.
 
@@
 \label{prop:spatial_boundedness}
-With the same assumptions as in proposition \ref{prop:classical_sols_seq},
+With the same assumptions as in Lemma \ref{prop:classical_sols_seq},
 the sequences $(w_n)$ and $(\nabla w_n)$ are uniformly bounded in $L^2(Q_T)$.
@@
 	\item We define the subsequence $(w_{n_j})$ by $w_{n_j} = w_{n_j}^j$, which will converge to some $w$ in $L^2(Q_T^\tau)$ for every $\tau > 0$, and hence in $L^2_{loc}(Q_T)$.
-Without loss of generality we assume $w_{n_j}$ converges to $w$ almost everywhere in $Q_T$ (If not, take yet another subsequence so that it does).
+
 \end{enumerate}	 
+	To ensure that we get a subsequence that converges almost everywhere to $w$, we need to make use of an additional diagonal argument on $w_{n_j}$.
+To that end, let $A_n$ be a sequence of compact subsets of $Q_T$, so that $A_k \subset A_{k+1}$ for every $k$, and $\cup_{k \in \mathbb{N}}A_k = Q_T$.
+We proceed as follows:
+	\begin{enumerate}[i)]
+		\item There is a subsequence $w_{n_j}^1$ that converges pointwise almost everwhere to $w$ in $A_1$. Denote by $N_1$, the null set for which pointwise convergence isn't guaranteed.
+		\item Take a subsequence $w_{n_j}^1$ that converges almost everywhere to $w$ in $A_2$. Call this subsequence $w_{n_j}^2$, and $N_2$ the null set for which convergence doesn't hold.
+
+		\item Proceed in this manner for each $k$ to get subsequences $w_{n_j}^k$ that converge everywhere in $A_k \setminus N_k$ to $w$.
+
+		\item Finally define the subsequence $w_{n_j} = w_{n_j}^j$.	
+	\end{enumerate}
+	This final subsequence will converge almost everywhere in $Q_T$.
+To see this, consider any $(x,t) \in Q_T \setminus \left( \cup_{k \in \mathbb{N}}N_k \right)$.
+Then there is some $k$ so that $(x,t) \in A_k\setminus N_k$ which implies that $w_{n_j}(x,t) \to w(x,t)$.
+As a consequence the set where $w_{n_j}$ doesn't converge must be a subset of $\cup_{k\in \mathbb{N}} N_k$, and by the countable subadditivity of the Lebesgue measure, this has measure $0$.
 
@@
 
-With this list of propositions we are in a position to prove our first lemma, which reads
+With this list of propositions we are in a position to prove our first existence Lemma, which reads
 \begin{lemma}
@@
 
+	\item[$u \in L^\infty(0,T: L_\Psi(\Omega)$:]
+	For any $t \in [0,T]$ we have by Fatou's Lemma \citep[p. 162]{weiss1999course} that 
+	\begin{equation*}
+	||u(t)||_{L^1(\Omega)} \leq \liminf_{n \to \infty} ||u_n(t)||_{L^1(\Omega)}.
+	\end{equation*}
+	Here we use Corollary \ref{cor:l1-contractivity_classical} with $\hat{u}=0$ as the solution to zero loading and initial data to get that
+	\begin{align}
+	||u(t)||_{L^1(\Omega)} &\leq \liminf_{n \to \infty} \left( ||u_{0,n}||_{L^1(\Omega)} + ||f_n||_{L^1(Q_T)}\right) \nonumber \\
+	&= ||u_0||_{L^1(\Omega)} + ||f||_{L^1(Q_T)},	
+	\end{align}
+	implying that $u \in L^\infty(0,T: L^1(\Omega))$.
+
+	We do similarly for $\Psi(u(t))$, but first we need to show that $\Psi_n(u_n)$ converges almost everwhere to $\Psi(u)$. We use the triangle inequality as
+	\begin{equation}
+	|\Psi_n(u_n) - \Psi(u)| \leq |\Psi_n(u_n) - \Psi(u_n)| + |\Psi(u_n) + \Psi(u)|.
+	\end{equation}
+	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see proposition \ref{prop:Psi_uniform_convergence}) to control the first term.
+The second term is controlled by the almost everywhere convergence of $u_n$ to $u$ and the continuity of $\Psi$.
+
+	Then, by Fatou's Lemma
+	\begin{equation*}
+	\int_\Omega \Psi(u(t))dx \leq \liminf_{n \to \infty} \int_\Omega \Psi_n(u_n(t))dx,
+	\end{equation*}
+	since $\Psi_n$ is nonnegative. Using Corollary \ref{cor:spatial_bound_w_poincare} we get
+	\begin{align*}
+	\int_\Omega \Psi(u(t))dx &\leq \liminf_{n \to \infty} \left( \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt \right)\nonumber \\
+	&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f^2dxdt, 
+	\end{align*}
+	and so we have that $u \in L^\infty(0,T: L_\Psi(\Omega))$.
+
 	\item[$u$ is a weak solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}_0(\Omega))\subset L^2(0,T: H^1_0(\Omega))$ since $\Omega$ is bounded.
@@
 	\item[Fulfillment of the energy inequality:]
-	We note that $\Psi_n(u_n)$ converges almost everywhere to $\Psi(u)$, which is shown similarly to how we showed that $u_{n_j}$ converges almost everywhere to $u$. We use the triangle inequality as
-	\begin{equation}
-	|\Psi_n(u_n) - \Psi(u)| \leq |\Psi_n(u_n) - \Psi(u_n)| + |\Psi(u_n) + \Psi(u)|.
-	\end{equation}
-	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see proposition \ref{prop:Psi_uniform_convergence}) to control the first term.
-The second term is controlled by the almost everywhere convergence of $u_n$ to $u$ and the continuity of $\Psi$.
-By Fatou's lemma \citep[p.
-162]{weiss1999course} and that $\Psi_n(u_n)$ are all nonnegative
+	By Fatou's lemma \citep[p. 162]{weiss1999course} and that $\Psi_n(u_n)$ are all nonnegative
 	\begin{equation}
@@
 \subsubsection{$\Phi$ no longer locally Lipschitz}
-We proceed by generalising Lemma \ref{lem:existence_part1} to the case when $\Phi$ is no longer locally Lipschitz, i.e. lifting assumption \ref{ass:Phi_lipschitz}.
-
-Looking back at the previous section, we see that the only place where we actually made use of $\Phi$ being locally Lipschitz, was in getting a uniform bound on $\partial_t w_n$ in $L^2(Q_T^\tau)$ by way of proposition \ref{prop:temporal_bound}.
+We proceed by generalising Lemma \ref{lem:existence_part1} to the case when $\Phi$ is no longer locally Lipschitz, i.e.
+lifting assumption \ref{ass:Phi_lipschitz}.
+This is the case for example with $\Phi(u) = |u|^{m-1}u$ with $0< m < 1$, i.e.
+the fast diffusion equation.
+Looking back at the previous section, we see that the only place where we actually made use of $\Phi$ being locally Lipschitz, was in getting a uniform bound on $\partial_t w_n$ in $L^2(Q_T^\tau)$ by way of Lemma \ref{prop:temporal_bound}.
 Because of this we'll take a small detour to find a sequence that enjoys the same uniform bounds as $w_n$ did in the previous section.
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:z_n_bounded_H1}
 With assumptions \ref{ass:Phi_general}-\ref{ass:u_0}, \ref{ass:f_ft_u_0_bounded} and \ref{ass:smooth_boundary}, the sequence $(z_n)$ is uniformly bounded in $H^1(Q_T^\tau)$ for $0<\tau < \frac{T}{2}$.
-\end{proposition}
+\end{lemma}
 
@@
 \label{prop:z_n_weak_convergence}
-Under the same assumptions as proposition \ref{prop:z_n_bounded_H1}, $z_n$ contains a subsequence $(z_{n_j})$ that converges almost everywhere to some $z$.
+Under the same assumptions as Lemma \ref{prop:z_n_bounded_H1}, $z_n$ contains a subsequence $(z_{n_j})$ that converges almost everywhere to some $z$.
 The convergence happens also weakly in $L^2(Q_T)$.
@@
 We will continue on with lifting more of the assumptions, in particular those on $f$ and $u_0$, but first an intermediate result is needed.
-The result is simply the $L^1$-stability presented in lemma \ref{lem:l1_stability_classical} only now for weak solutions.
-
-\begin{proposition}
+The result is simply the $L^1$-stability presented in Lemma \ref{lem:l1_stability_classical} only now for weak solutions.
+
+\begin{lemma}
 \label{prop:l1_stability_weak_part1}
-Assume the assumptions as in lemma \ref{lem:weak_existence_part2}, and let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
+Assume the same as in Lemma \ref{lem:weak_existence_part2}, and let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
 They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively.
@@
 for almost every $t\in [0,T]$.
-\end{proposition}
+\end{lemma}
 
@@
 All the above approximations are as already presented in the foregoing proofs.
-Hence we have by proposition \ref{prop:classical_sols_seq} sequences of classical solutions $u_n$ and $\hat{u}_n$.
-With the same argument as was done in lemma \ref{lem:weak_existence_part2}, these sequences converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
+Hence we have by Lemma \ref{prop:classical_sols_seq} sequences of classical solutions $u_n$ and $\hat{u}_n$.
+With the same argument as was done in Lemma \ref{lem:weak_existence_part2}, these sequences converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
 
@@
 The first and last term on the right hand side are easily controlled by the convergence of $u_n$ and $\hat{u}_n$.
-As for the middle term we use corollary \ref{cor:l1-contractivity_classical}, and so for any $\epsilon > 0$,
+As for the middle term we use Corollary \ref{cor:l1-contractivity_classical}, and so for any $\epsilon > 0$,
 \begin{equation*}
@@
 
-To conclude this section, is a proposition on an estimate for $\partial_t z$ in $L^2(Q_T)$, which will prove useful in the coming section.
-
-\begin{proposition}
+To conclude this section, is a Lemma on an estimate for $\partial_t z$ in $L^2(Q_T)$, which will prove useful in the coming section.
+
+\begin{lemma}
 \label{prop:z_t_estimate}
-Under the same assumptions as proposition \ref{prop:z_n_bounded_H1}, $\partial_t z_n$ converges weakly to $\partial_t z$ in $L^2(Q_T^\tau)$, for $0 < \tau < \frac{T}{2}$. Moreover, the esimate
+Under the same assumptions as Lemma \ref{prop:z_n_bounded_H1}, $\partial_t z_n$ converges weakly to $\partial_t z$ in $L^2(Q_T^\tau)$, for $0 < \tau < \frac{T}{2}$. Moreover, the esimate
 \begin{equation}
@@
 
-\end{proposition}
-\begin{proof}
-That $\partial_t z_n$ converges weakly to $\partial_t z$ in follows by almost the exact same approach we used in proving proposition \ref{prop:gradw_weak_convergence}: First by noting that since $z_n$ converges weakly to $z$ in $L^2(Q_T)$, $\partial_t z_n$ must converge to $\partial_t z$ in the distributional sense.
-
-For every $\tau > 0$, $\partial_t z_n$ is a uniformly bounded sequence in $L^2(Q_T^\tau)$, and so we can use the same argument as in proposition \ref{prop:gradw_weak_convergence} to deduce that $\partial_t z_n$ converges weakly to $\partial_t z$ in $L^2(Q_T^\tau)$ for every $0 < \tau < \frac{T}{2}$.
+\end{lemma}
+\begin{proof}
+That $\partial_t z_n$ converges weakly to $\partial_t z$ in follows by almost the exact same approach we used in proving Lemma \ref{prop:gradw_weak_convergence}: First by noting that since $z_n$ converges weakly to $z$ in $L^2(Q_T)$, $\partial_t z_n$ must converge to $\partial_t z$ in the distributional sense.
+
+For every $\tau > 0$, $\partial_t z_n$ is a uniformly bounded sequence in $L^2(Q_T^\tau)$, and so we can use the same argument as in Lemma \ref{prop:gradw_weak_convergence} to deduce that $\partial_t z_n$ converges weakly to $\partial_t z$ in $L^2(Q_T^\tau)$ for every $0 < \tau < \frac{T}{2}$.
 
@@
 \end{equation}
-and by proposition \ref{prop:temporal_bound}, we get that for any smooth cutoff function $\zeta$ with the above stated properties
+and by Lemma \ref{prop:temporal_bound}, we get that for any smooth cutoff function $\zeta$ with the above stated properties
 \begin{align*}
@@
 \end{equation}
-On the first term on the right hand side, we use the estimate (\ref{gradwn_bound_uniform}) provided by proposition \ref{prop:spatial_boundedness} to get
+On the first term on the right hand side, we use the estimate (\ref{gradwn_bound_uniform}) provided by Lemma \ref{prop:spatial_boundedness} to get
 \begin{equation*}
@@
 \begin{equation}
-\iint_{Q_T^\tau} |\partial_t z|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}\right) + \iint_{Q_T}|\partial_t (f_n \zeta) w_n| dxdt = \iint_{Q_T}|\partial_t (f \zeta ) w| dxdt.
+\iint_{Q_T^\tau} |\partial_t z|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}\right) +  \iint_{Q_T}|\partial_t (f \zeta ) w| dxdt.
 \end{equation}
@@
 \subsubsection{No longer $C^{2,\alpha}$ boundary}
-Following suit from the previous section, we'll now aim to prove lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$.
-
-To that end, we take a sequence of simply connected compact sets $K_n \subset \Omega$ so that $K_n \subset K_{n+1}$ and $\cup_{n \in \mathbb{N}}K_n = \Omega$.
+Following suit from the previous section, we'll now aim to prove Lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$, of course, this is usually the case in applications, where the domain can have corners and such, making the boundary not sufficiently smooth to satisfy the assumptions in theorem \ref{thm:classical_existence} to provide a classical solution.
+The strategy for proving existence now will be to get a sequence of weak solution on smaller subdomains that will eventually converge to all of $Q_T$.
+
+To that end, we will in this section alter the approximations on $u_0$ and $f$ that were provided in section \ref{sec:approximations}.
+Take a sequence of simply connected compact sets $K_n \subset \Omega$ so that $K_n \subset K_{n+1}$ and $\cup_{n \in \mathbb{N}}K_n = \Omega$.
 Quite similarly to how we did when approximating $u_0$ in section \ref{sec:approximations}, but now with the additional asssumption that $\partial K_n$ is $C^{2,\alpha}$ smooth for each $n$.
-We'll also denote by $Q_n$ the time-space sylinder $K_n \times (0,T)$.
+We'll also denote by $Q_n$ the time-space cylinder $K_n \times (0,T)$.
 
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:sequence_weak_solution_nonsmoothboundary}
 With assumptions \ref{ass:Phi_general}-\ref{ass:f_ft_u_0_bounded}, we can identify a sequence $u_n$ in $L^1(Q_T)$ that are weak energy solutions on $Q_n \subset Q_T$. 
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 \end{equation}
-which has by lemma \ref{lem:weak_existence_part2} a weak energy solution. We'll denote by $u_n$ the weak solution extended by $0$ to be defined in all of $Q_T$.
+which has by Lemma \ref{lem:weak_existence_part2} a weak energy solution. We'll denote by $u_n$ the weak solution extended by $0$ to be defined in all of $Q_T$.
 \end{proof}
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:w_n_nonsmooth_spatial_boundedness}
-With the same assumptions as proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}, the sequence $w_n$ is bounded in $L^2(0,T: H_0^1(\Omega))$.
-\end{proposition}
-\begin{proof}
-Notice that for each $n$, $w_n= |\nabla w_n|=0$ in $Q_T\setminus Q_n$ by the construction done in proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}, and so
+With the same assumptions as Lemma \ref{prop:sequence_weak_solution_nonsmoothboundary}, the sequence $w_n$ is bounded in $L^2(0,T: H_0^1(\Omega))$.
+\end{lemma}
+\begin{proof}
+Notice that for each $n$, $w_n= |\nabla w_n|=0$ in $Q_T\setminus Q_n$ by the construction done in Lemma \ref{prop:sequence_weak_solution_nonsmoothboundary}, and so
 
@@
 where we've also made use of that $|u_{0,n}| \leq |u_0|$, as well as that $w_n$ and $u_{0,n}$ vanish outside of $Q_n$ and $K_n$ respectively.
-$w_n$ is in $L^2(0,T:H_0^1(\Omega)$ for each $n$, so use of the inequality $ab \leq \frac{a^2}{4c} + cb^2$ on the last term on the right hand side yields
+$w_n$ is in $L^2(0,T:H_0^1(\Omega))$ for each $n$, so use of the inequality $ab \leq \frac{a^2}{4c} + cb^2$ on the last term on the right hand side yields
 \begin{equation*}
@@
 
-We use a Poincaré inequality, set $c$ as was done in corollary \ref{cor:spatial_bound_w_poincare} and notice that $f_n^2 \leq f^2$ in $Q_T$ to arrive at
+We use a Poincaré inequality, set $c$ as was done in Corollary \ref{cor:spatial_bound_w_poincare} and notice that $f_n^2 \leq f^2$ in $Q_T$ to arrive at
 \begin{equation*}
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:z_n_bounded_in_H1}
-With the same assumptions as proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}, the sequence $z_n$ is bounded in $H^1(Q_T^\tau)$ for every $0 < \tau < \frac{T}{2}$.
-\end{proposition}
-
-\begin{proof}
-That $z_n$ is bounded in $L^2(0,T: H_0^1(\Omega))$ follows from the observation that $|\nabla z_n| \leq |\nabla w_n|$ almost everywhere and proposition \ref{prop:w_n_nonsmooth_spatial_boundedness}.
+With the same assumptions as Lemma \ref{prop:sequence_weak_solution_nonsmoothboundary}, the sequence $z_n$ is bounded in $H^1(Q_T^\tau)$ for every $0 < \tau < \frac{T}{2}$.
+\end{lemma}
+
+\begin{proof}
+That $z_n$ is bounded in $L^2(0,T: H_0^1(\Omega))$ follows from the observation that $|\nabla z_n| \leq |\nabla w_n|$ almost everywhere and Lemma \ref{prop:w_n_nonsmooth_spatial_boundedness}.
 We have for every $n$ that $z_n = 0$ in $Q_T\setminus Q_n$, and as a consequence $\partial_t z_n = 0$ also.
@@
 
-By proposition \ref{prop:z_t_estimate} we can use the estimate (\ref{z_t_estimate}) as
+By Lemma \ref{prop:z_t_estimate} we can use the estimate (\ref{z_t_estimate}) as
 \begin{equation}
@@
 \end{equation}
-where $\zeta = \zeta(t)$ is a smooth cutoff function from proposition \ref{prop:z_t_estimate}, which has a bounded derivative.
+where $\zeta = \zeta(t)$ is a smooth cutoff function from Lemma \ref{prop:z_t_estimate}, which has a bounded derivative.
 
@@
 
-With that last proposition we are able to prove existence of weak energy solutions
+With that last Lemma we are able to prove existence of weak energy solutions
 
@@
 \label{lem:weak_existence_part3}
-Theorem \ref{thm:weak_existence} holds with additional assumptions \ref{ass:f_ft_u_0_bounded} and \ref{ass:Phi_strictly_increasing}.
+Theorem \ref{thm:weak_existence} holds with the additional assumption \ref{ass:f_ft_u_0_bounded}.
 \end{lemma}
@@
 \begin{proof}
-We start by constructing a sequence of weak solutions $(u_n)$ in $Q_n$ defined in $Q_T$ as done in proposition \ref{prop:sequence_weak_solution_nonsmoothboundary}.
-With $z_n = Z(u_n)$ and $w_n = \Phi(u_n)$, $(z_n)$ is bounded in $H^1(Q_T^\tau)$ for every $0< \tau < \frac{T}{2}$ by proposition \ref{prop:z_n_bounded_in_H1}.
-A diagonal argument, as was done in the proof of \ref{prop:weak_convergence_w_n} to extract a subsequence of $(z_n)$ that converges pointwise almost everywhere to some $z$.
-With a pointwise limit for a subsequence $z_{n_j}$, the rest of the proof is identical to the proof of lemma \ref{lem:weak_existence_part2}.
-\end{proof}
-
-Before we move on to remove the assumption regarding the boundedness of $u_0$ and $f$ we need to ensure the $L^1$-contractivity result of proposition \ref{prop:l1_stability_weak_part1} still holds after passing to limit as we did in the proof of lemma \ref{lem:weak_existence_part3}, it will become useful in the coming section.
-
-\begin{proposition}
+We start by constructing a sequence of weak solutions $(u_n)$ in $Q_n$ defined in $Q_T$ as done in Lemma \ref{prop:sequence_weak_solution_nonsmoothboundary}.
+With $z_n = Z(u_n)$ and $w_n = \Phi(u_n)$, $(z_n)$ is bounded in $H^1(Q_T^\tau)$ for every $0< \tau < \frac{T}{2}$ by Lemma \ref{prop:z_n_bounded_in_H1}.
+A diagonal argument, as was done in the proof of Lemma \ref{prop:weak_convergence_w_n} to extract a subsequence of $(z_n)$ that converges pointwise almost everywhere to some $z$.
+With a pointwise limit for a subsequence $z_{n_j}$, the rest of the proof is identical to the proof of Lemma \ref{lem:weak_existence_part2}.
+\end{proof}
+
+Before we move on to remove the assumption regarding the boundedness of $u_0$ and $f$ we need to ensure the $L^1$-contractivity result of Lemma \ref{prop:l1_stability_weak_part1} still holds after passing to limit as we did in the proof of Lemma \ref{lem:weak_existence_part3}, it will become useful in the coming section.
+
+\begin{lemma}
 \label{prop:l1_stability_weak_part2}
-With assumptions \ref{ass:Phi_general}-\ref{ass:Phi_strictly_increasing},  let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
+With assumptions \ref{ass:Phi_general}-\ref{ass:f_ft_u_0_bounded},  let $u$ and $\hat{u}$ be two weak energy solutions with nonlinearity $\Phi$.
 They have initial data $u_0$ and $\hat{u}_0$, as well as loading $f$ and $\hat{f}$ respectively.
@@
 holds for almost every $t\in [0,T]$.
-\end{proposition}
-
-\begin{proof}
-The proof follows closely that of proposition \ref{prop:l1_stability_weak_part1}.
+\end{lemma}
+
+\begin{proof}
+The proof follows closely that of Lemma \ref{prop:l1_stability_weak_part1}.
 Indeed, we start by constructing sequences of weak solutions $u_n$ and $\hat{u}_n$ by proposition \ref{prop:sequence_weak_solution_nonsmoothboundary} that converge to $u$ and $\hat{u}$ in $L^1(Q_T)$.
@@
 for sufficiently large $n$.
-Since both $u_n$ and $\hat{u}_n$ vanish on $Q_T\setminus Q_n$ the integration can be restricted to $K_n$ instead of $\Omega$, leaving us in a position to make use of proposition \ref{prop:l1_stability_weak_part1}, resulting in
+Since both $u_n$ and $\hat{u}_n$ vanish on $Q_T\setminus Q_n$ the integration can be restricted to $K_n$ instead of $\Omega$, leaving us in a position to make use of Lemma \ref{prop:l1_stability_weak_part1}, resulting in
 \begin{align*}
@@
 \begin{proof}[Proof of theorem \ref{thm:weak_existence}]
-
+As opposed to the previous weak existence proofs, the strategy here will be to use the $L^1$-contractivity to establish convergence, rather than a compactness argument.
 \begin{description}
@@
 Let $(u_{0,n})$ be sequence of bounded functions converging to $u_0$ in $L_{\Psi}(\Omega)$, and $(f_n)$ a sequence of bounded functions converging to $f$ in $L^2(Q_T)$, as well as $\partial_t f_n$ being bounded in $Q_T$ for each $n$.
-It will also be useful to assume $|u_{0,n}| \leq |u_0|$ and $|f_n| \leq |f|$ for all $n$.
-A way, to do this is first truncate $u_0$ and $f$ below and above by $-n$ and $n$, and then mollify.
-
-For example, for $f$ we define $\tilde{f}_n = \mathrm{max}\{ -n, \mathrm{\min}\{f,n\}\}$ and then $f_n = \tilde{f}_n * \varphi_{\frac{1}{n}}$, with $\varphi_{\frac{1}{n}}$ is the scaled standard mollifier in $\mathbb{R}^{d+1}$.
+It will also be useful to assume $|u_{0,n}| \leq |u_0|$.
+A way, to do this is first truncate $u_0$ and $f$ below and above by $-n$ and $n$, and then for the approximations of $f$, mollify, as was done in section \ref{sec:approximations}.
 The mollification is there to ensure that also $\partial_t f_n$ is bounded for each $n$.
 
-Using lemma \ref{lem:weak_existence_part3} we get a sequence of weak energy solutions, $(u_n)$. By lemma \ref{prop:l1_stability_weak_part2}
+Using Lemma \ref{lem:weak_existence_part3} we get a sequence of weak energy solutions, $(u_n)$, and by Lemma \ref{prop:l1_stability_weak_part2}
 \begin{equation*}
@@
 \item[$\Phi(u)$ is in $L^2(Q_T)$:]
-This part of the proof will closely resemble the part of the proof for lemma \ref{prop:weak_convergence_w_n}.
+This part of the proof will closely resemble the part of the proof for Lemma \ref{prop:weak_convergence_w_n}.
 See that since $\Phi$ is continuous, $\Phi(u_n)$ converges almost everywhere to $\Phi(u)$.
@@
 With the assumptions we've put on $f_n$ and $u_{0,n}$ we can conclude that $||f_n||_{L^2(Q_T)} \leq ||f||_{L^2(Q_T)}$ and $||\Psi(u_{0,n})||_{L^1(\Omega)} \leq ||\Psi(u_0)||_{L^1(\Omega)}$.
+This last inequality comes from the fact that $\Psi(s) \leq \Psi(r)$ whenever $|s|\leq |r|$ and the have equal sign, which is the case with $u_{0,n}$ and $u_0$.
 This implies that $\nabla \Phi(u_n)$ is uniformly bounded in $L^2(Q_T)$, and as an extension $\Phi(u_n)$ is also bounded in $L^2(Q_T)$ from the Poincaré inequality.
 
-By Banach-Alaoglu every subsequence of $\Phi(u_n)$ has a weakly convergent subsequence, and by the pointwise convergence we can, after arguing as in the proof in lemma \ref{prop:weak_convergence_w_n}, conclude that the weak limit is always $\Phi(u)$.
+By Banach-Alaoglu every subsequence of $\Phi(u_n)$ has a weakly convergent subsequence, and by the pointwise convergence we can, after arguing as in the proof in Lemma \ref{prop:weak_convergence_w_n}, conclude that the weak limit is always $\Phi(u)$.
 This implies that $\Phi(u_n)$ converges weakly to $\Phi(u)$.
@@
 
-\begin{lemma}
+\begin{theorem}
 \label{lem:l1_stability_weak_final}
@@
 holds for almost every $t\in [0,T]$.
-\end{lemma}
-
-\begin{proof}
-The proof is identical to that of proposition \ref{prop:l1_stability_weak_part2}, only now the use of proposition \ref{prop:l1_stability_weak_part1} is exchanged with use of \ref{prop:l1_stability_weak_part2}.
+\end{theorem}
+
+\begin{proof}
+The proof is identical to that of Lemma \ref{prop:l1_stability_weak_part2}, only now the use of Lemma \ref{prop:l1_stability_weak_part1} is exchanged with use of Lemma \ref{prop:l1_stability_weak_part2}.
 \end{proof}

### 2014-12-17 draft_project.tex
En siste runde med korrektur nå...

@@
 
-\abstract{For now, heavily reliant on \citep{vazquez2007porous}.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%				ABSTRACT:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\abstract{This project is an exposition of the General Porous Medium Equation, which contains both the porous medium equation and the heat equation as special cases as well as the Stefan problem when considering the degenerate case.
+The first part is devoted to presenting some theory on classical solution with attention paid to important estimates.
+
+ The theory is then extended to a weak setting for the weakly degenerate case.
+Again, proving well posedness will be the main focus, and to that end the concept of weak energy solutions is presented.
+In this framework existence, uniqueness and stability is proved, and attention is paid to showing that the estimates for classical solutions are inherited by weak solutions.
+}
 
 \newpage
+
 \tableofcontents
+\pagestyle{plain}
 \pagenumbering{arabic}
@@
 \section{Introduction}
-
-Let $\Omega \subset \mathbb{R}^d$ be an open, bounded, and simply connected domain. Then the filtration, or general porous medium equation is
-
+As a student first learning partial differential equations, one is bound to come across the heat equation early on. Its most common derivation stems from conservation principles of the form
+\begin{equation}
+\label{conservation_law}
+\partial_t u + \nabla \cdot \textbf{j} = f,
+\end{equation}
+where $u$ is some density, $\textbf{j}$ is the flux and $f$ is the production term, together with Fick's law of diffusion, stating that the density flux is negatively proportional to the density gradient.
+Put in symbols,
+\begin{equation*}
+\textbf{j} = -K\nabla u,
+\end{equation*}
+where $K$ is some constant.
+
+Although widely acclaimed, there are diffusive processes which the heat equation fails to model satisfactory, e.g.
+viscous groundwater flow.
+In that particular case a popular alternative for modelling the flux is Darcy's law.
+Here flux is negatively proportional to gradient of the pressure, rather than density.
+Then comes the second question of how to model the pressure.
+A common method is using the state equation for perfect gases, relating pressure to density by
+\begin{equation*}
+p = p_0 u^\gamma, 
+\end{equation*}
+for some constants $p_0$ and $\gamma \geq 1$. Putting this in for the flux in (\ref{conservation_law}) results in the PDE
+\begin{equation}
+\partial_t \rho = c \Delta u^\gamma +f,
+\end{equation}
+which is commonly called the Porous medium equation (PME).
+
+Taking it one step further, we can generalise the density flux as $\textbf{j} = -K\nabla \Phi(u)$ for some nondecreasing function $\Phi$.
+Then (\ref{conservation_law}) becomes what is called the Filtration equation, or the General porous medium equation and is written
 \begin{equation}
 \label{GPME}
-	\partial_t u = \Delta \Phi(u) + f,
-\end{equation}
-
- where $u, f: \Omega \times (0,\infty) \to \mathbb{R}$, and $\Phi: \mathbb{R} \to \mathbb{R}$.
+	\partial_t u = \Delta \Phi(u) + f.
+\end{equation}
+
+It is (\ref{GPME}) that we will focus on in this project and we'll consider $u: \Omega \times [0,\infty) \to \mathbb{R}$, for some open, bounded and simply connected subset $\Omega \subset \mathbb{R}^d$.
 
@@
 \begin{example}[PME]
-When $\Phi(u) = u^m$ for $m>1$, (\ref{GPME}) is the Porous Medium Equation (PME), whose name is derived from its main application: Describing gas concentration flow in porous media, like rock.
+When $\Phi(u) = u^m$ for $m>1$, (\ref{GPME}) is as already mentioned the Porous Medium Equation, whose name is derived from its main application: Describing fluid concentration flow in porous media, like rock.
 To allow for solutions with changing signs, one has $\Phi(u) = |u|^{m-1}u$.
 Notice that this choice of $\Phi$ is strictly increasing and locally Lipschitz continuous.
+The fact that $\Phi'(0) = 0$ makes the PME a weakly degenerate problem.
 \end{example}
@@
 melting an ice cube in a glass of water.
-Here $\Phi$ is no longer strictly increasing, which constitutes a degenerate problem.
+Here $\Phi$ is no longer strictly increasing, which constitutes a  strongly degenerate problem.
 \end{example}
@@
 \subsection{Problem statement}
-We will consider on the following Dirichlet problem:
+Rather than analysing all variants of well posed formulations of (\ref{GPME}), we will in this text restrict ourselves to consider the initial value problem with homogeneous Dirichlet boundary conditions on a bounded domain, which can be formulated as
 \begin{equation}
@@
 \end{equation}
-Here $Q_T = \Omega \times (0,T]$, where $T$ may very well be infinite. Furthermore we denote by $\Gamma_T = \overline{Q}_T\backslash Q_T$ the parabolic boundary.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%		ASSUMPTIONS CAN POSSIBLY GO HERE???
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This restriction is of course so we can spend more time on the details for a hopefully richer understanding of some of the properties inherent in the general porous medium equation.
+
+The general layout of the project will be as follows: We'll begin by considering classical solutions of (\ref{HDP}) that satisfy (\ref{GPME}) at every point in $Q_T$.
+Here we will derive some important a priori estimates, including stability in $L^\infty$ and $L^1$ as well as control of both the spatial and temporal derivative.
+The section concludes with an existence result under quite strict assumptions.
+The results of this section can be found in books like \citep{vazquez2007porous} and \citep{ladyzhenskaya}.
+
+Then follows a discussion of weak solutions, showing uniqueness, existence and stability in $L^\infty(0,T: L^1(\Omega))$, most of the results in this section can be found in \citep[chapter 5]{vazquez2007porous}.
+However, here the proofs are much more detailed than can be found there, and as great care as the author could manage was placed on making sure that the a priori estimates for classical solutions, especially $L^1$-stability, was inherited to weak solutions as well.
+This focus on detail has the advantage of better showing how reliant PDE theory are on other branches of mathematics like functional analysis and measure theory, perhaps at the cost of making for a more cumbersome read.
+
+In addition the uniqueness result for weak solutions was also slightly improved upon relative to \citep{vazquez2007porous} in that the proof here includes the possibility that $\Phi$ is only nondecreasing.
 

### 2014-12-18 draft_project.tex
Tror jeg skal levere nå...

@@
 \begin{enumerate}[i)]
-	Suppose $\Omega$ is connected, and $u\in C^{2,1}(Q_T)\cap C(\overline{Q}_T)$, and $\partial_t + L$ is uniformly parabolic, then:
+	Suppose $\Omega$ is connected, and $u\in C^2_1(Q_T)\cap C(\overline{Q}_T)$, and $\partial_t + L$ is uniformly parabolic, then:
 	\item If
@@
 \label{lady_parabolic_eq}
-	u_t - \sum_{i=1}^d\frac{d}{dx_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
+	u_t - \sum_{i=1}^d\frac{\partial}{\partial x_i}a_i(x,t,u,\nabla u) + a(x,t,u,\nabla u) = 0
 \end{equation}
@@
 
-		\item $u_0$ is in $C^2_c(\Omega)$; $u_0\in C^2(\Omega)$ and has compact support.
-
-		\item $\partial \Omega$ is $C^{2+\beta}$-smooth.
+		\item $u_0\in C^2(\Omega)$, and $u_0$, $\nabla u_0$ and $\Delta u_0$ vanish at the boundary.
+
+		\item $\partial \Omega$ is $C^{2,\beta}$-smooth.
 
@@
 	\begin{equation*}
-		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)\xi^2,
+		\sum_{i,j=1}^d \frac{\partial a_i(x,t,u,p)}{\partial p_j} \xi_i \xi_j = \sum_{i=1}^d \Phi'(u)\xi_i^2 =\Phi'(u)|\xi|^2,
 	\end{equation*}
@@
 \begin{obs}
-If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as we did in deriving (\ref{spatial_derivative_bound_w_poincare}), to get that $\Phi(u) \in L^2(0,T: H^1_0(\Omega))$.
+If $f\in L^2(Q_T)$ we can do the same trick on the right hand side as we did in deriving (\ref{spatial_derivative_bound_w_poaincare}), to get that $\Phi(u) \in L^2(0,T: H^1_0(\Omega))$.
 \end{obs}
@@
 Notice that by Young's inequality $||f_n||_{L^2(Q_T)} \leq ||\tilde{f}_n||_{L^2(Q_T)} \leq ||f||_{L^2(Q_T)}$.
+Because of $\partial_t (\tilde{f}_n* \varphi_{\frac{1}{n}}) = (\partial_t \tilde{f}_n) *\varphi_{\frac{1}{n}}$, we also have that $||\partial_t f_n||_\infty \leq ||\partial_t f||_\infty$.
+This is true for any derivative of $f$ that exists, but it's only the time derivative estimate here that will become useful to us.
 
@@
 In other words $(w_n)$ is uniformly bounded $L^2(0,T: H^1_0(\Omega))$.
-Moreover, there is some $K >0$, depending only on $M$ from Lemma \ref{prop:classical_sols_seq} and $\Phi$, so that
+Moreover, there are constants $B_1, B_2 >0$ depending only on $M$ from Lemma \ref{prop:classical_sols_seq} and $\Phi$, so that
 \begin{equation}
 \label{gradwn_bound_uniform}
-||\nabla w_n||_{L^2(Q_T)} \leq K||u_0||_{L^1(\Omega)} + ||f||_{L^2(Q_T)}.
+||\nabla w_n||_{L^2(Q_T)} \leq B_1||u_0||_{L^1(\Omega)} + B_2||f||_{L^2(Q_T)}.
 \end{equation}
@@
 \begin{proof}
-Since $u_n$ are classical solutions, we use (\ref{spatial_derivative_bound_w_poincare}) to get that
+Since $u_n$ are classical solutions, we use (\ref{spatial_derivative_bound_w_poaincare}) to get that
 	\begin{equation}
@@
 	& + \underset{\underset{y\in[-1/n,1/n]}{|s| \leq ||u_0||_{\infty}}}{\mathrm{sup}}|\Phi(s-y) - \Phi(s)| + \mathrm{max}\{|\Phi(-1)|, |\Phi(1)|\} \\
-	&=: K < \infty.
+	&=: \frac{B_1}{2} < \infty.
 	\end{align*}
@@
 	\begin{align*}
-	\int_\Omega \Psi_n(u_{0,n})dx &\leq K ||u_{0,n}||_{L^1(\Omega)} \\
-	&\leq K ||u_0||_{L^1(\Omega)}
+	\int_\Omega \Psi_n(u_{0,n})dx &\leq \frac{B_1}{2} ||u_{0,n}||_{L^1(\Omega)} \\
+	&\leq \frac{B_1}{2} ||u_0||_{L^1(\Omega)}
 	\end{align*}
@@
 	\end{equation*}
-	$w_n$ is also uniformly bounded in $L^2(Q_T)$.
+	$w_n$ is also uniformly bounded in $L^2(Q_T)$. Lastly, setting $B_2 = 2C$ and multplying (\ref{exist_proof_spatial}) by $2$ we get
+	\begin{equation}
+	\iint_{Q_T} |\nabla w_n|^2 dxdt \leq B_1 ||u_0||_{L^1(\Omega)} + B_2 ||f||_{L^2(Q_T)}.
+	\end{equation}
 \end{proof}
@@
 \label{prop:gradw_weak_convergence}
-With the same assumptions as in proposition \ref{prop:classical_sols_seq},
+With the same assumptions as in Lemma \ref{prop:classical_sols_seq},
 $\nabla w_{n_j}$ converges weakly to $\nabla w$ in $L^2(Q_T)$.
@@
 	 We have that $w_{n_j}$ is a bounded sequence, seeing as $u_{n_j}$ is bounded.
-Hence we can use proposition \ref{prop:inverse_uniform} to make the first term in the above inequality arbitrarily small.
+Hence we can use Lemma \ref{prop:inverse_uniform} to make the first term in the above inequality arbitrarily small.
 The second term is controlled by the almost everywhere convergence of $w_{n_j}$ to $w$ and the continuity of $\Phi^{-1}$.
@@
 	\item[$u \in L^\infty(0,T: L_\Psi(\Omega)$:]
-	For any $t \in [0,T]$ we have by Fatou's Lemma \citep[p. 162]{weiss1999course} that 
-	\begin{equation*}
-	||u(t)||_{L^1(\Omega)} \leq \liminf_{n \to \infty} ||u_n(t)||_{L^1(\Omega)}.
+	For almost every $t \in [0,T]$ we have by Fatou's Lemma \citep[p. 162]{weiss1999course} that since $|u_{n_j}(t)|$ converges almost everywhere to $|u(t)|$ and are nonnegative, then
+	\begin{equation*}
+	||u(t)||_{L^1(\Omega)} \leq \liminf_{j \to \infty} ||u_{n_j}(t)||_{L^1(\Omega)}.
 	\end{equation*}
@@
 	\begin{align}
-	||u(t)||_{L^1(\Omega)} &\leq \liminf_{n \to \infty} \left( ||u_{0,n}||_{L^1(\Omega)} + ||f_n||_{L^1(Q_T)}\right) \nonumber \\
+	||u(t)||_{L^1(\Omega)} &\leq \liminf_{j \to \infty} \left( ||u_{0,n_j}||_{L^1(\Omega)} + ||f_{n_j}||_{L^1(Q_T)}\right) \nonumber \\
 	&= ||u_0||_{L^1(\Omega)} + ||f||_{L^1(Q_T)},	
@@
 	\begin{equation}
-	|\Psi_n(u_n) - \Psi(u)| \leq |\Psi_n(u_n) - \Psi(u_n)| + |\Psi(u_n) + \Psi(u)|.
-	\end{equation}
-	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see proposition \ref{prop:Psi_uniform_convergence}) to control the first term.
-The second term is controlled by the almost everywhere convergence of $u_n$ to $u$ and the continuity of $\Psi$.
+	|\Psi_{n_j}(u_{n_j}) - \Psi(u)| \leq |\Psi_{n_j}(u_{n_j}) - \Psi(u_{n_j})| + |\Psi(u_{n_j}) + \Psi(u)|.
+	\end{equation}
+	Because $|u_n| \leq M$ we use that $\Psi_n$ converges uniformly on compact sets (see Lemma \ref{prop:Psi_uniform_convergence}) to control the first term.
+The second term is controlled by the almost everywhere convergence of $u_{n_j}$ to $u$ and the continuity of $\Psi$.
 
@@
 	\begin{align*}
-	\int_\Omega \Psi(u(t))dx &\leq \liminf_{n \to \infty} \left( \int_\Omega \Psi_n(u_{0,n})dx + C\iint_{Q_T}f_n^2 dxdt \right)\nonumber \\
+	\int_\Omega \Psi(u(t))dx &\leq \liminf_{j \to \infty} \left( \int_\Omega \Psi_{n_j}(u_{0,n_j})dx + C\iint_{Q_T}f_{n_j}^2 dxdt \right)\nonumber \\
 	&= \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f^2dxdt, 
@@
 	We have from before that $u\in L^2(Q_T)$ as well as $\Phi(u) \in L^2(0,T: H^1(\Omega))$, so the solution is unique.
-In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak solution, and so the uniqueness in theorem \ref{thm:uniqueness} precludes any other accumulation point than $u$.
+In addition it is worth noticing that any accumulation point of the sequence of classical solutions is a weak solution, and so the uniqueness in Theorem \ref{thm:uniqueness} precludes any other accumulation point than $u$.
 I.e.
@@
 \subsubsection{No longer $C^{2,\alpha}$ boundary}
-Following suit from the previous section, we'll now aim to prove Lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$, of course, this is usually the case in applications, where the domain can have corners and such, making the boundary not sufficiently smooth to satisfy the assumptions in theorem \ref{thm:classical_existence} to provide a classical solution.
+Following suit from the previous section, we'll now aim to prove Lemma \ref{lem:weak_existence_part2} without the assumption that $\partial \Omega$ is $C^{2,\alpha}$, of course, this is usually the case in applications, where the domain can have corners and such, making the boundary not sufficiently smooth to satisfy the assumptions in Theorem \ref{thm:classical_existence} to provide a classical solution.
 The strategy for proving existence now will be to get a sequence of weak solution on smaller subdomains that will eventually converge to all of $Q_T$.
@@
 \end{equation*}
-For each $n$, $u_n$ is a weak energy solution in $Q_n$ and as satisfies \ref{energy_ineq}, giving
+For each $n$, $u_n$ is a weak energy solution in $Q_n$ and as satisfies (\ref{energy_ineq}), giving
 \begin{align}
@@
 \label{z_n_bounded_in_H1_start}
-\iint_{Q_T^\tau} |\partial_t z_n|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( K||u_{0,n}||_{L^1(K_n)} + ||f_n||_{L^2(Q_n)}\right) + \iint_{Q_n}|\partial_t (f_n \zeta ) w_n| dxdt,
+\iint_{Q_T^\tau} |\partial_t z_n|^2 dxdt \leq \frac{||\partial_t \zeta||_\infty}{2}\left( B_1||u_{0,n}||_{L^1(K_n)} + B_2||f_n||_{L^2(Q_n)}\right) + \iint_{Q_n}|\partial_t (f_n \zeta ) w_n| dxdt,
 \end{equation}
@@
 \subsubsection{Removing the assumptions on $f$ and $u_0$}
-We've finally arrived at the last section, where we'll prove theorem \ref{thm:weak_existence} without the assumption \ref{ass:f_ft_u_0_bounded}, which have proved so very useful for us up to this point.
+We've finally arrived at the last section, where we'll prove Theorem \ref{thm:weak_existence} without the assumption \ref{ass:f_ft_u_0_bounded}, which have proved so very useful for us up to this point.
 Let's just get to it then.
@@
 \item[$\nabla \Phi(u_n)$ converges weakly to $\nabla \Phi(u)$:]
-The proof of this assertion is done, as in the proof of proposition \ref{prop:gradw_weak_convergence}, by noticing from the weak convergence of $\Phi(u_n)$ we can deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
+The proof of this assertion is done, as in the proof of Lemma \ref{prop:gradw_weak_convergence}, by noticing from the weak convergence of $\Phi(u_n)$ we can deduce that $\nabla \Phi(u_n)$ converges to $\nabla \Phi(u)$ in the distributional sense.
 In addition $\nabla \Phi(u_n)$ is a bounded sequence in $L^2(Q_T)$, and so every subsequence has a weakly convergent subsequence.
@@
 \item[$u$ is a weak solution:]
-With the various convergences shown above or given by assumption, showing that $u$ is a weak solution and satisfies the energy inequality (\ref{energy_ineq}) is done identically as in the proof of lemma \ref{lem:existence_part1}.
+With the various convergences shown above or given by assumption, showing that $u$ is a weak solution and satisfies the energy inequality (\ref{energy_ineq}) is done identically as in the proof of Lemma \ref{lem:existence_part1}.
 The same is true for showing that $u$ satisfies the energy inequality (\ref{energy_ineq}).
@@
 The first property we'll consider is summarised in the following proposition.
-\begin{proposition}
+\begin{lemma}
 \label{prop:Phi_uniform_convergence}
 If $\Phi$ is continuous, $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:Psi_uniform_convergence}
 $\Psi_n$ converges uniformly to $\Psi$ on compact sets.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 \end{align*}
-By proposition \ref{prop:Phi_uniform_convergence} we can take find an $N \in \mathbb{N}$ so that
+By Lemma \ref{prop:Phi_uniform_convergence} we can take find an $N \in \mathbb{N}$ so that
 \begin{equation*}
@@
 
-In the remainder of this section we'll assume that $\Phi$ is continuous and strictly increasing, and that $\Phi( \pm \infty) = \pm \infty$.
+In the remainder of this section we'll assume that $\Phi$ is continuous and strictly increasing, and that $\Phi( \pm \infty) = \pm \infty$, i.e.
+satisfies assumption \ref{ass:Phi_general}.
 Then it is obvious that both $\Phi$ is both one-to-one and onto, and so has an inverse $\Phi^{-1}$.
 
-\begin{proposition}
-$\Phi^{-1}$ is strictly increasing, and continuous.
-\end{proposition}
+\begin{lemma}
+\label{lem:Phi_inv_cont}
+With assumption \ref{ass:Phi_general} $\Phi^{-1}$ is strictly increasing, and continuous.
+\end{lemma}
 \begin{proof}
@@
 
-\begin{proposition}
-$\Phi_n^{-1}$ converges pointwise to $\Phi^{-1}$.
-\end{proposition}
+\begin{lemma}
+With the same assumptions as Lemma \ref{lem:Phi_inv_cont} $\Phi_n^{-1}$ converges pointwise to $\Phi^{-1}$.
+\end{lemma}
 
@@
 A similar argument yields $x_n \geq x_1$, and so we have that for every $n \geq N$ that $x_n \in [x_1, x_2]$.
-This means that $x_n$ is a bounded sequence, and hence we can use the unform convergence of $\Phi_n$ on compact sets to conclude that $y_n$ converges to $y$.
+This means that $x_n$ is a bounded sequence, and hence we can use the uniform convergence of $\Phi_n$ on compact sets to conclude that $y_n$ converges to $y$.
 Finally we have that
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:inverse_uniform}
-$\Phi_n^{-1}$ converges to $\Phi^{-1}$ uniformly on compact sets.
-\end{proposition}
+With the same assumptions as Lemma \ref{lem:Phi_inv_cont} $\Phi_n^{-1}$ converges to $\Phi^{-1}$ uniformly on compact sets.
+\end{lemma}
 
@@
 Looking back at this proof, the only things we needed were that $\Phi$ is strictly increasing and continuous, and is locally Lipschitz, and that $\Phi_n$ converges to $\Phi$ uniformly on compact sets.
-So we can generalise our result in the following lemma.
+So we can generalise our result in the following Lemma.
 
@@
 Let $f: \mathbb{R} \to \mathbb{R}$ be a strictly monotone, continuous function, and let $\{f_n\}$ be a family of strictly monotone, continuous functions that converge to $f$ uniformly on compact sets.
+All functions are so that $f(\pm \infty) = \pm \infty$.
 Then $f_n^{-1}$ converges to $f^{-1}$ uniformly on compact sets.
@@
 \begin{proof}
-The proof is identical to that of proposition \ref{prop:inverse_uniform} with only minor alterations in notation.
+The proof is identical to that of Lemma \ref{prop:inverse_uniform} with only minor alterations in notation.
 \end{proof}
@@
 
-\begin{proposition}
+\begin{lemma}
 $Z_n$ converges pointwise to $Z$.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 For the first term we use part iv) of theorem 7 of appendix C in \citep{evans}, to state that $\Phi'*\varphi_{\frac{1}{n}}$ converges to $\Phi$ in $L^1_{loc}(\mathbb{R})$.
-With this we deduce that $Z_n$ converges pointwise to $Z$.
+With this we deduce that $Z_n$ converges pointwise almost everywhere to $Z$ on any compact set, at least along a subsequence.
+Since all $Z_n$ and $Z$ are continuous the convergence happens everywhere on any compact set.
 \end{proof}
@@
 
-Using this powerful theorem we can prove the following:
-\begin{proposition}
+Using this powerful Theorem we can prove the following:
+\begin{lemma}
 \label{prop:Z_uniform_convergence}
-$Z_n$ converges to $Z$ uniformly on compact sets.
-\end{proposition}
+With the same assumptions as Lemma \ref{lem:Phi_inv_cont} $Z_n$ converges to $Z$ uniformly on compact sets.
+\end{lemma}
 \begin{proof}
@@
 We'll continue on with the last result of this section.
-\begin{proposition}
+\begin{lemma}
 \label{prop:Zinv_uniform_convergence}
-With $\Phi$ strictly increasing and continuos, $Z$ is strictly increasing and continuous, and thus permits a strictly increasing and continuous inverse.
+With the same assumptions as Lemma \ref{lem:Phi_inv_cont}, $Z$ is strictly increasing and continuous, and thus permits a strictly increasing and continuous inverse.
 Furthermore $Z_n^{-1}$ converges to $Z^{-1}$ uniformly on compact sets.
-\end{proposition}
+\end{lemma}
 \begin{proof}
@@
 
-We have from proposition \ref{prop:Z_uniform_convergence} that $Z_n$ converges uniformly to $Z$ on compact sets, and so we can simply use lemma \ref{lem:Inverse_uniform_general} to conclude that $Z_n^{-1}$ converges uniformly to $Z^{-1}$ on compact sets.
+We have from Lemma \ref{prop:Z_uniform_convergence} that $Z_n$ converges uniformly to $Z$ on compact sets, and so we can simply use Lemma \ref{lem:Inverse_uniform_general} to conclude that $Z_n^{-1}$ converges uniformly to $Z^{-1}$ on compact sets.
 \end{proof}
